### 2024-10-25 scripts/05-exploratory_data_analysis.qmd
simulation right now more comprehensive, bugs fixed, and more files added
simulation updated, download_data.R's comment fixed,
variable description added,
and EDA now updated

#### Preamble ####
# Purpose: Models... [...UPDATE THIS...]
# Author: Rohan Alexander [...UPDATE THIS...]
# Date: 11 February 2023 [...UPDATE THIS...]
# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
# License: MIT
# Pre-requisites: [...UPDATE THIS...]
# Any other information needed? [...UPDATE THIS...]

```{r}
#### Workspace setup ####
library(tidyverse)
library(rstanarm)

#### Read data ####
analysis_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
```

```{r}
# Check for missing values in each column
missing_values <- sapply(analysis_data, function(x) sum(is.na(x)))
print(missing_values)
```

```{r}
# Get unique pollster IDs
unique_pollster_ids <- unique(analysis_data$pollster_id)
print(unique_pollster_ids)
```
```{r}
# Get unique question IDs
unique_question_ids <- unique(analysis_data$question_id)
print(unique_question_ids)
```
```{r}
unique_question_ids_str <- paste(unique(unique_question_ids), collapse = ",")
print(unique_question_ids_str)
```

```{r}
View(unique_question_ids_str)
```

```{r}
# Get the maximum and minimum values of numeric_grade
max_numeric_grade <- max(analysis_data$numeric_grade, na.rm = TRUE)
min_numeric_grade <- min(analysis_data$numeric_grade, na.rm = TRUE)
print(paste("Maximum numeric grade:", max_numeric_grade))
print(paste("Minimum numeric grade:", min_numeric_grade))
```

```{r}
# Plot histogram of numeric_grade
ggplot(analysis_data, aes(x = numeric_grade)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of Numeric Grade", x = "Numeric Grade", y = "Count")
```
```{r}
# Plot histogram of pollscore
ggplot(analysis_data, aes(x = pollscore)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of pollscore", x = "pollscore", y = "Count")
```
```{r}
# Get unique methodologys
unique_methodologys <- unique(analysis_data$methodology)
print(unique_methodologys)
```
```{r}
# Plot histogram of transparency_score
ggplot(analysis_data, aes(x = transparency_score)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of transparency_score", x = "transparency_score", y = "Count")
```
```{r}
# Find the earliest start date and the latest end date
earliest_start_date <- min(analysis_data$start_date, na.rm = TRUE)
latest_end_date <- max(analysis_data$end_date, na.rm = TRUE)
print(paste("Earliest start date:", earliest_start_date))
print(paste("Latest end date:", latest_end_date))
```

```{r}
# Plot histogram of sample_size
ggplot(analysis_data, aes(x = sample_size)) +
  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of sample_size", x = "sample_size", y = "Count")
```
```{r}
# Get unique population
unique_population <- unique(analysis_data$population)
print(unique_population)
```
```{r}
# Get unique race_id
unique_race_id <- unique(analysis_data$race_id)
print(unique_race_id)
```

```{r}
unique_race_id_str <- paste(unique(unique_race_id), collapse = ",")
clipr::write_clip(unique_race_id_str)
```

```{r}
# Get unique stage
unique_stage <- unique(analysis_data$stage)
print(unique_stage)
```

```{r}
# Get unique stage
unique_nationwide_batch <- unique(analysis_data$nationwide_batch)
print(unique_nationwide_batch)
```

```{r}
# Get unique ranked_choice_reallocated
unique_ranked_choice_reallocated <- unique(analysis_data$ranked_choice_reallocated)
print(unique_ranked_choice_reallocated)
```

```{r}
# Get unique hypothetical
unique_hypothetical <- unique(analysis_data$hypothetical)
print(unique_hypothetical)
```
```{r}
# Calculate the ratio of FALSE to TRUE in the hypothetical column
hypothetical_ratio <- table(simulated_candidate_1$hypothetical)
print(hypothetical_ratio)
false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
print(paste("False to True Ratio:", false_to_true_ratio))
```

```{r}
# Get unique party
unique_party <- unique(analysis_data$party)
print(unique_party)
```

```{r}
# Find the maximum difference between start_date and end_date
date_diff <- simulated_candidate_1 %>%
  mutate(date_difference = as.numeric(difftime(end_date, start_date, units = "days"))) %>%
  summarise(max_difference = max(date_difference))

print(date_diff)
```

### 2024-10-25 scripts/00-simulate_data.R

@@ -11,30 +11,99 @@
 # Load required libraries
 library(tidyverse)
 
-simulate_data <- function(n) {
-  # Set a random seed for reproducibility
-  set.seed(123)
-  
-  # Generate simulated data
-  simulated_data <- data.frame(
-    pollscore = round(rnorm(n, mean = 0, sd = 0.5), 1),  # Normal distribution around 0, rounded to 1 decimal
-    numeric_grade = round(rnorm(n, mean = 2, sd = 1), 1),  # Normal distribution around 2, rounded to 1 decimal
-    duration = sample(2:35, n, replace = TRUE),  # Random duration between 2 and 35 days
-    sample_size = sample(400:1250, n, replace = TRUE),  # Random sample size between 400 and 1250
-    population = sample(c("lv", "rv"), n, replace = TRUE),  # Randomly choosing "lv" or "rv"
-    party = sample(c("DEM", "REP"), n, replace = TRUE),  # Randomly choosing party
-    hypothetical = sample(c("false", "true"), n, replace = TRUE),  # Randomly choosing hypothetical status
-    internal = sample(c("false", "true"), n, replace = TRUE),  # Randomly choosing internal status
-    pct = round(runif(n, min = 30, max = 70), 1)  # Uniform distribution for pct between 30 and 70, rounded to 1 decimal
-  )
-  
-  # Return the simulated data
-  return(simulated_data)
-}
 
-# Usage example to simulate 100 rows of data
-simulated_data <- simulate_data(100)
+# Set a random seed for reproducibility
+set.seed(123)
+  
+# Generate simulated data
+simulated_candidate_1 <- tibble(
+  poll_id = 1:500, 
+  # Generate numeric_grade based on a normal distribution with mean 2 and standard deviation 1.2,
+  # then ensure the values are within the range [0, 3] and round to one decimal places
+  numeric_grade = round(pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3), 1),
+  
+  # Generate pollscore based on a normal distribution with mean -0.5 and variance 0.3,
+  # then ensure the values are within the range [-1, 1] and round to one decimal place
[…]

### 2024-10-25 scripts/02-download_data.R

@@ -15,7 +15,6 @@ url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
 the_raw_data <- read.csv(url)
 
 #### Save data ####
-# [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
 

### 2024-10-25 scripts/05-exploratory_data_analysis.qmd
simulation revised
simulation revised

@@
 # Calculate the ratio of FALSE to TRUE in the hypothetical column
-hypothetical_ratio <- table(simulated_candidate_1$hypothetical)
+hypothetical_ratio <- table(analysis_data$hypothetical)
 print(hypothetical_ratio)
@@
 ```{r}
-# Find the maximum difference between start_date and end_date
-date_diff <- simulated_candidate_1 %>%
-  mutate(date_difference = as.numeric(difftime(end_date, start_date, units = "days"))) %>%
-  summarise(max_difference = max(date_difference))
-
-print(date_diff)
+linear_model <- lm(pct ~ numeric_grade + pollscore + transparency_score + sample_size + partisan + methodology + population + race_id + stage + nationwide_batch + ranked_choice_reallocated + hypothetical, data = analysis_data)
+summary(linear_model)
 ```

### 2024-10-25 scripts/00-simulate_data.R

@@ -19,12 +19,12 @@ set.seed(123)
 simulated_candidate_1 <- tibble(
   poll_id = 1:500, 
   # Generate numeric_grade based on a normal distribution with mean 2 and standard deviation 1.2,
-  # then ensure the values are within the range [0, 3] and round to one decimal places
-  numeric_grade = round(pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3), 1),
+  # then ensure the values are within the range [0, 3] and round to two decimal places, then map to a range of 0 to 10
+  numeric_grade = round((pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3) / 3) * 10, 2),
   
   # Generate pollscore based on a normal distribution with mean -0.5 and variance 0.3,
-  # then ensure the values are within the range [-1, 1] and round to one decimal place
-  pollscore = round(pmin(pmax(rnorm(500, mean = -0.5, sd = sqrt(0.3)), -1), 1), 1),
+  # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
+  pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = sqrt(0.3)), -1), 1) + 1) * 5, 1),
   
   methodology = sample(c(
     "Online Panel", "App Panel", "IVR/Text", "Online Ad", "IVR/Online Panel/Text-to-Web",
@@ -41,10 +41,8 @@ simulated_candidate_1 <- tibble(
     "Live Phone/Online Panel/Mail-to-Web", "IVR/Text-to-Web/Email"), 500, replace = TRUE),
   
   # Generate transparency_score based on a normal distribution with mean 6 and variance 1.5,
-  # then ensure the values are within the range [1, 10], round to the nearest 0.5
-  transparency_score = round(pmin(pmax(rnorm(500, mean = 6, sd = sqrt(1.5)), 1), 10) * 2) / 2,
-  
-  state = sample(state.abb, 500, replace = TRUE),
+  # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
+  transparency_score = round((pmin(pmax(rnorm(500, mean = 6, sd = sqrt(1.5)), 1), 10) / 10) * 10, 1),
   
   duration = round(pmin(pmax(rnorm(500, mean = 183, sd = 100), 15), 365)),
[…]

### 2024-10-25 scripts/05-exploratory_data_analysis.qmd
scores weighted in simulation
scores weighted in simulation

@@
 ```{r}
-linear_model <- lm(pct ~ numeric_grade + pollscore + transparency_score + sample_size + partisan + methodology + population + race_id + stage + nationwide_batch + ranked_choice_reallocated + hypothetical, data = analysis_data)
-summary(linear_model)
+# Get unique population
+unique_population <- unique(analysis_data$population)
+print(unique_population)
 ```

### 2024-10-25 scripts/00-simulate_data.R

@@ -26,29 +26,13 @@ simulated_candidate_1 <- tibble(
   # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
   pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = sqrt(0.3)), -1), 1) + 1) * 5, 1),
   
-  methodology = sample(c(
-    "Online Panel", "App Panel", "IVR/Text", "Online Ad", "IVR/Online Panel/Text-to-Web",
-    "IVR", "IVR/Online Panel", "Live Phone/Text-to-Web", "Live Phone", "IVR/Text-to-Web", "Probability Panel",
-    "IVR/Live Phone/Text/Online Panel/Email", "Online Panel/Text-to-Web", "IVR/Live Phone/Text-to-Web", "Text",
-    "Text-to-Web", "Live Phone/Online Panel/Text-to-Web", "Text-to-Web/Online Ad", "Email",
-    "Live Phone/Online Panel", "Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Live Phone/Online Panel/App Panel",
-    "Text-to-Web/Email", "Mail-to-Web/Mail-to-Phone", "Live Phone/Online Panel/Text", "Live Phone/Email", "Live Phone/Probability Panel", "Online Panel/Probability Panel", "IVR/Live Phone/Online Panel/Text-to-Web",
-    "Online Panel/Online Ad", "Live Phone/Text-to-Web/Online Ad", "Live Phone/Text/Online Panel", "IVR/Live Phone/Text",
-    "IVR/Online Panel/Email", "Live Phone/Online Panel/Text-to-Web/Text", "Live Phone/Text/Online Ad",
-    "IVR/Online Panel/Text-to-Web/Email", "Online Panel/Email/Text-to-Web", "Online Panel/Text",
-    "Online Panel/Text-to-Web/Text", "Live Phone/Text-to-Web/Email", "Live Phone/Text", "Live Phone/Text-to-Web/App Panel",
-    "Live Phone/Text-to-Web/Email/Mail-to-Web", "Email/Online Ad", "Online Panel/Email", "IVR/Live Phone/Online Panel",
-    "Live Phone/Online Panel/Mail-to-Web", "IVR/Text-to-Web/Email"), 500, replace = TRUE),
+  methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
   
[…]

### 2024-10-25 scripts/00-simulate_data.R
simulation datasets are uploaded
simulation datasets are uploaded

@@ -11,64 +11,169 @@
 # Load required libraries
 library(tidyverse)
 
-
 # Set a random seed for reproducibility
 set.seed(123)
   
-# Generate simulated data
+## Generate simulated data for candidate_1
 simulated_candidate_1 <- tibble(
   poll_id = 1:500, 
   # Generate numeric_grade based on a normal distribution with mean 2 and standard deviation 1.2,
   # then ensure the values are within the range [0, 3] and round to two decimal places, then map to a range of 0 to 10
   numeric_grade = round((pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3) / 3) * 10, 2),
-  
-  # Generate pollscore based on a normal distribution with mean -0.5 and variance 0.3,
+  # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
   # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
-  pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = sqrt(0.3)), -1), 1) + 1) * 5, 1),
-  
+  pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = 0.3), -1), 1) + 1) * 5, 1),
+  # The methodology is divided into four levels: level 1 represents the least reliable type of methodology, while level 4 represents the most reliable.
   methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
-  
-  # Generate transparency_score based on a normal distribution with mean 6 and variance 1.5,
+  # Generate transparency_score based on a normal distribution with mean 6 and standard deviation 1.5,
   # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
-  transparency_score = round((pmin(pmax(rnorm(500, mean = 6, sd = sqrt(1.5)), 1), 10) / 10) * 10, 1),
-  
+  transparency_score = round((pmin(pmax(rnorm(500, mean = 6, sd = 1.5), 1), 10) / 10) * 10, 1),
+  # The duration of this poll in days. Duration based on a normal distribution with mean 183 and standard deviation 100,
   duration = round(pmin(pmax(rnorm(500, mean = 183, sd = 100), 15), 365)),
-  
-  # Generate sample_size based on a normal distribution with mean 1200 and variance 5000, then round to the nearest integer
[…]

### 2024-10-25 scripts/02-download_data.R

@@ -15,6 +15,5 @@ url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
 the_raw_data <- read.csv(url)
 
 #### Save data ####
-# change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
 

### 2024-10-25 scripts/00-simulate_data.R
simulated datasets' file structure fixed
simulated datasets' file structure fixed

@@ -174,6 +174,6 @@ simulated_candidate_3$score =
   , 2)
     
 #### Save data ####
-write_csv(simulated_candidate_1, "data/00-simulated_data/simulated_candidate_1") 
-write_csv(simulated_candidate_2, "data/00-simulated_data/simulated_candidate_2") 
-write_csv(simulated_candidate_3, "data/00-simulated_data/simulated_candidate_3") 
+write_csv(simulated_candidate_1, "data/00-simulated_data/simulated_candidate_1.csv") 
+write_csv(simulated_candidate_2, "data/00-simulated_data/simulated_candidate_2.csv") 
+write_csv(simulated_candidate_3, "data/00-simulated_data/simulated_candidate_3.csv") 

### 2024-10-25 scripts/03-clean_data.R
Update 03-clean_data.R
Changed column selected

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Cleans the raw US president rolls data by selecting columns.
+# Purpose: Cleans the raw US president polls data by selecting columns and scaling values.
 # Author: Haowei Fan, Fangning Zhang, Shaotong Li
 # Date: 13 October 2024
 # Contact: haowei.fan@mail.utoronto.ca
@@ -10,6 +10,8 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
+library(janitor)  # For clean_names
+library(tidyr)   # For drop_na
 
 clean_data <- function(input_file, output_dir) {
   # Ensure output directory exists
@@ -19,6 +21,9 @@ clean_data <- function(input_file, output_dir) {
   
   # Load data
   president_polls <- read.csv(input_file)
+  
+  # Clean column names
+  president_polls <- janitor::clean_names(president_polls)
   
   # Custom function to handle two date formats
   parse_dates <- function(date_col) {
@@ -41,16 +46,61 @@ clean_data <- function(input_file, output_dir) {
   # Replace NA values in pollscore and numeric_grade with 0
   president_polls$pollscore[is.na(president_polls$pollscore)] <- 0
   president_polls$numeric_grade[is.na(president_polls$numeric_grade)] <- 0
+  president_polls$transparency_score[is.na(president_polls$transparency_score)] <- 1
+  
+  # Scale numeric_grade (0-3) to 0-10
+  president_polls$numeric_grade <- round(president_polls$numeric_grade * (10 / 3), 1)
+  
+  # Scale pollscore (-1.5 to 1.7) to 0-10
+  president_polls$pollscore <- round((president_polls$pollscore + 1.5) / 3.2 * 10, 1)
+  
+  # Scale transparency_score (1 to 10) to 0-10
+  president_polls$transparency_score <- round((president_polls$transparency_score - 1) * (10 / 9), 1)
   
   # Group data by candidate_name
   candidates <- unique(president_polls$candidate_name)
   
+  president_polls$Methodology <- case_when(
+    president_polls$methodology %in% c(
+      "Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", 
+      "Online Panel/Probability Panel", "Probability Panel"
+    ) ~ "level4",
+    
+    president_polls$methodology %in% c(
[…]

### 2024-10-26 scripts/01-test_simulated_data.R
Update 01-test_simulated_data.R
Update testing method based on new version of 00_simulate_data.R

@@ -1,15 +1,18 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated_data 
+# Purpose: Tests the structure and validity of the simulated_data electoral divisions dataset.
 # Author: Haowei Fan, Fangning Zhang, Shaotong Li
 # Date: 13 October 2024
 # Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
+# Pre-requisites: Requires simulated data files generated by 00-simulate_data.R
 # Any other information needed? None
 
 library(tidyverse)
 
-test_simulated_data <- function(data) {
+# Function to test individual candidate datasets
+test_simulated_candidate_data <- function(data, candidate_name) {
+  message(paste("Testing data for", candidate_name))
+  
   # Test if the data was successfully loaded
   if (exists("data")) {
     message("Test Passed: The dataset was successfully loaded.")
@@ -17,60 +20,80 @@ test_simulated_data <- function(data) {
     stop("Test Failed: The dataset could not be loaded.")
   }
   
-  # Check if the dataset has 100 rows (adjust if needed)
-  if (nrow(data) == 100) {
-    message("Test Passed: The dataset has 100 rows.")
+  # Check if the dataset has 500 rows
+  if (nrow(data) == 500) {
+    message("Test Passed: The dataset has 500 rows.")
   } else {
-    stop("Test Failed: The dataset does not have 100 rows.")
+    stop("Test Failed: The dataset does not have 500 rows.")
   }
   
-  # Check if the dataset has 9 columns (based on your simulated data)
-  if (ncol(data) == 9) {
-    message("Test Passed: The dataset has 9 columns.")
+  # Check if the dataset has 10 columns
+  if (ncol(data) == 10) {
+    message("Test Passed: The dataset has 10 columns.")
   } else {
-    stop("Test Failed: The dataset does not have 9 columns.")
+    stop("Test Failed: The dataset does not have 10 columns.")
   }
   
-  # Check if all values in the 'internal' column are valid (true or false)
-  if (all(data$internal %in% c("TRUE", "FALSE"))) {
-    message("Test Passed: All values in 'internal' are valid (true or false).")
+  # Check value ranges and types for specific columns
+  if (all(data$numeric_grade >= 0 & data$numeric_grade <= 10)) {
+    message("Test Passed: All 'numeric_grade' values are within the range 0-10.")
   } else {
-    stop("Test Failed: The 'internal' column contains invalid values.")
[…]

### 2024-10-26 scripts/03-clean_data.R
Update 03-clean_data.R
add pct to cleaned data

@@ -99,7 +99,7 @@ clean_data <- function(input_file, output_dir) {
     candidate_data <- president_polls %>%
       filter(candidate_name == candidate) %>%
       select(poll_id, pollscore, numeric_grade, transparency_score, duration,
-             sample_size, population, hypothetical, Methodology) %>%
+             sample_size, population, hypothetical, Methodology, pct) %>%
       tidyr::drop_na()  # Remove rows with any NA values
     
     # Define output file path for each candidate

### 2024-10-26 scripts/05-exploratory_data_analysis.R
Update 05-exploratory_data_analysis.R
First draft of exploratory data analysis

@@ -1,37 +1,102 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Create and explore the analysis data
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(patchwork)
 
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 3)                       
 
+print("Top three candidates by average of poll count * pct:")
+print(candidate_ranking)
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+# Define file paths
+source_folder <- "data/03-cleaned_data/cleaned_data_by_candidate/"
+destination_folder <- "data/02-analysis_data/"
+
+# Define filenames
+files_to_move <- c("Donald Trump_cleaned_data.csv", "Kamala Harris_cleaned_data.csv", "Joe Biden_cleaned_data.csv")
+
+# Copy each file from source to destination
[…]

### 2024-10-26 scripts/04-test_analysis_data.R
Update 04-test_analysis_data.R
test_analysis_data first draft

@@ -1,69 +1,67 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and contents of the analysis datasets for each candidate
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
-
-#### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+# Set working directory to project root
+setwd("..")  # Move up one level from the 'scripts' folder to the project root
 
+# Define paths for each candidate's data
+candidate_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+)
 
-#### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
+# Define expected columns
+expected_cols <- c("poll_id", "numeric_grade", "pollscore", "Methodology", 
+                   "transparency_score", "duration", "sample_size", 
+                   "population", "hypothetical", "pct")
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
+# Function to run tests on a given dataset
+test_candidate_data <- function(file_path, candidate_name) {
+  data <- read_csv(file_path)
+  
+  test_that(paste("dataset for", candidate_name, "has correct number of columns"), {
+    expect_equal(ncol(data), length(expected_cols))
+  })
+  
+  test_that(paste("dataset for", candidate_name, "contains expected columns"), {
[…]

### 2024-10-26 scripts/06-model_data.R
Update 06-model_data.R
first draft of model_data

@@ -1,37 +1,75 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Illustrate and save model data
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
 
-#### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
+library(patchwork) # For combining plots
 
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+# Create models directory if it doesn't exist
+if (!dir.exists("models")) {
+  dir.create("models")
+}
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Load data for each candidate
+donald_trump_data <- read_csv("data/02-analysis_data/Donald Trump_cleaned_data.csv") 
+joe_biden_data <- read_csv("data/02-analysis_data/Joe Biden_cleaned_data.csv") 
+kamala_harris_data <- read_csv("data/02-analysis_data/Kamala Harris_cleaned_data.csv") 
 
+# Define a function to build, summarize, and save the model for a given dataset
+build_and_save_model <- function(data, candidate_name, file_path) {
+  # Fit the linear model with pct as the dependent variable
+  model <- lm(pct ~ pollscore + numeric_grade + transparency_score + duration 
+              + sample_size + population + hypothetical + Methodology, data = data)
+  message(paste("Model summary for", candidate_name))
+  print(summary(model))
+  
+  # Save the model as an .rds file
+  saveRDS(model, file = file_path)
[…]

### 2024-10-26 scripts/07-replications.R
Update 07-replications.R
Update first draft of replication

@@ -1,19 +1,39 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Complete replication of the data analysis pipeline
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Requires all provided scripts and necessary data files
+# Any other information needed? None
 
-
-#### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
-#### Load data ####
-# [...ADD CODE HERE...]
+# 1. Simulate Data
+source("scripts/00-simulate_data.R")
+message("Data simulation complete.")
 
+# 2. Download Data
+source("scripts/02-download_data.R")
+message("Data download complete.")
 
+# 3. Clean Data
+source("scripts/03-clean_data.R")
+message("Data cleaning complete.")
 
+# 4. Test Simulated Data
+source("scripts/01-test_simulated_data.R")
+message("Simulated data testing complete.")
+
+# 5. Test Analysis Data
+setwd("scripts")
+source("04-test_analysis_data.R")
+message("Analysis data testing complete.")
+
+# 6. Exploratory Data Analysis
+source("scripts/05-exploratory_data_analysis.R")
+message("Exploratory data analysis complete.")
+
+# 7. Model Data
+source("scripts/06-model_data.R")
+message("Modeling data complete.")

### 2024-10-27 scripts/05-exploratory_data_analysis.R
Update 05-exploratory_data_analysis.R
remove model part to model data and add finding representative values

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Create and explore the analysis data
+# Purpose: Explore the analysis data and find representitive values
 # Author: Haowei Fan, Fangning Zhang, Shaotong Li
 # Date: 13 October 2024
 # Contact: haowei.fan@mail.utoronto.ca
@@ -100,3 +100,40 @@ for (candidate_name in names(candidate_data)) {
   combined_plot <- plot_distributions(data, candidate_name)
   print(combined_plot)
 }
+
+# Define paths for each candidate's data
+candidate_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+)
+
+# Function to calculate representative values
+calculate_representative_value <- function(data) {
+  data %>%
+    summarise(
+      pollscore_mean = mean(pollscore, na.rm = TRUE),
+      numeric_grade_median = median(numeric_grade, na.rm = TRUE),
+      transparency_score_mean = mean(transparency_score, na.rm = TRUE),
+      duration_mean = mean(duration, na.rm = TRUE),
+      sample_size_mean = mean(sample_size, na.rm = TRUE),
+      population_mode = as.character(names(sort(table(population), decreasing = TRUE)[1])),  # Calculate mode
+      hypothetical_mode = as.logical(names(sort(table(hypothetical), decreasing = TRUE)[1])),  # Calculate mode
+      Methodology_mode = as.character(names(sort(table(Methodology), decreasing = TRUE)[1])),  # Calculate mode
+      pct_mean = mean(pct, na.rm = TRUE)
+    )
+}
+
+# Calculate and display representative values for each candidate
+all_representative_values <- list()
+for (candidate_name in names(candidate_files)) {
+  data <- read_csv(candidate_files[[candidate_name]])
+  representative_values <- calculate_representative_value(data)
+  print(paste("Representative values for", candidate_name, ":"))
+  print(representative_values)
+  all_representative_values[[candidate_name]] <- representative_values
+}
+
+# Combine and display full results as a single data frame
+full_representative_values <- bind_rows(all_representative_values, .id = "Candidate")
+print(full_representative_values, width = Inf)

### 2024-10-27 scripts/06-model_data.R
Update 06-model_data.R
add Bayesian model

@@ -9,67 +9,123 @@
 
 
 library(tidyverse)
-library(patchwork) # For combining plots
+library(rstanarm)  # For Bayesian modeling
 
-# Create models directory if it doesn't exist
+# Define paths to each candidate's data
+candidate_data_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+)
+
+# Ensure a 'models' folder exists for saving model files
 if (!dir.exists("models")) {
   dir.create("models")
 }
 
-# Load data for each candidate
-donald_trump_data <- read_csv("data/02-analysis_data/Donald Trump_cleaned_data.csv") 
-joe_biden_data <- read_csv("data/02-analysis_data/Joe Biden_cleaned_data.csv") 
-kamala_harris_data <- read_csv("data/02-analysis_data/Kamala Harris_cleaned_data.csv") 
+# Representative data for predictions (assuming representative_data_for_prediction is already created)
 
-# Define a function to build, summarize, and save the model for a given dataset
-build_and_save_model <- function(data, candidate_name, file_path) {
-  # Fit the linear model with pct as the dependent variable
-  model <- lm(pct ~ pollscore + numeric_grade + transparency_score + duration 
-              + sample_size + population + hypothetical + Methodology, data = data)
-  message(paste("Model summary for", candidate_name))
-  print(summary(model))
+# Function to create and save a linear model for a candidate
+create_and_save_linear_model <- function(data, candidate_name) {
+  # Fit a linear model
+  linear_model <- lm(
+    pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + hypothetical + Methodology,
+    data = data
+  )
   
-  # Save the model as an .rds file
-  saveRDS(model, file = file_path)
-  message(paste("Model saved to", file_path))
+  # Save the model
+  saveRDS(linear_model, file = paste0("models/", candidate_name, "_linear_model.rds"))
+  message(paste("Linear model saved as", paste0(candidate_name, "_linear_model.rds")))
   
-  return(model)
+  return(linear_model)
 }
 
-# Function to plot actual vs. predicted values and residuals for a given model
[…]

### 2024-10-29 scripts/03-clean_data.R
Change clean_data and model_data
create train and test data in analysis data and use them for model

@@ -116,3 +116,71 @@ clean_data <- function(input_file, output_dir) {
 input_file <- "data/01-raw_data/raw_data.csv"   
 output_dir <- "data/03-cleaned_data/cleaned_data_by_candidate"  
 cleaned_data <- clean_data(input_file, output_dir)
+
+raw_data <- read_csv("data/01-raw_data/raw_data.csv")
+
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 3)                       
+
+print("Top three candidates by average of poll count * pct:")
+print(candidate_ranking)
+
+# Define file paths
+source_folder <- "data/03-cleaned_data/cleaned_data_by_candidate/"
+destination_folder <- "data/02-analysis_data/"
+
+# Define filenames
+files_to_move <- c("Donald Trump_cleaned_data.csv", "Kamala Harris_cleaned_data.csv", "Joe Biden_cleaned_data.csv")
+
+# Copy each file from source to destination
+for (file_name in files_to_move) {
+  file_path <- file.path(source_folder, file_name)
+  destination_path <- file.path(destination_folder, file_name)
+  
+  # Copy file
+  file.copy(file_path, destination_path, overwrite = TRUE)
+  message(paste("File saved to:", destination_path))
+}
+
+# Define paths for each candidate's analysis data
+candidate_data_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+)
+
+# Function to split data into training (70%) and test (30%) sets
+split_data <- function(data, train_ratio = 0.7) {
+  set.seed(123)  # Set seed for reproducibility
+  train_indices <- sample(seq_len(nrow(data)), size = floor(train_ratio * nrow(data)))
+  train_data <- data[train_indices, ]
+  test_data <- data[-train_indices, ]
+  list(train = train_data, test = test_data)
+}
+
+# Process each candidate's data
+for (candidate_name in names(candidate_data_files)) {
+  # Load the data
+  data <- read.csv(candidate_data_files[[candidate_name]])
+  
[…]

### 2024-10-29 scripts/06-model_data.R

@@ -11,19 +11,23 @@
 library(tidyverse)
 library(rstanarm)  # For Bayesian modeling
 
-# Define paths to each candidate's data
-candidate_data_files <- list(
-  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
-  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
-  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+# Define paths to each candidate's analysis data (training and testing data)
+candidate_train_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_train.csv",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_train.csv",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_train.csv"
+)
+
+candidate_test_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_test.csv",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_test.csv",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_test.csv"
 )
 
 # Ensure a 'models' folder exists for saving model files
 if (!dir.exists("models")) {
   dir.create("models")
 }
-
-# Representative data for predictions (assuming representative_data_for_prediction is already created)
 
 # Function to create and save a linear model for a candidate
 create_and_save_linear_model <- function(data, candidate_name) {
@@ -40,15 +44,13 @@ create_and_save_linear_model <- function(data, candidate_name) {
   return(linear_model)
 }
 
-# Function to create and save a Bayesian model for a candidate, excluding constant variables and poll_id
+# Function to create and save a Bayesian model for a candidate, excluding constant variables
 create_and_save_bayesian_model <- function(data, candidate_name) {
-  # Exclude constant variables and poll_id
   constant_vars <- names(data)[sapply(data, function(x) length(unique(x)) == 1)]
   formula <- as.formula(
     paste("pct ~", paste(setdiff(names(data), c("pct", "poll_id", constant_vars)), collapse = " + "))
   )
   
-  # Fit a Bayesian model
   bayesian_model <- stan_glm(
     formula,
     data = data,
@@ -59,73 +61,76 @@ create_and_save_bayesian_model <- function(data, candidate_name) {
     seed = 123
   )
   
-  # Save the model
[…]

### 2024-10-30 paper/paper.qmd
Update paper.qmd
Update YAML metadata，introduction part and overview part in data

---
title: "The 2024 U.S. Presidential Election Forecast"
subtitle: "Multiple Linear Regression and Bayesian Models Accounting for Poll Quality"
author: Haowei Fan, Fangning Zhang, Shaotong Li
thanks: "Code and data are available at: https://github.com/HaoweiFan0912/The-2024-U.S.-Presidential-Election-Forecast"
date: 13/10/2024
contact: haowei.fan@mail.utoronto.ca
licence: MIT
date-format: long
abstract: "This study presents a forecast for the 2024 U.S. presidential election using aggregated poll data to predict support for key candidates. By implementing both linear and Bayesian models, we analyze poll data from diverse sources to assess how factors related to poll quality influence candidate support predictions. Our findings reveal possible outcome of election. Additionally, this paper includes an idealized polling methodology to demonstrate best practices in survey design and sample representation."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
toc-title: "Table of Contents"
toc-depth: 2
toc-location: left
---

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(dplyr)
library(ggplot2)
library(patchwork)
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
```

# Introduction

The U.S. presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights. As the world anticipates the 2024 U.S. electoral contest, predicting the election’s possible outcomes can provide critical insights for policymakers, businesses, and civil society groups. This study aims to forecast the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.

To provide a robust prediction, we utilize a “poll-of-polls” approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support. Our analysis applies both a linear regression model and a Bayesian approach, with a focus on the key parameter of each candidate's predicted vote share. By considering variations in pollster methodology and geographic distinctions, we account for the nuances of state-level political landscapes and the potential influence of polling organizations.

The results of our models reveal consistent patterns in voter support across both Harris and Trump. The linear model estimates a stable support rate for Donald Trump at approximately 47.8%, with similar results for Harris at 46.7%. The Bayesian model, which incorporates pollster and state-level random effects, yields slightly more conservative support estimates, predicting 47.9% for Trump and 46.0% for Harris. These findings suggest that, while both candidates maintain stable support, Trump holds a slight advantage. The consistency across both models underlines the importance of accounting for variability across polling methodologies and regional voter bases.

Beyond the immediate electoral forecast, this study contributes valuable insights for understanding how polling predictions can inform societal and international expectations. Predicting election outcomes allows global stakeholders—such as policymakers, investors, and international organizations—to anticipate and adapt to potential shifts in U.S. policy. For instance, a leadership change could bring alterations in U.S. positions on trade, climate commitments, and foreign policy, influencing global economic stability and strategic alliances. Additionally, our findings underscore the importance of transparency in polling methodologies, as well as the potential for more nuanced and accurate forecasts that consider the heterogeneity in polling sources and voter demographics.

This paper is organized as follows. The next section outlines the data collection and filtering processes, detailing the key variables and sources. Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models. In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings. Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.

# Data {#sec-data}

## Overview

This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S. presidential election forecast. The raw polling data was sourced from FiveThirtyEight's 2024 presidential election polls[@fivethirtyeight2024], providing a comprehensive foundation for our analysis. Together, these packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.

## Raw data
raw data一共有52个variables，以及15891条样本。
去掉重复variables，以及无关紧要的url,还有全空的varibales后还剩下以下variables以及description。
部分重要的在此显示，不重要的在appendix。
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-main_columns
#| tbl-cap: "Main column descriptions of the raw data"

# Define the selected variable names
selected_variables <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "numeric_grade", "pollscore", "methodology", "transparency_score", "state", "start_date", "end_date", "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "sample_size", "population", "tracking", "created_at", "notes", "source", "internal", "partisan", "race_id", "cycle", "office_type", "election_date", "stage", "nationwide_batch", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical", "party", "answer", "pct")

# Define their descriptions
variable_descriptions <- c(
  "Unique identifier for each poll conducted.",
  "Unique identifier for the polling organization conducting the poll.",
  "Unique identifier(s) for the sponsor(s) of the poll, typically organizations that fund the poll.",
  "Unique identifier for the pollster's rating within a rating system.",
  "A numeric rating given to the pollster to indicate their quality or reliability .",
  "A numeric value representing the score or reliability of the pollster in question .",
  "The method used to conduct the poll .",
  "A score reflecting the pollster's transparency about their methodology .",
  "The U.S. state where the poll was conducted or focused, if applicable.",
  "The date the poll began .",
  "The date the poll ended .",
  "Unique identifier for the candidate sponsored by the sponsoring organization (if applicable).",
  "The political party of the candidate sponsored by the sponsor (if applicable).",
  "Unique identifier for the question asked in the poll.",
  "The total number of respondents participating in the poll .",
  "The abbreviated description of the respondent group, typically indicating their voting status .",
  "Indicates whether the poll is part of a tracking series .",
  "The timestamp when the poll data was created or entered into the system .",
  "Any additional notes or comments related to the poll.",
  "The source from where the poll data was derived.",
  "Indicates whether the poll is conducted internally by a campaign or organization.",
  "Indicates whether the poll has partisan sponsorship or is conducted by a partisan organization.",
  "A unique identifier for the political race being polled .",
  "The election cycle in which the poll is conducted .",
  "The type of political office being polled .",
  "The date of the election the poll is related to .",
  "The stage of the election being polled .",
  "Indicates whether the poll is part of a nationwide batch.",
  "Indicates if ranked-choice voting reallocations have been applied in the results.",
  "The round of ranked-choice voting, if applicable.",
  "Indicates whether the poll is about a hypothetical match-up.",
  "The political party of the candidate in the poll .",
  "The response or answer choice given in the poll .",
  "The percentage of the vote or support that the candidate received in the poll ."
)

# Create a tibble with variable names and descriptions
variable_tibble <- tibble(
  Variable = selected_variables,
  Description = variable_descriptions
)

# Define the variables to extract for the table of selected variables
variables_to_extract <- c("poll_id", "pollscore", "numeric_grade", "transparency_score", "start_date", "end_date", "sample_size", "population", "hypothetical", "methodology", "pct")

# Extract the relevant rows from the tibble
extracted_tibble <- variable_tibble %>% filter(Variable %in% variables_to_extract)

# Create the table using kable for selected variables
kable(extracted_tibble)
```
所有variable的na值
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-variable_na
#| tbl-cap: "Number of Missing Values and Percentages for Variables"
# Calculate the number of missing values for each selected variable
na_counts <- sapply(raw_data[ , selected_variables], function(x) sum(is.na(x)))

# Calculate the percentage of missing values for each selected variable
na_percentages <- sapply(raw_data[ , selected_variables], function(x) mean(is.na(x)) * 100)

# Create a tibble for missing value counts and percentages
na_tibble <- tibble(
  Variable = names(na_counts),
  Missing_Values = na_counts,
  Percentage_Missing = round(na_percentages,2)
)

# Split the tibble into two halves for side-by-side display
na_tibble_1 <- na_tibble[1:ceiling(nrow(na_tibble)/2), ]
na_tibble_2 <- na_tibble[(ceiling(nrow(na_tibble)/2) + 1):nrow(na_tibble), ]

# Create the table using kable for missing values
kable(na_tibble)
```
重要的numerical variable的分布：
```{r, fig.pos="H", fig.width=22, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-numdis
#| fig-cap: "Distribution of numerical varibales"
### Define Variables and Prepare Data ###
# Define the numeric variables to plot
numeric_variables <- c("pollscore", "numeric_grade", "transparency_score", "sample_size", "pct")

# Convert start_date and end_date to Date type
raw_data$start_date <- ymd(raw_data$start_date)
raw_data$end_date <- ymd(raw_data$end_date)

# Define the date variables to plot
date_variables <- c("start_date", "end_date")

### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()

# Loop through selected numeric variables and plot their distributions
for (variable in numeric_variables) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 0.7, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}

### Create Plots for Date Variables ###
# Loop through selected date variables and plot their distributions
for (variable in date_variables) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 30, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}

### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 3, nrow = 3, heights = unit(rep(3, 4), "in")) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )

# Print the combined plot
print(combined_plot)

```
接下来是categorical
```{r, fig.pos="H", fig.width=22, fig.height=8}
#| warning: false
#| message: false
#| echo: false
#| label: fig-catdis
#| fig-cap: "Distribution of categorical varibales"

### Plot distributions for categorical variables ###
# Define the categorical variables to plot
categorical_variables <- setdiff(variables_to_extract, c(numeric_variables, "start_date", "end_date"))
categorical_variables <- categorical_variables[categorical_variables != "methodology" ]
categorical_variables <- categorical_variables[categorical_variables != "poll_id" ]
# Create a list to store plots for categorical variables
categorical_plots <- list()

# Loop through categorical variables and plot their distributions
for (variable in categorical_variables) {
  plot <- ggplot(raw_data, aes_string(x = variable)) +
    geom_bar(fill = "#69b3a2", color = "black") +
    labs(title = paste(variable), x = variable, y = "Count") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5))

  # Add plot to list
  categorical_plots[[variable]] <- plot
}

### Plot top 5 methodologies ###
# Extract top 5 methodologies by frequency
top_5_methodologies <- raw_data %>%
  count(methodology, sort = TRUE) %>%
  top_n(5) %>%
  pull(methodology)

# Create a new column to categorize methodologies into top 5 and 'Other'
raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_5_methodologies, raw_data$methodology, 'Other')

# Plot the distribution of the top 5 methodologies plus 'Other'
methodology_plot <- ggplot(raw_data, aes(x = methodology_grouped)) +
  geom_bar(fill = "#69b3a2", color = "black") +
  labs(title = "Top 5 Methodologies and Others", x = "Methodology", y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

# Add methodology plot to categorical plots list
categorical_plots[["methodology_grouped"]] <- methodology_plot

# Combine all individual plots for categorical variables into one using patchwork
combined_categorical_plot <- wrap_plots(categorical_plots) +
  plot_annotation(title = "Distributions of Categorical Variables")

# Print the combined plot for categorical variables
print(combined_categorical_plot)

### Create a list for non-numeric variables ###
non_numeric_variables <- setdiff(variables_to_extract, numeric_variables)

```
#######注意，appendix其他的图还没画

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}

```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}

```

```{r}
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details
raw data 部分没有解释的varibale
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-remain_columns
#| tbl-cap: "Remaining column descriptions of the raw data"

# Define the variables to extract for the remaining variables
remaining_variables <- setdiff(selected_variables, variables_to_extract)

# Extract the relevant rows from the tibble for remaining variables
remaining_tibble <- variable_tibble %>% filter(Variable %in% remaining_variables)

# Create the table using kable for remaining variables
kable(remaining_tibble, caption = "Descriptions of Remaining Variables")
```
raw data里没画的图
```{r}
#to be done
```

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}

```

\newpage

# References

### 2024-10-30 paper/paper.qmd
Update paper.qmd
update draft for measurement

@@
 
-This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S.
+This project leverages several R packages[@citeR], including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S.
 presidential election forecast.
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+This study uses polling data from FiveThirtyEight to capture public sentiment for the 2024 U.S.
+presidential election.
+Each observation in the dataset represents public support levels for key candidates as recorded by national and state-level polling organizations.
+Given the diversity in polling methodologies, question formats, and sampling techniques, the transformation of real-world opinions into structured data requires a standardized approach to ensure accuracy and comparability across sources.
+
+The raw data underwent a comprehensive cleaning process to improve reliability.
+Initial filtering was applied to remove polls with missing key variables, such as support percentages, sample sizes, or poll ratings, ensuring that only complete and meaningful entries were retained.
+Duplicate entries were identified and eliminated to prevent redundancy.
+Polls with extreme support values or small sample sizes, which could introduce bias, were carefully reviewed and either adjusted or excluded based on consistency criteria.
+
+Further, the data was standardized to unify variable formats and scales.
+Poll results reported in percentages were converted to decimal values, and state names were formatted consistently.
+After cleaning, the dataset was divided into training and test sets, with 70% allocated to training the model and 30% reserved for validation.
+This approach provided a robust dataset that accurately reflects public opinion trends, reducing the impact of inconsistencies across polling sources and supporting a reliable forecast of the 2024 U.S.
+presidential election.
 

### 2024-10-30 scripts/05-exploratory_data_analysis.qmd
simulation datasets are uploaded
simulation datasets are uploaded
Change csv  to parquet when saving analysis data
also make a small change in replications

@@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Explore the analysis data and find representitive values
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 #### Workspace setup ####
@@
 library(rstanarm)
-
+library(patchwork)
 #### Read data ####
-analysis_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
+raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
 ```
 
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Check for missing values in each column
-missing_values <- sapply(analysis_data, function(x) sum(is.na(x)))
+missing_values <- sapply(raw_data, function(x) sum(is.na(x)))
 print(missing_values)
 ```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+### Remove columns with more than 50% missing values ###
 
-```{r}
+# Find columns with missing value percentage greater than 50%
+total_rows <- nrow(raw_data)
+columns_to_keep <- sapply(raw_data, function(x) sum(is.na(x)) <= total_rows / 2)
+
+# Filter raw_data to keep only the columns with less than or equal to 50% missing values
+raw_data <- raw_data[, columns_to_keep]
+
+# View the columns kept
+print(sapply(raw_data, function(x) sum(is.na(x))))
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+### Remove columns with all identical values ###
+# Find columns where all values are identical
+columns_to_keep <- sapply(raw_data, function(x) length(unique(x)) > 1)
+
+# Filter raw_data to remove columns with all identical values
+raw_data <- raw_data[, columns_to_keep]
+
+# View the columns kept
+print(sapply(raw_data, function(x) sum(is.na(x))))
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Get unique pollster IDs
-unique_pollster_ids <- unique(analysis_data$pollster_id)
+unique_pollster_ids <- unique(raw_data$pollster_id)
 print(unique_pollster_ids)
 ```
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Get unique question IDs
-unique_question_ids <- unique(analysis_data$question_id)
+unique_question_ids <- unique(raw_data$question_id)
 print(unique_question_ids)
 ```
-```{r}
-unique_question_ids_str <- paste(unique(unique_question_ids), collapse = ",")
-print(unique_question_ids_str)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique methodologys
+unique_methodologys <- unique(raw_data$methodology)
+print(unique_methodologys)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique population
+unique_population <- unique(raw_data$population)
+print(unique_population)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique race_id
+unique_race_id <- unique(raw_data$race_id)
+print(unique_race_id)
 ```
 
-```{r}
-View(unique_question_ids_str)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique ranked_choice_reallocated
+unique_ranked_choice_reallocated <- unique(raw_data$ranked_choice_reallocated)
+print(unique_ranked_choice_reallocated)
 ```
-
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique hypothetical
+unique_hypothetical <- unique(raw_data$hypothetical)
+print(unique_hypothetical)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique party
+unique_party <- unique(raw_data$party)
+print(unique_party)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Get the maximum and minimum values of numeric_grade
-max_numeric_grade <- max(analysis_data$numeric_grade, na.rm = TRUE)
-min_numeric_grade <- min(analysis_data$numeric_grade, na.rm = TRUE)
+max_numeric_grade <- max(raw_data$numeric_grade, na.rm = TRUE)
+min_numeric_grade <- min(raw_data$numeric_grade, na.rm = TRUE)
 print(paste("Maximum numeric grade:", max_numeric_grade))
@@
 ```
-
-```{r}
-# Plot histogram of numeric_grade
-ggplot(analysis_data, aes(x = numeric_grade)) +
-  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
-  theme_minimal() +
-  labs(title = "Histogram of Numeric Grade", x = "Numeric Grade", y = "Count")
-```
-```{r}
-# Plot histogram of pollscore
-ggplot(analysis_data, aes(x = pollscore)) +
-  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
-  theme_minimal() +
-  labs(title = "Histogram of pollscore", x = "pollscore", y = "Count")
-```
-```{r}
-# Get unique methodologys
-unique_methodologys <- unique(analysis_data$methodology)
-print(unique_methodologys)
-```
-```{r}
-# Plot histogram of transparency_score
-ggplot(analysis_data, aes(x = transparency_score)) +
-  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
-  theme_minimal() +
-  labs(title = "Histogram of transparency_score", x = "transparency_score", y = "Count")
-```
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Find the earliest start date and the latest end date
-earliest_start_date <- min(analysis_data$start_date, na.rm = TRUE)
-latest_end_date <- max(analysis_data$end_date, na.rm = TRUE)
+earliest_start_date <- min(raw_data$start_date, na.rm = TRUE)
+latest_end_date <- max(raw_data$end_date, na.rm = TRUE)
 print(paste("Earliest start date:", earliest_start_date))
@@
 ```
-
-```{r}
-# Plot histogram of sample_size
-ggplot(analysis_data, aes(x = sample_size)) +
-  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
-  theme_minimal() +
-  labs(title = "Histogram of sample_size", x = "sample_size", y = "Count")
-```
-```{r}
-# Get unique population
-unique_population <- unique(analysis_data$population)
-print(unique_population)
-```
-```{r}
-# Get unique race_id
-unique_race_id <- unique(analysis_data$race_id)
-print(unique_race_id)
-```
-
-```{r}
-unique_race_id_str <- paste(unique(unique_race_id), collapse = ",")
-clipr::write_clip(unique_race_id_str)
-```
-
-```{r}
-# Get unique stage
-unique_stage <- unique(analysis_data$stage)
-print(unique_stage)
-```
-
-```{r}
-# Get unique stage
-unique_nationwide_batch <- unique(analysis_data$nationwide_batch)
-print(unique_nationwide_batch)
-```
-
-```{r}
-# Get unique ranked_choice_reallocated
-unique_ranked_choice_reallocated <- unique(analysis_data$ranked_choice_reallocated)
-print(unique_ranked_choice_reallocated)
-```
-
-```{r}
-# Get unique hypothetical
-unique_hypothetical <- unique(analysis_data$hypothetical)
-print(unique_hypothetical)
-```
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Calculate the ratio of FALSE to TRUE in the hypothetical column
-hypothetical_ratio <- table(analysis_data$hypothetical)
+hypothetical_ratio <- table(raw_data$hypothetical)
 print(hypothetical_ratio)
@@
 
-```{r}
-# Get unique party
-unique_party <- unique(analysis_data$party)
-print(unique_party)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Find the range of pollscore in the original dataset
+pollscore_range <- range(raw_data$pollscore, na.rm = TRUE)
+print(paste("Pollscore range:", pollscore_range[1], "to", pollscore_range[2]))
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Plot histogram of numeric_grade
+ggplot(raw_data, aes(x = numeric_grade)) +
+  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
+  theme_minimal() +
+  labs(title = "Histogram of Numeric Grade", x = "Numeric Grade", y = "Count")
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Plot histogram of pollscore
+ggplot(raw_data, aes(x = pollscore)) +
+  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
+  theme_minimal() +
+  labs(title = "Histogram of pollscore", x = "pollscore", y = "Count")
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Plot histogram of transparency_score
+ggplot(raw_data, aes(x = transparency_score)) +
+  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
+  theme_minimal() +
+  labs(title = "Histogram of transparency_score", x = "transparency_score", y = "Count")
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Plot histogram of sample_size
+ggplot(raw_data, aes(x = sample_size)) +
+  geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
+  theme_minimal() +
+  labs(title = "Histogram of sample_size", x = "sample_size", y = "Count")
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Find the top 3 candidates.
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 3)                       
+print(candidate_ranking)
 ```
 
-```{r}
-# Get unique population
-unique_population <- unique(analysis_data$population)
-print(unique_population)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Load data for each candidate
+donald_trump_data <- read_parquet(here::here("data/02-analysis_data/Donald Trump_cleaned_data.parquet"))
+joe_biden_data <- read_parquet(here::here("data/02-analysis_data/Joe Biden_cleaned_data.parquet")) 
+kamala_harris_data <- read_parquet(here::here("data/02-analysis_data/Kamala Harris_cleaned_data.parquet"))
+
+# Define and load data for each candidate
+candidate_data <- list(
+  "Donald Trump" = donald_trump_data %>% select(-poll_id, -pct),
+  "Kamala Harris" = joe_biden_data %>% select(-poll_id, -pct),
+  "Joe Biden" = kamala_harris_data %>% select(-poll_id, -pct)
+)
+
+# Function to create distribution plots for each variable in a dataset
+plot_distributions <- function(data, candidate_name) {
+  plots <- list()
+
+  for (var in names(data)) {
+    if (is.numeric(data[[var]])) {
+      # Histogram for numeric variables
+      plot <- ggplot(data, aes(x = .data[[var]])) +
+        geom_histogram(bins = 30, color = "black", fill = "skyblue") +
+        labs(title = paste("Distribution of", var, "for", candidate_name), x = var, y = "Frequency") +
+        theme_minimal()
+
+    } else if (is.character(data[[var]]) || is.factor(data[[var]])) {
+      # Bar plot for categorical variables
+      plot <- ggplot(data, aes(x = .data[[var]])) +
+        geom_bar(color = "black", fill = "skyblue") +
+        labs(title = paste("Distribution of", var, "for", candidate_name), x = var, y = "Count") +
+        theme_minimal()
+
+    } else if (is.logical(data[[var]])) {
+      # Bar plot for logical variables (TRUE/FALSE)
+      plot <- ggplot(data, aes(x = factor(.data[[var]], levels = c(TRUE, FALSE)))) +
+        geom_bar(color = "black", fill = "skyblue") +
+        labs(title = paste("Distribution of", var, "for", candidate_name), x = var, y = "Count") +
+        theme_minimal()
+    }
+
+    # Add plot to list
+    plots[[var]] <- plot
+  }
+
+  # Combine all individual plots into one using patchwork
+  combined_plot <- wrap_plots(plots) +
+    plot_annotation(title = paste("Distributions of Variables for", candidate_name))
+
+  return(combined_plot)
+}
+
+# Create and display combined plots for each candidate
+for (candidate_name in names(candidate_data)) {
+  data <- candidate_data[[candidate_name]]
+  combined_plot <- plot_distributions(data, candidate_name)
+  print(combined_plot)
+}
+
 ```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Define paths for each candidate's data
+candidate_files <- list(
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.parquet",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.parquet",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.parquet"
+)
+
+# Function to calculate representative values
+calculate_representative_value <- function(data) {
+  data %>%
+    summarise(
+      pollscore_mean = mean(pollscore, na.rm = TRUE),
+      numeric_grade_median = median(numeric_grade, na.rm = TRUE),
+      transparency_score_mean = mean(transparency_score, na.rm = TRUE),
+      duration_mean = mean(duration, na.rm = TRUE),
+      sample_size_mean = mean(sample_size, na.rm = TRUE),
+      population_mode = as.character(names(sort(table(population), decreasing = TRUE)[1])),  # Calculate mode
+      hypothetical_mode = as.logical(names(sort(table(hypothetical), decreasing = TRUE)[1])),  # Calculate mode
+      Methodology_mode = as.character(names(sort(table(Methodology), decreasing = TRUE)[1])),  # Calculate mode
+      pct_mean = mean(pct, na.rm = TRUE)
+    )
+}
+
+# Calculate and display representative values for each candidate
+all_representative_values <- list()
+for (candidate_name in names(candidate_files)) {
+  data <- read_parquet(here::here(candidate_files[[candidate_name]]))
+  representative_values <- calculate_representative_value(data)
+  all_representative_values[[candidate_name]] <- representative_values
+}
+
+# Combine and display full results as a single data frame
+full_representative_values <- bind_rows(all_representative_values, .id = "Candidate")
+print(full_representative_values, width = Inf)
+```

### 2024-10-30 scripts/03-clean_data.R

@@ -131,28 +131,33 @@ candidate_ranking <- raw_data %>%
 print("Top three candidates by average of poll count * pct:")
 print(candidate_ranking)
 
+# Load necessary library
+library(arrow)
+
 # Define file paths
 source_folder <- "data/03-cleaned_data/cleaned_data_by_candidate/"
 destination_folder <- "data/02-analysis_data/"
 
 # Define filenames
-files_to_move <- c("Donald Trump_cleaned_data.csv", "Kamala Harris_cleaned_data.csv", "Joe Biden_cleaned_data.csv")
+files_to_convert <- c("Donald Trump_cleaned_data.csv", "Kamala Harris_cleaned_data.csv", "Joe Biden_cleaned_data.csv")
 
-# Copy each file from source to destination
-for (file_name in files_to_move) {
-  file_path <- file.path(source_folder, file_name)
-  destination_path <- file.path(destination_folder, file_name)
+# Convert each cleaned data file from CSV to Parquet
+for (file_name in files_to_convert) {
+  csv_path <- file.path(source_folder, file_name)
+  parquet_path <- file.path(destination_folder, sub(".csv$", ".parquet", file_name))  # Change .csv to .parquet
   
-  # Copy file
-  file.copy(file_path, destination_path, overwrite = TRUE)
-  message(paste("File saved to:", destination_path))
+  # Read CSV and save as Parquet
+  data <- read.csv(csv_path)
+  write_parquet(data, parquet_path)
+  
+  message(paste("File converted to Parquet and saved to:", parquet_path))
 }
 
 # Define paths for each candidate's analysis data
 candidate_data_files <- list(
-  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
-  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
-  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.parquet",
+  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.parquet",
+  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.parquet"
 )
 
 # Function to split data into training (70%) and test (30%) sets
@@ -166,19 +171,19 @@ split_data <- function(data, train_ratio = 0.7) {
 
 # Process each candidate's data
 for (candidate_name in names(candidate_data_files)) {
-  # Load the data
[…]

### 2024-10-30 scripts/04-test_analysis_data.R

@@ -7,61 +7,61 @@
 # Pre-requisites: 02-analysis_data saved and loaded
 # Any other information needed? None
 
+# Load necessary libraries
 library(tidyverse)
 library(testthat)
+library(arrow)  # For reading Parquet files
+library(here)
 
-# Set working directory to project root
-setwd("..")  # Move up one level from the 'scripts' folder to the project root
+# Define directory path for analysis data files
+analysis_data_dir <- here("data/02-analysis_data")
 
-# Define paths for each candidate's data
-candidate_files <- list(
-  "Donald Trump" = "data/02-analysis_data/Donald Trump_cleaned_data.csv",
-  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_cleaned_data.csv",
-  "Joe Biden" = "data/02-analysis_data/Joe Biden_cleaned_data.csv"
+# Get a list of all Parquet files in the directory
+candidate_files <- list.files(analysis_data_dir, pattern = "\\.parquet$", full.names = TRUE)
+
+# Define expected columns and data types (allowing both integer and double for numeric columns)
+expected_columns <- c("poll_id", "numeric_grade", "pollscore", "Methodology", 
+                      "transparency_score", "duration", "sample_size", 
+                      "population", "hypothetical", "pct")
+expected_types <- list(
+  poll_id = c("double", "integer"),
+  numeric_grade = c("double", "integer"),
+  pollscore = c("double", "integer"),
+  Methodology = "character",
+  transparency_score = c("double", "integer"),
+  duration = c("double", "integer"),
+  sample_size = c("double", "integer"),
+  population = "character",
+  hypothetical = c("logical", "character"),
+  pct = c("double", "integer")
 )
 
-# Define expected columns
-expected_cols <- c("poll_id", "numeric_grade", "pollscore", "Methodology", 
-                   "transparency_score", "duration", "sample_size", 
-                   "population", "hypothetical", "pct")
-
-# Function to run tests on a given dataset
-test_candidate_data <- function(file_path, candidate_name) {
-  data <- read_csv(file_path)
+# Function to test each candidate's data
+test_candidate_data <- function(file_path) {
+  data <- read_parquet(file_path)
+  candidate_name <- tools::file_path_sans_ext(basename(file_path))
   
-  test_that(paste("dataset for", candidate_name, "has correct number of columns"), {
-    expect_equal(ncol(data), length(expected_cols))
[…]

### 2024-10-30 scripts/06-model_data.R

@@ -7,21 +7,23 @@
 # Pre-requisites: 02-analysis_data saved and loaded
 # Any other information needed? None
 
-
+# Load necessary libraries
 library(tidyverse)
 library(rstanarm)  # For Bayesian modeling
+library(arrow)     # For reading/writing Parquet files
+library(here)
 
 # Define paths to each candidate's analysis data (training and testing data)
 candidate_train_files <- list(
-  "Donald Trump" = "data/02-analysis_data/Donald Trump_train.csv",
-  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_train.csv",
-  "Joe Biden" = "data/02-analysis_data/Joe Biden_train.csv"
+  "Donald Trump" = here::here("data/02-analysis_data/Donald Trump_train.parquet"),
+  "Kamala Harris" = here::here("data/02-analysis_data/Kamala Harris_train.parquet"),
+  "Joe Biden" = here::here("data/02-analysis_data/Joe Biden_train.parquet")
 )
 
 candidate_test_files <- list(
-  "Donald Trump" = "data/02-analysis_data/Donald Trump_test.csv",
-  "Kamala Harris" = "data/02-analysis_data/Kamala Harris_test.csv",
-  "Joe Biden" = "data/02-analysis_data/Joe Biden_test.csv"
+  "Donald Trump" = here::here("data/02-analysis_data/Donald Trump_test.parquet"),
+  "Kamala Harris" = here::here("data/02-analysis_data/Kamala Harris_test.parquet"),
+  "Joe Biden" = here::here("data/02-analysis_data/Joe Biden_test.parquet")
 )
 
 # Ensure a 'models' folder exists for saving model files
@@ -29,28 +31,55 @@ if (!dir.exists("models")) {
   dir.create("models")
 }
 
-# Function to create and save a linear model for a candidate
+# Function to create and save a linear model for a candidate, excluding constant and single-level variables
 create_and_save_linear_model <- function(data, candidate_name) {
-  # Fit a linear model
-  linear_model <- lm(
-    pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + hypothetical + Methodology,
-    data = data
+  # Identify constant variables
+  constant_vars <- names(data)[sapply(data, function(x) length(unique(x)) == 1)]
+  
+  # Identify and remove single-level categorical variables
+  categorical_vars <- names(data)[sapply(data, is.factor)]
[…]

### 2024-10-30 scripts/07-replications.R

@@ -26,14 +26,13 @@ source("scripts/01-test_simulated_data.R")
 message("Simulated data testing complete.")
 
 # 5. Test Analysis Data
-setwd("scripts")
-source("04-test_analysis_data.R")
+source("scripts/04-test_analysis_data.R")
 message("Analysis data testing complete.")
 
-# 6. Exploratory Data Analysis
-source("scripts/05-exploratory_data_analysis.R")
-message("Exploratory data analysis complete.")
-
-# 7. Model Data
+# 6. Model Data
 source("scripts/06-model_data.R")
 message("Modeling data complete.")
+
+
+
+

### 2024-10-31 paper/paper.qmd
Update paper.qmd
Update model part

@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modeling strategy is to estimate the support percentages for leading candidates in the 2024 U.S.
+presidential election, with a specific focus on Kamala Harris and Donald Trump.
+This approach accounts for potential variations in support across time, different pollsters, and geographic regions, ensuring a robust prediction framework that balances accuracy with interpretability.
+We implement both linear and Bayesian models to capture these patterns and examine the influence of polling quality and state-specific factors on the predicted support levels.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The linear model employs multiple regression, with candidate support percentage as the dependent variable and key predictors such as pollster rating, sample size, geographic region, and polling methodology.
+This model provides an interpretable framework, allowing us to assess the direct impact of each factor on candidate support.
+However, to account for more nuanced, hierarchical patterns within the data, we extend this analysis using a Bayesian framework.
 
-## Model set-up
+The Bayesian model incorporates pollster and state-level random effects, enabling us to model variations across different polling organizations and geographic areas more effectively.
+By including weakly informative priors, the Bayesian model offers greater flexibility while controlling for overfitting, providing a more comprehensive view of voter support trends.
+Together, these models create a reliable foundation for forecasting support in the 2024 election, with each approach highlighting distinct aspects of the polling data.
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+## linear Model set-up
+
+Define $y_i$ as the support percentage (pct) for a candidate in the 2024 U.S.
+presidential election polls.
+The linear model includes several predictors: $α_i$ (poll reliability score), $β_i$ (numeric grade indicating poll quality), $γ_i$ (transparency score of poll methodology), $δ_i$ (poll duration), $θ_i$ (sample size), $κ_i$ (type of population surveyed), $λ_i$ (whether the poll is hypothetical), and $μ_i$ (poll methodology type).
+
+The model is specified as follows:
+
+```{=tex}
 
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
+y_i | \mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_1 \times \phi_i + \beta_2 \times \beta_i + \beta_3 \times \gamma_i + \beta_4 \times \delta_i \\
+      &\quad + \beta_5 \times \theta_i + \beta_6 \times \kappa_i + \beta_7 \times \lambda_i + \beta_8 \times \mu_i \\
+\alpha &\sim \mbox{Normal}(0, 10) \\
+\beta_j &\sim \mbox{Normal}(0, 2.5) \quad \text{for each } j = 1, \dots, 8 \\
 \sigma &\sim \mbox{Exponential}(1)
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+```
+We run the model in R [@citeR] using the lm() for linear regression, along with tidyverse [@tidyverse] for data manipulation and visualization.
+
+### Model Justification
+
+This linear model aims to estimate candidate support percentages in the 2024 U.S.
+presidential election by accounting for various poll characteristics and methodological factors.
+The model includes multiple predictors, represented by $φ_i$, $β_i$, $γ_i$, $δ_i$, $θ_i$, $κ_i$, $λ_i$, and $μ_i$, each of which captures different aspects of the polling data that may impact candidate support.
+
+The variable $φ_i$ represents poll reliability scores, with higher values expected to correlate with more stable support estimates.
+Similarly, $β_i$ and $γ_i$ denote quality-related factors such as numeric grade and transparency score, which likely influence the reliability of the polls.
+Poll duration ($δ_i$) and sample size ($θ_i$) add further depth to the model by reflecting the scope and stability of each poll's data.
+The variables $κ_i$, $λ_i$, and $μ_i$ account for population type, the hypothetical nature of the poll, and poll methodology, respectively, allowing the model to adjust for methodological differences across polling organizations.
+
+By incorporating these predictors with normal priors centered at zero, the model balances complexity with interpretability, providing a nuanced view of the factors influencing candidate support.
+This approach enables us to evaluate how each factor contributes to variations in support predictions while maintaining flexibility to capture unique patterns within the data.
+The inclusion of weakly informative priors prevents overfitting and ensures that the model remains generalizable across different polling scenarios.
+
+### Results
+
+Our results are summarized in:
+
+```{r}
+#| label: linear-model
+#| fig-cap: linear model analysis
+#| echo: false
+#| warning: false
+#| message: false
+
+# Load the Trump and Harris linear models
+trump_linear_model <- readRDS(here::here("models", "Donald Trump_linear_model.rds"))
+harris_linear_model <- readRDS(here::here("models", "Kamala Harris_linear_model.rds"))
+
+# Load test data for Trump and Harris from Parquet files
+trump_test <- read_parquet(here::here("data/02-analysis_data", "Donald Trump_test.parquet"))
+harris_test <- read_parquet(here::here("data/02-analysis_data", "Kamala Harris_test.parquet"))
+
+# Convert 'hypothetical' column to logical if it's not already logical
+convert_to_logical <- function(df) {
+  if ("hypothetical" %in% names(df) && !is.logical(df$hypothetical)) {
+    df$hypothetical <- as.logical(df$hypothetical)
+  }
+  return(df)
+}
+
+# Make predictions using the linear models
+trump_test$Predicted_Support <- predict(trump_linear_model, newdata = trump_test)
+harris_test$Predicted_Support <- predict(harris_linear_model, newdata = harris_test)
+
+# Combine predictions into a single dataframe for plotting
+predictions_df <- data.frame(
+  Candidate = c("Donald Trump", "Kamala Harris"),
+  Predicted_Support = c(mean(trump_test$Predicted_Support), mean(harris_test$Predicted_Support))
+)
+
+# Create a pie chart for predicted support
+pie_chart <- ggplot(predictions_df, aes(x = "", y = Predicted_Support, fill = Candidate)) +
+  geom_bar(stat = "identity", width = 1, color = "white") +
+  coord_polar("y", start = 0) +
+  geom_text(aes(label = paste0(round(Predicted_Support, 1), "%")), 
+            position = position_stack(vjust = 0.5), size = 5) +
+  labs(title = "Average Predicted Support for Trump and Harris (Linear Model)") +
+  theme_void() +
+  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon"))
+
+# Print the pie chart
+print(pie_chart)
+
+# Prepare data for scatter plot of actual vs. predicted values
+combined_test_data <- bind_rows(
+  trump_test %>% select(Actual_Support = pct, Predicted_Support) %>% mutate(Candidate = "Donald Trump"),
+  harris_test %>% select(Actual_Support = pct, Predicted_Support) %>% mutate(Candidate = "Kamala Harris")
+)
+
+# Create a scatter plot for actual vs. predicted support
+scatter_plot <- ggplot(combined_test_data, aes(x = Actual_Support, y = Predicted_Support, color = Candidate)) +
+  geom_point(alpha = 0.6) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "black") + # Reference line
+  labs(title = "Actual vs. Predicted Support (Linear Model)",
+       x = "Actual Support (%)",
+       y = "Predicted Support (%)") +
+  theme_minimal() +
+  scale_color_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon"))
+
+# Print the scatter plot
+print(scatter_plot)
+
+```
+## Bayesian Model set-up
+
+Define $y_i$ as the support percentage (pct) for a candidate in the 2024 U.S.
+presidential election polls.
+This Bayesian model incorporates several predictors: $α_i$ (poll reliability score), $β_i$ (numeric grade indicating poll quality), $γ_i$ (transparency score of poll methodology), $δ_i$ (poll duration), $θ_i$ (sample size), $κ_i$ (type of population surveyed), $λ_i$ (whether the poll is hypothetical), and $μ_i$ (poll methodology type).
+
+```{=tex}
+\begin{align} 
+y_i | \mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
+\mu_i &= \alpha + \beta_1 \times \phi_i + \beta_2 \times \beta_i + \beta_3 \times \gamma_i + \beta_4 \times \delta_i \\
+      &\quad + \beta_5 \times \theta_i + \beta_6 \times \kappa_i + \beta_7 \times \lambda_i + \beta_8 \times \mu_i \\
+\alpha &\sim \mbox{Normal}(0, 10) \\
+\beta_j &\sim \mbox{Normal}(0, 2.5) \quad \text{for each } j = 1, \dots, 8 \\
+\sigma &\sim \mbox{Exponential}(1)
+\end{align}
+
+```
+
+We implemented this Bayesian model in R [@citeR] using the rstanarm package [@rstanarm], specifying weakly informative priors for regression coefficients to encapsulate reasonable uncertainty around the model parameters.
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+This Bayesian model is designed to estimate candidate support percentages in the 2024 U.S.
+presidential election by integrating various poll characteristics and methodological factors.
+The predictors, denoted by $\phi_i$, $\beta_i$, $\gamma_i$, $\delta_i$, $\theta_i$, $\kappa_i$, $\lambda_i$, and $\mu_i$, capture multiple dimensions of polling data that could impact candidate support levels.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+The variable $\phi_i$ represents the poll reliability score, where higher scores suggest greater stability in support estimates.
+The predictors $\beta_i$ and $\gamma_i$ correspond to numeric grade and transparency score, which are both indicative of poll quality, likely contributing to more dependable support assessments.
+Additionally, poll duration ($\delta_i$) and sample size ($\theta_i$) reflect the
+scope and breadth of each poll, offering insights into the representativeness and consistency of the data.
+The variables $\kappa_i$, $\lambda_i$, and $\mu_i$ control for factors such as the population type surveyed, whether the poll is hypothetical, and the methodological specifics, allowing the model to account for differences across polling organizations.
 
-# Results
+By employing normal priors centered at zero for the regression coefficients, this Bayesian approach balances complexity and interpretability, enabling a nuanced understanding of each predictor’s contribution to candidate support variation.
+Weakly informative priors on coefficients prevent overfitting, supporting the model's generalizability across diverse polling scenarios while remaining sensitive to unique data patterns.
+This setup allows us to capture meaningful trends in candidate support and adjust for methodological variability among polls, providing robust insights for election forecasting."
 
-Our results are summarized in @tbl-modelresults.
+### Results
 
-```{r}
+Our results are summarized in:
 
-```
-
-```{r}
-```
+#######代码有问题暂时run不出来
 

### 2024-10-31 scripts/00-simulate_data.R
Delete scripts directory

@@ -1,179 +1,0 @@
-#### Preamble ####
-# Purpose: Simulates a dataset of US president rolls
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-# Any other information needed? None
-
-#### Setup ####
-# Load required libraries
-library(tidyverse)
-
-# Set a random seed for reproducibility
-set.seed(123)
-  
-## Generate simulated data for candidate_1
-simulated_candidate_1 <- tibble(
-  poll_id = 1:500, 
-  # Generate numeric_grade based on a normal distribution with mean 2 and standard deviation 1.2,
-  # then ensure the values are within the range [0, 3] and round to two decimal places, then map to a range of 0 to 10
-  numeric_grade = round((pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3) / 3) * 10, 2),
-  # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
-  # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
-  pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = 0.3), -1), 1) + 1) * 5, 1),
-  # The methodology is divided into four levels: level 1 represents the least reliable type of methodology, while level 4 represents the most reliable.
-  methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
-  # Generate transparency_score based on a normal distribution with mean 6 and standard deviation 1.5,
-  # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
-  transparency_score = round((pmin(pmax(rnorm(500, mean = 6, sd = 1.5), 1), 10) / 10) * 10, 1),
-  # The duration of this poll in days. Duration based on a normal distribution with mean 183 and standard deviation 100,
-  duration = round(pmin(pmax(rnorm(500, mean = 183, sd = 100), 15), 365)),
-  # Generate sample_size based on a normal distribution with mean 1200 and standard deviation 5000, then round to the nearest integer
-  sample_size = round(pmin(pmax(rnorm(500, mean = 1200, sd = 5000), 100), 200000)),
-  # Population types：Likely Voters，Registered Voters, Voters, Adult
[…]

### 2024-10-31 scripts/01-test_simulated_data.R

@@ -1,99 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the structure and validity of the simulated_data electoral divisions dataset.
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Requires simulated data files generated by 00-simulate_data.R
-# Any other information needed? None
-
-library(tidyverse)
-
-# Function to test individual candidate datasets
-test_simulated_candidate_data <- function(data, candidate_name) {
-  message(paste("Testing data for", candidate_name))
-  
-  # Test if the data was successfully loaded
-  if (exists("data")) {
-    message("Test Passed: The dataset was successfully loaded.")
-  } else {
-    stop("Test Failed: The dataset could not be loaded.")
-  }
-  
-  # Check if the dataset has 500 rows
-  if (nrow(data) == 500) {
-    message("Test Passed: The dataset has 500 rows.")
-  } else {
-    stop("Test Failed: The dataset does not have 500 rows.")
-  }
-  
-  # Check if the dataset has 10 columns
-  if (ncol(data) == 10) {
-    message("Test Passed: The dataset has 10 columns.")
-  } else {
-    stop("Test Failed: The dataset does not have 10 columns.")
-  }
-  
-  # Check value ranges and types for specific columns
-  if (all(data$numeric_grade >= 0 & data$numeric_grade <= 10)) {
-    message("Test Passed: All 'numeric_grade' values are within the range 0-10.")
-  } else {
-    stop("Test Failed: 'numeric_grade' contains values outside the range 0-10.")
-  }
-  
-  if (all(data$pollscore >= 0 & data$pollscore <= 10)) {
-    message("Test Passed: All 'pollscore' values are within the range 0-10.")
-  } else {
-    stop("Test Failed: 'pollscore' contains values outside the range 0-10.")
-  }
-  
-  if (all(data$transparency_score >= 0 & data$transparency_score <= 10)) {
-    message("Test Passed: All 'transparency_score' values are within the range 0-10.")
-  } else {
-    stop("Test Failed: 'transparency_score' contains values outside the range 0-10.")
-  }
-  
-  # Check categorical values for methodology and population
-  if (all(data$methodology %in% c("level1", "level2", "level3", "level4"))) {
-    message("Test Passed: 'methodology' column contains only valid levels.")
-  } else {
[…]

### 2024-10-31 scripts/02-download_data.R

@@ -1,19 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from fivethirtyeight.
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-# Any other information needed? None
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Download data ####
-url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
-the_raw_data <- read.csv(url)
-
-#### Save data ####
-write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
-

### 2024-10-31 scripts/03-clean_data.R

@@ -1,191 +1,0 @@
-#### Preamble ####
-# Purpose: Cleans the raw US president polls data by selecting columns and scaling values.
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-# Any other information needed? None
-
-#### Workspace setup ####
-library(tidyverse)
-library(dplyr)
-library(janitor)  # For clean_names
-library(tidyr)   # For drop_na
-
-clean_data <- function(input_file, output_dir) {
-  # Ensure output directory exists
-  if (!dir.exists(output_dir)) {
-    dir.create(output_dir, recursive = TRUE)
-  }
-  
-  # Load data
-  president_polls <- read.csv(input_file)
-  
-  # Clean column names
-  president_polls <- janitor::clean_names(president_polls)
-  
-  # Custom function to handle two date formats
-  parse_dates <- function(date_col) {
-    date_col <- ifelse(grepl("^\\d{4}/\\d{1,2}/\\d{1,2}$", date_col),
-                       as.Date(date_col, format = "%Y/%m/%d"),  # YYYY/MM/DD format
-                       as.Date(date_col, format = "%m/%d/%y"))  # MM/DD/YY format
-    return(date_col)
-  }
-  
-  # Convert start_date and end_date columns
-  president_polls$start_date <- parse_dates(president_polls$start_date)
-  president_polls$end_date <- parse_dates(president_polls$end_date)
-  
-  # Calculate the duration column
-  president_polls$duration <- as.numeric(president_polls$end_date - president_polls$start_date)
-  
-  # Replace blank values in the internal column with "true"
-  president_polls$internal[president_polls$internal == ""] <- "true"
-  
-  # Replace NA values in pollscore and numeric_grade with 0
-  president_polls$pollscore[is.na(president_polls$pollscore)] <- 0
-  president_polls$numeric_grade[is.na(president_polls$numeric_grade)] <- 0
-  president_polls$transparency_score[is.na(president_polls$transparency_score)] <- 1
-  
-  # Scale numeric_grade (0-3) to 0-10
-  president_polls$numeric_grade <- round(president_polls$numeric_grade * (10 / 3), 1)
-  
-  # Scale pollscore (-1.5 to 1.7) to 0-10
[…]

### 2024-10-31 scripts/04-test_analysis_data.R

@@ -1,67 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the structure and contents of the analysis datasets for each candidate
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 02-analysis_data saved and loaded
-# Any other information needed? None
-
-# Load necessary libraries
-library(tidyverse)
-library(testthat)
-library(arrow)  # For reading Parquet files
-library(here)
-
-# Define directory path for analysis data files
-analysis_data_dir <- here("data/02-analysis_data")
-
-# Get a list of all Parquet files in the directory
-candidate_files <- list.files(analysis_data_dir, pattern = "\\.parquet$", full.names = TRUE)
-
-# Define expected columns and data types (allowing both integer and double for numeric columns)
-expected_columns <- c("poll_id", "numeric_grade", "pollscore", "Methodology", 
-                      "transparency_score", "duration", "sample_size", 
-                      "population", "hypothetical", "pct")
-expected_types <- list(
-  poll_id = c("double", "integer"),
-  numeric_grade = c("double", "integer"),
-  pollscore = c("double", "integer"),
-  Methodology = "character",
-  transparency_score = c("double", "integer"),
-  duration = c("double", "integer"),
-  sample_size = c("double", "integer"),
-  population = "character",
-  hypothetical = c("logical", "character"),
-  pct = c("double", "integer")
-)
-
-# Function to test each candidate's data
-test_candidate_data <- function(file_path) {
-  data <- read_parquet(file_path)
-  candidate_name <- tools::file_path_sans_ext(basename(file_path))
-  
-  test_that(paste("Dataset for", candidate_name, "has correct columns"), {
-    expect_equal(sort(names(data)), sort(expected_columns))
-  })
-  
-  test_that(paste("Dataset for", candidate_name, "has correct data types"), {
-    for (col_name in names(expected_types)) {
-      # Check if the column type is among the accepted types
-      actual_type <- typeof(data[[col_name]])
-      expect_true(actual_type %in% expected_types[[col_name]], 
-                  info = paste("Expected", col_name, "to be one of", toString(expected_types[[col_name]]), 
-                               "but got", actual_type))
-    }
-  })
-  
[…]

### 2024-10-31 scripts/06-model_data.R

@@ -1,166 +1,0 @@
-#### Preamble ####
-# Purpose: Illustrate and save model data
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 02-analysis_data saved and loaded
-# Any other information needed? None
-
-# Load necessary libraries
-library(tidyverse)
-library(rstanarm)  # For Bayesian modeling
-library(arrow)     # For reading/writing Parquet files
-library(here)
-
-# Define paths to each candidate's analysis data (training and testing data)
-candidate_train_files <- list(
-  "Donald Trump" = here::here("data/02-analysis_data/Donald Trump_train.parquet"),
-  "Kamala Harris" = here::here("data/02-analysis_data/Kamala Harris_train.parquet"),
-  "Joe Biden" = here::here("data/02-analysis_data/Joe Biden_train.parquet")
-)
-
-candidate_test_files <- list(
-  "Donald Trump" = here::here("data/02-analysis_data/Donald Trump_test.parquet"),
-  "Kamala Harris" = here::here("data/02-analysis_data/Kamala Harris_test.parquet"),
-  "Joe Biden" = here::here("data/02-analysis_data/Joe Biden_test.parquet")
-)
-
-# Ensure a 'models' folder exists for saving model files
-if (!dir.exists("models")) {
-  dir.create("models")
-}
-
-# Function to create and save a linear model for a candidate, excluding constant and single-level variables
-create_and_save_linear_model <- function(data, candidate_name) {
-  # Identify constant variables
-  constant_vars <- names(data)[sapply(data, function(x) length(unique(x)) == 1)]
-  
-  # Identify and remove single-level categorical variables
-  categorical_vars <- names(data)[sapply(data, is.factor)]
-  single_level_categorical_vars <- categorical_vars[sapply(data[categorical_vars], function(x) length(unique(x)) < 2) %>% as.logical()]
-  
-  # Remove single-level categorical variables and constant variables from the data
-  data <- data %>% select(-all_of(single_level_categorical_vars), -all_of(constant_vars))
-  
-  # Define the formula, excluding these variables
-  formula <- as.formula(
-    paste("pct ~", paste(setdiff(names(data), c("pct", "poll_id")), collapse = " + "))
-  )
-  
-  # Fit the linear model
[…]

### 2024-10-31 scripts/07-replications.R

@@ -1,38 +1,0 @@
-#### Preamble ####
-# Purpose: Complete replication of the data analysis pipeline
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Requires all provided scripts and necessary data files
-# Any other information needed? None
-
-library(tidyverse)
-
-# 1. Simulate Data
-source("scripts/00-simulate_data.R")
-message("Data simulation complete.")
-
-# 2. Download Data
-source("scripts/02-download_data.R")
-message("Data download complete.")
-
-# 3. Clean Data
-source("scripts/03-clean_data.R")
-message("Data cleaning complete.")
-
-# 4. Test Simulated Data
-source("scripts/01-test_simulated_data.R")
-message("Simulated data testing complete.")
-
-# 5. Test Analysis Data
-source("scripts/04-test_analysis_data.R")
-message("Analysis data testing complete.")
-
-# 6. Model Data
-source("scripts/06-model_data.R")
-message("Modeling data complete.")
-
-
-
-

### 2024-10-31 scripts/00-simulate_data.R
All files re-formatted, datafile renamed
All files re-formatted, datafile renamed, model changed

@@ -1,0 +1,179 @@
+#### Preamble ####
+# Purpose: Simulates a dataset of US president rolls
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+#### Setup ####
+# Load required libraries
+library(tidyverse)
+
+# Set a random seed for reproducibility
+set.seed(123)
+  
+## Generate simulated data for candidate_1
+simulated_candidate_1 <- tibble(
+  poll_id = 1:500, 
+  # Generate numeric_grade based on a normal distribution with mean 2 and standard deviation 1.2,
+  # then ensure the values are within the range [0, 3] and round to two decimal places, then map to a range of 0 to 10
+  numeric_grade = round((pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3) / 3) * 10, 2),
+  # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
+  # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
+  pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = 0.3), -1), 1) + 1) * 5, 1),
+  # The methodology is divided into four levels: level 1 represents the least reliable type of methodology, while level 4 represents the most reliable.
+  methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
+  # Generate transparency_score based on a normal distribution with mean 6 and standard deviation 1.5,
+  # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
+  transparency_score = round((pmin(pmax(rnorm(500, mean = 6, sd = 1.5), 1), 10) / 10) * 10, 1),
+  # The duration of this poll in days. Duration based on a normal distribution with mean 183 and standard deviation 100,
+  duration = round(pmin(pmax(rnorm(500, mean = 183, sd = 100), 15), 365)),
+  # Generate sample_size based on a normal distribution with mean 1200 and standard deviation 5000, then round to the nearest integer
+  sample_size = round(pmin(pmax(rnorm(500, mean = 1200, sd = 5000), 100), 200000)),
+  # Population types：Likely Voters，Registered Voters, Voters, Adult
[…]

### 2024-10-31 scripts/02-download_data.R

@@ -1,0 +1,20 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from fivethirtyeight.
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Download data ####
+url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
+the_raw_data <- read.csv(url)
+
+#### Save data ####
+write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
+
+

### 2024-10-31 scripts/03-clean_data.R

@@ -1,0 +1,123 @@
+#### Preamble ####
+# Purpose: Cleans the raw US president polls data by selecting columns and scaling values.
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+library(janitor)  # For clean_names
+library(tidyr)   # For drop_na
+library(lubridate)
+library(arrow)
+
+
+
+set.seed(123)  # Set seed for reproducibility
+raw_data <- read_csv("data/01-raw_data/raw_data.csv")
+# Step 1: Remove variables (columns) with all NA values
+raw_data_cleaned <- raw_data %>%
+  select_if(~!all(is.na(.)))
+
+# Step 2: Remove variables with more than 40% NA values
+threshold <- 0.4 * nrow(raw_data_cleaned)
+raw_data_cleaned <- raw_data_cleaned %>%
+  select_if(~sum(is.na(.)) <= threshold)
+
+# Step 3: Remove variables with all identical values
+raw_data_cleaned <- raw_data_cleaned %>%
+  select_if(~is.numeric(.) || n_distinct(.) > 1)
+
+# Step 4: Remove duplicated, unrelated variables
+raw_data_cleaned <- raw_data_cleaned %>%
+  select(-any_of(c("pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name", 
+                   "question_id", "population_full", "created_at", "url", "url_article", "race_id", 
+                   "candidate_id", "candidate_name", "party", "seat_number", "cycle")))
+
+# Step 5: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
+raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date)-mdy(raw_data_cleaned$start_date))
+raw_data_cleaned <- raw_data_cleaned %>%
+  select(-start_date, -end_date)
+
+# Step 6: Group methodology by level
+raw_data_cleaned$methodology <- case_when(
+  raw_data_cleaned$methodology %in% c(
[…]

### 2024-10-31 scripts/04-test_analysis_data.R

@@ -1,0 +1,130 @@
+#### Preamble ####
+# Purpose: Tests... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 26 September 2024 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+<<<<<<< HEAD
+
+#### Workspace setup ####
+=======
+# Load necessary libraries
+>>>>>>> 15d932b68ef20c88ef288ebba19468b185b47d9c
+library(tidyverse)
+library(testthat)
+library(arrow)  # For reading Parquet files
+library(here)
+
+<<<<<<< HEAD
+data <- read_csv("data/02-analysis_data/analysis_data.csv")
+
+
+#### Test data ####
+# Test that the dataset has 151 rows - there are 151 divisions in Australia
+test_that("dataset has 151 rows", {
+  expect_equal(nrow(analysis_data), 151)
+})
+
+# Test that the dataset has 3 columns
+test_that("dataset has 3 columns", {
+  expect_equal(ncol(analysis_data), 3)
+})
+
+# Test that the 'division' column is character type
+test_that("'division' is character", {
+  expect_type(analysis_data$division, "character")
+})
+
+# Test that the 'party' column is character type
+test_that("'party' is character", {
+  expect_type(analysis_data$party, "character")
+})
+
+# Test that the 'state' column is character type
+test_that("'state' is character", {
+  expect_type(analysis_data$state, "character")
+})
+
+# Test that there are no missing values in the dataset
+test_that("no missing values in dataset", {
+  expect_true(all(!is.na(analysis_data)))
+})
+
+# Test that 'division' contains unique values (no duplicates)
+test_that("'division' column contains unique values", {
+  expect_equal(length(unique(analysis_data$division)), 151)
+})
+
+# Test that 'state' contains only valid Australian state or territory names
+valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", "Western Australia", 
+                  "Tasmania", "Northern Territory", "Australian Capital Territory")
+test_that("'state' contains valid Australian state names", {
+  expect_true(all(analysis_data$state %in% valid_states))
+})
+
+# Test that there are no empty strings in 'division', 'party', or 'state' columns
+test_that("no empty strings in 'division', 'party', or 'state' columns", {
[…]

### 2024-10-31 scripts/06-model_data.R

@@ -1,0 +1,21 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+# Define paths to each candidate's analysis data (training and testing data)
+candidate_data_files <- list(
+  "Donald Trump" = "data/02-analysis_data/01-trianing/train_Trump.parquet",
+  "Kamala Harris" = "data/02-analysis_data/01-trianing/train_Harris.parquet",
+  "Ron DeSantis" = "data/02-analysis_data/01-trianing/train_DeSantis.parquet"
+)
+
+########################xiamian

### 2024-10-31 scripts/07-replications.R

@@ -1,0 +1,38 @@
+#### Preamble ####
+# Purpose: Complete replication of the data analysis pipeline
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Requires all provided scripts and necessary data files
+# Any other information needed? None
+
+library(tidyverse)
+
+# 1. Simulate Data
+source("scripts/00-simulate_data.R")
+message("Data simulation complete.")
+
+# 2. Download Data
+source("scripts/02-download_data.R")
+message("Data download complete.")
+
+# 3. Clean Data
+source("scripts/03-clean_data.R")
+message("Data cleaning complete.")
+
+# 4. Test Simulated Data
+source("scripts/01-test_simulated_data.R")
+message("Simulated data testing complete.")
+
+# 5. Test Analysis Data
+source("scripts/04-test_analysis_data.R")
+message("Analysis data testing complete.")
+
+# 6. Model Data
+source("scripts/06-model_data.R")
+message("Modeling data complete.")
+
+
+
+

### 2024-10-31 paper/paper.qmd
Project name fixed, model changed
Project name fixed, model changed

--- 2024-10-30 paper/paper.qmd
@@
 ---
-title: "The 2024 U.S. Presidential Election Forecast"
-subtitle: "Multiple Linear Regression and Bayesian Models Accounting for Poll Quality"
-author: Haowei Fan, Fangning Zhang, Shaotong Li
-thanks: "Code and data are available at: https://github.com/HaoweiFan0912/The-2024-U.S.-Presidential-Election-Forecast"
-date: 13/10/2024
-contact: haowei.fan@mail.utoronto.ca
-licence: MIT
+title: "My title"
+subtitle: "My subtitle if needed"
+author: 
+  - First author
+  - Another author
+thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+date: today
 date-format: long
-abstract: "This study presents a forecast for the 2024 U.S.
-presidential election using aggregated poll data to predict support for key candidates.
-By implementing both linear and Bayesian models, we analyze poll data from diverse sources to assess how factors related to poll quality influence candidate support predictions.
-Our findings reveal possible outcome of election.
-Additionally, this paper includes an idealized polling methodology to demonstrate best practices in survey design and sample representation."
+abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 format: pdf
@@
 bibliography: references.bib
-toc: true
-toc-title: "Table of Contents"
-toc-depth: 2
-toc-location: left
 ---
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-library(tidyverse)
-library(knitr)
-library(dplyr)
-library(ggplot2)
-library(patchwork)
-raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
-```
-
-# Introduction
-
-The U.S.
-presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights.
-As the world anticipates the 2024 U.S.
-electoral contest, predicting the election’s possible outcomes can provide critical insights for policymakers, businesses, and civil society groups.
-This study aims to forecast the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.
-
-To provide a robust prediction, we utilize a “poll-of-polls” approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support.
-Our analysis applies both a linear regression model and a Bayesian approach, with a focus on the key parameter of each candidate's predicted vote share.
-By considering variations in pollster methodology and geographic distinctions, we account for the nuances of state-level political landscapes and the potential influence of polling organizations.
-
-The results of our models reveal consistent patterns in voter support across both Harris and Trump.
-The linear model estimates a stable support rate for Donald Trump at approximately 47.8%, with similar results for Harris at 46.7%.
-The Bayesian model, which incorporates pollster and state-level random effects, yields slightly more conservative support estimates, predicting 47.9% for Trump and 46.0% for Harris.
-These findings suggest that, while both candidates maintain stable support, Trump holds a slight advantage.
-The consistency across both models underlines the importance of accounting for variability across polling methodologies and regional voter bases.
-
-Beyond the immediate electoral forecast, this study contributes valuable insights for understanding how polling predictions can inform societal and international expectations.
-Predicting election outcomes allows global stakeholders—such as policymakers, investors, and international organizations—to anticipate and adapt to potential shifts in U.S.
-policy.
-For instance, a leadership change could bring alterations in U.S.
-positions on trade, climate commitments, and foreign policy, influencing global economic stability and strategic alliances.
-Additionally, our findings underscore the importance of transparency in polling methodologies, as well as the potential for more nuanced and accurate forecasts that consider the heterogeneity in polling sources and voter demographics.
-
-This paper is organized as follows.
-The next section outlines the data collection and filtering processes, detailing the key variables and sources.
-Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models.
-In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings.
-Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
-
-# Data {#sec-data}
-
-## Overview
-
-This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S.
-presidential election forecast.
-The raw polling data was sourced from FiveThirtyEight's 2024 presidential election polls[@fivethirtyeight2024], providing a comprehensive foundation for our analysis.
-Together, these packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.
-
-## Raw data
-raw data一共有52个variables，以及15891条样本。
-去掉重复variables，以及无关紧要的url,还有全空的varibales后还剩下以下variables以及description。
-部分重要的在此显示，不重要的在appendix。
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-main_columns
-#| tbl-cap: "Main column descriptions of the raw data"
-
-# Define the selected variable names
-selected_variables <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "numeric_grade", "pollscore", "methodology", "transparency_score", "state", "start_date", "end_date", "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "sample_size", "population", "tracking", "created_at", "notes", "source", "internal", "partisan", "race_id", "cycle", "office_type", "election_date", "stage", "nationwide_batch", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical", "party", "answer", "pct")
-
-# Define their descriptions
-variable_descriptions <- c(
-  "Unique identifier for each poll conducted.",
-  "Unique identifier for the polling organization conducting the poll.",
-  "Unique identifier(s) for the sponsor(s) of the poll, typically organizations that fund the poll.",
-  "Unique identifier for the pollster's rating within a rating system.",
-  "A numeric rating given to the pollster to indicate their quality or reliability .",
-  "A numeric value representing the score or reliability of the pollster in question .",
-  "The method used to conduct the poll .",
-  "A score reflecting the pollster's transparency about their methodology .",
-  "The U.S. state where the poll was conducted or focused, if applicable.",
-  "The date the poll began .",
-  "The date the poll ended .",
-  "Unique identifier for the candidate sponsored by the sponsoring organization (if applicable).",
-  "The political party of the candidate sponsored by the sponsor (if applicable).",
-  "Unique identifier for the question asked in the poll.",
-  "The total number of respondents participating in the poll .",
-  "The abbreviated description of the respondent group, typically indicating their voting status .",
-  "Indicates whether the poll is part of a tracking series .",
-  "The timestamp when the poll data was created or entered into the system .",
-  "Any additional notes or comments related to the poll.",
-  "The source from where the poll data was derived.",
-  "Indicates whether the poll is conducted internally by a campaign or organization.",
-  "Indicates whether the poll has partisan sponsorship or is conducted by a partisan organization.",
-  "A unique identifier for the political race being polled .",
-  "The election cycle in which the poll is conducted .",
-  "The type of political office being polled .",
-  "The date of the election the poll is related to .",
-  "The stage of the election being polled .",
-  "Indicates whether the poll is part of a nationwide batch.",
-  "Indicates if ranked-choice voting reallocations have been applied in the results.",
-  "The round of ranked-choice voting, if applicable.",
-  "Indicates whether the poll is about a hypothetical match-up.",
-  "The political party of the candidate in the poll .",
-  "The response or answer choice given in the poll .",
-  "The percentage of the vote or support that the candidate received in the poll ."
-)
-
-# Create a tibble with variable names and descriptions
-variable_tibble <- tibble(
-  Variable = selected_variables,
-  Description = variable_descriptions
-)
-
-# Define the variables to extract for the table of selected variables
-variables_to_extract <- c("poll_id", "pollscore", "numeric_grade", "transparency_score", "start_date", "end_date", "sample_size", "population", "hypothetical", "methodology", "pct")
-
-# Extract the relevant rows from the tibble
-extracted_tibble <- variable_tibble %>% filter(Variable %in% variables_to_extract)
-
-# Create the table using kable for selected variables
-kable(extracted_tibble)
-```
-所有variable的na值
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-variable_na
-#| tbl-cap: "Number of Missing Values and Percentages for Variables"
-# Calculate the number of missing values for each selected variable
-na_counts <- sapply(raw_data[ , selected_variables], function(x) sum(is.na(x)))
-
-# Calculate the percentage of missing values for each selected variable
-na_percentages <- sapply(raw_data[ , selected_variables], function(x) mean(is.na(x)) * 100)
-
-# Create a tibble for missing value counts and percentages
-na_tibble <- tibble(
-  Variable = names(na_counts),
-  Missing_Values = na_counts,
-  Percentage_Missing = round(na_percentages,2)
-)
-
-# Split the tibble into two halves for side-by-side display
-na_tibble_1 <- na_tibble[1:ceiling(nrow(na_tibble)/2), ]
-na_tibble_2 <- na_tibble[(ceiling(nrow(na_tibble)/2) + 1):nrow(na_tibble), ]
-
-# Create the table using kable for missing values
-kable(na_tibble)
-```
-重要的numerical variable的分布：
-```{r, fig.pos="H", fig.width=22, fig.height=18}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-numdis
-#| fig-cap: "Distribution of numerical varibales"
-### Define Variables and Prepare Data ###
-# Define the numeric variables to plot
-numeric_variables <- c("pollscore", "numeric_grade", "transparency_score", "sample_size", "pct")
-
-# Convert start_date and end_date to Date type
-raw_data$start_date <- ymd(raw_data$start_date)
-raw_data$end_date <- ymd(raw_data$end_date)
-
-# Define the date variables to plot
-date_variables <- c("start_date", "end_date")
-
-### Create Plots for Numeric Variables ###
-# Create a list to store plots
-plots <- list()
-
-# Loop through selected numeric variables and plot their distributions
-for (variable in numeric_variables) {
-  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
-    geom_histogram(binwidth = 0.7, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 30) +
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
-    )
-}
-
-### Create Plots for Date Variables ###
-# Loop through selected date variables and plot their distributions
-for (variable in date_variables) {
-  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
-    geom_histogram(binwidth = 30, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 30) +
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
-    )
-}
-
-### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 3, heights = unit(rep(3, 4), "in")) +
-  plot_annotation(
-    theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
-
-# Print the combined plot
-print(combined_plot)
-
-```
-接下来是categorical
-```{r, fig.pos="H", fig.width=22, fig.height=8}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-catdis
-#| fig-cap: "Distribution of categorical varibales"
-
-### Plot distributions for categorical variables ###
-# Define the categorical variables to plot
-categorical_variables <- setdiff(variables_to_extract, c(numeric_variables, "start_date", "end_date"))
-categorical_variables <- categorical_variables[categorical_variables != "methodology" ]
-categorical_variables <- categorical_variables[categorical_variables != "poll_id" ]
-# Create a list to store plots for categorical variables
-categorical_plots <- list()
-
-# Loop through categorical variables and plot their distributions
-for (variable in categorical_variables) {
-  plot <- ggplot(raw_data, aes_string(x = variable)) +
-    geom_bar(fill = "#69b3a2", color = "black") +
-    labs(title = paste(variable), x = variable, y = "Count") +
-    theme_minimal() +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  # Add plot to list
-  categorical_plots[[variable]] <- plot
-}
-
-### Plot top 5 methodologies ###
-# Extract top 5 methodologies by frequency
-top_5_methodologies <- raw_data %>%
-  count(methodology, sort = TRUE) %>%
-  top_n(5) %>%
-  pull(methodology)
-
-# Create a new column to categorize methodologies into top 5 and 'Other'
-raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_5_methodologies, raw_data$methodology, 'Other')
-
-# Plot the distribution of the top 5 methodologies plus 'Other'
-methodology_plot <- ggplot(raw_data, aes(x = methodology_grouped)) +
-  geom_bar(fill = "#69b3a2", color = "black") +
-  labs(title = "Top 5 Methodologies and Others", x = "Methodology", y = "Count") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-# Add methodology plot to categorical plots list
-categorical_plots[["methodology_grouped"]] <- methodology_plot
-
-# Combine all individual plots for categorical variables into one using patchwork
-combined_categorical_plot <- wrap_plots(categorical_plots) +
-  plot_annotation(title = "Distributions of Categorical Variables")
-
-# Print the combined plot for categorical variables
-print(combined_categorical_plot)
-
-### Create a list for non-numeric variables ###
-non_numeric_variables <- setdiff(variables_to_extract, numeric_variables)
-
-```
-#######注意，appendix其他的图还没画
-
-## Measurement
-
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
-
-## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-
-```
-
-Talk way more about it.
-
-## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-
-```
-
-```{r}
-```
-
-# Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-raw data 部分没有解释的varibale
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-remain_columns
-#| tbl-cap: "Remaining column descriptions of the raw data"
-
-# Define the variables to extract for the remaining variables
-remaining_variables <- setdiff(selected_variables, variables_to_extract)
-
-# Extract the relevant rows from the tibble for remaining variables
-remaining_tibble <- variable_tibble %>% filter(Variable %in% remaining_variables)
-
-# Create the table using kable for remaining variables
-kable(remaining_tibble, caption = "Descriptions of Remaining Variables")
-```
-raw data里没画的图
-```{r}
-#to be done
-```
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-
-```
-
-\newpage
-
-# References

### 2024-10-31 scripts/00-simulate_data.R

@@ -34,6 +34,8 @@ simulated_candidate_1 <- tibble(
   sample_size = round(pmin(pmax(rnorm(500, mean = 1200, sd = 5000), 100), 200000)),
   # Population types：Likely Voters，Registered Voters, Voters, Adult
   population = sample(c("a", "v", "lv", "rv"), 500, replace = TRUE),
+  # Set TRUE/FALSE ratio to 0.9 for the hypothetical column
+  ranked_choice_reallocated= sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.9, 0.1)),
   # Set TRUE/FALSE ratio to 0.3 for the hypothetical column
   hypothetical = sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.3, 0.7)),
   # Use NA as a placeholder for the score.
@@ -52,6 +54,8 @@ simulated_candidate_1$score =
          ifelse((simulated_candidate_1$sample_size >= 3000) & (simulated_candidate_1$sample_size <= 8000), 7, 
                 ifelse(simulated_candidate_1$sample_size < 3000, 3, 0
                        ))) +
+  # When the poll is reallocated, it get 0 in this factor. Otherwise it will get 10.
+  ifelse(simulated_candidate_1$ranked_choice_reallocated, 0, 10) +
   # When the poll is based on hypothtical, it get 0 in this factor. Otherwise it will get 10.
   ifelse(simulated_candidate_1$hypothetical, 0, 10) +
   # Assume likely voter is the best population, voter and registered voter are worse, and adult is the worst.
@@ -87,6 +91,8 @@ simulated_candidate_2 <- tibble(
   sample_size = round(pmin(pmax(rnorm(500, mean = 1200, sd = 5000), 100), 200000)),
   # Population types：Likely Voters，Registered Voters, Voters, Adult
   population = sample(c("a", "v", "lv", "rv"), 500, replace = TRUE),
+  # Set TRUE/FALSE ratio to 0.9 for the hypothetical column
+  ranked_choice_reallocated= sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.9, 0.1)),
   # Set TRUE/FALSE ratio to 0.3 for the hypothetical column
   hypothetical = sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.3, 0.7)),
   # Use NA as a placeholder for the score.
@@ -96,30 +102,31 @@ simulated_candidate_2 <- tibble(
[…]

### 2024-10-31 scripts/01-test_simulated_data.R

@@ -26,64 +26,3 @@ if (exists("analysis_data")) {
 
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 151 rows.")
-}
-
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
-
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
-}
-
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
-
-if (all(analysis_data$state %in% valid_states)) {
-  message("Test Passed: The 'state' column contains only valid Australian state names.")
-} else {
-  stop("Test Failed: The 'state' column contains invalid state names.")
-}
-
-# Check if the 'party' column contains only valid party names
-valid_parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-if (all(analysis_data$party %in% valid_parties)) {
-  message("Test Passed: The 'party' column contains only valid party names.")
-} else {
-  stop("Test Failed: The 'party' column contains invalid party names.")
-}
-
-# Check if there are any missing values in the dataset
-if (all(!is.na(analysis_data))) {
-  message("Test Passed: The dataset contains no missing values.")
-} else {
-  stop("Test Failed: The dataset contains missing values.")
-}
-
-# Check if there are no empty strings in 'division', 'state', and 'party' columns
-if (all(analysis_data$division != "" & analysis_data$state != "" & analysis_data$party != "")) {
-  message("Test Passed: There are no empty strings in 'division', 'state', or 'party'.")
-} else {
-  stop("Test Failed: There are empty strings in one or more columns.")
-}
-
-# Check if the 'party' column has at least two unique values
-if (n_distinct(analysis_data$party) >= 2) {
-  message("Test Passed: The 'party' column contains at least two unique values.")
[…]

### 2024-10-31 scripts/03-clean_data.R

@@ -19,31 +19,28 @@ library(arrow)
 
 set.seed(123)  # Set seed for reproducibility
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
-# Step 1: Remove variables (columns) with all NA values
-raw_data_cleaned <- raw_data %>%
-  select_if(~!all(is.na(.)))
 
-# Step 2: Remove variables with more than 40% NA values
+# Step 1: Remove variables with more than 40% NA values
 threshold <- 0.4 * nrow(raw_data_cleaned)
 raw_data_cleaned <- raw_data_cleaned %>%
   select_if(~sum(is.na(.)) <= threshold)
 
-# Step 3: Remove variables with all identical values
+# Step 2: Remove variables with all identical values
 raw_data_cleaned <- raw_data_cleaned %>%
   select_if(~is.numeric(.) || n_distinct(.) > 1)
 
-# Step 4: Remove duplicated, unrelated variables
+# Step 3: Remove duplicated, unrelated variables
 raw_data_cleaned <- raw_data_cleaned %>%
   select(-any_of(c("pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name", 
                    "question_id", "population_full", "created_at", "url", "url_article", "race_id", 
                    "candidate_id", "candidate_name", "party", "seat_number", "cycle")))
 
-# Step 5: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
+# Step 4: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
 raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date)-mdy(raw_data_cleaned$start_date))
 raw_data_cleaned <- raw_data_cleaned %>%
   select(-start_date, -end_date)
 
-# Step 6: Group methodology by level
+# Step 5: Group methodology by level
 raw_data_cleaned$methodology <- case_when(
   raw_data_cleaned$methodology %in% c(
     "Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", 
@@ -77,15 +74,15 @@ raw_data_cleaned$methodology <- case_when(
     "Mail-to-Web/Mail-to-Phone", "Online Ad"
   ) ~ "level1")
 
-# Step 7: Replace NA values - numerical variables with mean, categorical variables with mode
[…]

### 2024-10-31 scripts/04-test_analysis_data.R

@@ -7,124 +7,18 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
-<<<<<<< HEAD
+
 
 #### Workspace setup ####
-=======
+
 # Load necessary libraries
->>>>>>> 15d932b68ef20c88ef288ebba19468b185b47d9c
 library(tidyverse)
 library(testthat)
 library(arrow)  # For reading Parquet files
 library(here)
 
-<<<<<<< HEAD
 data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
-
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
-
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
-})
-
-# Test that the 'state' column is character type
-test_that("'state' is character", {
-  expect_type(analysis_data$state, "character")
-})
-
-# Test that there are no missing values in the dataset
-test_that("no missing values in dataset", {
-  expect_true(all(!is.na(analysis_data)))
-})
-
-# Test that 'division' contains unique values (no duplicates)
-test_that("'division' column contains unique values", {
-  expect_equal(length(unique(analysis_data$division)), 151)
-})
-
-# Test that 'state' contains only valid Australian state or territory names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", "Western Australia", 
-                  "Tasmania", "Northern Territory", "Australian Capital Territory")
-test_that("'state' contains valid Australian state names", {
-  expect_true(all(analysis_data$state %in% valid_states))
-})
-
-# Test that there are no empty strings in 'division', 'party', or 'state' columns
-test_that("no empty strings in 'division', 'party', or 'state' columns", {
-  expect_false(any(analysis_data$division == "" | analysis_data$party == "" | analysis_data$state == ""))
-})
-
-# Test that the 'party' column contains at least 2 unique values
-test_that("'party' column contains at least 2 unique values", {
-  expect_true(length(unique(analysis_data$party)) >= 2)
[…]

### 2024-10-31 scripts/06-model_data.R

@@ -12,10 +12,25 @@
 library(tidyverse)
 
 # Define paths to each candidate's analysis data (training and testing data)
-candidate_data_files <- list(
-  "Donald Trump" = "data/02-analysis_data/01-trianing/train_Trump.parquet",
-  "Kamala Harris" = "data/02-analysis_data/01-trianing/train_Harris.parquet",
-  "Ron DeSantis" = "data/02-analysis_data/01-trianing/train_DeSantis.parquet"
-)
 
-########################xiamian
+Trump <- read_parquet("data/02-analysis_data/01-training/train_Trump.parquet")
+Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
+DeSantis <- read_parquet("data/02-analysis_data/01-training/train_DeSantis.parquet")
+
+# Function to create and save a linear model for a candidate
+
+Trump_model <- lm(
+  pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + 
+    ranked_choice_reallocated + hypothetical + methodology, data = Trump)
+Harris_model <- lm(
+  pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + 
+    ranked_choice_reallocated + hypothetical + methodology, data = Harris)
+DeSantis_model <- lm(
+  pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + 
+    ranked_choice_reallocated + hypothetical + methodology, data = DeSantis)
+
+# Save the model
+saveRDS(Trump_model, file = "models/Trump_model.rds")
+saveRDS(Harris_model, file = "models/Harris_model.rds")
+saveRDS(DeSantis_model, file = "models/DeSantis_model.rds")
+

### 2024-10-31 scripts/03-clean_data.R
pct renamed as score
pct renamed as score

@@ -21,8 +21,8 @@ set.seed(123)  # Set seed for reproducibility
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
 # Step 1: Remove variables with more than 40% NA values
-threshold <- 0.4 * nrow(raw_data_cleaned)
-raw_data_cleaned <- raw_data_cleaned %>%
+threshold <- 0.4 * nrow(raw_data)
+raw_data_cleaned <- raw_data %>%
   select_if(~sum(is.na(.)) <= threshold)
 
 # Step 2: Remove variables with all identical values
@@ -79,10 +79,13 @@ raw_data_cleaned <- raw_data_cleaned %>%
   mutate(across(where(is.numeric), ~ifelse(is.na(.), round(mean(., na.rm = TRUE), 1), .))) %>%
   mutate(across(where(is.character), ~ifelse(is.na(.), names(which.max(table(.))), .)))
 
-# Step 7: Clean name
+# Step 7: Rename pct
+names(raw_data_cleaned)[names(raw_data_cleaned) == "pct"] <- "score"
+
+# Step 8: Clean name
 raw_data_cleaned <- janitor::clean_names(raw_data_cleaned)
 
-# Step 8: Filter data set by unique answer
+# Step 9: Filter data set by unique answer
 candidates <- unique(raw_data_cleaned$answer)
 for (candidate in candidates) {
   # Filter data for each candidate and remove rows with NA values
@@ -95,7 +98,7 @@ for (candidate in candidates) {
   write_parquet(candidate_data, output_file)
 }
 
-# Step 9: find analysis data
+# Step 10: find analysis data
 # Split the top 3 files into 3:7 ratio and save them
 for (file in c("Trump_cleaned_data.parquet", "Harris_cleaned_data.parquet", "DeSantis_cleaned_data.parquet")) {
   # Read the Parquet file into a data frame

### 2024-11-01 paper/paper.qmd
model updated
model updated

@@
 ---
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+#| echo: false
+#### Workspace setup ####
+library(tidyverse)
+library(knitr)
+library(dplyr)
+library(arrow)
+set.seed(912)
+#### Read data ####
+train_DeeSantis <- read_parquet(here::here("data/02-analysis_data/01-training/train_DeSantis.parquet"))
+train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
+train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
+Trump_model <- readRDS(here::here("models/Trump_model.rds"))
+
+```
+
+# Introduction
+
+# Data {#sec-data}
+
+## Overview
+
+## Raw data
+
+## Cleaned data
+
+## Measurement
+
+## Similar dataset
+
+# Model
+
+## Model set-up
+```{r}
+names(train_Trump)
+```
+
+```{r, fig.width=10, fig.height=10}
+data2 = train_Trump %>% select("numeric_grade","pollscore","transparency_score","sample_size","duration")
+pairs( data2 , main = "Predictor vs predictor")
+```
+
+```{r}
+par(mfrow=c(2,2))
+plot(Trump_model,1)
+plot(Trump_model,2)
+plot(Trump_model,3)
+plot(Trump_model,4)
+```
+
+```{r}
+column_names <- c("transparency_score", "ranked_choice_reallocated","methodology","hypothetical", "population")
+variables_string <- paste(column_names, collapse = " + ")
+formula_string <- paste("score ~", variables_string)
+formula <- as.formula(formula_string)
+m2 <- lm(formula, data = train_Trump)
+summary(m2)
+```
+
+## Predictor variables

### 2024-11-01 scripts/00-simulate_data.R

@@ -10,16 +10,13 @@
 #### Setup ####
 # Load required libraries
 library(tidyverse)
-
+library(arrow)
 # Set a random seed for reproducibility
 set.seed(123)
   
 ## Generate simulated data for candidate_1
 simulated_candidate_1 <- tibble(
   poll_id = 1:500, 
-  # Generate numeric_grade based on a normal distribution with mean 2 and standard deviation 1.2,
-  # then ensure the values are within the range [0, 3] and round to two decimal places, then map to a range of 0 to 10
-  numeric_grade = round((pmin(pmax(rnorm(500, mean = 2, sd = 1.2), 0), 3) / 3) * 10, 2),
   # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
   # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
   pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = 0.3), -1), 1) + 1) * 5, 1),
@@ -46,7 +43,6 @@ simulated_candidate_1 <- tibble(
 simulated_candidate_1$score = 
   round(
   # Assume that numeric_grade, pollscore, and transparency_score are equally important, and their ranges are all from 0 to 10.
-  simulated_candidate_1$numeric_grade + 
   (10 - simulated_candidate_1$pollscore) + # Because pollscore is the less the better
   simulated_candidate_1$transparency_score + 
   # When sample size > 800, the score + 10. When 300 <= sample size <= 800, the score +7. Other wise score +3

### 2024-11-01 scripts/03-clean_data.R

@@ -15,8 +15,6 @@ library(tidyr)   # For drop_na
 library(lubridate)
 library(arrow)
 
-
-
 set.seed(123)  # Set seed for reproducibility
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
@@ -31,14 +29,14 @@ raw_data_cleaned <- raw_data_cleaned %>%
 
 # Step 3: Remove duplicated, unrelated variables
 raw_data_cleaned <- raw_data_cleaned %>%
-  select(-any_of(c("pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name", 
-                   "question_id", "population_full", "created_at", "url", "url_article", "race_id", 
-                   "candidate_id", "candidate_name", "party", "seat_number", "cycle")))
-
+  dplyr::select(-any_of(c("pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name", 
+                          "question_id", "population_full", "created_at", "url", "url_article", "race_id", 
+                          "candidate_id", "candidate_name", "party", "seat_number", "cycle"))) 
+  
 # Step 4: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
 raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date)-mdy(raw_data_cleaned$start_date))
 raw_data_cleaned <- raw_data_cleaned %>%
-  select(-start_date, -end_date)
+  dplyr::select(-start_date, -end_date)
 
 # Step 5: Group methodology by level
 raw_data_cleaned$methodology <- case_when(
@@ -91,7 +89,8 @@ for (candidate in candidates) {
   # Filter data for each candidate and remove rows with NA values
   candidate_data <- raw_data_cleaned %>%
     filter(answer == candidate) %>% 
-    select(-answer)
+    dplyr::select(-answer)%>% 
+    dplyr::select(-poll_id)
   # Define output file path for each candidate
   output_file <- file.path("data/03-cleaned_data", paste0(candidate, "_cleaned_data.parquet"))
   # Save each candidate's cleaned data to a separate Parquet file

### 2024-11-01 scripts/06-model_data.R

@@ -20,13 +20,13 @@ DeSantis <- read_parquet("data/02-analysis_data/01-training/train_DeSantis.parqu
 # Function to create and save a linear model for a candidate
 
 Trump_model <- lm(
-  pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + 
+  score ~ pollscore + transparency_score + duration + sample_size + population + 
     ranked_choice_reallocated + hypothetical + methodology, data = Trump)
 Harris_model <- lm(
-  pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + 
+  score ~ pollscore + transparency_score + duration + sample_size + population + 
     ranked_choice_reallocated + hypothetical + methodology, data = Harris)
 DeSantis_model <- lm(
-  pct ~ pollscore + numeric_grade + transparency_score + duration + sample_size + population + 
+  score ~ pollscore + transparency_score + duration + sample_size + population + 
     ranked_choice_reallocated + hypothetical + methodology, data = DeSantis)
 
 # Save the model

### 2024-11-01 paper/paper.qmd
paper updated
paper updated

--- 2024-10-31 paper/paper.qmd
@@
 ---
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+#| echo: false
+#### Workspace setup ####
+library(tidyverse)
+library(knitr)
+library(dplyr)
+library(arrow)
+set.seed(912)
+#### Read data ####
+raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
+train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
+train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
+Trump_model <- readRDS(here::here("models/Trump_model.rds"))
+Harris_model <- readRDS(here::here("models/Harris_model.rds"))
+```
+
+# Introduction
+
+# Data {#sec-data}
+
+## Overview
+
+## Raw data
+```{r}
+# Identify variables (columns) that are completely empty (all NA values)
+empty_variables <- names(raw_data)[sapply(raw_data, function(x) all(is.na(x)))]
+
+# Print the names of empty variables
+print(empty_variables)
+```
+
+```{r}
+names(raw_data)
+```
+
+Raw data 一共包含了52个variable以及17133个sample。52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
+```{r}
+# 这里需要画一个table，展示无关变量
+del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
+droped_data <- raw_data %>% select(-any_of(del_1))
+names(droped_data)
+```
+此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括：
+```{r}
+# 这里需要画一个table，展示删除的重复变量
+del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
+           "population_full", "candidate_id", "candidate_name")
+droped_data <- droped_data %>% select(-any_of(del_2))
+names(droped_data)
+```
+此外，在已知我们分析的是美国总统竞选的前提下，我们删除以下variables：
+```{r}
+# 这里需要画一个table，展示以知变量
+del_3 <- c("office_type", "seat_number", "seat_name")
+droped_data <- droped_data %>% select(-any_of(del_3))
+names(droped_data)
+```
+常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
+```{r}
+# Identify variables where all values are the same (including NA)
+same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
+# Create a data frame with variables and their unique values
+same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
+unique(na.omit(droped_data[[var]]))[1]))
+# Print the names of variables with all identical values using kable
+kable(same_value_data, col.names = c("Variable", "Value"))
+```
+```{r}
+del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch")
+droped_data <- droped_data %>% select(-any_of(del_4))
+names(droped_data)
+```
+其中categorical的有
+```{r}
+catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state", "start_date", "end_date",
+         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
+         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
+```
+重要的categorical为下面的，剩下的将在appendix阐述
+```{r}
+catego_inp <- c("poll_id", "methodology", )
+```
+
+以及numerical的variables
+```{r}
+muner <- droped_data %>% select(-any_of(catego))
+names(muner)
+```
+
+## Cleaned data
+
+## Measurement
+
+## Similar dataset
+
+# Model
+
+## Model set-up
+
+## Model validation
+
+```{r, fig.width=10, fig.height=10}
+data2 = raw_data %>% select("pollscore","transparency_score","sample_size")
+pairs( data2 , main = "Predictor vs predictor")
+```
+
+```{r}
+par(mfrow=c(2,2))
+plot(Trump_model,1)
+plot(Trump_model,2)
+
+```
+
+## Predictor variables

### 2024-11-01 scripts/05-exploratory_data_analysis.qmd
paper updated
paper updated

--- 2024-10-25 scripts/05-exploratory_data_analysis.qmd
@@
 library(rstanarm)
-
-#### Read data ####
-analysis_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
+library(patchwork)
+raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
 ```
-
-```{r}
-# Check for missing values in each column
-missing_values <- sapply(analysis_data, function(x) sum(is.na(x)))
-print(missing_values)
-```
-
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Get unique pollster IDs
-unique_pollster_ids <- unique(analysis_data$pollster_id)
+unique_pollster_ids <- unique(raw_data$pollster_id)
 print(unique_pollster_ids)
 ```
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Get unique question IDs
-unique_question_ids <- unique(analysis_data$question_id)
+unique_question_ids <- unique(raw_data$question_id)
 print(unique_question_ids)
 ```
-```{r}
-unique_question_ids_str <- paste(unique(unique_question_ids), collapse = ",")
-print(unique_question_ids_str)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique methodologys
+unique_methodologys <- unique(raw_data$methodology)
+print(unique_methodologys)
 ```
-
-```{r}
-View(unique_question_ids_str)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique population
+unique_population <- unique(raw_data$population)
+print(unique_population)
 ```
-
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique race_id
+unique_race_id <- unique(raw_data$race_id)
+print(unique_race_id)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique ranked_choice_reallocated
+unique_ranked_choice_reallocated <- unique(raw_data$ranked_choice_reallocated)
+print(unique_ranked_choice_reallocated)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique hypothetical
+unique_hypothetical <- unique(raw_data$hypothetical)
+print(unique_hypothetical)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique party
+unique_party <- unique(raw_data$party)
+print(unique_party)
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Get the maximum and minimum values of numeric_grade
-max_numeric_grade <- max(analysis_data$numeric_grade, na.rm = TRUE)
-min_numeric_grade <- min(analysis_data$numeric_grade, na.rm = TRUE)
+max_numeric_grade <- max(raw_data$numeric_grade, na.rm = TRUE)
+min_numeric_grade <- min(raw_data$numeric_grade, na.rm = TRUE)
 print(paste("Maximum numeric grade:", max_numeric_grade))
@@
 ```
-
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Find the earliest start date and the latest end date
+earliest_start_date <- min(raw_data$start_date, na.rm = TRUE)
+latest_end_date <- max(raw_data$end_date, na.rm = TRUE)
+print(paste("Earliest start date:", earliest_start_date))
+print(paste("Latest end date:", latest_end_date))
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Calculate the ratio of FALSE to TRUE in the hypothetical column
+hypothetical_ratio <- table(raw_data$hypothetical)
+print(hypothetical_ratio)
+false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
+print(paste("False to True Ratio:", false_to_true_ratio))
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Find the range of pollscore in the original dataset
+pollscore_range <- range(raw_data$pollscore, na.rm = TRUE)
+print(paste("Pollscore range:", pollscore_range[1], "to", pollscore_range[2]))
+```
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Plot histogram of numeric_grade
-ggplot(analysis_data, aes(x = numeric_grade)) +
+ggplot(raw_data, aes(x = numeric_grade)) +
   geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
@@
 ```
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Plot histogram of pollscore
-ggplot(analysis_data, aes(x = pollscore)) +
+ggplot(raw_data, aes(x = pollscore)) +
   geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
@@
 ```
-```{r}
-# Get unique methodologys
-unique_methodologys <- unique(analysis_data$methodology)
-print(unique_methodologys)
-```
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Plot histogram of transparency_score
-ggplot(analysis_data, aes(x = transparency_score)) +
+ggplot(raw_data, aes(x = transparency_score)) +
   geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
@@
 ```
-```{r}
-# Find the earliest start date and the latest end date
-earliest_start_date <- min(analysis_data$start_date, na.rm = TRUE)
-latest_end_date <- max(analysis_data$end_date, na.rm = TRUE)
-print(paste("Earliest start date:", earliest_start_date))
-print(paste("Latest end date:", latest_end_date))
-```
-
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # Plot histogram of sample_size
-ggplot(analysis_data, aes(x = sample_size)) +
+ggplot(raw_data, aes(x = sample_size)) +
   geom_histogram(binwidth = 0.5, fill = "blue", color = "black") +
@@
 ```
-```{r}
-# Get unique population
-unique_population <- unique(analysis_data$population)
-print(unique_population)
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Find the top 3 candidates.
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 3)                       
+print(candidate_ranking)
 ```
-```{r}
-# Get unique race_id
-unique_race_id <- unique(analysis_data$race_id)
-print(unique_race_id)
-```
-
-```{r}
-unique_race_id_str <- paste(unique(unique_race_id), collapse = ",")
-clipr::write_clip(unique_race_id_str)
-```
-
-```{r}
-# Get unique stage
-unique_stage <- unique(analysis_data$stage)
-print(unique_stage)
-```
-
-```{r}
-# Get unique stage
-unique_nationwide_batch <- unique(analysis_data$nationwide_batch)
-print(unique_nationwide_batch)
-```
-
-```{r}
-# Get unique ranked_choice_reallocated
-unique_ranked_choice_reallocated <- unique(analysis_data$ranked_choice_reallocated)
-print(unique_ranked_choice_reallocated)
-```
-
-```{r}
-# Get unique hypothetical
-unique_hypothetical <- unique(analysis_data$hypothetical)
-print(unique_hypothetical)
-```
-```{r}
-# Calculate the ratio of FALSE to TRUE in the hypothetical column
-hypothetical_ratio <- table(analysis_data$hypothetical)
-print(hypothetical_ratio)
-false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
-print(paste("False to True Ratio:", false_to_true_ratio))
-```
-
-```{r}
-# Get unique party
-unique_party <- unique(analysis_data$party)
-print(unique_party)
-```
-
-```{r}
-# Get unique population
-unique_population <- unique(analysis_data$population)
-print(unique_population)
-```

### 2024-11-01 scripts/06-model_data.R

@@ -15,7 +15,6 @@ library(tidyverse)
 
 Trump <- read_parquet("data/02-analysis_data/01-training/train_Trump.parquet")
 Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
-DeSantis <- read_parquet("data/02-analysis_data/01-training/train_DeSantis.parquet")
 
 # Function to create and save a linear model for a candidate
 
@@ -25,12 +24,9 @@ Trump_model <- lm(
 Harris_model <- lm(
   score ~ pollscore + transparency_score + duration + sample_size + population + 
     ranked_choice_reallocated + hypothetical + methodology, data = Harris)
-DeSantis_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + 
-    ranked_choice_reallocated + hypothetical + methodology, data = DeSantis)
 
 # Save the model
 saveRDS(Trump_model, file = "models/Trump_model.rds")
 saveRDS(Harris_model, file = "models/Harris_model.rds")
-saveRDS(DeSantis_model, file = "models/DeSantis_model.rds")
+
 

### 2024-11-01 scripts/05-exploratory_data_analysis.qmd
Added significant (featured) value selection

@@
 library(patchwork)
+library(moments)
 raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
@@
 ```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#select significant values based on variable type of each candidate
+
+# Define the function to select feature values based on variable type
+select_feature_value <- function(data, candidate_name) {
+  feature_values <- list()
+
+  for (col_name in names(data)) {
+    col_data <- data[[col_name]]
+
+    # Numeric variables: Choose mean or median based on skewness
+    if (is.numeric(col_data)) {
+      # Check if there are enough valid values to compute skewness
+      if (sum(!is.na(col_data)) > 1) {  # Ensure there is more than one valid value
+        skew_val <- skewness(col_data, na.rm = TRUE)
+        if (!is.na(skew_val) && skew_val < 1) {
+          feature_values[[col_name]] <- mean(col_data, na.rm = TRUE)
+        } else {
+          feature_values[[col_name]] <- median(col_data, na.rm = TRUE)
+        }
+      } else {
+        # Default to median if skewness cannot be computed
+        feature_values[[col_name]] <- median(col_data, na.rm = TRUE)
+      }
+    }
+
+    # Categorical variables: Choose mode (most frequent value)
+    else if (is.character(col_data)) {
+      feature_values[[col_name]] <- Mode(col_data)
+    }
+
+    # Boolean variables: Choose TRUE or FALSE based on which one appears more frequently
+    else if (is.logical(col_data)) {
+      true_count <- sum(col_data, na.rm = TRUE)
+      false_count <- sum(!col_data, na.rm = TRUE)
+      feature_values[[col_name]] <- if (true_count >= false_count) TRUE else FALSE
+    }
+  }
+
+  # Add the candidate name to the results
+  feature_values[["Candidate"]] <- candidate_name
+  return(feature_values)
+}
+
+# Define a function to calculate the mode (most frequent value)
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+# Calculate feature values for each candidate
+trump_features <- select_feature_value(trump_test, "Donald Trump")
+harris_features <- select_feature_value(harris_test, "Kamala Harris")
+
+# Combine results into a single data frame for easy viewing
+all_candidate_features <- bind_rows(trump_features, harris_features)
+
+# Display the final table of feature values
+print(all_candidate_features)
+
+```

### 2024-11-01 paper/paper.qmd
paper structure updated
paper  structure updated

--- 2024-10-31 paper/paper.qmd
@@
 ---
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+#| echo: false
+#### Workspace setup ####
+library(tidyverse)
+library(knitr)
+library(dplyr)
+library(arrow)
+library(patchwork)
+library(car)
+library(kableExtra)
+library(gridExtra)
+set.seed(912)
+#### Read data ####
+raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
+train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
+train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
+Trump_model <- readRDS(here::here("models/Trump_model.rds"))
+Harris_model <- readRDS(here::here("models/Harris_model.rds"))
+```
+
+# Introduction
+
+# Data {#sec-data}
+
+## Overview
+
+## Raw data
+
+```{r}
+names(raw_data)
+```
+
+Raw data 一共包含了52个variable以及17133个sample。52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
+```{r}
+# 这里需要画一个table，展示无关变量
+del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
+droped_data <- raw_data %>% select(-any_of(del_1))
+del_1
+```
+此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括：
+```{r}
+# 这里需要画一个table，展示删除的重复变量
+del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
+           "population_full", "candidate_id", "candidate_name")
+droped_data <- droped_data %>% select(-any_of(del_2))
+del_2
+```
+此外，在已知我们分析的是美国总统竞选的前提下，我们删除以下variables：
+```{r}
+# 这里需要画一个table，展示以知变量
+del_3 <- c("office_type", "seat_number", "seat_name")
+droped_data <- droped_data %>% select(-any_of(del_3))
+del_3
+```
+常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
+```{r}
+# Identify variables where all values are the same (including NA)
+same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
+# Create a data frame with variables and their unique values
+same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
+unique(na.omit(droped_data[[var]]))[1]))
+# Print the names of variables with all identical values using kable
+kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
+del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch")
+droped_data <- droped_data %>% select(-any_of(del_4))
+```
+
+其中categorical的有
+```{r}
+catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
+         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
+         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
+catego
+```
+重要的categorical为下面的，剩下的将在appendix阐述
+```{r}
+catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
+catego_inp
+```
+一共有3530个poll
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Get unique Poll IDs and print the count
+unique_poll_ids <- unique(raw_data$poll_id)
+print(length(unique_poll_ids))
+```
+描述
+```{r}
+plots <- list()
+# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
+plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Bar Chart of Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+
+plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Bar Chart of Hypothetical", x = "Hypothetical", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+
+# Combine and print the plots using patchwork
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(3, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+plots <- list()
+# Find the top 3 most frequent values in 'methodology' and group others as 'Other'
+methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
+top_3_methodologies <- names(methodology_counts)[1:3]
+raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
+# Create a bar chart for the grouped 'methodology'
+plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Top 3 Methodologies and Others", x = "Methodology", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Population", x = "Population", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+# Find the top 3 most frequent values in 'answer' and group others as 'Other'
+answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
+top_3_answer <- names(answer_counts)[1:3]
+raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
+# Create a bar chart for the grouped 'answer'
+plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Top 3 answer and Others", x = "answer", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+
+以及numerical的variables
+```{r}
+numer <- droped_data %>% select(-any_of(catego))
+names(numer)
+```
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-numdis_1
+#| fig-cap: "Distribution of numerical varibales"
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
+}
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-numdis_2
+#| fig-cap: "Distribution of numerical varibales"
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in names(numer %>% select(sample_size, pct))) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
+}
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 8), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-date
+#| fig-cap: "Distribution of date varibales"
+
+### Define Variables and Prepare Data ###
+# Convert start_date and end_date to Date type
+raw_data$start_date <- ymd(raw_data$start_date)
+raw_data$end_date <- ymd(raw_data$end_date)
+# Define the date variables to plot
+date_variables <- c("start_date", "end_date")
+### Create Plots for Date Variables ###
+# Loop through selected date variables and plot their distributions
+plots <- list()
+for (variable in names(numer %>% select(start_date, end_date))) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+        theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
+}
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+
+## Cleaned data
+在raw data中我们提到过，只有以下variables对我们的project有意义：
+```{r}
+names(droped_data)
+```
+在清理过程中，我们首先删除了NA值占比大于40%的值
+```{r}
+na_proportions <- sapply(names(droped_data), function(var) {
+  round(mean(is.na(raw_data[[var]])), 2)
+})
+
+# Create a data frame with variable names and their NA proportions
+na_proportions_data <- data.frame(Variable = names(droped_data), NA_Proportion = na_proportions)
+
+# Print the NA proportions using kable
+kable(na_proportions_data[, 2, drop = FALSE], col.names = c("NA Proportion"))
+```
+```{r}
+# Filter variables with NA proportion greater than 40%
+high_na_proportions <- na_proportions_data[na_proportions_data$NA_Proportion > 0.4, ]
+
+# Print the NA proportions greater than 40% using kable
+kable(high_na_proportions[, 2, drop = FALSE], col.names = c("Variable", "NA Proportion"))
+```
+```{r}
+del_5 <- c("sponsor_ids", "state", "sponsor_candidate_id", "sponsor_candidate_party", "tracking",
+           "internal","partisan","ranked_choice_round")
+droped_data <- droped_data %>% select(-any_of(del_5))
+names(droped_data)
+```
+
+我们选择了一些感兴趣的variables
+```{r}
+final <- c("poll_id","numeric_grade","pollscore","methodology","transparency_score","sample_size","population", 
+           "ranked_choice_reallocated", "hypothetical", "answer","pct","start_date", "end_date")
+final
+```
+
+然后我们Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
+然后Group methodology by level
+然后Replace NA values - numerical variables with mean, categorical variables with mode
+然后Rename pct as score
+然后我们用janitor::clean_names。
+然后我们把每个candidate的数据单独提了出来。
+通过计算每个候选人加权过的score（score平均值*poll的个数）。发现前三名川普，哈里斯，拜登与剩下的候选人分数悬殊。又由于
+拜登已经退出参选。我们现在只考虑川普和哈里斯。
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Find the top 5 candidates.
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 5)                       
+print(candidate_ranking)
+```
+我们将它们两人的数据单独提出来，并且分成了train（70%）,test(30%)
+这四个文件就是我们的analysisdata。
+以下是川普训练集的部分数据以供参考
+```{r}
+kable(head(train_Trump), col.names = names(train_Trump))
+```
+
+## Measurement
+
+## Similar dataset
+
+# Model
+## Model set-up
+### response variable
+我的的response variable是score，我们首先检查了两个训练集里面score的分布。
+```{r}
+# Plot a histogram for the 'pct' variable
+ggplot(train_Trump, aes(x = score)) +
+  geom_histogram(binwidth = 5, fill = "blue", color = "black", alpha = 0.7) +
+  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+ggplot(train_Harris, aes(x = score)) +
+  geom_histogram(binwidth = 5, fill = "blue", color = "black", alpha = 0.7) +
+  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+```
+它们都呈现正态分布，这是使用MLR的条件之一。
+
+### Predictor
+在我们的两个train数据集里面，我们首先检查了所有numerical variable的关系。
+```{r, fig.width=10, fig.height=10}
+data2 = raw_data %>% select("numeric_grade", "pollscore","transparency_score","sample_size")
+pairs( data2 , main = "Predictor vs predictor")
+```
+由于我们发现pollscore和numerical grade之间呈现了明显的线性关系，因此，我们舍弃掉了numerical grade。
+因此我们的模型predictor是：
+```{r}
+predictors <- c("pollscore","methodology","transparency_score","sample_size","population", 
+           "ranked_choice_reallocated", "hypothetical", "duration")
+```
+### alternative models
+最开始我们的模型是
+```{r}
+Trump_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Trump)
+Harris_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Harris)
+```
+
+```{r}
+# Get the summary of the model
+Harris_summary <- summary(Harris_model_1)
+# Extract coefficients from the summary
+coefficients <- Harris_summary$coefficients
+# Extract p-values
+Harris_p_values <- coefficients[, 4]
+# Create a data frame with the results
+Harris_results_table <- data.frame(
+  Variable = rownames(coefficients),
+  P_Value = format(Harris_p_values, scientific = TRUE)
+)
+Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Harris", col.names = c("Variable", "P-value"))
+# Get the summary of the model
+Trump_summary <- summary(Trump_model_1)
+# Extract coefficients from the summary
+coefficients <- Trump_summary$coefficients
+# Extract p-values
+Trump_p_values <- coefficients[, 4]
+# Create a data frame with the results
+Trump_results_table <- data.frame(
+  Variable = rownames(coefficients),
+  P_Value = format(Trump_p_values, scientific = TRUE)
+)
+Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Trump", col.names = c("Variable", "P-value"))
+
+grid.arrange(tableGrob(Trump_kable), tableGrob(Harris_kable), nrow = 1)
+
+```
+
+去掉不显著的变量：methodology，ranked_choice_reallocated
+
+```{r}
+summary(Trump_model_1)
+summary(Harris_model_1)
+```
+
+```{r}
+summary(Trump_model)
+summary(Harris_model)
+```
+
+## validation
+从您的结果来看，所有变量的 GVIF 值都在 1 到 1.3 之间，这些数值非常低，表明各个自变量之间的共线性很小，模型并没有因为共线性而受到显著影响。
+```{r}
+vif(Trump_model)
+vif(Harris_model)
+```
+
+```{r}
+par(mfrow=c(2,2))
+plot(Harris_model,1)
+plot(Harris_model,2)
+```
+
+```{r}
+par(mfrow=c(2,2))
+plot(Trump_model,1)
+plot(Trump_model,2)
+```
+然后就是描述一下response variable是normal的，然后numerical variable没有显著关系（这些在打他部分有讲过）
+
+总结，满足了MLR的条件，说明我们的好

### 2024-11-01 scripts/06-model_data.R

@@ -19,11 +19,9 @@ Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
 # Function to create and save a linear model for a candidate
 
 Trump_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + 
-    ranked_choice_reallocated + hypothetical + methodology, data = Trump)
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical , data = Trump)
 Harris_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + 
-    ranked_choice_reallocated + hypothetical + methodology, data = Harris)
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical , data = Harris)
 
 # Save the model
 saveRDS(Trump_model, file = "models/Trump_model.rds")

### 2024-11-01 other/literature/ElectionForcast_linearmodel.qmd

---
title: "The 2024 U.S. Presidential Election Forecast"
subtitle: "Summary of technical model details"
author: Haowei Fan, Fangning Zhang, Shaotong Li
date: 13/10/2024
contact: haowei.fan@mail.utoronto.ca
licence: MIT
date-format: long
format: pdf
---

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(dplyr)
library(ggplot2)
library(patchwork)
library(gridExtra)
library(arrow)
library(knitr)  
library(kableExtra) 
```

# Overview

The purpose of this document is to explain the details used in the linear model.This linear model is used to forecast the U.S. 2024 president election by predicting the wining rate outcomes of polls based on several features of polls. Broadly, the model can be described as a Linear hierachical model:

1. A model to capture the association between the outcome (the support or winning rate of candidate) and the input variables (poll reliability score, quality-related factors, and etc)

2.Each independent variables in this model is consider distributed normally, so as the intercept.

## Overview of the input values for prediction

The values are selected based on the significant value of variables of each candidate.The significant values of variables are chosen based on the their distribution.

For numeric variables, we chose either the mean or the median as the representative feature value, depending on the data's distribution.
If the data distribution was approximately symmetric (low skewness), we used the mean, as it best represents the central tendency。

For highly skewed data, we used the median to avoid the influence of outliers, providing a more robust measure of central tendency.

For categorical variables, we selected the mode (the most frequent category) as the feature value.
The mode is often the best representative of categorical data, as it reflects the most common category and thus the main trend within the data.

For Boolean variables, we identified whether TRUE or FALSE was more frequent and used the most common value as the feature value.
This approach ensures that the feature value represents the predominant condition in the data, rather than relying on a percentage or proportion.

Here are the chosen significant values for Trump and Harris:

```{r}
#| echo: false
#| warning: false
#| message: false

# Load the Trump and Harris linear models
trump_linear_model <- readRDS(here::here("models", "Trump_model.rds"))
harris_linear_model <- readRDS(here::here("models", "Harris_model.rds"))

# Define the modified candidate data
candidate_data <- tibble(
  numeric_grade = c(2.15, 2.20),
  pollscore = c(-0.368, -0.4),
  methodology = c("level3", "level3"),
  transparency_score = c(6.17, 6.37),
  sample_size = c(1003, 1000),
  ranked_choice_reallocated = c(FALSE, FALSE),
  hypothetical = c(TRUE, FALSE),
  score = c(45.0, 46.8),
  duration = c(3, 3)
)

# Ensure population is a factor if it’s needed in the model (use any appropriate levels)
candidate_data$population <- factor(c("rv", "lv"), levels = c("rv", "lv"))

# Make predictions for Trump and Harris using the modified candidate_data
candidate_data$Trump_Predicted_Support <- predict(trump_linear_model, newdata = candidate_data)
candidate_data$Harris_Predicted_Support <- predict(harris_linear_model, newdata = candidate_data)

# Create a combined data frame for plotting purposes
predictions_df <- data.frame(
  Candidate = c("Donald Trump", "Kamala Harris"),
  Predicted_Support = c(mean(candidate_data$Trump_Predicted_Support, na.rm = TRUE), 
                        mean(candidate_data$Harris_Predicted_Support, na.rm = TRUE))
)

# Remove the prediction and score columns from the candidate data
candidate_data <- candidate_data %>%
  select(-Trump_Predicted_Support, -Harris_Predicted_Support, -score)

# Convert all remaining columns to character for compatibility in pivot_longer
candidate_data <- candidate_data %>% mutate(across(everything(), as.character))

# Transpose the data for a two-column format
feature_values_table <- candidate_data %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  mutate(Candidate = rep(c("Donald Trump", "Kamala Harris"), each = ncol(candidate_data))) %>%
  select(Candidate, Variable, Value) %>%
  pivot_wider(names_from = "Candidate", values_from = "Value")  # Reshape into two columns

# Display the feature values table in a two-column, aesthetic format
kable(feature_values_table, align = c("l", "c", "c"), caption = "Candidate Feature Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, width = "6cm") %>%   # Widen the Variable column
  column_spec(2, width = "5cm") %>%                # Increase width of Trump column
  column_spec(3, width = "5cm") %>%                # Increase width of Harris column
  add_header_above(c(" " = 1, "Candidate Feature Summary" = 2))
```

# Variables explained and outcomes estimated

These are the independent variables used in the model:

```{=tex}
\begin{itemize}
\item $\alpha_i$: Poll reliability score
\item $\beta_i$: Poll quality score (numeric grade)
\item $\gamma_i$: Poll transparency score
\item $\delta_i$: Poll duration
\item $\theta_i$: Sample size
\item $\kappa_i$: Population type surveyed
\item $\lambda_i$: Indicator of whether the poll is hypothetical
\item $\mu_i$: Poll methodology type
\item $\rho_i$: Rank-choice reallocation usage
\end{itemize}
```

This is the dependent variable, or the outcome of this model:

```{=tex}
$y_i$ : Winning rate (percentage) for a candidate in the 2024 U.S. presidential election polls
```

# Model

```{=tex}
\begin{align} 
y_i | \mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_1 \times \phi_i + \beta_2 \times \beta_i + \beta_3 \times \gamma_i + \beta_4 \times \delta_i \\
      &\quad + \beta_5 \times \theta_i + \beta_6 \times \kappa_i + \beta_7 \times \lambda_i + \beta_8 \times \mu_i + \beta_9 \times \rho_i \\
\alpha &\sim \mbox{Normal}(0, 10) \\
\beta_j &\sim \mbox{Normal}(0, 2.5) \quad \text{for each } j = 1, \dots, 9 \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```

This model combines a normal likelihood with hierarchical priors, creating a Bayesian linear regression framework. The priors on the coefficients and intercept provide regularization, helping to avoid overfitting by constraining the values of $α_i$ and $β_j$ coefficients. The prior on $σ$ helps control the model's uncertainty about the data by penalizing very high variance. This setup allows for flexibility in estimating $μ_i$ while accounting for the effects of the predictors and controlling for the noise in the data.

## Hirerachical structure

The hierarchical structure in this model is established through the use of priors on both the intercept $α$ and the coefficients $β_j$, which represent the relationship between predictors and the outcome variable $y_i$. Each coefficient $β_j$ has a normal prior centered around zero with a moderate spread (standard deviation of 2.5), allowing for some variability in the effect of each predictor while constraining extreme values. The intercept $α$ also has a prior centered around zero with a larger standard deviation (10), reflecting greater uncertainty in its baseline effect. Additionally, the standard deviation $σ$, which governs the noise in the data, is given an exponential prior, favoring smaller values to encourage a tighter fit. This hierarchical structure allows the model to borrow strength across predictors, promoting more stable estimates and helping to regularize the model by introducing prior beliefs about the distribution of parameters, thereby preventing overfitting.

## Steps of prediction

### Load Models and Data
The linear models for both Trump and Harris were loaded using readRDS(). We use ths featured value mentioned before as input values in our model.

### Data Preprocessing
The hypothetical column was converted to logical data type where necessary, ensuring data compatibility with prediction models.

### Prediction and Visualization
```{r}
#| echo: false
#| warning: false
#| message: false
# Adjust the bar plot height
bar_plot <- ggplot(predictions_df, aes(x = Candidate, y = Predicted_Support, fill = Candidate)) +
  geom_bar(stat = "identity", width = 0.6, color = "white") +
  geom_text(aes(label = paste0(round(Predicted_Support, 1), "%")), 
            vjust = -0.5, size = 5) +
  labs(title = "",
       x = "Candidate",
       y = "Predicted Support (%)") +
  theme_minimal() +
  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon")) +
  ylim(0, max(predictions_df$Predicted_Support) * 1.2)  # Set upper limit to make space for labels

# Print the bar plot
print(bar_plot)

# Define data for the pie chart, including "Other Candidates" to fill up to 100%
pie_data <- data.frame(
  Candidate = c("Donald Trump", "Kamala Harris", "Other Candidates"),
  Support = c(45.2, 45.9, 100 - (45.2 + 45.9))
)

# Create the pie chart
pie_chart <- ggplot(pie_data, aes(x = "", y = Support, fill = Candidate)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  labs(title = "") +
  theme_void() +  # Remove background and axis
  theme(legend.position = "right") +
  scale_fill_manual(values = c("Donald Trump" = "skyblue", "Kamala Harris" = "salmon", "Other Candidates" = "grey")) +
  geom_text(aes(label = ifelse(Support > 5, paste0(round(Support, 1), "%"), "")), 
            position = position_stack(vjust = 0.5), color = "white", size = 5)

# Print the pie chart
print(pie_chart)

```

### 2024-11-01 scripts/00-simulate_data.R
simulation updated
simulation updated

@@ -16,23 +16,23 @@ set.seed(123)
   
 ## Generate simulated data for candidate_1
 simulated_candidate_1 <- tibble(
-  poll_id = 1:500, 
+  # Generate numeric_grade based on a normal distribution with mean 2.5 and standard deviation 2,
+  numeric_grade = round(rnorm(500, mean = 2.5, sd = 2), 1),
   # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
-  # then ensure the values are within the range [-1, 1] and round to one decimal place, then map to a range of 0 to 10
-  pollscore = round((pmin(pmax(rnorm(500, mean = -0.5, sd = 0.3), -1), 1) + 1) * 5, 1),
+  pollscore = round(rnorm(500, mean = -0.5, sd = 0.3), 1),
   # The methodology is divided into four levels: level 1 represents the least reliable type of methodology, while level 4 represents the most reliable.
   methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
   # Generate transparency_score based on a normal distribution with mean 6 and standard deviation 1.5,
   # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
-  transparency_score = round((pmin(pmax(rnorm(500, mean = 6, sd = 1.5), 1), 10) / 10) * 10, 1),
+  transparency_score = round(rnorm(500, mean = 6, sd = 1.5), 1),
   # The duration of this poll in days. Duration based on a normal distribution with mean 183 and standard deviation 100,
-  duration = round(pmin(pmax(rnorm(500, mean = 183, sd = 100), 15), 365)),
+  duration = round(rnorm(500, mean = 183, sd = 100)),
   # Generate sample_size based on a normal distribution with mean 1200 and standard deviation 5000, then round to the nearest integer
-  sample_size = round(pmin(pmax(rnorm(500, mean = 1200, sd = 5000), 100), 200000)),
+  sample_size = abs(round(rnorm(500, mean = 1200, sd = 5000))),
   # Population types：Likely Voters，Registered Voters, Voters, Adult
   population = sample(c("a", "v", "lv", "rv"), 500, replace = TRUE),
   # Set TRUE/FALSE ratio to 0.9 for the hypothetical column
-  ranked_choice_reallocated= sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.9, 0.1)),
[…]

### 2024-11-01 scripts/03-clean_data.R

@@ -80,26 +80,25 @@ raw_data_cleaned <- raw_data_cleaned %>%
 # Step 7: Rename pct
 names(raw_data_cleaned)[names(raw_data_cleaned) == "pct"] <- "score"
 
-# Step 8: Clean name
-raw_data_cleaned <- janitor::clean_names(raw_data_cleaned)
 
-# Step 9: Filter data set by unique answer
+# Step 8: Filter data set by unique answer
 candidates <- unique(raw_data_cleaned$answer)
 for (candidate in candidates) {
   # Filter data for each candidate and remove rows with NA values
   candidate_data <- raw_data_cleaned %>%
     filter(answer == candidate) %>% 
     dplyr::select(-answer)%>% 
-    dplyr::select(-poll_id)
+    dplyr::select(-poll_id)%>%
+    janitor::clean_names()
   # Define output file path for each candidate
   output_file <- file.path("data/03-cleaned_data", paste0(candidate, "_cleaned_data.parquet"))
   # Save each candidate's cleaned data to a separate Parquet file
   write_parquet(candidate_data, output_file)
 }
 
-# Step 10: find analysis data
-# Split the top 3 files into 3:7 ratio and save them
-for (file in c("Trump_cleaned_data.parquet", "Harris_cleaned_data.parquet", "DeSantis_cleaned_data.parquet")) {
+# Step 9: find analysis data
+# Split the top 2 files into 3:7 ratio and save them
+for (file in c("Trump_cleaned_data.parquet", "Harris_cleaned_data.parquet")) {
   # Read the Parquet file into a data frame
   df <- read_parquet(file.path("data/03-cleaned_data/", file))
   # Split the data into 3:7 ratio

### 2024-11-01 paper/paper.qmd
paper updated

@@
 ```
-此外，在已知我们分析的是美国总统竞选的前提下，我们删除以下variables：
-```{r}
-# 这里需要画一个table，展示以知变量
-del_3 <- c("office_type", "seat_number", "seat_name")
-droped_data <- droped_data %>% select(-any_of(del_3))
-del_3
-```
 常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
@@
 kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
-del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch")
+del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
+           "office_type", "seat_number", "seat_name")
 droped_data <- droped_data %>% select(-any_of(del_4))
@@
 ## Cleaned data
-在raw data中我们提到过，只有以下variables对我们的project有意义：
+在raw data中我们提到过，在总共的52个variables。其中一些比如“url”之类的变量与该项目明显无关。有一部分位常数variable，比如
+“election_date”的值全部都是“11/5/24”。还有一部分是意思相同的variables，比如说“pollster_id”和“pollster”。另外还有一部分是
+只有以下variables对我们的project有意义：
 ```{r}

### 2024-11-02 other/literature/ElectionForcast_linearmodel.qmd
literature grammar fixed

@@
 
-The purpose of this document is to explain the details used in the linear model.This linear model is used to forecast the U.S.
+The purpose of this document is to explain the details used in the linear model.
+This linear model is used to forecast the U.S.
 2024 president election by predicting the wining rate outcomes of polls based on several features of polls.
-Broadly, the model can be described as a Linear hierachical model:
+Broadly, the model can be described as a linear hierarchical model:
 
@@
 
-2.Each independent variables in this model is consider distributed normally, so as the intercept.
+2. Each independent variable in this model is consider distributed normally, so as the intercept.
 
@@
 
-For numeric variables, we chose either the mean or the median as the representative feature value, depending on the data's distribution.
+For numeric variables, we chose either the mean or the median as the representative feature value, depending on the data distribution.
 If the data distribution was approximately symmetric (low skewness), we used the mean, as it best represents the central tendency。
 
-For highly skewed data, we used the median to avoid the influence of outliers, providing a more robust measure of central tendency.
+For highly skewed data, we used the median to avoid the influence of the outliers, providing a more robust measure of central tendency.
 
@@
 ### Load Models and Data
-The linear models for both Trump and Harris were loaded using readRDS(). We use ths featured value mentioned before as input values in our model.
+The linear models for both Trump and Harris were loaded using readRDS(). We use this featured value mentioned before as input values in our model.
 

### 2024-11-02 scripts/05-exploratory_data_analysis.qmd
paper structure updated
paper  structure updated
Updated test simulated and analysis data
fixed bugs and changed preambles

@@
 raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
+Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
+Harris_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
 ```
@@
   arrange(desc(avg_weighted_pct)) %>%    
-  slice_head(n = 3)                       
+  slice_head(n = 5)                       
 print(candidate_ranking)
@@
 # Calculate feature values for each candidate
-trump_features <- select_feature_value(trump_test, "Donald Trump")
-harris_features <- select_feature_value(harris_test, "Kamala Harris")
+trump_features <- select_feature_value(Trump_test, "Donald Trump")
+harris_features <- select_feature_value(Harris_test, "Kamala Harris")
 

### 2024-11-02 scripts/01-test_simulated_data.R

@@ -1,28 +1,80 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated variables 
+  #of U.S. election candidates
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: 00-simulated_data saved and loaded
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(rstanarm)
+library(testthat)
+library(arrow)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
+analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
+analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
+analysis_data_3 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_3.parquet"))
 
 #### Test data ####
 
+# Convert sample_size to integer if necessary
+analysis_data_1$sample_size <- as.integer(analysis_data_1$sample_size)
+analysis_data_2$sample_size <- as.integer(analysis_data_2$sample_size)
+analysis_data_3$sample_size <- as.integer(analysis_data_3$sample_size)
+
+# Define expected columns (updated to match actual columns in datasets)
+expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
+                      "duration", "sample_size", "population", "ranked_choice_reallocated", 
+                      "hypothetical", "score")
+
+#### Test structure of datasets ####
+test_that("Simulated datasets contain all expected columns", {
+  for (data in list(analysis_data_1, analysis_data_2, analysis_data_3)) {
[…]

### 2024-11-02 scripts/04-test_analysis_data.R

@@ -1,13 +1,11 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: test on the analysis data for validation
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
 #### Workspace setup ####
 
@@ -17,8 +15,91 @@ library(testthat)
 library(arrow)  # For reading Parquet files
 library(here)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
+Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
+Harris_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
+Trump_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
+Harris_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
 
 #### Test data ####
 
+#### Test data ####
+
+# Ensure testthat setup
+context("Data validation tests for Trump and Harris datasets")
+
+# Test 1: Check if the datasets have the expected columns
+test_that("Expected columns are present in Trump and Harris test and train datasets", {
+  expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
+                        "sample_size", "population", "ranked_choice_reallocated", 
+                        "hypothetical", "score", "duration")
+  
+  # Check columns in each dataset
+  expect_true(all(expected_columns %in% colnames(Trump_test)))
+  expect_true(all(expected_columns %in% colnames(Harris_test)))
+  expect_true(all(expected_columns %in% colnames(Trump_train)))
+  expect_true(all(expected_columns %in% colnames(Harris_train)))
+})
+
+# Test 2: Check for missing values
+test_that("No missing values in critical columns of test and train datasets", {
+  # List critical columns
[…]

### 2024-11-02 paper/paper.qmd
graphing updated
graphing updated

--- 2024-11-01 paper/paper.qmd
@@
 library(arrow)
+library(patchwork)
+library(car)
+library(kableExtra)
+library(gridExtra)
 set.seed(912)
@@
 ## Raw data
-```{r}
-# Identify variables (columns) that are completely empty (all NA values)
-empty_variables <- names(raw_data)[sapply(raw_data, function(x) all(is.na(x)))]
+Raw data 一共包含了52个variable以及17133个sample.
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-vord
+#| tbl-cap: "Varibales of raw data"
 
-# Print the names of empty variables
-print(empty_variables)
+# Get the column names and arrange them into multiple columns
+column_names <- names(raw_data)
+num_columns <- 3  # Set the desired number of columns
+num_rows <- ceiling(length(column_names) / num_columns)
+matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
+                      nrow = num_rows, byrow = TRUE)
+
+# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
+kable(as.data.frame(matrix_data), 
+      col.names = NULL)
+```
+其中重要的variables，其余的在appdendix
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-ivatd
+#| tbl-cap: "Important variables and their descriptions"
+
+variable_descriptions <- data.frame(
+  Variable = c("poll_id", "methodology", "population", "ranked_choice_reallocated",
+               "hypothetical", "answer", "numeric_grade", "pollscore", 
+               "transparency_score", "start_date", "end_date", "sample_size", "pct"),
+  Description = c(
+    "Unique identifier for each poll conducted.",
+    "The method used to conduct the poll (e.g., Online Panel).",
+    "The abbreviated description of the respondent group, typically indicating their voting status (e.g., 'lv' for likely voters).",
+    "Indicates if ranked-choice voting reallocations have been applied in the results.",
+    "Indicates whether the poll is about a hypothetical match-up.",
+    "The response or answer choice given in the poll (e.g., the candidate's party).",
+    "A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).",
+    "A numeric value representing the score or reliability of the pollster in question (e.g., -1.1).",
+    "A score reflecting the pollster's transparency about their methodology (e.g., 9.0).",
+    "The date the poll began (e.g., 10/8/24).",
+    "The date the poll ended (e.g., 10/11/24).",
+    "The total number of respondents participating in the poll (e.g., 2712).",
+    "The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris)."
+  )
+)
+
+# Create the table using kable
+kable(variable_descriptions) %>%
+  kable_styling() %>%
+  column_spec(1, width = "4.5cm") %>% # Adjust the width of the first column
+  column_spec(2, width = "10cm")    # Adjust the width of the second column
 ```
 
-```{r}
-names(raw_data)
-```
+52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
+"notes", "url", "url_article", "url_topline", "url_crosstab", "source"
 
-Raw data 一共包含了52个variable以及17133个sample。52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
-```{r}
-# 这里需要画一个table，展示无关变量
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
 del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
 droped_data <- raw_data %>% select(-any_of(del_1))
-names(droped_data)
 ```
-此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括：
+此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括："pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name", "population_full", "candidate_id", "candidate_name"
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
 # 这里需要画一个table，展示删除的重复变量
@@
 droped_data <- droped_data %>% select(-any_of(del_2))
-names(droped_data)
-```
-此外，在已知我们分析的是美国总统竞选的前提下，我们删除以下variables：
-```{r}
-# 这里需要画一个table，展示以知变量
-del_3 <- c("office_type", "seat_number", "seat_name")
-droped_data <- droped_data %>% select(-any_of(del_3))
-names(droped_data)
 ```
 常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
-```{r}
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cv
+#| tbl-cap: "Constant variables"
 # Identify variables where all values are the same (including NA)
@@
 # Print the names of variables with all identical values using kable
-kable(same_value_data, col.names = c("Variable", "Value"))
+kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
+del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
+           "office_type", "seat_number", "seat_name")
+droped_data <- droped_data %>% select(-any_of(del_4))
 ```
+
+其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
+         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
+         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer"
 ```{r}
-del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch")
-droped_data <- droped_data %>% select(-any_of(del_4))
-names(droped_data)
-```
-其中categorical的有
-```{r}
-catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state", "start_date", "end_date",
+#| warning: false
+#| message: false
+#| echo: false
+catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
          "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
@@
 ```
-重要的categorical为下面的，剩下的将在appendix阐述
+重要的categorical为下面的，剩下的将在appendix阐述："poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer"
 ```{r}
-catego_inp <- c("poll_id", "methodology", )
+#| warning: false
+#| message: false
+#| echo: false
+catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
+```
+一共有3530个poll
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+# Get unique Poll IDs and print the count
+unique_poll_ids <- unique(raw_data$poll_id)
+```
+描述
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-bv
+#| fig-cap: "Boolean variables"
+plots <- list()
+# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
+plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+
+plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Hypothetical", x = "Hypothetical", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+
+# Combine and print the plots using patchwork
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(3, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-cv
+#| fig-cap: "Catogorical variables"
+
+plots <- list()
+# Find the top 3 most frequent values in 'methodology' and group others as 'Other'
+methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
+top_3_methodologies <- names(methodology_counts)[1:3]
+raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
+# Create a bar chart for the grouped 'methodology'
+plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Top 3 Methodologies and Others", x = "Methodology", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Population", x = "Population", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+# Find the top 3 most frequent values in 'answer' and group others as 'Other'
+answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
+top_3_answer <- names(answer_counts)[1:3]
+raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
+# Create a bar chart for the grouped 'answer'
+plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
+  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+  labs(title = "Top 3 answer and Others", x = "answer", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10)
+  )
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
 ```
 
-以及numerical的variables
+以及numerical的variables："numeric_grade"      "pollscore"          "transparency_score" "start_date"         "end_date"        "sample_size" "pct"
 ```{r}
-muner <- droped_data %>% select(-any_of(catego))
-names(muner)
+#| warning: false
+#| message: false
+#| echo: false
+numer <- droped_data %>% select(-any_of(catego))
+```
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-donvp1
+#| fig-cap: "Distribution of numerical varibales part 1"
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
+}
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-donvp2
+#| fig-cap: "Distribution of numerical varibales part 2"
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in names(numer %>% select(sample_size, pct))) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
+}
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 8), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+
+描述
+```{r, fig.pos="H", fig.width=18, fig.height=18}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-dodv
+#| fig-cap: "Distribution of date varibales"
+
+### Define Variables and Prepare Data ###
+# Convert start_date and end_date to Date type
+raw_data$start_date <- ymd(raw_data$start_date)
+raw_data$end_date <- ymd(raw_data$end_date)
+# Define the date variables to plot
+date_variables <- c("start_date", "end_date")
+### Create Plots for Date Variables ###
+# Loop through selected date variables and plot their distributions
+plots <- list()
+for (variable in names(numer %>% select(start_date, end_date))) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+        theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
+}
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
 ```
@@
 ## Cleaned data
+In the raw data, we initially identified a total of 52 variables.
+Some of these variables, such as 'url', are clearly unrelated to the objectives of this project.
+There are also constant variables, such as 'election_date', which consistently contains the value '11/5/24'.
+Additionally, we found duplicate variables conveying the same information, like 'pollster_id' and 'pollster'.
+Therefore, we first removed these irrelevant and redundant variables.
+The remaining variables are as follows:
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-rv
+#| tbl-cap: "Remained variables"
+
+# Get the column names and arrange them into multiple columns
+column_names <- names(droped_data)
+num_columns <- 3  # Set the desired number of columns
+num_rows <- ceiling(length(column_names) / num_columns)
+matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
+                      nrow = num_rows, byrow = TRUE)
+
+# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
+kable(as.data.frame(matrix_data), 
+      col.names = NULL)
+```
+
+Next, we calculated the percentage of missing values for each variable across the entire dataset.
+We then removed all variables with more than 40% missing values.
+These variables, along with their respective proportions of missing values, are as follows:
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-vwbpomv
+#| tbl-cap: "Variables with big porpotion of missing values"
+na_proportions <- sapply(names(droped_data), function(var) {
+  round(mean(is.na(raw_data[[var]])), 2)
+})
+
+# Create a data frame with variable names and their NA proportions
+na_proportions_data <- data.frame(Variable = names(droped_data), NA_Proportion = na_proportions)
+
+# Filter variables with NA proportion greater than 40%
+high_na_proportions <- na_proportions_data[na_proportions_data$NA_Proportion > 0.4, ]
+
+# Print the NA proportions greater than 40% using kable
+kable(high_na_proportions[, 2, drop = FALSE], col.names = c("Variable", "NA Proportion"))
+
+del_5 <- c("sponsor_ids", "state", "sponsor_candidate_id", "sponsor_candidate_party", "tracking",
+           "internal","partisan","ranked_choice_round")
+droped_data <- droped_data %>% select(-any_of(del_5))
+
+```
+
+Since the influence of pollsters can be quantified using their ratings, such as 'numeric_grade', 'pollscore', and 'transparency_score', we removed these variables to simplify the dataset and the model.
+Similarly, 'created_at' was also removed due to its strong correlation with 'start_date'.
+At this point, the remaining variables are as follows:
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+del_6 <- c("pollster_id", "pollster_rating_id", "created_at")
+droped_data <- droped_data %>% select(-any_of(del_6))
+```
+Finally, due to the limitations of our model, we removed 'race_id', 'party', and 'question_id'.
+The reason for this is that we will extract and analyze the data for each candidate individually, which makes 'race_id' and 'party' constant within the corresponding dataset.
+Additionally, 'question_id' contains 6,421 unique values, making it unsuitable for categorization, and we removed it to avoid overfitting the model.
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+# Get unique Question IDs and print the count
+unique_question_ids <- unique(raw_data$question_id)
+```
+
+Finally, the remaining variables are as follows:
+
+```{r, fig.height=30, fig.width=30}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-fv
+#| tbl-cap: "Final variables"
+final <- c("poll_id","numeric_grade","pollscore","methodology","transparency_score","sample_size","population", 
+           "ranked_choice_reallocated", "hypothetical", "answer","pct","start_date", "end_date")
+
+# Get the column names and arrange them into multiple columns
+column_names <- final
+num_columns <- 3  # Set the desired number of columns
+num_rows <- ceiling(length(column_names) / num_columns)
+matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
+                      nrow = num_rows, byrow = TRUE)
+
+# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
+kable(as.data.frame(matrix_data), 
+      col.names = NULL)
+```
+
+After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
+This new variable represents the number of days between 'start_date' and 'end_date'.Next, we categorized the 51 different methodologies into four levels, ranging from the least reliable and accurate (level_1) to the most reliable (level_4).
+The specific classifications are as follows:
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-mc
+#| tbl-cap: "Methodology classfication"
+
+# Create a summary data frame for the methodologies and their levels
+methodology_summary <- data.frame(
+  Level = c("level 1", "level 2", "level 3", "level 4"),
+  Methodologies = c(
+    paste(c("Email", "Email/Online Ad", "Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Mail-to-Web/Mail-to-Phone", "Online Ad"), collapse = ", "),
+    paste(c("App Panel", "IVR", "IVR/Live Phone/Text/Online Panel/Email", "IVR/Online Panel", "IVR/Online Panel/Email", "IVR/Online Panel/Text-to-Web", "IVR/Online Panel/Text-to-Web/Email", "IVR/Text", "IVR/Text-to-Web", "IVR/Text-to-Web/Email", "Live Phone/Email", "Live Phone/Online Panel/Mail-to-Web", "Live Phone/Text/Online Ad", "Live Phone/Text-to-Web/Email", "Live Phone/Text-to-Web/Email/Mail-to-Web", "Live Phone/Text-to-Web/Online Ad", "Online Panel/Email", "Online Panel/Email/Text-to-Web", "Online Panel/Online Ad", "Text-to-Web/Email", "Text-to-Web/Online Ad"), collapse = ", "),
+    paste(c("IVR/Live Phone/Online Panel", "IVR/Live Phone/Online Panel/Text-to-Web", "IVR/Live Phone/Text", "IVR/Live Phone/Text-to-Web", "Live Phone/Online Panel/App Panel", "Live Phone/Online Panel/Text", "Live Phone/Online Panel/Text-to-Web", "Live Phone/Online Panel/Text-to-Web/Text", "Live Phone/Text", "Live Phone/Text/Online Panel", "Live Phone/Text-to-Web", "Live Phone/Text-to-Web/App Panel", "Online Panel", "Online Panel/Text", "Online Panel/Text-to-Web", "Online Panel/Text-to-Web/Text", "Text", "Text-to-Web"), collapse = ", "),
+    paste(c("Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", "Online Panel/Probability Panel", "Probability Panel"), collapse = ", ")
+  )
+)
+
+# Print the summary of methodologies and their levels using kable
+kable(methodology_summary, col.names = c("Level", "Methodologies")) %>%
+  column_spec(1, width = "1.5cm") %>% # Adjust the width of the first column
+  column_spec(2, width = "13cm")
+```
+In our classification, we primarily considered whether the survey method was active or passive, giving higher scores to methodologies involving active outreach by statistical agencies.
+We then averaged the scores of all methods used in each poll; the higher the average, the higher the assigned level.
+
+Subsequently, we handled the missing values by imputing numerical variables with their mean values and categorical variables with their mode.
+Since our results are not exact percentages, we used 'score' to name what would typically be called 'pct'.
+We then used janitor::clean_names to finalize and tidy up the variable names.Next, we extracted the data for each candidate individually.
+We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
+After comparison, we observed that the top three candidates—Trump, Harris, and Biden—had significantly higher scores than the remaining candidates.
+Given that Biden has withdrawn from the race, we are now focusing only on the datasets for Trump and Harris for further analysis.
+The specific weighted scores for the top five candidates are as follows:
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-t5c
+#| tbl-cap: "Top 5 Candidates"
+# Find the top 5 candidates.
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 5)                       
+kable(candidate_ranking, col.names = c("candidate", "number of polls", "weighted score"))
+
+```
+Next, we split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+kable(head(train_Trump), col.names = names(train_Trump))
+```
 
@@
 # Model
+## Model overview
+我们一共有2个model，分别用来预测川普和哈里斯在2024年11月5日美国总统竞选的最终支持率。
+
+\begin{align} 
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+\end{align}
+
+其中
+
+score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical
 
 ## Model set-up
+### response variable
+在此章节中，我们用到的数据都是哈里斯和特朗普的训练集。
+score是我们模型的response variable，它代表的是某个候选人在某次选票中胜利的可能性，越大代表着该候选人竞选成功的概率越大，通常情况下与该候选人在那次选票中的支持率一样。
+下图可以看出来哈里斯和特朗普的score都接近于正态分布。其中川普的score呈现一个对称的趋势，其中最多的score是在50左右。训练集中，川普的score平均数是44.63，方差是24.68。相比之下，哈里斯的score分布有一些偏向于左侧的倾斜。训练集中，哈里斯的score平均数高于特朗普为46.92，方差略低于川普为20.96。值得注意的是川普数据的样本量为3960，而哈里斯只有1636.
 
-## Model validation
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+# Calculate mean, variance, and sample size
+summary_stats <- bind_rows(
+  train_Trump %>% summarise(mean = round(mean(score, na.rm = TRUE), 2), variance = round(var(score, na.rm = TRUE), 2), sample_size = n()) %>% mutate(dataset = "train_Trump"),
+  train_Harris %>% summarise(mean = round(mean(score, na.rm = TRUE), 2), variance = round(var(score, na.rm = TRUE), 2), sample_size = n()) %>% mutate(dataset = "train_Harris")
+)
 
+# Display results using kable
+summary_stats %>%
+  select(dataset, mean, variance, sample_size) %>%
+  kable()
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+# Plot a histogram for the 'pct' variable
+ggplot(train_Trump, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
+  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+ggplot(train_Harris, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
+  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+```
+
+### Predictor
+我们的predictors包含以下变量：
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+predictors <- c("pollscore","methodology","transparency_score","sample_size","population", 
+           "ranked_choice_reallocated", "hypothetical", "duration")
+predictors
+```
+
+下图展示了在川普的训练集中，numerical predictor 之间的关系。没有明显的趋势代表着它们之间没有明显的correlation。
 ```{r, fig.width=10, fig.height=10}
-data2 = raw_data %>% select("pollscore","transparency_score","sample_size")
+#| warning: false
+#| message: false
+#| echo: false
+data2 = train_Trump %>% select("pollscore","transparency_score","sample_size","duration")
 pairs( data2 , main = "Predictor vs predictor")
@@
 
+关于categorical的：。。。。。。。。。。。。。。。。
+
+### alternative models
+最开始我们的模型是
+
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
+Trump_model_0 <- lm(
+  score ~ numeric_grade + pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Trump)
+Harris_model_0 <- lm(
+  score ~ numeric_grade + pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Harris)
+```
+
+因为我们考虑到numeric_grade和pollscore之间有强线性相关，我们舍弃了这一方案。
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+# Plot relationship between numeric_grade and pollscore for train_Trump
+ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  labs(title = "Relationship between Numeric Grade and Pollscore (train_Trump)",
+       x = "Numeric Grade",
+       y = "Pollscore")
+
+# Plot relationship between numeric_grade and pollscore for train_Harris
+ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  labs(title = "Relationship between Numeric Grade and Pollscore (train_Harris)",
+       x = "Numeric Grade",
+       y = "Pollscore")
+```
+
+这个是我们的第二个方案。虽然predictors之间没有了相关性，但是methodology，ranked_choice_reallocated，这两个变量并不statistical significant，因为他们的p value都大于0.05.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+Trump_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Trump)
+Harris_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Harris)
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+# Get the summary of the model
+Harris_summary <- summary(Harris_model_1)
+# Extract coefficients from the summary
+coefficients <- Harris_summary$coefficients
+# Extract p-values
+Harris_p_values <- coefficients[, 4]
+# Create a data frame with the results
+Harris_results_table <- data.frame(
+  Variable = rownames(coefficients),
+  P_Value = format(Harris_p_values, scientific = TRUE)
+)
+Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Harris", col.names = c("Variable", "P-value"))
+# Get the summary of the model
+Trump_summary <- summary(Trump_model_1)
+# Extract coefficients from the summary
+coefficients <- Trump_summary$coefficients
+# Extract p-values
+Trump_p_values <- coefficients[, 4]
+# Create a data frame with the results
+Trump_results_table <- data.frame(
+  Variable = rownames(coefficients),
+  P_Value = format(Trump_p_values, scientific = TRUE)
+)
+Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Trump", col.names = c("Variable", "P-value"))
+
+grid.arrange(tableGrob(Trump_kable), tableGrob(Harris_kable), nrow = 1)
+
+```
+
+因此，我们有有了最后的模型。
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+"
+Trump_model <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical, data = train_Trump)
+Harris_model <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical, data = train_Harris)
+"
+summary(Trump_model)
+summary(Harris_model)
+```
+
+## validation
+从您的结果来看，所有变量的 GVIF 值都在 1 到 1.3 之间，这些数值非常低，表明各个自变量之间的共线性很小，模型并没有因为共线性而受到显著影响。
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+vif(Trump_model)
+vif(Harris_model)
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+par(mfrow=c(2,2))
+plot(Harris_model,1)
+plot(Harris_model,2)
+```
+
+```{r}
+
 par(mfrow=c(2,2))
@@
 plot(Trump_model,2)
+```
+然后就是描述一下response variable是normal的，然后numerical variable没有显著关系（这些在打他部分有讲过）
 
-```
-
-## Predictor variables
+总结，满足了MLR的条件，说明我们的好

### 2024-11-02 scripts/01-test_simulated_data.R
Added more test of simulated data

@@ -1,28 +1,150 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated variables 
+  #of U.S. election candidates
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: 00-simulated_data saved and loaded
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(rstanarm)
+library(testthat)
+library(arrow)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
+analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
+analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
+analysis_data_3 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_3.parquet"))
 
 #### Test data ####
 
+# Load simulated data files
+analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
+analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
+analysis_data_3 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_3.parquet"))
+
+# Convert sample_size to integer if necessary
+analysis_data_1$sample_size <- as.integer(analysis_data_1$sample_size)
+analysis_data_2$sample_size <- as.integer(analysis_data_2$sample_size)
+analysis_data_3$sample_size <- as.integer(analysis_data_3$sample_size)
+
[…]

### 2024-11-02 paper/paper.qmd
model part of paper updated
model part of paper updated

@@
 library(gridExtra)
+library(moments)
 set.seed(912)
@@
 train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
+test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
+test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
+full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
+full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
 Trump_model <- readRDS(here::here("models/Trump_model.rds"))
@@
 ```
-
 52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
 "notes", "url", "url_article", "url_topline", "url_crosstab", "source"
-
 ```{r, fig.height=90, fig.width=90}
@@
 ```
-
 其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
@@
 ```
-
 以及numerical的variables："numeric_grade"      "pollscore"          "transparency_score" "start_date"         "end_date"        "sample_size" "pct"
@@
 ```
-
 描述
@@
 ```
-
 ## Cleaned data
@@
 The remaining variables are as follows:
-
 ```{r, fig.height=90, fig.width=90}
@@
 ```
-
 Next, we calculated the percentage of missing values for each variable across the entire dataset.
@@
 ```
-
 Since the influence of pollsters can be quantified using their ratings, such as 'numeric_grade', 'pollscore', and 'transparency_score', we removed these variables to simplify the dataset and the model.
 Similarly, 'created_at' was also removed due to its strong correlation with 'start_date'.
-At this point, the remaining variables are as follows:
 ```{r}
@@
 ```
-
 Finally, the remaining variables are as follows:
-
 ```{r, fig.height=30, fig.width=30}
@@
 ```
-
 After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
 This new variable represents the number of days between 'start_date' and 'end_date'.Next, we categorized the 51 different methodologies into four levels, ranging from the least reliable and accurate (level_1) to the most reliable (level_4).
-The specific classifications are as follows:
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-mc
-#| tbl-cap: "Methodology classfication"
-
-# Create a summary data frame for the methodologies and their levels
-methodology_summary <- data.frame(
-  Level = c("level 1", "level 2", "level 3", "level 4"),
-  Methodologies = c(
-    paste(c("Email", "Email/Online Ad", "Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Mail-to-Web/Mail-to-Phone", "Online Ad"), collapse = ", "),
-    paste(c("App Panel", "IVR", "IVR/Live Phone/Text/Online Panel/Email", "IVR/Online Panel", "IVR/Online Panel/Email", "IVR/Online Panel/Text-to-Web", "IVR/Online Panel/Text-to-Web/Email", "IVR/Text", "IVR/Text-to-Web", "IVR/Text-to-Web/Email", "Live Phone/Email", "Live Phone/Online Panel/Mail-to-Web", "Live Phone/Text/Online Ad", "Live Phone/Text-to-Web/Email", "Live Phone/Text-to-Web/Email/Mail-to-Web", "Live Phone/Text-to-Web/Online Ad", "Online Panel/Email", "Online Panel/Email/Text-to-Web", "Online Panel/Online Ad", "Text-to-Web/Email", "Text-to-Web/Online Ad"), collapse = ", "),
-    paste(c("IVR/Live Phone/Online Panel", "IVR/Live Phone/Online Panel/Text-to-Web", "IVR/Live Phone/Text", "IVR/Live Phone/Text-to-Web", "Live Phone/Online Panel/App Panel", "Live Phone/Online Panel/Text", "Live Phone/Online Panel/Text-to-Web", "Live Phone/Online Panel/Text-to-Web/Text", "Live Phone/Text", "Live Phone/Text/Online Panel", "Live Phone/Text-to-Web", "Live Phone/Text-to-Web/App Panel", "Online Panel", "Online Panel/Text", "Online Panel/Text-to-Web", "Online Panel/Text-to-Web/Text", "Text", "Text-to-Web"), collapse = ", "),
-    paste(c("Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", "Online Panel/Probability Panel", "Probability Panel"), collapse = ", ")
-  )
-)
-
-# Print the summary of methodologies and their levels using kable
-kable(methodology_summary, col.names = c("Level", "Methodologies")) %>%
-  column_spec(1, width = "1.5cm") %>% # Adjust the width of the first column
-  column_spec(2, width = "13cm")
-```
-In our classification, we primarily considered whether the survey method was active or passive, giving higher scores to methodologies involving active outreach by statistical agencies.
-We then averaged the scores of all methods used in each poll; the higher the average, the higher the assigned level.
 
@@
 Since our results are not exact percentages, we used 'score' to name what would typically be called 'pct'.
-We then used janitor::clean_names to finalize and tidy up the variable names.Next, we extracted the data for each candidate individually.
+We then finalize and tidy up the variable names.
+
+Next, we extracted the data for each candidate individually.
 We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
@@
 The specific weighted scores for the top five candidates are as follows:
-
 ```{r}
@@
 ```
-
 ## Measurement
@@
 # Model
+
 ## Model overview
@@
 
-其中
+值得注意的是我们使用的是Multiple linear regression (MLR), 意味着我们的假设：
+1. 多元线性回归的核心前提是因变量（结果变量）与自变量之间存在线性关系。可以通过散点图直观检查这种线性关系，理想情况下应显示出直线关系而非曲线关系。
+2. 残差（观测值与预测值之间的差异）呈正态分布。可以通过观察Q-Q 图来评估这一假设。
+3. 自变量之间的相关性不过高，即避免多重共线性。这可以通过方差膨胀因子（VIF）来检测。
+4. 同方差性：误差项（残差）的方差应在自变量的所有水平上保持一致。残差与预测值的散点图不应显示出明显的模式。
 
-score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical
+此外，在我们的模型中，duration变量是原数据中“start_date” 和 “end_date” 的差值，这意味着我们的模型无法解释时间序列对结果带来的影响。但是考虑到这两者之间存在的线性关系，我们不得已将其简化，以满足使用MLR的假设。
+
+另外，原数据中methodology有51种不同的总类。categorical variable 过多的种类会增加我们模型的复杂度，因此我们将其简化为了4个level。
+其中level 1 代表该种methodology的可靠性最低，level 4 代表该种methodology的可靠性最高。具体的分类如下：
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-mc
+#| tbl-cap: "Methodology classfication"
+
+# Create a summary data frame for the methodologies and their levels
+methodology_summary <- data.frame(
+  Level = c("level 1", "level 2", "level 3", "level 4"),
+  Methodologies = c(
+    paste(c("Email", "Email/Online Ad", "Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Mail-to-Web/Mail-to-Phone", "Online Ad"), collapse = ", "),
+    paste(c("App Panel", "IVR", "IVR/Live Phone/Text/Online Panel/Email", "IVR/Online Panel", "IVR/Online Panel/Email", "IVR/Online Panel/Text-to-Web", "IVR/Online Panel/Text-to-Web/Email", "IVR/Text", "IVR/Text-to-Web", "IVR/Text-to-Web/Email", "Live Phone/Email", "Live Phone/Online Panel/Mail-to-Web", "Live Phone/Text/Online Ad", "Live Phone/Text-to-Web/Email", "Live Phone/Text-to-Web/Email/Mail-to-Web", "Live Phone/Text-to-Web/Online Ad", "Online Panel/Email", "Online Panel/Email/Text-to-Web", "Online Panel/Online Ad", "Text-to-Web/Email", "Text-to-Web/Online Ad"), collapse = ", "),
+    paste(c("IVR/Live Phone/Online Panel", "IVR/Live Phone/Online Panel/Text-to-Web", "IVR/Live Phone/Text", "IVR/Live Phone/Text-to-Web", "Live Phone/Online Panel/App Panel", "Live Phone/Online Panel/Text", "Live Phone/Online Panel/Text-to-Web", "Live Phone/Online Panel/Text-to-Web/Text", "Live Phone/Text", "Live Phone/Text/Online Panel", "Live Phone/Text-to-Web", "Live Phone/Text-to-Web/App Panel", "Online Panel", "Online Panel/Text", "Online Panel/Text-to-Web", "Online Panel/Text-to-Web/Text", "Text", "Text-to-Web"), collapse = ", "),
+    paste(c("Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", "Online Panel/Probability Panel", "Probability Panel"), collapse = ", ")
+  )
+)
+
+# Print the summary of methodologies and their levels using kable
+kable(methodology_summary, col.names = c("Level", "Methodologies")) %>%
+  column_spec(1, width = "1.5cm") %>% # Adjust the width of the first column
+  column_spec(2, width = "13cm")
+```
+这样分的原因是：。。。。。。。。。。。。。。。
+
+此外，之所以我们只对川普和哈里斯的数据进行比较，预测他们之间谁会竞选成功。是因为我们通过比较所有候选人的加权竞争力得分后发现，前三名：川普，哈里斯，以及拜登与其余候选人差距非常大。@tbl-t5c可以看出其中第三名哈里斯的加权竞争力得分是109501.54是第四名的18822.81分的5.8倍之多。考虑到拜登以及推出参选，我们最后决定只对竞争力最大的川普和哈里斯进行预测。具体加权公式如下：
+
+weighted\_score =  \frac{ {\textstyle \sum_{i=1}^{n}score_i} }{n}\times \frac{ {\textstyle \sum_{i=1}^{n}Sample\_Size_i} }{n}
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-t5c
+#| tbl-cap: "Top 5 Candidates"
+# Find the top 5 candidates.
+candidate_ranking <- raw_data %>%
+  group_by(candidate_name) %>%
+  summarize(
+    poll_count = n(),                    
+    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
+  ) %>%
+  arrange(desc(avg_weighted_pct)) %>%    
+  slice_head(n = 5)                       
+kable(candidate_ranking, col.names = c("candidate", "number of polls", "weighted score"))
+
+```
 
@@
 然后就是描述一下response variable是normal的，然后numerical variable没有显著关系（这些在打他部分有讲过）
+总结，满足了MLR的条件，说明我们的好
+```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 10, fig.width=10}
+# Generate predictions using the model
+plots <- list()
+predictions <- predict(Harris_model, newdata = test_Harris)
 
-总结，满足了MLR的条件，说明我们的好
+actual <- test_Harris$score
+
+results_df <- data.frame(Actual = actual, Predicted = predictions)
+
+# Plot the predicted values vs actual values
+plots[["Harris"]]<-ggplot(results_df, aes(x = predictions, y = actual)) +
+  geom_point(color = "blue") + # Scatter plot of predicted vs actual values
+  labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
+  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + # Add reference line y = x
+  theme_minimal() # Use minimal theme for the plot
+
+# Generate predictions using the model
+predictions_1 <- predict(Trump_model, newdata = test_Trump)
+
+actual_1 <- test_Trump$score
+
+results_df_1 <- data.frame(Actual = actual_1, Predicted = predictions_1)
+
+# Plot the predicted values vs actual values
+plots[["Trump"]] <-ggplot(results_df_1, aes(x = predictions_1, y = actual_1)) +
+  geom_point(color = "blue") + # Scatter plot of predicted vs actual values
+  labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
+  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + # Add reference line y = x
+  theme_minimal() # Use minimal theme for the plot
+
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 8), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+
+# Result
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#select significant values based on variable type of each candidate
+
+# Define the function to select feature values based on variable type
+select_feature_value <- function(data, candidate_name) {
+  feature_values <- list()
+  for (col_name in names(data)) {
+    col_data <- data[[col_name]]
+    # Numeric variables: Choose mean or median based on skewness
+    if (is.numeric(col_data)) {
+      # Check if there are enough valid values to compute skewness
+      if (sum(!is.na(col_data)) > 1) {  # Ensure there is more than one valid value
+        skew_val <- skewness(col_data, na.rm = TRUE)
+        if (!is.na(skew_val) && skew_val < 1) {
+          feature_values[[col_name]] <- mean(col_data, na.rm = TRUE)
+        } else {
+          feature_values[[col_name]] <- median(col_data, na.rm = TRUE)
+        }
+      } else {
+        # Default to median if skewness cannot be computed
+        feature_values[[col_name]] <- median(col_data, na.rm = TRUE)
+      }
+    }
+
+    # Categorical variables: Choose mode (most frequent value)
+    else if (is.character(col_data)) {
+      feature_values[[col_name]] <- Mode(col_data)
+    }
+
+    # Boolean variables: Choose TRUE or FALSE based on which one appears more frequently
+    else if (is.logical(col_data)) {
+      true_count <- sum(col_data, na.rm = TRUE)
+      false_count <- sum(!col_data, na.rm = TRUE)
+      feature_values[[col_name]] <- if (true_count >= false_count) TRUE else FALSE
+    }
+  }
+  # Add the candidate name to the results
+  feature_values[["Candidate"]] <- candidate_name
+  return(feature_values)
+}
+
+# Define a function to calculate the mode (most frequent value)
+Mode <- function(x) {
+  ux <- unique(x)
+  ux[which.max(tabulate(match(x, ux)))]
+}
+
+# Calculate feature values for each candidate
+trump_features <- select_feature_value(full_Trump, "Donald Trump")
+harris_features <- select_feature_value(full_Harris, "Kamala Harris")
+
+# Combine results into a single data frame for easy viewing
+all_candidate_features <- bind_rows(trump_features, harris_features)
+
+# Display the final table of feature values
+print(all_candidate_features)
+
+```
+
+```{r}
+Harris_predict<- round(predict(Harris_model, newdata = harris_features),2)
+Trump_predict <- round(predict(Trump_model, newdata = trump_features),2)
+Harris_predict
+Trump_predict
+```
+
+# Discussion

### 2024-11-02 scripts/03-clean_data.R

@@ -101,6 +101,7 @@ for (candidate in candidates) {
 for (file in c("Trump_cleaned_data.parquet", "Harris_cleaned_data.parquet")) {
   # Read the Parquet file into a data frame
   df <- read_parquet(file.path("data/03-cleaned_data/", file))
+  write_parquet(df, file.path("data/02-analysis_data/00-full", paste0("full_", gsub("_cleaned_data", "", file))))
   # Split the data into 3:7 ratio
   sample_indices <- sample(seq_len(nrow(df)), size = floor(0.3 * nrow(df)))
   df_3 <- df[sample_indices, ]

### 2024-11-02 paper/paper.qmd
result section updated

@@
 Given that Biden has withdrawn from the race, we are now focusing only on the datasets for Trump and Harris for further analysis.
-The specific weighted scores for the top five candidates are as follows:
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-t5c
-#| tbl-cap: "Top 5 Candidates"
-# Find the top 5 candidates.
-candidate_ranking <- raw_data %>%
-  group_by(candidate_name) %>%
-  summarize(
-    poll_count = n(),                    
-    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
-  ) %>%
-  arrange(desc(avg_weighted_pct)) %>%    
-  slice_head(n = 5)                       
-kable(candidate_ranking, col.names = c("candidate", "number of polls", "weighted score"))
 
-```
 Next, we split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
@@
 
-值得注意的是我们使用的是Multiple linear regression (MLR), 意味着我们的假设：
-1. 多元线性回归的核心前提是因变量（结果变量）与自变量之间存在线性关系。可以通过散点图直观检查这种线性关系，理想情况下应显示出直线关系而非曲线关系。
-2. 残差（观测值与预测值之间的差异）呈正态分布。可以通过观察Q-Q 图来评估这一假设。
-3. 自变量之间的相关性不过高，即避免多重共线性。这可以通过方差膨胀因子（VIF）来检测。
-4. 同方差性：误差项（残差）的方差应在自变量的所有水平上保持一致。残差与预测值的散点图不应显示出明显的模式。
+Notably, we used Multiple Linear Regression (MLR), which implies the following assumptions:
 
-此外，在我们的模型中，duration变量是原数据中“start_date” 和 “end_date” 的差值，这意味着我们的模型无法解释时间序列对结果带来的影响。但是考虑到这两者之间存在的线性关系，我们不得已将其简化，以满足使用MLR的假设。
+The core assumption of multiple linear regression is that there is a linear relationship between the dependent variable (outcome) and the independent variables.
+This linear relationship can be visually checked using scatter plots, which ideally should display a straight-line pattern rather than a curve.
+The residuals (the differences between observed and predicted values) should be normally distributed. This assumption can be assessed by examining a Q-Q plot.
+The correlation between independent variables should not be too high, meaning multicollinearity should be avoided. This can be checked using the Variance Inflation Factor (VIF).
+Homoscedasticity: The variance of the error terms (residuals) should be consistent across all levels of the independent variables.
+Residuals plotted against predicted values should not display any obvious pattern.
+Furthermore, in our model, the variable "duration" is derived from the difference between "start_date" and "end_date" in the original data.
+This means our model cannot account for the effects brought by time series, but considering the linear relationship between these two, we simplified it to meet the assumptions of using MLR.
 
-另外，原数据中methodology有51种不同的总类。categorical variable 过多的种类会增加我们模型的复杂度，因此我们将其简化为了4个level。
-其中level 1 代表该种methodology的可靠性最低，level 4 代表该种methodology的可靠性最高。具体的分类如下：
+Additionally, there are 51 different categories for the "methodology" variable in the original dataset.
+Having too many categories for a categorical variable would increase the complexity of our model, so we simplified it into four levels.
+Level 1 represents the lowest reliability of the methodology, while level 4 represents the highest.
+The specific classifications are as follows:
+
 ```{r}
@@
 ```
-这样分的原因是：。。。。。。。。。。。。。。。
+The different methodologies were evaluated based on reliability scores ranging from 1 to 10.
+The scores of 51 combinations were calculated by averaging the individual scores of each methodology in the combination.
+The results were classified into four levels: high reliability (8.5-10), medium-high reliability (7-8.49), medium reliability (5-6.99), and low reliability (below 5).
+Methodologies were scored based on several criteria, including statistical rigor, representativeness, response rate, interaction quality, and cost efficiency.
+High-scoring methodologies, such as those employing strict statistical sampling methods like Probability Panels or those using Live Phone surveys with broad coverage and low refusal rates, received high scores due to their strong representativeness and reliability.
+Medium-high scoring methodologies included Online Panels, which offer good coverage and low cost but are susceptible to self-selection bias, and Text-to-Web methods, which improve response rates but may have limited representativeness depending on the target demographics.
+Medium-scoring methodologies, such as App Panels and IVR (Interactive Voice Response), tend to lack broad representativeness or have limitations in interaction quality, making them suitable for niche audiences but not generalizable to a wider population.
+Low-scoring methodologies, including Email Surveys and methods relying on Online Ads, often suffer from low response rates and significant selection bias, which negatively impact their reliability.
+These scoring criteria ensure that the methodologies are evaluated in a consistent manner, with higher scores reflecting stronger statistical foundations, broader representativeness, and better data quality.
 
-此外，之所以我们只对川普和哈里斯的数据进行比较，预测他们之间谁会竞选成功。是因为我们通过比较所有候选人的加权竞争力得分后发现，前三名：川普，哈里斯，以及拜登与其余候选人差距非常大。@tbl-t5c可以看出其中第三名哈里斯的加权竞争力得分是109501.54是第四名的18822.81分的5.8倍之多。考虑到拜登以及推出参选，我们最后决定只对竞争力最大的川普和哈里斯进行预测。具体加权公式如下：
+Additionally, the reason we only compared the data of Trump and Harris to predict which of them would win the election is that, after comparing the weighted competitiveness scores of all candidates, we found that the top three — Trump, Harris, and Biden — had significantly higher scores than the others.
+As shown in @tbl-t5c, the third-place candidate, Harris, had a weighted competitiveness score of 180714535, which is 5.15 times higher than the fourth-place score of 34987031.
+Considering that Biden has withdrawn from the race, we ultimately decided to only predict between the most competitive candidates, Trump and Harris.
+The specific weighting formula is as follows:
 
-weighted\_score =  \frac{ {\textstyle \sum_{i=1}^{n}score_i} }{n}\times \frac{ {\textstyle \sum_{i=1}^{n}Sample\_Size_i} }{n}
+\begin{align}
+& weighted\_score  = \frac{ {\textstyle \sum_{i  = 1}^{n}score_i} }{n}\times {\textstyle \sum_{i  = 1}^{n}Sample\_Size_i} \\
+& \text{Where: }\notag\\
+&\hspace{1cm}n\text{ represents the number of polls nominating this candidate.}\notag\\
+&\hspace{1cm}Score_i\text{ represents the score obtained by the candidate in the } i^{th}\text{ poll.}\notag\\
+&\hspace{1cm}Sample\_Size_i\text{ represents the sample size of the } i^{th}\text{ poll.}\notag
+\end{align}
+
+```{r}
+# Define the directory path containing the parquet files
+p <- "data/03-cleaned_data"
+parquet_files <- list.files(path = here::here(p), full.names = TRUE)
+
+# Initialize an empty dataframe to store the weighted score for each file
+weighted_scores <- data.frame(Candidate = character(), Weighted_Score = numeric(), stringsAsFactors = FALSE)
+
+# Iterate over each parquet file
+for (file in parquet_files) {
+  # Read the parquet file
+  df <- read_parquet(here::here(file))
+
+  # Calculate the mean of score and sample_size
+  score_mean <- mean(df$score, na.rm = TRUE)
+  sample_size_mean <- mean(df$sample_size, na.rm = TRUE)
+
+  # Calculate the weighted score (multiply by total number of rows)
+  weighted_score <- score_mean * sample_size_mean * nrow(df)
+
+  # Append the result to the weighted_scores dataframe
+  weighted_scores <- rbind(weighted_scores, data.frame(Candidate = sub('_cleaned_data.parquet$', '', basename(file)), Weighted_Score = weighted_score))
+}
+
+# Get the top 5 weighted scores
+top_5_weighted_scores <- weighted_scores %>% 
+  arrange(desc(Weighted_Score)) %>% 
+  head(5)
+
+# Print the top 5 weighted scores using kable
+top_5_weighted_scores %>% kable()
+
+```
 
@@
 # Result
+## featured values used in prediction
+
+In our analysis, we designated specific poll-related features as "featured values" to serve as representative indicators within each candidate's dataset.
+These featured values were chosen to highlight the most impactful aspects of the polling data that consistently influenced the support scores for Donald Trump and Kamala Harris.
+By selecting these representative values, we aimed to streamline the analysis and focus on the factors that most strongly characterized each candidate’s data.
+
+We selected representative feature values for each candidate's dataset by processing each variable based on its type.
+For numeric variables (e.g., numeric_grade, pollscore, transparency_score, duration, sample_size), we determined whether to use the mean or median by evaluating skewness; variables with low skewness used the mean, while more skewed variables used the median to represent typical values.
+Categorical variables (e.g., methodology, population) were represented by the most frequent category, while Boolean variables (e.g., ranked_choice_reallocated, hypothetical) were set to TRUE or FALSE based on the most common value.
+This approach allowed us to capture the key characteristics of each candidate's data in a summarized form.
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#select significant values based on variable type of each candidate
-
-# Define the function to select feature values based on variable type
 select_feature_value <- function(data, candidate_name) {
@@
 
-# Combine results into a single data frame for easy viewing
-all_candidate_features <- bind_rows(trump_features, harris_features)
+# Round numeric columns to two decimal places before pivoting
+all_candidate_features <- all_candidate_features %>%
+  mutate(across(everything(), as.character))  # Convert all columns to character for compatibility in pivot_longer
 
-# Display the final table of feature values
-print(all_candidate_features)
+# Pivot the data to create a vertically aligned table with candidate names in the first row
+all_candidate_features_long <- all_candidate_features %>%
+  pivot_longer(cols = -Candidate, names_to = "Variable", values_to = "Value") %>%
+  pivot_wider(names_from = Candidate, values_from = Value)
+
+# Display the final table with kable
+kable(all_candidate_features_long, caption = "Featured Values for Each Candidate")
 
 ```
+## Prediction result of the linear model
 
-```{r}
-Harris_predict<- round(predict(Harris_model, newdata = harris_features),2)
-Trump_predict <- round(predict(Trump_model, newdata = trump_features),2)
-Harris_predict
-Trump_predict
+Using the selected feature values for each candidate, we applied our trained predictive models to estimate the support levels for Kamala Harris and Donald Trump.
+The bar plot above illustrates the predicted values derived from our analysis.
+According to the model, Kamala Harris has a predicted support value of approximately 47.65, while Donald Trump is predicted to receive a support value of around 43.51.
+These predictions suggest an advantage for Kamala Harris over Donald Trump in terms of expected support within the context of the data used.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Store predictions in a data frame
+predictions <- data.frame(
+  Candidate = c("Kamala Harris", "Donald Trump"),
+  Prediction = c(Harris_predict, Trump_predict)
+)
+
+# Create the bar plot
+ggplot(predictions, aes(x = Candidate, y = Prediction, fill = Candidate)) +
+  geom_bar(stat = "identity", width = 0.5) +
+  labs(title = "Predicted Values for Each Candidate",
+       x = "Candidate",
+       y = "Prediction") +
+  theme_minimal() +
+  theme(legend.position = "none") +
+  geom_text(aes(label = Prediction), vjust = -0.3)
 ```
+## Conclusion
+
+Overall, our approach demonstrates how feature engineering and predictive modeling can offer insights into candidate support based on the available data.
+However, it is important to interpret these results cautiously, as they rely on specific variables and assumptions embedded within the dataset.
+In this analysis, we aggregated representative feature values for each candidate by using the mean or median for numeric variables, the mode for categorical variables, and the most frequent occurrence for Boolean values.
+Further refinement and additional data could enhance the robustness of these predictions, contributing to a more comprehensive forecast in future studies.
 

### 2024-11-02 paper/paper.qmd
graphing updated
graphing updated

@@
 Next, we split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
-```{r}
+```{r, fig.height=30, fig.width=60}
 #| warning: false
@@
 #| echo: false
+#| label: tbl-eoad
+#| tbl-cap: "Example of analysis data"
 kable(head(train_Trump), col.names = names(train_Trump))
@@
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-wsft5c
+#| tbl-cap: "Weighted score for top 5 candidates"
 # Define the directory path containing the parquet files
@@
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-t5c
-#| tbl-cap: "Top 5 Candidates"
-# Find the top 5 candidates.
-candidate_ranking <- raw_data %>%
-  group_by(candidate_name) %>%
-  summarize(
-    poll_count = n(),                    
-    avg_weighted_pct = mean(poll_count * pct, na.rm = TRUE)  
-  ) %>%
-  arrange(desc(avg_weighted_pct)) %>%    
-  slice_head(n = 5)                       
-kable(candidate_ranking, col.names = c("candidate", "number of polls", "weighted score"))
-
-```
-
 ## Model set-up
@@
 #| echo: false
+#| label: tbl-sositd
+#| tbl-cap: "Sumarry of score in training datasets"
 # Calculate mean, variance, and sample size
@@
         if (!is.na(skew_val) && skew_val < 1) {
-          feature_values[[col_name]] <- mean(col_data, na.rm = TRUE)
+          feature_values[[col_name]] <- round(mean(col_data, na.rm = TRUE),2)
         } else {
-          feature_values[[col_name]] <- median(col_data, na.rm = TRUE)
+          feature_values[[col_name]] <- round(median(col_data, na.rm = TRUE),2)
         }
@@
 
+all_candidate_features <- data_frame(trump = trump_features, harris = harris_features)
+
 # Round numeric columns to two decimal places before pivoting
@@
 
-# Pivot the data to create a vertically aligned table with candidate names in the first row
-all_candidate_features_long <- all_candidate_features %>%
-  pivot_longer(cols = -Candidate, names_to = "Variable", values_to = "Value") %>%
-  pivot_wider(names_from = Candidate, values_from = Value)
+all_candidate_features <- head(all_candidate_features, -1)
+
+variables <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
+               "sample_size", "population", "ranked_choice_reallocated", 
+               "hypothetical", "score", "duration")
+
+all_candidate_features$variables <- variables
+
+all_candidate_features <- all_candidate_features[, c("variables", setdiff(names(all_candidate_features), "variables"))]
 
 # Display the final table with kable
-kable(all_candidate_features_long, caption = "Featured Values for Each Candidate")
+kable(all_candidate_features)
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+Harris_predict <- round(predict(Harris_model, newdata = harris_features),2)
+Trump_predict <- round(predict(Trump_model, newdata = trump_features),2)
+
 # Store predictions in a data frame

### 2024-11-02 paper/paper.qmd
paper section combined
paper section combined

@@
 library(moments)
+library(grid)
 set.seed(912)
@@
 # Introduction
+The U.S.
+presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights.
+As the world anticipates the 2024 U.S.
+electoral contest, forecasting the possible outcomes can provide critical insights for policymakers, businesses, and civil society groups.
+Predicting election outcomes has long been one of the most challenging tasks for political scientists, statisticians, and analysts.
+This study aims to predict the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.
+
+To provide a robust prediction, we utilize a "poll-of-polls" approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support.
+Our analysis applies a multilinear regression model, focusing on key variables like pollster reliability, sample size, and duration, which contribute to the prediction of each candidate's support level.
+we aim to predict the percentage of support for the main candidates Kamala Harris and Donald Trump.
+
+The results of our linear model indicate closely matched levels of voter support for both candidates.
+Donald Trump’s predicted support is approximately 45.2%, while Kamala Harris's predicted support is slightly higher at 45.9%.
+These findings suggest that, while both candidates maintain stable support, Harris holds a slight advantage.
+The consistency across both models underlines the importance of accounting for variability in polling methodologies and regional voter bases.
+【等result出来再改】
+
+This study is important because it not only forecasts the immediate electoral outcomes but also provides critical insights into the potential global impact of the U.S.
+presidential election.
+Predicting election results helps global stakeholders—such as policymakers, investors, and international organizations—prepare for possible changes in U.S.
+policy, which could significantly affect trade, climate commitments, and foreign relations, thereby influencing global economic stability and strategic alliances.
+Furthermore, our findings highlight the need for transparency in polling methodologies and emphasize the importance of developing more precise and comprehensive forecasts.
+
+This paper is organized as follows: The next section outlines the data collection and filtering processes, detailing the key variables and sources.
+Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models.
+In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings.
+Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
+【最后改结构描述加cross-reference】
 
@@
 ## Overview
+The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' (Ryan Best and Wiederkehr, 2024).
+FiveThirtyEight is a well-known website recognized for its political, economic, and sports analyses.
+Its polling aggregation methodology is highly regarded in the field, aiming to provide readers with transparent, scientific, and as accurate as possible predictions.
+This polling data is compiled from various polling agencies, encompassing a wide range of demographic information, which serves as an essential basis for analyzing public voting preferences in the upcoming presidential election.
+
+The analysis and visualizations in this paper are based on polling results as of October 22.
+The dataset includes 52 variables and 17,133 samples from various polling sources, asking participants who they support in the upcoming presidential election.
+To ensure accuracy and consistency, the data has been carefully processed and cleaned to remove biases and guarantee data integrity and comparability.
+
+This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S.
+presidential election forecast.
+These packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.
 
@@
       plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
+      axis.title = element_text(size = 20),
+      axis.text = element_text(size = 20)
     )
@@
 ## Measurement
+The method used to forecast the presidential election results is the poll-of-polls, which aggregates results from multiple polls instead of relying on a single survey, aiming to make the results more accurate and stable.
+In this method, each poll is assigned a weight based on factors such as sample size, recency, and the pollster’s historical accuracy.
+
+The dataset used for this prediction is from FiveThirtyEight, which includes scientifically sound public polls that meet methodological standards.
+Polling organizations are rated based on accuracy, transparency, and sample quality, represented by a numeric_grade (ranging from 0.5 to 3.0).
+Higher scores indicate greater reliability.
+The histogram of numeric_grade values shows a concentration around scores of 2 and 3, suggesting most pollsters are of moderate to good quality.
+
+Polling organizations use different survey methods but follow similar principles.
+They select representative samples, publish surveys through chosen platforms, and aim to ask clear, unbiased questions.
+YouGov, discussed in the appendix, is one such example.
+
+Survey data accuracy is limited by several factors.
+Sampling bias can lead to an unrepresentative sample, underrepresenting certain demographics.
+Response bias may occur if participants are not truthful or are influenced by question phrasing.
+Platform differences also impact reliability, as social media polls may attract different audiences compared to phone or in-person surveys.
+Pollscore and numeric grade filters help ensure quality, but they are based on historical data and may not reflect current survey quality.
+Additionally, the rapidly changing political narrative and voter sentiment during campaigns can affect polling accuracy.
+These factors contribute to inaccuracies in survey results, affecting the reliability of aggregated data.
 
@@
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+```{r, fig.pos="H", fig.height=30, fig.width=60}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-dositd
+#| fig-cap: "Distribution of scores in training dataset"
+
+plots <- list()
 # Plot a histogram for the 'pct' variable
-ggplot(train_Trump, aes(x = score)) +
+plots[["Trump"]]<-ggplot(train_Trump, aes(x = score)) +
   geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
   labs(title = "Histogram of pct", x = "pct", y = "Frequency")
-ggplot(train_Harris, aes(x = score)) +
+plots[["Harris"]]<-ggplot(train_Harris, aes(x = score)) +
   geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
   labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(20, 20), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
 ```
@@
 因为我们考虑到numeric_grade和pollscore之间有强线性相关，我们舍弃了这一方案。
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+```{r, fig.pos="H", fig.height=10, fig.width=10}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-rbnap
+#| fig-cap: "Relationship between numeric_grade and pollscore"
+
+plots <- list()
 # Plot relationship between numeric_grade and pollscore for train_Trump
-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
+plots[["Trump"]]<-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
   geom_point() +
@@
 # Plot relationship between numeric_grade and pollscore for train_Harris
-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
+plots[["Harris"]]<-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
   geom_point() +
@@
        y = "Pollscore")
+
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 10), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
 ```
@@
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+```{r, fig.height=100,fig.width=100}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-alovitahm
+#| tbl-cap: "Significant level of variblaes in the aboanded Harris's model"
 # Get the summary of the model
@@
 )
-Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Harris", col.names = c("Variable", "P-value"))
+Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Model for Harris", col.names = c("Variable", "P-value"))
+
+Harris_kable
+
+```
+
+```{r, fig.height=100,fig.width=100}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-alovitatm
+#| tbl-cap: "Significant level of variblaes in the aboanded Trump's model"
+
 # Get the summary of the model
@@
 )
-Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Trump", col.names = c("Variable", "P-value"))
-
-grid.arrange(tableGrob(Trump_kable), tableGrob(Harris_kable), nrow = 1)
-
+Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Model for Trump", col.names = c("Variable", "P-value"))
+
+Trump_kable
 ```
@@
 因此，我们有有了最后的模型。
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-"
-Trump_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical, data = train_Trump)
-Harris_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical, data = train_Harris)
-"
-summary(Trump_model)
-summary(Harris_model)
-```
 
@@
 #| echo: false
-vif(Trump_model)
-vif(Harris_model)
+#| label: tbl-vohfm
+#| tbl-cap: "VIF of Harris's final model"
+# Add a column for variable names (convert row names to a column)
+
+harris_vif <- vif(Harris_model)
+
+# 将 VIF 结果转换为数据框
+# 如果是 GVIF（针对多分类变量），则处理为数据框
+
+harris_vif_df <- as.data.frame(harris_vif)
+
+harris_vif_df$Variable <- rownames(harris_vif_df)
+
+# Rearrange columns so that the variable name column is the first column
+
+harris_vif_df <- harris_vif_df[, c(ncol(harris_vif_df), 1:(ncol(harris_vif_df)-1))]
+
+# Use kable to create a formatted table from VIF results
+
+kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
+
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-votfm
+#| tbl-cap: "VIF of Trump's final model"
+
+trump_vif <- vif(Trump_model)
+
+# 将 VIF 结果转换为数据框
+# 如果是 GVIF（针对多分类变量），则处理为数据框
+trump_vif_df <- as.data.frame(trump_vif)
+
+# Add a column for variable names (convert row names to a column)
+trump_vif_df$Variable <- rownames(trump_vif_df)
+
+# Rearrange columns so that the variable name column is the first column
+trump_vif_df <- trump_vif_df[, c(ncol(trump_vif_df), 1:(ncol(trump_vif_df)-1))]
+
+# Use kable to create a formatted table from VIF results
+
+kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
+
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-dffp
+#| tbl-cap: "Datas for final prediction"
+
 select_feature_value <- function(data, candidate_name) {
@@
 # Discussion
+
+# Appendix
+
+## Analysis of YouGov Pollster Methodology
+
+In this appendix, we provide a deep-dive analysis of the methodology employed by YouGov, one of the pollsters included in our sample.
+YouGov is an international online research data and analytics technology group.
+It is a leading platform for online survey, which has a continuously growing dataset of over 27 million registered members.
+This pollster has a 3.0 grade according to FiveThirtyEight, which is the highest score.
+This analysis covers key aspects of YouGov's survey methodology, highlighting its strengths, weaknesses, and the unique features of its approach.
+
+### Population, Frame, and Sample
+
+YouGov utilizes an online panel to collect survey responses, with participants drawn from a broad population base, which typically comprises all U.S.
+adults citizens.
+Respondents are chosen based on a non-probability sampling, which means not everyone in the population has an equal chance of being selected.
+However, the sample is adjusted using statistical weighting to better represent the target population.
+The sampling frame consists of individuals who have signed up to participate in surveys, representing a range of demographic characteristics.
+However, as an online panel, there may be limitations regarding coverage bias, particularly for individuals with limited internet access.
+
+### Sample Recruitment
+
+YouGov recruits participants through online advertisements and other digital marketing techniques,  with surveys offers surveys in multiple languages.
+The recruitment process is designed to ensure that the panel is as representative as possible.
+For instance, YouGov collects information such as email addresses and IP addresses when new members join the panel.
+Additionally, YouGov monitors survey completion time and answer consistency to ensure the data is accurate.
+Respondents who fail quality checks are removed.
+
+### Sampling Approach and Trade-offs
+
+YouGov employs a form of quota sampling combined with weighting adjustments to make the sample representative of the target population.
+To ensure representativeness, YouGov selects respondents based on key demographic characteristics such as age, gender, race, education, and voting behavior.
+These characteristics are used to set quotas, and the sample is adjusted with statistical weighting to align with the distribution of these characteristics in the target population.
+For example, if a particular demographic group is underrepresented in the sample, their responses are given greater weight to correct the imbalance.
+One trade-off of this method is that, although it helps improve representativeness, it may not fully eliminate selection bias due to the reliance on an online panel, which can lead to overrepresentation or underrepresentation of certain groups.
+Additionally, the process of weighting adjustments may introduce additional errors if the weights are inaccurate or if certain groups are given disproportionately high weights, leading to increased variability and potential bias in the final results.
+
+### Handling Non-response
+
+Non-response is managed by using statistical weighting to adjust the sample to more closely reflect the demographic makeup of the target population.
+While this helps mitigate some of the biases associated with non-response, it cannot fully account for differences between respondents and non-respondents, especially when non-response is correlated with key survey variables.
+
+### Strengths and Weaknesses of the Questionnaire
+
+The YouGov questionnaire is well-designed to capture a wide range of attitudes and behaviors.
+The use of standardized questions ensures consistency across surveys, allowing for longitudinal analysis.
+However, as an online survey, there is the risk of respondents providing socially desirable answers or rushing through the survey without providing thoughtful responses.
+Additionally, the format may limit the depth of responses compared to in-person interviews.
+
+Overall, YouGov's methodology provides a cost-effective and timely approach to data collection, particularly useful for understanding trends across large populations.
+However, the use of an online panel introduces certain limitations that must be acknowledged when interpreting the results.
+
+## Ideal Methodology and Survey for Predicting the U.S. Presidential Election
+
+### Budget Overview
+With a budget of $100,000, the goal is to design an efficient and representative method for predicting the U.S.
+presidential election.
+This methodology will include sampling strategies, respondent recruitment, data validation, poll aggregation, and survey implementation details.
+
+### Sampling Methodology
+A stratified sampling approach will be used to ensure diversity and representation.
+The population will be divided into relevant strata such as age, gender, geographic region, race, and political affiliation.
+This approach ensures that each subgroup is adequately represented, thereby reducing sampling bias.
+
+### Respondent Recruitment
+Respondents will be recruited through online panels.
+Partnerships with established survey platforms and third-party providers will help reach a broad and representative group of participants, such as through platforms like Instagram, YouTube, and various news websites.
+Small monetary compensation or gift cards will be offered as incentives to encourage participation.
+Additional incentives will be provided to underrepresented groups, such as individuals with lower educational attainment or residents of rural areas, to ensure more inclusive recruitment.
+The aim is for a sample size of approximately 10,000 respondents, which would achieve a margin of error of ±1% at a 95% confidence level.
+
+### Data Validation
+Data validation will involve cross-referencing respondent demographic information with census data to confirm representativeness.
+Additionally, responses will be reviewed for accuracy, and suspicious or incomplete answers will be flagged for further inspection.
+Responses completed too quickly or that include repeated answers such as "prefer not to say" or "other" will be discarded.
+IP addresses will be tracked to prevent duplicate submissions.
+
+### Poll Aggregation and Methodology Features
+Once all responses are collected, weights will be applied according to electoral demographics and voter turnout to ensure the sample represents the U.S.
+population.
+Poll aggregation will also involve adjustments for known biases, such as overreporting in certain demographic groups or historical voting trends.
+Bayesian updating will be used to refine predictions continuously as more data becomes available.
+
+### Survey Implementation
+The survey will be implemented using Google Forms, which allows for easy distribution and data collection.
+The survey will include questions related to voter preferences, key issues, and demographic information.
+Questions will be designed to minimize leading language and provide a range of response options to avoid bias.
+Keeping the survey brief (approximately 5 minutes with 12 questions) will help maintain respondent focus.
+
+### Budget Allocation
+- $60K for Recruitment Costs and Survey Platform Fees, including advertising
+- $10K for respondent incentives
+- $20K for data processing, weighting, and modeling
+- $10K for data security and administrative costs
+
+### Survey Link and Copy
+The Google Forms survey link will be included here: https://docs.google.com/forms/d/e/1FAIpQLSdcd_neJf83lJMZGzmcUcPkDd-R1vPk98gPIDsD4KC_X6T8tQ/viewform.
+
+The survey questions are listed below: 
+1. **What is your age group?** 
+   - 18-24
+   - 25-34
+   - 35-44
+   - 45-54
+   - 55+
+
+2. **What is your gender?**
+   - Male
+   - Female
+   - Non-binary
+   - Prefer not to say
+
+3. **What is your ethnicity?**
+   - White
+   - Black or African American
+   - Asian
+   - Hispanic or Latino
+   - Native American or Alaska Native
+   - Two or more races
+   - Other
+   - Prefer not to say
+
+4. **In which state do you currently reside?** *(Open-ended response)*
+
+5. **What is your highest level of education completed?**
+   - High school
+   - Associate degree
+   - Bachelor's degree
+   - Other/Prefer not to say
+
+6. **What is your political affiliation?**
+   - Democrat
+   - Republican
+   - Independent
+   - Other/Prefer not to say
+
+7. **How likely are you to vote in the upcoming presidential election?** *(Scale of 1-5)*
+
+8. **Which candidate do you currently support for president?**
+   - Kamala Harris
+   - Donald Trump
+   - Other
+
+9. **What is the most important issue to you in the upcoming election?**
+   - Economy
+   - Healthcare
+   - Education
+   - Climate change
+   - Other/Prefer not to say
+
+10. **What do you consider your economic status?**
+    - Lower class
+    - Lower-middle class
+    - Middle class
+    - Upper-middle class
+    - Upper class
+    - Prefer not to say
+
+11. **How would you describe your household's financial situation compared to last year?**
+    - Better
+    - Worse
+    - About the same
+    - Prefer not to say
+
+12. **How satisfied are you with the current administration's handling of key issues?** *(Scale of 1-5)*
+
+## Raw data full descriptions
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-rdd
+#| fig-cap: "Raw Data Distribution"
+
+# Define variable groups
+set1_vars <- c("pollster_rating_id", "pollster_id", "sponsor_candidate_id", "sponsor_candidate_party")
+set2_vars <- c("tracking", "internal", "partisan")
+set3_vars <- c("sponsor_ids", "question_id", "internal", "race_id")
+
+# Define a function to generate a grid of plots for a given set of variables with increased text size
+plot_variable_distributions <- function(data, vars) {
+  plots <- list()
+  for (var in vars) {
+    if (is.numeric(data[[var]])) {
+      p <- ggplot(data, aes(x = .data[[var]])) +
+        geom_histogram(bins = 30, fill = "steelblue", color = "black") +
+        labs(title = var) +
+        theme_minimal() +
+        theme(
+          plot.title = element_text(size = 18, face = "bold"),
+          axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+          axis.text.x = element_blank(),
+          axis.text.y = element_blank()
+        )
+    } else {
+      p <- ggplot(data, aes(x = .data[[var]])) +
+        geom_bar(fill = "steelblue", color = "black") +
+        labs(title = var) +
+        theme_minimal() +
+        theme(
+          plot.title = element_text(size = 18, face = "bold"),
+          axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+          axis.text.y = element_blank(),
+          axis.text.x = element_text(size = 14, angle = 45, hjust = 1)
+        )
+    }
+    plots[[var]] <- p
+  }
+  return(plots)
+}
+
+# Generate plots for each set of variables
+plot1 <- plot_variable_distributions(raw_data, set1_vars)
+plot2 <- plot_variable_distributions(raw_data, set2_vars)
+plot3 <- plot_variable_distributions(raw_data, set3_vars)
+
+# Arrange the first three sets of plots into grids and display them
+grid.arrange(grobs = plot1, ncol = 2, top = textGrob("Distribution of Variables (Set 1)", gp=gpar(fontsize=20, fontface="bold")))
+grid.arrange(grobs = plot2, ncol = 2, top = textGrob("Distribution of Variables (Set 2)", gp=gpar(fontsize=20, fontface="bold")))
+grid.arrange(grobs = plot3, ncol = 2, top = textGrob("Distribution of Variables (Set 3)", gp=gpar(fontsize=20, fontface="bold")))
+
+# Separate set4, set5, and set6 variables for individual adjustments
+
+# Set 4: State Plot (excluding NA)
+state_plot <- raw_data %>%
+  filter(!is.na(state)) %>%  
+  count(state, sort = TRUE) %>%
+  top_n(10) %>%
+  ggplot(aes(y = reorder(state, n), x = n)) +
+  geom_bar(stat = "identity", fill = "steelblue", color = "black") +
+  labs(title = "Distribution of State (Set 4)") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 20, face = "bold"),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text.x = element_text(size = 12),
+    axis.text.y = element_text(size = 12)
+  )
+
+# Set 5: ranked_choice_round_plot Plot (excluding NA)
+ranked_choice_round_plot <- raw_data %>%
+  filter(!is.na(ranked_choice_round)) %>%  
+  ggplot(aes(x = ranked_choice_round)) +
+  geom_density(fill = "steelblue", alpha = 0.7) +
+  labs(title = "Distribution of ranked_choice_round (Set 5)") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 20, face = "bold"),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
+    axis.text.y = element_text(size = 12)
+  )
+
+created_at_plot <- raw_data %>%
+  filter(!is.na(created_at)) %>%  # 去掉NA值
+  ggplot(aes(x = as.POSIXct(created_at, format = '%m/%d/%y %H:%M'))) +
+  geom_density(fill = "steelblue", alpha = 0.7) +
+  labs(title = "Distribution of Created At (Set 8)") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 20, face = "bold"),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
+    axis.text.y = element_text(size = 12)
+  )
+
+# Display each plot individually
+print(state_plot)
+print(ranked_choice_round_plot)
+print(created_at_plot)
+```

### 2024-11-02 paper/paper.qmd
Add discussion
Add discussion

@@
 # Discussion
+## Study Overview
+This paper presents a predictive analysis of voter support for 2024 U.S.
+presidential candidates Kamala Harris and Donald Trump.
+Using a “poll-of-polls” approach, it integrates polling data from diverse sources, emphasizing reliability, sample size, and methodology.
+Linear and Bayesian models were applied to improve prediction accuracy.
+
+## Key Insights
+The analysis provides two key insights.
+First, our model predicts a slight advantage for Kamala Harris, with a support estimate of 47.6% compared to Donald Trump’s 43.5%, indicating a competitive but narrow lead.
+Second, it underscores the impact of poll reliability on predictive accuracy.
+Traditional methods like live phone surveys show greater accuracy than online methods, reinforcing the importance of reliability-weighted data in improving forecast precision.
+
+## Limitations
+This analysis is limited by its use of static variables, which may not capture shifts in public opinion.
+For instance, major events like debates can influence voter sentiment, yet the model lacks real-time responsiveness.
+Additionally, aggregating data from different poll methodologies may introduce bias; for example, online panels may skew younger while live phone surveys often favor older demographics.
+Future work could include real-time data and refined weighting to enhance adaptability and consistency.
+
+## Future Directions
+Future research could incorporate time series analysis to track evolving voter sentiment and add demographic or economic factors for greater precision.
+Integrating social media sentiment and machine learning could provide deeper insights into regional voting patterns.
 

### 2024-11-02 paper/paper.qmd
Update paper.qmd
drop subtitles of discussion

@@
 # Discussion
-## Study Overview
+
 This paper presents a predictive analysis of voter support for 2024 U.S.
@@
 
-## Key Insights
 The analysis provides two key insights.
@@
 
-## Limitations
 This analysis is limited by its use of static variables, which may not capture shifts in public opinion.
@@
 
-## Future Directions
 Future research could incorporate time series analysis to track evolving voter sentiment and add demographic or economic factors for greater precision.

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Add introduction

@@
 The U.S.
-presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights.
-As the world anticipates the 2024 U.S.
-electoral contest, forecasting the possible outcomes can provide critical insights for policymakers, businesses, and civil society groups.
-Predicting election outcomes has long been one of the most challenging tasks for political scientists, statisticians, and analysts.
-This study aims to predict the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.
-
-To provide a robust prediction, we utilize a "poll-of-polls" approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support.
-Our analysis applies a multilinear regression model, focusing on key variables like pollster reliability, sample size, and duration, which contribute to the prediction of each candidate's support level.
-we aim to predict the percentage of support for the main candidates Kamala Harris and Donald Trump.
-
-The results of our linear model indicate closely matched levels of voter support for both candidates.
-Donald Trump’s predicted support is approximately 45.2%, while Kamala Harris's predicted support is slightly higher at 45.9%.
-These findings suggest that, while both candidates maintain stable support, Harris holds a slight advantage.
-The consistency across both models underlines the importance of accounting for variability in polling methodologies and regional voter bases.
-【等result出来再改】
-
-This study is important because it not only forecasts the immediate electoral outcomes but also provides critical insights into the potential global impact of the U.S.
-presidential election.
-Predicting election results helps global stakeholders—such as policymakers, investors, and international organizations—prepare for possible changes in U.S.
-policy, which could significantly affect trade, climate commitments, and foreign relations, thereby influencing global economic stability and strategic alliances.
-Furthermore, our findings highlight the need for transparency in polling methodologies and emphasize the importance of developing more precise and comprehensive forecasts.
-
-This paper is organized as follows: The next section outlines the data collection and filtering processes, detailing the key variables and sources.
-Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models.
-In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings.
-Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
+presidential election has profound implications on a global scale, shaping international relations, economic policy, and key social issues.
+As the 2024 election approaches, the ability to accurately forecast potential outcomes is essential for policymakers, businesses, and organizations seeking to anticipate shifts in U.S.
+policy that may affect trade, climate commitments, and strategic alliances (BBC News, 2024).
+Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning (Euronews, 2024).
+However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting (University of Oregon, 2024).
+Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further (Yale University, 2022).
+
+This study seeks to address these complexities by examining voter support for the 2024 presidential candidates Kamala Harris and Donald Trump.
+While substantial polling data exists, current aggregation methods often lack consistency and fail to adequately consider critical factors such as poll reliability and sample size, leading to unreliable predictions.
+To address this gap, the present study adopts a “poll-of-polls” methodology, drawing from multiple data sources at both national and state levels.
+Through the application of multiple linear regression models, the study integrates essential variables, including pollster reliability, sample size, and polling duration, to produce a forecast that is both stable and transparent.
+
+The findings suggest a slight advantage for Harris, with a predicted support level of 47.6% compared to Trump’s 43.5%.
+This marginal lead underscores the importance of methodological rigor, as systematically weighting data by reliability yields more consistent and interpretable predictions.
+The results indicate that while both candidates retain substantial support, polling methods and demographic representation can subtly shift the support dynamics, providing a deeper understanding of the electoral landscape beyond basic polling figures.
+
+This paper is structured as follows: first, the data collection and filtering processes are outlined, followed by a description of the methodological framework, introducing linear modeling approaches.
+The results are then presented and analyzed, with a discussion on broader implications.
+The paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
+
  【最后改结构描述加cross-reference】

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Add packages citation to introduction

@@
 
+This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S.
+presidential election.
+These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
  【最后改结构描述加cross-reference】

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Add estimand description

@@
 
+The estimand in this study represents the expected level of voter support for each primary candidate, Kamala Harris and Donald Trump, based on aggregated polling data across diverse demographics and polling methodologies.
+This measure aims to capture the central tendency of public opinion, adjusted for polling reliability and sample characteristics, to provide a stable estimate of each candidate's projected support under current conditions.
+By centering on this estimand, the analysis offers a robust and interpretable forecast applicable for strategic decision-making in both political and economic contexts.
+
 The findings suggest a slight advantage for Harris, with a predicted support level of 47.6% compared to Trump’s 43.5%.

### 2024-11-03 paper/paper.qmd
Update abstract of this paper

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study aggregates polling data to forecast 2024 U.S.
+presidential candidate support for Kamala Harris and Donald Trump.
+Employing linear models with adjustments, the analysis finds a modest lead for Harris at 47.6% compared to Trump’s 43.5%.
+The results demonstrate that rigorously weighted polling data enhances forecast stability, offering valuable insights for political and economic decision-makers."
 format: pdf

### 2024-11-03 paper/paper.qmd
Update abstract

--- 2024-11-03 paper/paper.qmd
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study aggregates polling data to forecast support for 2024 U.S.
+presidential candidates Kamala Harris and Donald Trump.
+By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%.
+The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
 format: pdf

### 2024-11-03 paper/paper.qmd
Update paper.qmd
Update graphs in data

@@
 #| fig-cap: "Boolean variables"
+
+# Create a list to store the plots
 plots <- list()
-# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
+
+# Bar chart for 'ranked_choice_reallocated' with count labels
 plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
+  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
+  labs(title = "Bar Chart of Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
   theme_minimal(base_size = 15) +
@@
     axis.text = element_text(size = 10)
-  )
-
+  ) +
+  ylim(0, max(table(raw_data$ranked_choice_reallocated)) * 1.2)  # Increase y-axis limit to fit labels
+
+# Bar chart for 'hypothetical' with count labels
 plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Hypothetical", x = "Hypothetical", y = "Count") +
+  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
+  labs(title = "Bar Chart of Hypothetical", x = "Hypothetical", y = "Count") +
   theme_minimal(base_size = 15) +
@@
     axis.text = element_text(size = 10)
-  )
+  ) +
+  ylim(0, max(table(raw_data$hypothetical)) * 1.2)  # Increase y-axis limit to fit labels
 
 # Combine and print the plots using patchwork
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(3, 4), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 2) +
   plot_annotation(
@@
   )
+
 # Print the combined plot
@@
 
+# Create a list to store the plots
 plots <- list()
-# Find the top 3 most frequent values in 'methodology' and group others as 'Other'
+
+# Top 3 Methodologies with 'Other' grouped
 methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
@@
 raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
-# Create a bar chart for the grouped 'methodology'
+
+# Create horizontal bar chart for 'methodology'
 plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Top 3 Methodologies and Others", x = "Methodology", y = "Count") +
-  theme_minimal(base_size = 15) +
+  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
+  labs(title = "Top 3 Methodologies and Others", x = "Count", y = "Methodology") +
+  theme_minimal(base_size = 24) +  # Increase base size for all text elements
   theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
+    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
+    axis.title = element_text(size = 28),  # Axis title font size
+    axis.text = element_text(size = 24)  # Axis text font size
+  ) +
+  coord_flip()
+
+# Population bar chart
 plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Population", x = "Population", y = "Count") +
-  theme_minimal(base_size = 15) +
+  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
+  labs(title = "Population", x = "Count", y = "Population") +
+  theme_minimal(base_size = 24) +  # Increase base size for all text elements
   theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
-# Find the top 3 most frequent values in 'answer' and group others as 'Other'
+    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
+    axis.title = element_text(size = 28),  # Axis title font size
+    axis.text = element_text(size = 24)  # Axis text font size
+  ) +
+  coord_flip()
+
+# Top 3 Answers with 'Other' grouped
 answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
@@
 raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
-# Create a bar chart for the grouped 'answer'
+
+# Create horizontal bar chart for 'answer'
 plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Top 3 answer and Others", x = "answer", y = "Count") +
-  theme_minimal(base_size = 15) +
+  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
+  labs(title = "Top 3 Answers and Others", x = "Count", y = "Answer") +
+  theme_minimal(base_size = 24) +  # Increase base size for all text elements
   theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
+    axis.title = element_text(size = 28),  # Axis title font size
+    axis.text = element_text(size = 24)  # Axis text font size
+  ) +
+  coord_flip()
+
+# Combine the plots using patchwork
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 32)
+    )
+  )
+
 # Print the combined plot
 print(combined_plot)
-```
-以及numerical的variables："numeric_grade"      "pollscore"          "transparency_score" "start_date"         "end_date"        "sample_size" "pct"
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-numer <- droped_data %>% select(-any_of(catego))
+
 ```
@@
 #| fig-cap: "Distribution of numerical varibales part 1"
+
 ### Create Plots for Numeric Variables ###
@@
 plots <- list()
-# Loop through selected numeric variables and plot their distributions
+
+# Loop through selected numeric variables and plot their distributions with a line connecting bar tops
 for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
+  # Calculate bin counts and midpoints
+  bin_data <- ggplot_build(
+    ggplot(raw_data, aes_string(x = variable)) +
+      geom_histogram(binwidth = 0.5)
+  )$data[[1]]
+
+  # Calculate the midpoint of each bin for line plotting
+  bin_data <- bin_data %>%
+    mutate(midpoint = (xmin + xmax) / 2)
+
+  # Create histogram plot with line connecting the bar tops
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
@@
     labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 30) +
+    theme_minimal(base_size = 24) +  # Adjusted base font size for readability
     theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 20),
-      axis.text = element_text(size = 20)
-    )
-}
+      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
+      axis.title = element_text(size = 35),  # Axis title font size
+      axis.text = element_text(size = 35)  # Axis text font size
+    )
+}
+
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+# Combine all individual plots into one vertical layout
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 35)
+    )
+  )
+
 # Print the combined plot
 print(combined_plot)
+
 ```
@@
 #| fig-cap: "Distribution of numerical varibales part 2"
+
 ### Create Plots for Numeric Variables ###
@@
 plots <- list()
+
 # Loop through selected numeric variables and plot their distributions
 for (variable in names(numer %>% select(sample_size, pct))) {
+  if (variable == "sample_size") {
+    # For sample_size, focus on the range 0-20000
+    plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+      geom_histogram(binwidth = 500, fill = "#69b3a2", color = "black", alpha = 0.8) +
+      xlim(0, 10000) +  # Set x-axis limits to focus on 0-10000 range
+      labs(title = "Distribution of Sample Size (0-10000)", x = variable, y = "Frequency") +
+      theme_minimal(base_size = 24) +
+      theme(
+        plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
+        axis.title = element_text(size = 30),  # Larger axis title font size
+        axis.text = element_text(size = 28)  # Larger axis text font size
+      )
+  } else {
+    # For other variables, keep the full range
     plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
@@
       labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 30) +
+      theme_minimal(base_size = 24) +
       theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
-    )
-}
+        plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
+        axis.title = element_text(size = 30),  # Larger axis title font size
+        axis.text = element_text(size = 28)  # Larger axis text font size
+      )
+  }
+}
+
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 8), "in")) +
+# Combine all individual plots into one vertical layout
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 35)
+    )
+  )
+
 # Print the combined plot
 print(combined_plot)
+
 ```
@@
 raw_data$end_date <- ymd(raw_data$end_date)
+
 # Define the date variables to plot
 date_variables <- c("start_date", "end_date")
+
 ### Create Plots for Date Variables ###
-# Loop through selected date variables and plot their distributions
+# Create a list to store plots
 plots <- list()
-for (variable in names(numer %>% select(start_date, end_date))) {
+
+# Loop through selected date variables and plot their distributions with a density curve
+for (variable in date_variables) {
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
-    geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    geom_histogram(fill = "#69b3a2", color = "black", alpha = 0.8) +  # Keep the original binwidth
     labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-        theme_minimal(base_size = 30) +
+    theme_minimal(base_size = 24) +
     theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
-    )
-}
+      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
+      axis.title = element_text(size = 30),  # Larger axis title font size
+      axis.text = element_text(size = 28)  # Larger axis text font size
+    )
+}
+
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 4), "in")) +
+# Arrange the plots vertically without changing their individual orientation
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 35)
+    )
+  )
+
 # Print the combined plot

### 2024-11-03 scripts/06-model_data.R
Update 06-model_data.R
update preamble

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: use train data to train linear model of Trump and Harris
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-11-03 paper/paper.qmd
Update paper.qmd
change title and subtitle

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Forecasting the 2024 U.S. Presidential Election: Comparative Support Analysis of Kamala Harris and Donald Trump"
+subtitle: "Predictive Models Indicate a Narrow Advantage for Harris in a Closely Contested Race"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+  - Haowei Fan
+  - Fangning Zhang
+  - Shaotong Li
+thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
 date: today
@@
 format: pdf
-number-sections: true
+toc: true           
+toc-title: "Table of Contents" 
+toc-depth: 2    
+number_sections: true    
 bibliography: references.bib

### 2024-11-03 paper/paper_HP.qmd
paper frist draft updated
paper frist draft updated

--- 2024-11-03 paper/paper.qmd
@@
 date-format: long
-abstract: "This study aggregates polling data to forecast support for 2024 U.S.
-presidential candidates Kamala Harris and Donald Trump.
-By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%.
-The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
+abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 format: pdf
@@
 The U.S.
-presidential election has profound implications on a global scale, shaping international relations, economic policy, and key social issues.
-As the 2024 election approaches, the ability to accurately forecast potential outcomes is essential for policymakers, businesses, and organizations seeking to anticipate shifts in U.S.
-policy that may affect trade, climate commitments, and strategic alliances (BBC News, 2024).
-Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning (Euronews, 2024).
-However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting (University of Oregon, 2024).
-Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further (Yale University, 2022).
-
-This study seeks to address these complexities by examining voter support for the 2024 presidential candidates Kamala Harris and Donald Trump.
-While substantial polling data exists, current aggregation methods often lack consistency and fail to adequately consider critical factors such as poll reliability and sample size, leading to unreliable predictions.
-To address this gap, the present study adopts a “poll-of-polls” methodology, drawing from multiple data sources at both national and state levels.
-Through the application of multiple linear regression models, the study integrates essential variables, including pollster reliability, sample size, and polling duration, to produce a forecast that is both stable and transparent.
-
-The estimand in this study represents the expected level of voter support for each primary candidate, Kamala Harris and Donald Trump, based on aggregated polling data across diverse demographics and polling methodologies.
-This measure aims to capture the central tendency of public opinion, adjusted for polling reliability and sample characteristics, to provide a stable estimate of each candidate's projected support under current conditions.
-By centering on this estimand, the analysis offers a robust and interpretable forecast applicable for strategic decision-making in both political and economic contexts.
-
-The findings suggest a slight advantage for Harris, with a predicted support level of 47.6% compared to Trump’s 43.5%.
-This marginal lead underscores the importance of methodological rigor, as systematically weighting data by reliability yields more consistent and interpretable predictions.
-The results indicate that while both candidates retain substantial support, polling methods and demographic representation can subtly shift the support dynamics, providing a deeper understanding of the electoral landscape beyond basic polling figures.
-
-This paper is structured as follows: first, the data collection and filtering processes are outlined, followed by a description of the methodological framework, introducing linear modeling approaches.
-The results are then presented and analyzed, with a discussion on broader implications.
-The paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
-
-This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S.
+presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights.
+As the world anticipates the 2024 U.S.
+electoral contest, forecasting the possible outcomes can provide critical insights for policymakers, businesses, and civil society groups.
+Predicting election outcomes has long been one of the most challenging tasks for political scientists, statisticians, and analysts.
+This study aims to predict the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.
+
+To provide a robust prediction, we utilize a "poll-of-polls" approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support.
+Our analysis applies a multilinear regression model, focusing on key variables like pollster reliability, sample size, and duration, which contribute to the prediction of each candidate's support level.
+we aim to predict the percentage of support for the main candidates Kamala Harris and Donald Trump.
+
+The results of our linear model indicate closely matched levels of voter support for both candidates.
+Donald Trump’s predicted support is approximately 45.2%, while Kamala Harris's predicted support is slightly higher at 45.9%.
+These findings suggest that, while both candidates maintain stable support, Harris holds a slight advantage.
+The consistency across both models underlines the importance of accounting for variability in polling methodologies and regional voter bases.
+【等result出来再改】
+
+This study is important because it not only forecasts the immediate electoral outcomes but also provides critical insights into the potential global impact of the U.S.
 presidential election.
-These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
+Predicting election results helps global stakeholders—such as policymakers, investors, and international organizations—prepare for possible changes in U.S.
+policy, which could significantly affect trade, climate commitments, and foreign relations, thereby influencing global economic stability and strategic alliances.
+Furthermore, our findings highlight the need for transparency in polling methodologies and emphasize the importance of developing more precise and comprehensive forecasts.
+
+This paper is organized as follows: The next section outlines the data collection and filtering processes, detailing the key variables and sources.
+Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models.
+In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings.
+Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
 【最后改结构描述加cross-reference】
@@
 ## Overview
-The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' (Ryan Best and Wiederkehr, 2024).
+The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' (@citeRawData).
 FiveThirtyEight is a well-known website recognized for its political, economic, and sports analyses.
@@
 
+In this section, we detail our selected variables, discuss key measurements, outline important limitations of our data, and our data cleaning process.
+
+## Raw data
 The analysis and visualizations in this paper are based on polling results as of October 22.
-The dataset includes 52 variables and 17,133 samples from various polling sources, asking participants who they support in the upcoming presidential election.
-To ensure accuracy and consistency, the data has been carefully processed and cleaned to remove biases and guarantee data integrity and comparability.
-
-This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S.
-presidential election forecast.
-These packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.
-
-## Raw data
-Raw data 一共包含了52个variable以及17133个sample.
+The dataset includes 52 variables, 17,133 samples and 3530 polls from various polling sources.
+These variables are shown in the below table(@tbl-vord).
+
 ```{r, fig.height=90, fig.width=90}
@@
 ```
-其中重要的variables，其余的在appdendix
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+# Get unique Poll IDs and print the count
+# 一共有3530个poll
+unique_poll_ids <- unique(raw_data$poll_id)
+```
+
+## Cleaning Process
+Firstly, there are several variables clearly irrelevant to the project and will not be discussed further: notes, url, url_article, url_topline, url_crosstab, and source.
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
+droped_data <- raw_data %>% select(-any_of(del_1))
+```
+
+Additionally, there are some duplicate variables, and we will retain only one of each, ignoring the rest: pollster, sponsors, display_name, pollster_rating_name, sponsor_candidate, endorsed_candidate_name, population_full, candidate_id, and candidate_name.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+# 这里需要画一个table，展示删除的重复变量
+del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
+           "population_full", "candidate_id", "candidate_name")
+droped_data <- droped_data %>% select(-any_of(del_2))
+```
+
+Constant variables, which cannot impact our predictions, will also be excluded from further discussion.
+These include: endorsed_candidate_id (NA), endorsed_candidate_party (NA), subpopulation (NA), cycle (2024), office_type (U.S.
+President), seat_number (0), seat_name (NA), election_date (11/5/24), stage (general), and nationwide_batch (FALSE).
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cv
+#| tbl-cap: "Constant variables"
+#| include: false
+# Identify variables where all values are the same (including NA)
+same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
+# Create a data frame with variables and their unique values
+same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
+unique(na.omit(droped_data[[var]]))[1]))
+# Print the names of variables with all identical values using kable
+kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
+del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
+           "office_type", "seat_number", "seat_name")
+droped_data <- droped_data %>% select(-any_of(del_4))
+```
+After cleaning, 27 out of the 52 variables remained potentially relevant to our research.
+We selected 10 variables (@tbl-ivatd) of interest and plotted their distributions in the 【data visualization section】, while the plots of the remaining variables are included in the 【appendix】.
 ```{r, fig.height=90, fig.width=90}
@@
                "hypothetical", "answer", "numeric_grade", "pollscore", 
-               "transparency_score", "start_date", "end_date", "sample_size", "pct"),
+               "transparency_score", "sample_size", "pct"),
   Description = c(
@@
     "A score reflecting the pollster's transparency about their methodology (e.g., 9.0).",
-    "The date the poll began (e.g., 10/8/24).",
-    "The date the poll ended (e.g., 10/11/24).",
     "The total number of respondents participating in the poll (e.g., 2712).",
@@
 ```
-52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
-"notes", "url", "url_article", "url_topline", "url_crosstab", "source"
-```{r, fig.height=90, fig.width=90}
-#| warning: false
-#| message: false
-#| echo: false
-del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
-droped_data <- raw_data %>% select(-any_of(del_1))
-```
-此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括："pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name", "population_full", "candidate_id", "candidate_name"
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-# 这里需要画一个table，展示删除的重复变量
-del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
-           "population_full", "candidate_id", "candidate_name")
-droped_data <- droped_data %>% select(-any_of(del_2))
-```
-常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
-```{r, fig.height=90, fig.width=90}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-cv
-#| tbl-cap: "Constant variables"
-# Identify variables where all values are the same (including NA)
-same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
-# Create a data frame with variables and their unique values
-same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
-unique(na.omit(droped_data[[var]]))[1]))
-# Print the names of variables with all identical values using kable
-kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
-del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
-           "office_type", "seat_number", "seat_name")
-droped_data <- droped_data %>% select(-any_of(del_4))
-```
-其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
-         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
-         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer"
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+
+After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
+This new variable represents the number of days between 'start_date' and 'end_date'.Next, we categorized the 51 different methodologies into four levels, ranging from the least reliable and accurate (level_1) to the most reliable (level_4).
+
+Subsequently, we handled the missing values by imputing numerical variables with their mean values and categorical variables with their mode.
+Since our results are not exact percentages, we used 'score' to name what would typically be called 'pct'.
+We then finalize and tidy up the variable names.
+
+Then, the data is extracted for each candidate individually.
+We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
+After comparison, we observed that the top three candidates—Trump, Harris, and Biden—had significantly higher scores than the remaining candidates.
+Given that Biden has withdrawn from the race, we are now focusing only on the datasets for Trump and Harris for further analysis.
+
+We also split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
+```{r, fig.height=30, fig.width=60}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-eoad
+#| tbl-cap: "Example of analysis data"
+#| include: false
+kable(head(train_Trump), col.names = names(train_Trump))
+```
+
+## Data Visualization
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
 catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
@@
 ```
-重要的categorical为下面的，剩下的将在appendix阐述："poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer"
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
 catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
 ```
-一共有3530个poll
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-# Get unique Poll IDs and print the count
-unique_poll_ids <- unique(raw_data$poll_id)
-```
-描述
+
+The left bar chart in (@fig-bv) shows the distribution of the `ranked_choice_reallocated` variable.
+The chart indicates that the majority of the data points are marked as `FALSE`, meaning ranked-choice voting reallocations have not been applied in most cases.
+Only a very small number of instances are marked as `TRUE`.
+
+The right bar chart in (@fig-bv) illustrates the distribution of the `hypothetical` variable.
+It shows that a larger proportion of the data is marked as `TRUE`, indicating that the poll results are often based on hypothetical match-ups.
+There are fewer instances marked as `FALSE`, where the poll is not hypothetical.
+
 ```{r}
@@
 ```
-描述
+
+The three charts depict the distribution of key variables in the dataset: `methodology`, `population`, and `answer`.
+In the most left chart of (@fig-cv), we see that the most frequently used polling methodology is "Online Panel," followed by "Live Phone" and "Live Phone/Text-to-Web." The "Online Panel" category significantly outnumbers the others, while the "Other" category also includes a notable count, representing various methodologies grouped together.
+
+The middle chart of (@fig-cv) shows the distribution of different respondent groups.
+"lv" (likely voters) and "rv" (registered voters) dominate, with "rv" showing a slightly higher count, indicating that these two groups make up the majority of the sample.
+Other groups, such as "a" (all adults), "v," and those with missing values ("NA"), represent much smaller portions of the respondent pool.
+
+The most right chart of (@fig-cv), `Top 3 Answer and Others`, illustrates the responses given in the polls.
+"Biden" and "Trump" have similar counts, with "Trump" being slightly higher, while the "Other" category also shows a significant proportion.
+The response for "Harris" is noticeably lower compared to the others.
+Overall, these charts provide a visual representation of the polling data, highlighting the dominant methodologies, respondent groups, and response preferences in the dataset.
 ```{r, fig.pos="H", fig.width=18, fig.height=18}
@@
 ```
-以及numerical的variables："numeric_grade"      "pollscore"          "transparency_score" "start_date"         "end_date"        "sample_size" "pct"
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
 numer <- droped_data %>% select(-any_of(catego))
 ```
-描述
+The `numeric_grade` histogram in (@fig-donvp1) shows the distribution of a numeric rating assigned to pollsters, representing their overall quality or reliability.
+The data appear to cluster heavily around scores of 2 and 3, suggesting that a large number of pollsters fall within these quality ranges.
+The distribution is fairly symmetric, with a noticeable concentration at these higher scores, indicating that most pollsters are considered to be of moderate to good quality.
+
+The `pollscore` histogram in (@fig-donvp1) indicates the reliability of each pollster, with lower (more negative) values being better.
+The distribution shows a peak around zero, with a significant number of pollsters having scores close to zero or slightly negative, and most values being negative, indicating relatively high reliability overall.
+This implies that most pollsters have moderate to high reliability, with fewer pollsters achieving highly negative scores, which indicate better performance.
+The tail towards positive values suggests that a small subset of pollsters may have issues with reliability.
+
+The distribution of `transparency_score` in (@fig-donvp1) shows a wide spread, with notable peaks at several discrete points, but no clear pattern overall.
+Higher scores, such as 7.5 and 10, have high frequencies, indicating that some pollsters tend to achieve relatively high transparency.
+On the other hand, lower scores, such as 2.5 and 5, also show some clustering, but with less consistency.
 ```{r, fig.pos="H", fig.width=18, fig.height=18}
@@
 ```
-描述
+
+The `Distribution of sample_size` histogram in (@fig-donvp2) illustrates the frequency of poll sample sizes.
+The majority of polls have relatively small sample sizes, with the frequency decreasing sharply as the sample size increases.
+The distribution appears highly right-skewed, suggesting that larger sample sizes are much less common than smaller ones.
+
+The `Distribution of pct` histogram in (@fig-donvp2) represents the frequency distribution of vote percentages received by candidates in various polls.
+Most polls have percentage values concentrated around the 30-40% range, with visible peaks at around 0% and 40%.
+The distribution shows some variation across a wide range but seems to have a higher frequency in the middle range (30-40%) compared to the lower and higher extremes.
 ```{r, fig.pos="H", fig.width=18, fig.height=18}
@@
 ```
-描述
+【放appendix】
+Both charts in (@fig-dodv) show the normal distribution of poll start and end dates over time.
+The left chart represents the frequency of polls by their start date, while the right chart represents the frequency of polls by their end date, with both distributions primarily concentrated around 2010.The frequency drops after 2010 in both charts.
 ```{r, fig.pos="H", fig.width=18, fig.height=18}
@@
 ```
-## Cleaned data
-In the raw data, we initially identified a total of 52 variables.
-Some of these variables, such as 'url', are clearly unrelated to the objectives of this project.
-There are also constant variables, such as 'election_date', which consistently contains the value '11/5/24'.
-Additionally, we found duplicate variables conveying the same information, like 'pollster_id' and 'pollster'.
-Therefore, we first removed these irrelevant and redundant variables.
-The remaining variables are as follows:
-```{r, fig.height=90, fig.width=90}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-rv
-#| tbl-cap: "Remained variables"
-
-# Get the column names and arrange them into multiple columns
-column_names <- names(droped_data)
-num_columns <- 3  # Set the desired number of columns
-num_rows <- ceiling(length(column_names) / num_columns)
-matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
-                      nrow = num_rows, byrow = TRUE)
-
-# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
-kable(as.data.frame(matrix_data), 
-      col.names = NULL)
-```
-Next, we calculated the percentage of missing values for each variable across the entire dataset.
-We then removed all variables with more than 40% missing values.
-These variables, along with their respective proportions of missing values, are as follows:
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-vwbpomv
-#| tbl-cap: "Variables with big porpotion of missing values"
-na_proportions <- sapply(names(droped_data), function(var) {
-  round(mean(is.na(raw_data[[var]])), 2)
-})
-
-# Create a data frame with variable names and their NA proportions
-na_proportions_data <- data.frame(Variable = names(droped_data), NA_Proportion = na_proportions)
-
-# Filter variables with NA proportion greater than 40%
-high_na_proportions <- na_proportions_data[na_proportions_data$NA_Proportion > 0.4, ]
-
-# Print the NA proportions greater than 40% using kable
-kable(high_na_proportions[, 2, drop = FALSE], col.names = c("Variable", "NA Proportion"))
-
-del_5 <- c("sponsor_ids", "state", "sponsor_candidate_id", "sponsor_candidate_party", "tracking",
-           "internal","partisan","ranked_choice_round")
-droped_data <- droped_data %>% select(-any_of(del_5))
-
-```
-Since the influence of pollsters can be quantified using their ratings, such as 'numeric_grade', 'pollscore', and 'transparency_score', we removed these variables to simplify the dataset and the model.
-Similarly, 'created_at' was also removed due to its strong correlation with 'start_date'.
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-del_6 <- c("pollster_id", "pollster_rating_id", "created_at")
-droped_data <- droped_data %>% select(-any_of(del_6))
-```
-Finally, due to the limitations of our model, we removed 'race_id', 'party', and 'question_id'.
-The reason for this is that we will extract and analyze the data for each candidate individually, which makes 'race_id' and 'party' constant within the corresponding dataset.
-Additionally, 'question_id' contains 6,421 unique values, making it unsuitable for categorization, and we removed it to avoid overfitting the model.
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-# Get unique Question IDs and print the count
-unique_question_ids <- unique(raw_data$question_id)
-```
-Finally, the remaining variables are as follows:
-```{r, fig.height=30, fig.width=30}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-fv
-#| tbl-cap: "Final variables"
-final <- c("poll_id","numeric_grade","pollscore","methodology","transparency_score","sample_size","population", 
-           "ranked_choice_reallocated", "hypothetical", "answer","pct","start_date", "end_date")
-
-# Get the column names and arrange them into multiple columns
-column_names <- final
-num_columns <- 3  # Set the desired number of columns
-num_rows <- ceiling(length(column_names) / num_columns)
-matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
-                      nrow = num_rows, byrow = TRUE)
-
-# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
-kable(as.data.frame(matrix_data), 
-      col.names = NULL)
-```
-After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
-This new variable represents the number of days between 'start_date' and 'end_date'.Next, we categorized the 51 different methodologies into four levels, ranging from the least reliable and accurate (level_1) to the most reliable (level_4).
-
-Subsequently, we handled the missing values by imputing numerical variables with their mean values and categorical variables with their mode.
-Since our results are not exact percentages, we used 'score' to name what would typically be called 'pct'.
-We then finalize and tidy up the variable names.
-
-Next, we extracted the data for each candidate individually.
-We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
-After comparison, we observed that the top three candidates—Trump, Harris, and Biden—had significantly higher scores than the remaining candidates.
-Given that Biden has withdrawn from the race, we are now focusing only on the datasets for Trump and Harris for further analysis.
-
-Next, we split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
-```{r, fig.height=30, fig.width=60}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-eoad
-#| tbl-cap: "Example of analysis data"
-kable(head(train_Trump), col.names = names(train_Trump))
-```
-## Measurement
+
+## Measurement and Limitations
 The method used to forecast the presidential election results is the poll-of-polls, which aggregates results from multiple polls instead of relying on a single survey, aiming to make the results more accurate and stable.
@@
 ## Similar dataset
+A dataset similar to ours titled 2024 National Polls (@citeNYTData) for the U.S.
+Presidential Election is found.
+It was Published by The New York Times, this dataset aggregates survey results from multiple polling organizations, focusing on the support levels for major presidential candidates and aiming to reflect voters’ preferences and election trends.
+However, compared to our dataset, this one has fewer variables, which might reduce its predictive accuracy.
 
@@
 # Discussion
-
-This paper presents a predictive analysis of voter support for 2024 U.S.
-presidential candidates Kamala Harris and Donald Trump.
-Using a “poll-of-polls” approach, it integrates polling data from diverse sources, emphasizing reliability, sample size, and methodology.
-Linear and Bayesian models were applied to improve prediction accuracy.
-
-The analysis provides two key insights.
-First, our model predicts a slight advantage for Kamala Harris, with a support estimate of 47.6% compared to Donald Trump’s 43.5%, indicating a competitive but narrow lead.
-Second, it underscores the impact of poll reliability on predictive accuracy.
-Traditional methods like live phone surveys show greater accuracy than online methods, reinforcing the importance of reliability-weighted data in improving forecast precision.
-
-This analysis is limited by its use of static variables, which may not capture shifts in public opinion.
-For instance, major events like debates can influence voter sentiment, yet the model lacks real-time responsiveness.
-Additionally, aggregating data from different poll methodologies may introduce bias; for example, online panels may skew younger while live phone surveys often favor older demographics.
-Future work could include real-time data and refined weighting to enhance adaptability and consistency.
-
-Future research could incorporate time series analysis to track evolving voter sentiment and add demographic or economic factors for greater precision.
-Integrating social media sentiment and machine learning could provide deeper insights into regional voting patterns.
 

### 2024-11-03 paper/paper_Max.qmd
paper frist draft updated
paper frist draft updated

--- 2024-11-03 paper/paper.qmd
@@
 As the 2024 election approaches, the ability to accurately forecast potential outcomes is essential for policymakers, businesses, and organizations seeking to anticipate shifts in U.S.
-policy that may affect trade, climate commitments, and strategic alliances (BBC News, 2024).
-Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning (Euronews, 2024).
-However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting (University of Oregon, 2024).
-Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further (Yale University, 2022).
+policy that may affect trade, climate commitments, and strategic alliances [@citeBBC].
+Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning [@citeEuronews].
+However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting [@citeOregon].
+Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further [@citeYale].
 

### 2024-11-03 paper/paper_draft_1.qmd
paper frist draft updated
paper frist draft updated

--- 2024-11-03 paper/paper_HP.qmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Poll-Based Forecasting of the 2024 U.S. Presidential Election"
+subtitle: "Valid Multiple Linear Regression Explains Why Kamala Harris Will Win"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+  - Haowei Fan
+  - Fangning Zhang
+  - Shaotong Li
+thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study aggregates polling data to forecast support for 2024 U.S.
+presidential candidates Kamala Harris and Donald Trump.
+By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%.
+The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
 format: pdf
-number-sections: true
+toc: true           
+toc-title: "Table of Contents" 
+toc-depth: 2    
+number_sections: true    
 bibliography: references.bib
@@
 The U.S.
-presidential election is a globally significant event, drawing substantial international attention due to its potential impact on economies, international relations, and pressing social issues, including climate change and human rights.
-As the world anticipates the 2024 U.S.
-electoral contest, forecasting the possible outcomes can provide critical insights for policymakers, businesses, and civil society groups.
-Predicting election outcomes has long been one of the most challenging tasks for political scientists, statisticians, and analysts.
-This study aims to predict the level of support for leading candidates, specifically Kamala Harris and Donald Trump, using aggregated poll data and statistical modeling.
-
-To provide a robust prediction, we utilize a "poll-of-polls" approach, combining polling data from multiple organizations at both national and state levels to enhance accuracy and stability in forecasted support.
-Our analysis applies a multilinear regression model, focusing on key variables like pollster reliability, sample size, and duration, which contribute to the prediction of each candidate's support level.
-we aim to predict the percentage of support for the main candidates Kamala Harris and Donald Trump.
-
-The results of our linear model indicate closely matched levels of voter support for both candidates.
-Donald Trump’s predicted support is approximately 45.2%, while Kamala Harris's predicted support is slightly higher at 45.9%.
-These findings suggest that, while both candidates maintain stable support, Harris holds a slight advantage.
-The consistency across both models underlines the importance of accounting for variability in polling methodologies and regional voter bases.
-【等result出来再改】
-
-This study is important because it not only forecasts the immediate electoral outcomes but also provides critical insights into the potential global impact of the U.S.
+presidential election has profound implications on a global scale, shaping international relations, economic policy, and key social issues.
+As the 2024 election approaches, the ability to accurately forecast potential outcomes is essential for policymakers, businesses, and organizations seeking to anticipate shifts in U.S.
+policy that may affect trade, climate commitments, and strategic alliances [@citeBBC].
+Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning [@citeEuronews].
+However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting [@citeOregon].
+Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further [@citeYale].
+
+This study seeks to address these complexities by examining voter support for the 2024 presidential candidates Kamala Harris and Donald Trump.
+While substantial polling data exists, current aggregation methods often lack consistency and fail to adequately consider critical factors such as poll reliability and sample size, leading to unreliable predictions.
+To address this gap, the present study adopts a “poll-of-polls” methodology, drawing from multiple data sources at both national and state levels.
+Through the application of multiple linear regression models, the study integrates essential variables, including pollster reliability, sample size, and polling duration, to produce a forecast that is both stable and transparent.
+
+The estimand in this study represents the expected level of voter support for each primary candidate, Kamala Harris and Donald Trump, based on aggregated polling data across diverse demographics and polling methodologies.
+This measure aims to capture the central tendency of public opinion, adjusted for polling reliability and sample characteristics, to provide a stable estimate of each candidate's projected support under current conditions.
+By centering on this estimand, the analysis offers a robust and interpretable forecast applicable for strategic decision-making in both political and economic contexts.
+
+The findings suggest a slight advantage for Harris, with a predicted support level of 47.6% compared to Trump’s 43.5%.
+This marginal lead underscores the importance of methodological rigor, as systematically weighting data by reliability yields more consistent and interpretable predictions.
+The results indicate that while both candidates retain substantial support, polling methods and demographic representation can subtly shift the support dynamics, providing a deeper understanding of the electoral landscape beyond basic polling figures.
+
+This paper is structured as follows: first, the data collection and filtering processes are outlined, followed by a description of the methodological framework, introducing linear modeling approaches.
+The results are then presented and analyzed, with a discussion on broader implications.
+The paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
+
+This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S.
 presidential election.
-Predicting election results helps global stakeholders—such as policymakers, investors, and international organizations—prepare for possible changes in U.S.
-policy, which could significantly affect trade, climate commitments, and foreign relations, thereby influencing global economic stability and strategic alliances.
-Furthermore, our findings highlight the need for transparency in polling methodologies and emphasize the importance of developing more precise and comprehensive forecasts.
-
-This paper is organized as follows: The next section outlines the data collection and filtering processes, detailing the key variables and sources.
-Following that, we discuss our methodological framework, including the construction of the linear and Bayesian models.
-In the results section, we present the outcomes of both models, and a discussion explores the broader implications of these findings.
-Finally, the paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
+These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
  【最后改结构描述加cross-reference】
@@
 
-## Model overview
-我们一共有2个model，分别用来预测川普和哈里斯在2024年11月5日美国总统竞选的最终支持率。
+## Overview
+
+In the modeling process, we used the `arrow` package to handle parquet files.
+The model parameters were examined using the `car` and `moments` packages.
+Additionally, `tidyverse`, `knitr`, `dplyr`, `patchwork`, `kableExtra`, `gridExtra`, and `grid` were employed to visualize and evaluate the model's performance and assumptions.
+
+We developed two models to predict the final competitiveness of Trump and Harris in the November 5, 2024, U.S.
+presidential election.
+Both models were trained using a training set (70%) for each candidate, while the remaining 30% served as the test set.
+
+The model formula is as follows:
 
@@
 
-Notably, we used Multiple Linear Regression (MLR), which implies the following assumptions:
-
-The core assumption of multiple linear regression is that there is a linear relationship between the dependent variable (outcome) and the independent variables.
-This linear relationship can be visually checked using scatter plots, which ideally should display a straight-line pattern rather than a curve.
-The residuals (the differences between observed and predicted values) should be normally distributed. This assumption can be assessed by examining a Q-Q plot.
-The correlation between independent variables should not be too high, meaning multicollinearity should be avoided. This can be checked using the Variance Inflation Factor (VIF).
-Homoscedasticity: The variance of the error terms (residuals) should be consistent across all levels of the independent variables.
-Residuals plotted against predicted values should not display any obvious pattern.
-Furthermore, in our model, the variable "duration" is derived from the difference between "start_date" and "end_date" in the original data.
-This means our model cannot account for the effects brought by time series, but considering the linear relationship between these two, we simplified it to meet the assumptions of using MLR.
-
-Additionally, there are 51 different categories for the "methodology" variable in the original dataset.
-Having too many categories for a categorical variable would increase the complexity of our model, so we simplified it into four levels.
-Level 1 represents the lowest reliability of the methodology, while level 4 represents the highest.
-The specific classifications are as follows:
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-mc
-#| tbl-cap: "Methodology classfication"
-
-# Create a summary data frame for the methodologies and their levels
-methodology_summary <- data.frame(
-  Level = c("level 1", "level 2", "level 3", "level 4"),
-  Methodologies = c(
-    paste(c("Email", "Email/Online Ad", "Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Mail-to-Web/Mail-to-Phone", "Online Ad"), collapse = ", "),
-    paste(c("App Panel", "IVR", "IVR/Live Phone/Text/Online Panel/Email", "IVR/Online Panel", "IVR/Online Panel/Email", "IVR/Online Panel/Text-to-Web", "IVR/Online Panel/Text-to-Web/Email", "IVR/Text", "IVR/Text-to-Web", "IVR/Text-to-Web/Email", "Live Phone/Email", "Live Phone/Online Panel/Mail-to-Web", "Live Phone/Text/Online Ad", "Live Phone/Text-to-Web/Email", "Live Phone/Text-to-Web/Email/Mail-to-Web", "Live Phone/Text-to-Web/Online Ad", "Online Panel/Email", "Online Panel/Email/Text-to-Web", "Online Panel/Online Ad", "Text-to-Web/Email", "Text-to-Web/Online Ad"), collapse = ", "),
-    paste(c("IVR/Live Phone/Online Panel", "IVR/Live Phone/Online Panel/Text-to-Web", "IVR/Live Phone/Text", "IVR/Live Phone/Text-to-Web", "Live Phone/Online Panel/App Panel", "Live Phone/Online Panel/Text", "Live Phone/Online Panel/Text-to-Web", "Live Phone/Online Panel/Text-to-Web/Text", "Live Phone/Text", "Live Phone/Text/Online Panel", "Live Phone/Text-to-Web", "Live Phone/Text-to-Web/App Panel", "Online Panel", "Online Panel/Text", "Online Panel/Text-to-Web", "Online Panel/Text-to-Web/Text", "Text", "Text-to-Web"), collapse = ", "),
-    paste(c("Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", "Online Panel/Probability Panel", "Probability Panel"), collapse = ", ")
-  )
-)
-
-# Print the summary of methodologies and their levels using kable
-kable(methodology_summary, col.names = c("Level", "Methodologies")) %>%
-  column_spec(1, width = "1.5cm") %>% # Adjust the width of the first column
-  column_spec(2, width = "13cm")
-```
-The different methodologies were evaluated based on reliability scores ranging from 1 to 10.
-The scores of 51 combinations were calculated by averaging the individual scores of each methodology in the combination.
-The results were classified into four levels: high reliability (8.5-10), medium-high reliability (7-8.49), medium reliability (5-6.99), and low reliability (below 5).
-Methodologies were scored based on several criteria, including statistical rigor, representativeness, response rate, interaction quality, and cost efficiency.
-High-scoring methodologies, such as those employing strict statistical sampling methods like Probability Panels or those using Live Phone surveys with broad coverage and low refusal rates, received high scores due to their strong representativeness and reliability.
-Medium-high scoring methodologies included Online Panels, which offer good coverage and low cost but are susceptible to self-selection bias, and Text-to-Web methods, which improve response rates but may have limited representativeness depending on the target demographics.
-Medium-scoring methodologies, such as App Panels and IVR (Interactive Voice Response), tend to lack broad representativeness or have limitations in interaction quality, making them suitable for niche audiences but not generalizable to a wider population.
-Low-scoring methodologies, including Email Surveys and methods relying on Online Ads, often suffer from low response rates and significant selection bias, which negatively impact their reliability.
-These scoring criteria ensure that the methodologies are evaluated in a consistent manner, with higher scores reflecting stronger statistical foundations, broader representativeness, and better data quality.
-
-Additionally, the reason we only compared the data of Trump and Harris to predict which of them would win the election is that, after comparing the weighted competitiveness scores of all candidates, we found that the top three — Trump, Harris, and Biden — had significantly higher scores than the others.
-As shown in @tbl-t5c, the third-place candidate, Harris, had a weighted competitiveness score of 180714535, which is 5.15 times higher than the fourth-place score of 34987031.
-Considering that Biden has withdrawn from the race, we ultimately decided to only predict between the most competitive candidates, Trump and Harris.
-The specific weighting formula is as follows:
-
-\begin{align}
-& weighted\_score  = \frac{ {\textstyle \sum_{i  = 1}^{n}score_i} }{n}\times {\textstyle \sum_{i  = 1}^{n}Sample\_Size_i} \\
-& \text{Where: }\notag\\
-&\hspace{1cm}n\text{ represents the number of polls nominating this candidate.}\notag\\
-&\hspace{1cm}Score_i\text{ represents the score obtained by the candidate in the } i^{th}\text{ poll.}\notag\\
-&\hspace{1cm}Sample\_Size_i\text{ represents the sample size of the } i^{th}\text{ poll.}\notag
-\end{align}
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-wsft5c
-#| tbl-cap: "Weighted score for top 5 candidates"
-# Define the directory path containing the parquet files
-p <- "data/03-cleaned_data"
-parquet_files <- list.files(path = here::here(p), full.names = TRUE)
-
-# Initialize an empty dataframe to store the weighted score for each file
-weighted_scores <- data.frame(Candidate = character(), Weighted_Score = numeric(), stringsAsFactors = FALSE)
-
-# Iterate over each parquet file
-for (file in parquet_files) {
-  # Read the parquet file
-  df <- read_parquet(here::here(file))
-
-  # Calculate the mean of score and sample_size
-  score_mean <- mean(df$score, na.rm = TRUE)
-  sample_size_mean <- mean(df$sample_size, na.rm = TRUE)
-
-  # Calculate the weighted score (multiply by total number of rows)
-  weighted_score <- score_mean * sample_size_mean * nrow(df)
-
-  # Append the result to the weighted_scores dataframe
-  weighted_scores <- rbind(weighted_scores, data.frame(Candidate = sub('_cleaned_data.parquet$', '', basename(file)), Weighted_Score = weighted_score))
-}
-
-# Get the top 5 weighted scores
-top_5_weighted_scores <- weighted_scores %>% 
-  arrange(desc(Weighted_Score)) %>% 
-  head(5)
-
-# Print the top 5 weighted scores using kable
-top_5_weighted_scores %>% kable()
-
-```
-
-## Model set-up
-### response variable
-在此章节中，我们用到的数据都是哈里斯和特朗普的训练集。
-score是我们模型的response variable，它代表的是某个候选人在某次选票中胜利的可能性，越大代表着该候选人竞选成功的概率越大，通常情况下与该候选人在那次选票中的支持率一样。
-下图可以看出来哈里斯和特朗普的score都接近于正态分布。其中川普的score呈现一个对称的趋势，其中最多的score是在50左右。训练集中，川普的score平均数是44.63，方差是24.68。相比之下，哈里斯的score分布有一些偏向于左侧的倾斜。训练集中，哈里斯的score平均数高于特朗普为46.92，方差略低于川普为20.96。值得注意的是川普数据的样本量为3960，而哈里斯只有1636.
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-sositd
-#| tbl-cap: "Sumarry of score in training datasets"
-# Calculate mean, variance, and sample size
-summary_stats <- bind_rows(
-  train_Trump %>% summarise(mean = round(mean(score, na.rm = TRUE), 2), variance = round(var(score, na.rm = TRUE), 2), sample_size = n()) %>% mutate(dataset = "train_Trump"),
-  train_Harris %>% summarise(mean = round(mean(score, na.rm = TRUE), 2), variance = round(var(score, na.rm = TRUE), 2), sample_size = n()) %>% mutate(dataset = "train_Harris")
-)
-
-# Display results using kable
-summary_stats %>%
-  select(dataset, mean, variance, sample_size) %>%
-  kable()
-
-```
+The estimands, Score\_Trump and Score\_Harris, represent the competitiveness of each candidate.
+A higher score indicates stronger competitiveness.
+If the predicted score for one candidate is higher than the other, we consider that candidate to be the likely winner of the election.
+
+"pollscore", "transparency\_score", "duration", "sample\_size", "population", and "hypothetical" are our estimators.
+"duration" represents the length of a poll in days.
+Detailed descriptions of the other estimators are provided in the data section.
+
+Notably, we used a Multiple Linear Regression (MLR) model, which implies the following assumptions:
+
+1. **Linear Relationship**: A linear relationship exists between the estimand and the estimators.
+2. **Multivariate Normality**: The residuals (differences between observed and predicted values) are normally distributed.
+3. **No Multicollinearity**: The correlations between independent variables are not too high.
+4. **Homoscedasticity**: The variance of residuals remains consistent across all values of the independent variables.
+
+## Estimand and Estimators
+
+Our estimand, "score," represents the support rate of a candidate in a particular poll, corresponding to the "pct" in the raw data.
+However, due to our methodology, the final result cannot be expressed as a proportion, and thus we named it "score." The figures below show the distribution of scores for Trump and Harris in their respective training sets.
+It can be observed that both distributions are approximately normal.
+Different form raw.......
 
@@
 
-### Predictor
-我们的predictors包含以下变量：
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-predictors <- c("pollscore","methodology","transparency_score","sample_size","population", 
-           "ranked_choice_reallocated", "hypothetical", "duration")
-predictors
-```
-
-下图展示了在川普的训练集中，numerical predictor 之间的关系。没有明显的趋势代表着它们之间没有明显的correlation。
-```{r, fig.width=10, fig.height=10}
-#| warning: false
-#| message: false
-#| echo: false
-data2 = train_Trump %>% select("pollscore","transparency_score","sample_size","duration")
-pairs( data2 , main = "Predictor vs predictor")
-```
-
-关于categorical的：。。。。。。。。。。。。。。。。
-
-### alternative models
-最开始我们的模型是
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-Trump_model_0 <- lm(
-  score ~ numeric_grade + pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Trump)
-Harris_model_0 <- lm(
-  score ~ numeric_grade + pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Harris)
-```
-
-因为我们考虑到numeric_grade和pollscore之间有强线性相关，我们舍弃了这一方案。
+Since our training set was obtained via simple random sampling, the distributions of "pollscore", "transparency\_score", "sample\_size", "population", and "hypothetical" are similar to those in the raw data, which will not be further elaborated here.
+The variable "duration" is derived from the difference between "start\_date" and "end\_date" in the original data.
+This means that our model cannot account for time series effects, but we simplified this to meet the assumptions of using MLR given the linear relationship between these two factors.
+Below are histograms that display the duration of polls nominating Trump and Harris.
+It can be observed that they follow a highly skewed distribution, with most values clustered around 1-2 days.
+
+```{r, fig.pos="H", fig.height=10, fig.width=20}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-doditd
+#| fig-cap: "Distribution of durations in training dataset"
+
+plots <- list()
+# Plot a histogram for the 'pct' variable
+plots[["Trump"]]<-ggplot(train_Trump, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
+  labs(title = "Histogram of duration for Trump", x = "Duration", y = "Frequency")
+plots[["Harris"]]<-ggplot(train_Harris, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
+  labs(title = "Histogram of duration", x = "Duration", y = "Frequency")
+
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(5, 5), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+
+It is worth noting that although our final model does not consider "methodology," in the initial model exploration phase, we simplified the 51 different categories of the "methodology" variable into four levels to maintain simplicity.
+Level 1 represents the lowest reliability, while level 4 represents the highest.
+The specific classifications are as follows:
+
+**Methodologies were scored based on several criteria, including statistical rigor, representativeness, response rate, interaction quality, and cost efficiency.**
+
+- **High-scoring methodologies**: Methods such as Probability Panels or Live Phone surveys with broad coverage and low refusal rates received high scores due to strong representativeness and reliability.
+- **Medium-high scoring methodologies**: Online Panels and Text-to-Web methods were rated in this category.
+Online Panels are cost-effective but susceptible to self-selection bias, whereas Text-to-Web improves response rates but may lack representativeness depending on the target demographics.
+- **Medium-scoring methodologies**: App Panels and IVR (Interactive Voice Response) tend to lack broad representativeness or interaction quality, making them suitable only for niche audiences.
+- **Low-scoring methodologies**: Email Surveys and methods relying on Online Ads often have low response rates and significant selection bias, which undermines their reliability.
+
+## Alternative Models
+
+Below are our initial models. Their estimators included all variables from the analysis datasets.
+
+\begin{align} 
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+\end{align}
+
+Upon comparing the relationship between "numeric\_grade" and "pollscore," we observed a significant linear relationship, as shown in the following figure.
+Therefore, we removed "numeric\_grade" from the model to satisfy MLR assumptions, resulting in our second model.
+
 ```{r, fig.pos="H", fig.height=10, fig.width=10}
@@
 
-这个是我们的第二个方案。虽然predictors之间没有了相关性，但是methodology，ranked_choice_reallocated，这两个变量并不statistical significant，因为他们的p value都大于0.05.
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+The second model is as follows:
+
+\begin{align} 
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+\end{align}
+
+We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
+As shown in the figure below, both "methodology" and "ranked\_choice\_reallocated" were found to be insignificant predictors in both models.
+Thus, they were excluded to reduce model complexity.
+
+```{r, fig.height=100,fig.width=100}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-alovitahm
+#| tbl-cap: "Significant level of variblaes in the aboanded Harris's model"
+
 Trump_model_1 <- lm(
@@
     methodology, data = train_Harris)
-```
-
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitahm
-#| tbl-cap: "Significant level of variblaes in the aboanded Harris's model"
 # Get the summary of the model
@@
 ```
-
 ```{r, fig.height=100,fig.width=100}
@@
 
-因此，我们有有了最后的模型。
-
-## validation
-从您的结果来看，所有变量的 GVIF 值都在 1 到 1.3 之间，这些数值非常低，表明各个自变量之间的共线性很小，模型并没有因为共线性而受到显著影响。
+Our final model is as follows:
+
+\begin{align} 
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+\end{align}
+
+## Validation
+
+First, we verified the assumptions mentioned in the overview.
+The table below shows the General Variance Inflation Factor (GVIF) for both models, which indicates that all predictors have a GVIF less than 1.3, suggesting no significant multicollinearity.&#x20;
+
 ```{r}
@@
 ```
-
 ```{r}
@@
 
+The following figure presents the diagnostic plots for the Harris model.
+The plot on the left shows the relationship between residuals and predicted values, and since no obvious pattern is observed, our model satisfies the Homoscedasticity assumption.
+The right-hand plot is a Q-Q plot, and the points align along the diagonal, indicating that residuals are  normally distributed and satisfy the Multivariate Normality condition.
+
 ```{r}
@@
 plot(Harris_model,2)
-```
-
-```{r}
-
-par(mfrow=c(2,2))
 plot(Trump_model,1)
@@
 ```
-然后就是描述一下response variable是normal的，然后numerical variable没有显著关系（这些在打他部分有讲过）
-总结，满足了MLR的条件，说明我们的好
+
+The next figure compares predicted and actual values from the test data.
+For both the Trump and Harris models, the trend between predicted and actual values is roughly linear, indicating that our models are effective.
+
 ```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 10, fig.width=10}
@@
 ```
+
+## Model Discussion
+
+As noted above, our model combines the start and end dates of a poll into the "duration" variable, which prevents it from effectively capturing the time series impact on the estimand.
+Additionally, due to the weak linear relationship between the estimators and the estimand, the explanatory power of our model, as reflected by the adjusted R-Square, is relatively low.
+Polynomial Regression or Generalized Linear Models might be better choices in this context.
+Moreover, when significant relationships exist between estimators, our model might fail.
 
@@
 
+This paper presents a predictive analysis of voter support for 2024 U.S.
+presidential candidates Kamala Harris and Donald Trump.
+Using a “poll-of-polls” approach, it integrates polling data from diverse sources, emphasizing reliability, sample size, and methodology.
+Linear and Bayesian models were applied to improve prediction accuracy.
+
+The analysis provides two key insights.
+First, our model predicts a slight advantage for Kamala Harris, with a support estimate of 47.6% compared to Donald Trump’s 43.5%, indicating a competitive but narrow lead.
+Second, it underscores the impact of poll reliability on predictive accuracy.
+Traditional methods like live phone surveys show greater accuracy than online methods, reinforcing the importance of reliability-weighted data in improving forecast precision.
+
+This analysis is limited by its use of static variables, which may not capture shifts in public opinion.
+For instance, major events like debates can influence voter sentiment, yet the model lacks real-time responsiveness.
+Additionally, aggregating data from different poll methodologies may introduce bias; for example, online panels may skew younger while live phone surveys often favor older demographics.
+Future work could include real-time data and refined weighting to enhance adaptability and consistency.
+
+Future research could incorporate time series analysis to track evolving voter sentiment and add demographic or economic factors for greater precision.
+Integrating social media sentiment and machine learning could provide deeper insights into regional voting patterns.
+
 # Appendix

### 2024-11-03 scripts/06-model_data.R

@@ -9,10 +9,9 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
+library(arrow)
 
 # Define paths to each candidate's analysis data (training and testing data)
-
 Trump <- read_parquet("data/02-analysis_data/01-training/train_Trump.parquet")
 Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
 

### 2024-11-03 paper/paper_draft_1.qmd
abstract update
abstract update

@@
 date-format: long
-abstract: "This study aggregates polling data to forecast support for 2024 U.S.
-presidential candidates Kamala Harris and Donald Trump.
-By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%.
-The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
+abstract: "The United States plays a major role in the global technological and economic landscape, with its political leadership having a significant influence on international technology cooperation and economic relations.
+This project uses multiple linear regression to predict the outcome of the 2024 U.S.
+presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing insights to help stakeholders prepare for potential shifts in U.S.
+policies.
+The project predicts that Kamala Harris will narrowly defeat Donald Trump who is predicted to come in second place and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
 format: pdf

### 2024-11-03 paper/paper_draft_1.qmd
Add files via upload

--- 2024-11-03 paper/paper_draft_1.qmd
@@
 #| fig-cap: "Boolean variables"
+# Create a list to store the plots
 plots <- list()
-# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
+
+# Bar chart for 'ranked_choice_reallocated' with count labels
 plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
+  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
+  labs(title = "Bar Chart of Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
   theme_minimal(base_size = 15) +
@@
 raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
-# Create a bar chart for the grouped 'methodology'
+
+# Create horizontal bar chart for 'methodology'
 plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Top 3 Methodologies and Others", x = "Methodology", y = "Count") +
-  theme_minimal(base_size = 15) +
-  theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
+  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Consistent count label size
+  labs(title = "Top 3 Methodologies and Others", x = "Count", y = "Methodology") +
+  theme_minimal(base_size = 24) +  # Set consistent base font size
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 24),  # Consistent axis title font size
+    axis.text = element_text(size = 20)  # Consistent axis text font size
+  ) +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 10000))  # Set y-axis limit to 10000
+
+# Population bar chart
 plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Population", x = "Population", y = "Count") +
-  theme_minimal(base_size = 15) +
-  theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
-# Find the top 3 most frequent values in 'answer' and group others as 'Other'
+  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Consistent count label size
+  labs(title = "Population", x = "Count", y = "Population") +
+  theme_minimal(base_size = 24) +  # Set consistent base font size
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 24),  # Consistent axis title font size
+    axis.text = element_text(size = 20)  # Consistent axis text font size
+  ) +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 10000))  # Set y-axis limit to 10000
+
+# Top 3 Answers with 'Other' grouped
 answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
@@
 raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
-# Create a bar chart for the grouped 'answer'
+
+# Create horizontal bar chart for 'answer'
 plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Top 3 answer and Others", x = "answer", y = "Count") +
-  theme_minimal(base_size = 15) +
-  theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Consistent count label size
+  labs(title = "Top 3 Answers and Others", x = "Count", y = "Answer") +
+  theme_minimal(base_size = 24) +  # Set consistent base font size
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 24),  # Consistent axis title font size
+    axis.text = element_text(size = 20)  # Consistent axis text font size
+  ) +
+  coord_flip() +
+  scale_y_continuous(limits = c(0, 10000))  # Set y-axis limit to 10000
+
+# Combine the plots using patchwork
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 28)
+    )
+  )
+
 # Print the combined plot
 print(combined_plot)
+
 ```
@@
 plots <- list()
-# Loop through selected numeric variables and plot their distributions
-for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
+
+# Loop through selected numeric variables and plot their distributions with a line connecting bar tops
+for (variable in c("numeric_grade", "pollscore", "transparency_score")) {
+  # Calculate bin counts and midpoints
+  bin_data <- ggplot_build(
+    ggplot(raw_data, aes_string(x = variable)) +
+      geom_histogram(binwidth = 0.5)
+  )$data[[1]]
+
+  # Calculate the midpoint of each bin for line plotting
+  bin_data <- bin_data %>%
+    mutate(midpoint = (xmin + xmax) / 2)
+
+  # Create histogram plot with line connecting the bar tops
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
@@
     labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 30) +
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 20),
-      axis.text = element_text(size = 20)
-    )
-}
+    theme_minimal(base_size = 18) +  # Adjusted base font size for readability
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),  # Reduced title font size
+      axis.title = element_text(size = 20),  # Reduced axis title font size
+      axis.text = element_text(size = 18)  # Reduced axis text font size
+    )
+}
+
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+# Combine all individual plots into one vertical layout
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 28)
+    )
+  )
+
 # Print the combined plot
 print(combined_plot)
+
 ```
@@
 plots <- list()
+
 # Loop through selected numeric variables and plot their distributions
-for (variable in names(numer %>% select(sample_size, pct))) {
+for (variable in c("sample_size", "pct")) {
+  if (variable == "sample_size") {
+    # For sample_size, focus on the range 0-10000
+    plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+      geom_histogram(binwidth = 500, fill = "#69b3a2", color = "black", alpha = 0.8) +
+      xlim(0, 10000) +  # Set x-axis limits to focus on 0-10000 range
+      labs(title = "Distribution of Sample Size (0-10000)", x = variable, y = "Frequency") +
+      theme_minimal(base_size = 20) +  # Set consistent base font size
+      theme(
+        plot.title = element_text(hjust = 0.5, size = 24, face = "bold"),  # Consistent title font size
+        axis.title = element_text(size = 20),  # Consistent axis title font size
+        axis.text = element_text(size = 16)  # Consistent axis text font size
+      )
+  } else {
+    # For other variables, keep the full range
     plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
@@
       labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 30) +
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
-    )
-}
+      theme_minimal(base_size = 20) +  # Set consistent base font size
+      theme(
+        plot.title = element_text(hjust = 0.5, size = 24, face = "bold"),  # Consistent title font size
+        axis.title = element_text(size = 20),  # Consistent axis title font size
+        axis.text = element_text(size = 16)  # Consistent axis text font size
+      )
+  }
+}
+
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 8), "in")) +
+# Combine all individual plots into one vertical layout
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 24)
+    )
+  )
+
 # Print the combined plot
 print(combined_plot)
+
 ```
@@
 #| fig-cap: "Distribution of date varibales"
-
 ### Define Variables and Prepare Data ###
@@
 raw_data$end_date <- ymd(raw_data$end_date)
+
 # Define the date variables to plot
 date_variables <- c("start_date", "end_date")
+
 ### Create Plots for Date Variables ###
-# Loop through selected date variables and plot their distributions
+# Create a list to store plots
 plots <- list()
-for (variable in names(numer %>% select(start_date, end_date))) {
+
+# Loop through selected date variables and plot their distributions with a density curve
+for (variable in date_variables) {
+  # Use gsub to replace underscores with spaces and add "Distribution of"
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
-    geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-        theme_minimal(base_size = 30) +
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
-    )
-}
+    geom_histogram(fill = "#69b3a2", color = "black", alpha = 0.8) +  # Keep the original binwidth
+    labs(title = paste("Distribution of", gsub("_", " ", variable)), x = gsub("_", " ", variable), y = "Frequency") +
+    theme_minimal(base_size = 20) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 24, face = "bold"),  # Consistent title font size
+      axis.title = element_text(size = 20),  # Consistent axis title font size
+      axis.text = element_text(size = 16)  # Consistent axis text font size
+    )
+}
+
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 4), "in")) +
+# Arrange the plots vertically without changing their individual orientation
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 24)
+    )
+  )
+
 # Print the combined plot
@@
 
+```{=tex}
 \begin{align} 
@@
 \end{align}
+```
 
@@
 
-```{r, fig.pos="H", fig.height=30, fig.width=60}
+```{r, fig.pos="H", fig.width=18, fig.height=18}
 #| warning: false
@@
 
+# Create a list to store the plots
 plots <- list()
-# Plot a histogram for the 'pct' variable
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = score)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = score)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+
+# Plot a histogram for the 'pct' variable in Trump data
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Pct for Trump", x = "pct", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
+
+# Plot a histogram for the 'pct' variable in Harris data
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Pct for Harris", x = "pct", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
 
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(20, 20), "in")) +
+# Arrange the plots vertically with one column and consistent styling
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 18)
+    )
+  )
+
 # Print the combined plot
@@
 
-```{r, fig.pos="H", fig.height=10, fig.width=20}
+```{r, fig.pos="H", fig.height=10, fig.width=10 }
 #| warning: false
@@
 
+# Create a list to store the plots
 plots <- list()
-# Plot a histogram for the 'pct' variable
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = duration)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of duration for Trump", x = "Duration", y = "Frequency")
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = duration)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of duration", x = "Duration", y = "Frequency")
+
+# Plot a histogram for the 'duration' variable in Trump data
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Duration for Trump", x = "Duration", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
+
+# Plot a histogram for the 'duration' variable in Harris data
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Duration for Harris", x = "Duration", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
 
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(5, 5), "in")) +
+# Arrange the plots vertically with one column
+combined_plot <- wrap_plots(plots, ncol = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 18)
+    )
+  )
+
 # Print the combined plot
@@
 Below are our initial models. Their estimators included all variables from the analysis datasets.
+
+```{=tex}
+\begin{align} 
+\text{Score}_{Trump} = &\ \beta_1 \, \text{Pollscore} + \beta_2 \, \text{Transparency\_score} + \beta_3 \, \text{Duration} + \notag \\
+        &\ \beta_4 \, \text{Sample\_size} + \beta_5 \, \text{Population} + \beta_6 \, \text{Hypothetical} + \beta_7 \, \text{Numeric\_grade} + \notag \\
+        &\ \beta_8 \, \text{Methodology} + \beta_9 \, \text{Ranked\_choice\_reallocated} + \beta_0 \\[0.5cm]
+\text{Score}_{Harris} = &\ \alpha_1 \, \text{Pollscore} + \alpha_2 \, \text{Transparency\_score} + \alpha_3 \, \text{Duration} + \notag \\
+        &\ \alpha_4 \, \text{Sample\_size} + \alpha_5 \, \text{Population} + \alpha_6 \, \text{Hypothetical} + \alpha_7 \, \text{Numeric\_grade} + \notag \\
+        &\ \alpha_8 \, \text{Methodology} + \alpha_9 \, \text{Ranked\_choice\_reallocated} + \alpha_0
+\end{align}
+
+```
+
+Upon comparing the relationship between "numeric\_grade" and "pollscore," we observed a significant linear relationship, as shown in the following figure.
+Therefore, we removed "numeric\_grade" from the model to satisfy MLR assumptions, resulting in our second model.
+
+```{r, fig.pos="H", fig.height=10, fig.width=10}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-rbnap
+#| fig-cap: "Relationship between numeric_grade and pollscore"
+
+plots <- list()
+# Plot relationship between numeric_grade and pollscore for train_Trump
+plots[["Trump"]]<-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "#A9CCE3") +
+  labs(title = "Relationship between Numeric Grade and Pollscore (train_Trump)",
+       x = "Numeric Grade",
+       y = "Pollscore")
+
+# Plot relationship between numeric_grade and pollscore for train_Harris
+plots[["Harris"]]<-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "#F1948A") +
+  labs(title = "Relationship between Numeric Grade and Pollscore (train_Harris)",
+       x = "Numeric Grade",
+       y = "Pollscore")
+
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 10), "in")) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+
+The second model is as follows:
+
+```{=tex}
+\begin{align} 
+\text{Score}_{Trump} = &\ \beta_1 \, \text{Pollscore} + \beta_2 \, \text{Transparency\_score} + \beta_3 \, \text{Duration} + \notag \\
+        &\ \beta_4 \, \text{Sample\_size} + \beta_5 \, \text{Population} + \beta_6 \, \text{Hypothetical} + \notag \\
+        &\ \beta_7 \, \text{Methodology} + \beta_8 \, \text{Ranked\_choice\_reallocated} + \beta_0 \\[0.5cm]
+\text{Score}_{Harris} = &\ \alpha_1 \, \text{Pollscore} + \alpha_2 \, \text{Transparency\_score} + \alpha_3 \, \text{Duration} + \notag \\
+        &\ \alpha_4 \, \text{Sample\_size} + \alpha_5 \, \text{Population} + \alpha_6 \, \text{Hypothetical} + \notag \\
+        &\ \alpha_7 \, \text{Methodology} + \alpha_8 \, \text{Ranked\_choice\_reallocated} + \alpha_0
+\end{align}
+```
+
+We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
+As shown in the figure below, both "methodology" and "ranked\_choice\_reallocated" were found to be insignificant predictors in both models.
+Thus, they were excluded to reduce model complexity.
+
+```{r, fig.height=100,fig.width=100}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-alovitahm
+#| tbl-cap: "Significant level of variblaes in the aboanded Harris and Trump's model"
+
+# Define and fit models for Trump and Harris
+Trump_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Trump)
+Harris_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Harris)
+
+# Get summaries of the models and extract coefficients
+Harris_summary <- summary(Harris_model_1)
+Trump_summary <- summary(Trump_model_1)
+
+# Extract p-values for Harris and Trump models
+Harris_p_values <- Harris_summary$coefficients[, 4]
+Trump_p_values <- Trump_summary$coefficients[, 4]
+
+# Create a data frame with the results, using row names for the variable names
+combined_results_table <- data.frame(
+  Harris = format(Harris_p_values, scientific = TRUE),
+  Trump = format(Trump_p_values, scientific = TRUE),
+  row.names = rownames(Harris_summary$coefficients)
+)
+
+# Display the combined table with kable, without the Variable column
+combined_kable <- kable(
+  combined_results_table, 
+  caption = "P-Values for Models of Harris and Trump", 
+  col.names = c("Harris", "Trump"),
+  align = "cc"
+)
+
+combined_kable
+
+```
+
+Our final model is as follows:
 
@@
 
-Upon comparing the relationship between "numeric\_grade" and "pollscore," we observed a significant linear relationship, as shown in the following figure.
-Therefore, we removed "numeric\_grade" from the model to satisfy MLR assumptions, resulting in our second model.
-
-```{r, fig.pos="H", fig.height=10, fig.width=10}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-rbnap
-#| fig-cap: "Relationship between numeric_grade and pollscore"
-
-plots <- list()
-# Plot relationship between numeric_grade and pollscore for train_Trump
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "blue") +
-  labs(title = "Relationship between Numeric Grade and Pollscore (train_Trump)",
-       x = "Numeric Grade",
-       y = "Pollscore")
-
-# Plot relationship between numeric_grade and pollscore for train_Harris
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "red") +
-  labs(title = "Relationship between Numeric Grade and Pollscore (train_Harris)",
-       x = "Numeric Grade",
-       y = "Pollscore")
-
-### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 10), "in")) +
-  plot_annotation(
-    theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
-# Print the combined plot
-print(combined_plot)
-
-```
-
-The second model is as follows:
-
-\begin{align} 
-Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
-        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
-Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
-\end{align}
-
-We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
-As shown in the figure below, both "methodology" and "ranked\_choice\_reallocated" were found to be insignificant predictors in both models.
-Thus, they were excluded to reduce model complexity.
-
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitahm
-#| tbl-cap: "Significant level of variblaes in the aboanded Harris's model"
-
-Trump_model_1 <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Trump)
-Harris_model_1 <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Harris)
-# Get the summary of the model
-Harris_summary <- summary(Harris_model_1)
-# Extract coefficients from the summary
-coefficients <- Harris_summary$coefficients
-# Extract p-values
-Harris_p_values <- coefficients[, 4]
-# Create a data frame with the results
-Harris_results_table <- data.frame(
-  Variable = rownames(coefficients),
-  P_Value = format(Harris_p_values, scientific = TRUE)
-)
-Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Model for Harris", col.names = c("Variable", "P-value"))
-
-Harris_kable
-
-```
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitatm
-#| tbl-cap: "Significant level of variblaes in the aboanded Trump's model"
-
-# Get the summary of the model
-Trump_summary <- summary(Trump_model_1)
-# Extract coefficients from the summary
-coefficients <- Trump_summary$coefficients
-# Extract p-values
-Trump_p_values <- coefficients[, 4]
-# Create a data frame with the results
-Trump_results_table <- data.frame(
-  Variable = rownames(coefficients),
-  P_Value = format(Trump_p_values, scientific = TRUE)
-)
-Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Model for Trump", col.names = c("Variable", "P-value"))
-
-Trump_kable
-```
-
-Our final model is as follows:
-
-\begin{align} 
-Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
-        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
-Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
-\end{align}
-
 ## Validation
@@
 #| label: tbl-vohfm
-#| tbl-cap: "VIF of Harris's final model"
-# Add a column for variable names (convert row names to a column)
-
-harris_vif <- vif(Harris_model)
-
-# 将 VIF 结果转换为数据框
-# 如果是 GVIF（针对多分类变量），则处理为数据框
-
+#| tbl-cap: "VIF of Trump and Harris's final model"
+# Calculate VIF for Harris model
+harris_vif <- vif(Harris_model_1)
 harris_vif_df <- as.data.frame(harris_vif)
-
 harris_vif_df$Variable <- rownames(harris_vif_df)
 
-# Rearrange columns so that the variable name column is the first column
-
-harris_vif_df <- harris_vif_df[, c(ncol(harris_vif_df), 1:(ncol(harris_vif_df)-1))]
-
-# Use kable to create a formatted table from VIF results
-
-kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
-
-```
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-votfm
-#| tbl-cap: "VIF of Trump's final model"
-
-trump_vif <- vif(Trump_model)
-
-# 将 VIF 结果转换为数据框
-# 如果是 GVIF（针对多分类变量），则处理为数据框
+# Calculate VIF for Trump model
+trump_vif <- vif(Trump_model_1)
 trump_vif_df <- as.data.frame(trump_vif)
-
-# Add a column for variable names (convert row names to a column)
 trump_vif_df$Variable <- rownames(trump_vif_df)
 
-# Rearrange columns so that the variable name column is the first column
-trump_vif_df <- trump_vif_df[, c(ncol(trump_vif_df), 1:(ncol(trump_vif_df)-1))]
-
-# Use kable to create a formatted table from VIF results
-
-kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
+# Select only the necessary columns: "Variable", "GVIF_Harris", and "GVIF_Trump"
+combined_vif_table <- combined_vif_df[, c("Variable", "GVIF_Harris", "GVIF_Trump")]
+
+# Rename columns for clarity
+colnames(combined_vif_table) <- c("Variable", "Harris VIF", "Trump VIF")
+
+# Use kable to display the combined VIF table
+kable(combined_vif_table, caption = "VIF for Harris and Trump Models", col.names = c("Variable", "Harris VIF", "Trump VIF"))
 
@@
 plots[["Harris"]]<-ggplot(results_df, aes(x = predictions, y = actual)) +
-  geom_point(color = "blue") + # Scatter plot of predicted vs actual values
+  geom_point(color = "#A9CCE3") + # Scatter plot of predicted vs actual values
   labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
-  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + # Add reference line y = x
+  geom_abline(slope = 1, intercept = 0, color = "#F1948A", linetype = "dashed") + # Add reference line y = x
   theme_minimal() # Use minimal theme for the plot
@@
 plots[["Trump"]] <-ggplot(results_df_1, aes(x = predictions_1, y = actual_1)) +
-  geom_point(color = "blue") + # Scatter plot of predicted vs actual values
+  geom_point(color = "#A9CCE3") + # Scatter plot of predicted vs actual values
   labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
-  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + # Add reference line y = x
+  geom_abline(slope = 1, intercept = 0, color = "#F1948A", linetype = "dashed") + # Add reference line y = x
   theme_minimal() # Use minimal theme for the plot
@@
         if (!is.na(skew_val) && skew_val < 1) {
-          feature_values[[col_name]] <- round(mean(col_data, na.rm = TRUE),2)
+          feature_values[[col_name]] <- round(mean(col_data, na.rm = TRUE), 2)
         } else {
-          feature_values[[col_name]] <- round(median(col_data, na.rm = TRUE),2)
+          feature_values[[col_name]] <- round(median(col_data, na.rm = TRUE), 2)
         }
@@
 
-all_candidate_features <- data_frame(trump = trump_features, harris = harris_features)
-
-# Round numeric columns to two decimal places before pivoting
-all_candidate_features <- all_candidate_features %>%
-  mutate(across(everything(), as.character))  # Convert all columns to character for compatibility in pivot_longer
-
-all_candidate_features <- head(all_candidate_features, -1)
-
+# Combine features into a data frame with rows representing variables
+all_candidate_features <- data.frame(
+  Trump = unlist(trump_features),
+  Harris = unlist(harris_features),
+  row.names = names(trump_features)
+)
+
+# Filter the combined data frame to include only the selected variables (excluding "score")
 variables <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
                "sample_size", "population", "ranked_choice_reallocated", 
-               "hypothetical", "score", "duration")
-
-all_candidate_features$variables <- variables
-
-all_candidate_features <- all_candidate_features[, c("variables", setdiff(names(all_candidate_features), "variables"))]
+               "hypothetical", "duration")
+all_candidate_features <- all_candidate_features[variables, ]
 
 # Display the final table with kable
-kable(all_candidate_features)
+kable(all_candidate_features, caption = "Feature Values for Donald Trump and Kamala Harris", col.names = c("Donald Trump", "Kamala Harris"))
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-Harris_predict <- round(predict(Harris_model, newdata = harris_features),2)
-Trump_predict <- round(predict(Trump_model, newdata = trump_features),2)
+```{r,message=FALSE, echo=FALSE,warning=FALSE}
+Harris_predict <- round(predict(Harris_model, newdata = harris_features), 2)
+Trump_predict <- round(predict(Trump_model, newdata = trump_features), 2)
 
@@
 
-# Create the bar plot
+# Create the bar plot with y-axis limit set to 100
 ggplot(predictions, aes(x = Candidate, y = Prediction, fill = Candidate)) +
@@
        y = "Prediction") +
+  ylim(0, 60) +  # Set y-axis limit to 100
   theme_minimal() +
@@
   geom_text(aes(label = Prediction), vjust = -0.3)
+
 ```
@@
 # Define variable groups
-set1_vars <- c("pollster_rating_id", "pollster_id", "sponsor_candidate_id", "sponsor_candidate_party")
-set2_vars <- c("tracking", "internal", "partisan")
-set3_vars <- c("sponsor_ids", "question_id", "internal", "race_id")
-
-# Define a function to generate a grid of plots for a given set of variables with increased text size
+set1_vars <- c("pollster_rating_id", "pollster_id", "sponsor_candidate_id", "sponsor_ids", "question_id", "race_id")
+set2_vars <- c("tracking", "internal", "partisan", "sponsor_candidate_party", "internal")
+
+# Define a function to generate a grid of plots for a given set of variables with smaller text size
 plot_variable_distributions <- function(data, vars) {
@@
       p <- ggplot(data, aes(x = .data[[var]])) +
-        geom_histogram(bins = 30, fill = "steelblue", color = "black") +
+        geom_histogram(bins = 30, fill = "#69b3a2", color = "black") +
         labs(title = var) +
@@
         theme(
-          plot.title = element_text(size = 18, face = "bold"),
+          plot.title = element_text(size = 12, face = "bold"), # Further reduced font size
           axis.title.x = element_blank(),
@@
       p <- ggplot(data, aes(x = .data[[var]])) +
-        geom_bar(fill = "steelblue", color = "black") +
+        geom_bar(fill = "#69b3a2", color = "black") +
         labs(title = var) +
@@
           axis.text.y = element_blank(),
-          axis.text.x = element_text(size = 14, angle = 45, hjust = 1)
+          axis.text.x = element_text(size = 8, angle = 45, hjust = 1) # Further reduced font size
         )
@@
 plot2 <- plot_variable_distributions(raw_data, set2_vars)
-plot3 <- plot_variable_distributions(raw_data, set3_vars)
 
 # Arrange the first three sets of plots into grids and display them
-grid.arrange(grobs = plot1, ncol = 2, top = textGrob("Distribution of Variables (Set 1)", gp=gpar(fontsize=20, fontface="bold")))
-grid.arrange(grobs = plot2, ncol = 2, top = textGrob("Distribution of Variables (Set 2)", gp=gpar(fontsize=20, fontface="bold")))
-grid.arrange(grobs = plot3, ncol = 2, top = textGrob("Distribution of Variables (Set 3)", gp=gpar(fontsize=20, fontface="bold")))
+grid.arrange(grobs = plot1, ncol = 2, top = textGrob("Distribution of Numeric Variables (Set 1)", gp=gpar(fontsize=14, fontface="bold")))
+grid.arrange(grobs = plot2, ncol = 2, top = textGrob("Distribution of Boolean and Categorical Variables (Set 2)", gp=gpar(fontsize=14, fontface="bold")))
 
@@
   ggplot(aes(y = reorder(state, n), x = n)) +
-  geom_bar(stat = "identity", fill = "steelblue", color = "black") +
+  geom_bar(stat = "identity", fill = "#69b3a2", color = "black") +
   labs(title = "Distribution of State (Set 4)") +
@@
   theme(
-    plot.title = element_text(size = 20, face = "bold"),
+    plot.title = element_text(size = 14, face = "bold"), # Further reduced font size
     axis.title.x = element_blank(),
     axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12),
-    axis.text.y = element_text(size = 12)
+    axis.text.x = element_text(size = 8), # Further reduced font size
+    axis.text.y = element_text(size = 8)  # Further reduced font size
   )
@@
   ggplot(aes(x = ranked_choice_round)) +
-  geom_density(fill = "steelblue", alpha = 0.7) +
+  geom_density(fill = "#69b3a2", alpha = 0.7) +
   labs(title = "Distribution of ranked_choice_round (Set 5)") +
@@
   theme(
-    plot.title = element_text(size = 20, face = "bold"),
+    plot.title = element_text(size = 14, face = "bold"), # Further reduced font size
     axis.title.x = element_blank(),
     axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 12)
-  )
-
+    axis.text.x = element_text(size = 8, angle = 45, hjust = 1), # Further reduced font size
+    axis.text.y = element_text(size = 8)  # Further reduced font size
+  )
+
+# Set 8: Created At Plot
 created_at_plot <- raw_data %>%
-  filter(!is.na(created_at)) %>%  # 去掉NA值
+  filter(!is.na(created_at)) %>%  
   ggplot(aes(x = as.POSIXct(created_at, format = '%m/%d/%y %H:%M'))) +
-  geom_density(fill = "steelblue", alpha = 0.7) +
+  geom_density(fill = "#69b3a2", alpha = 0.7) +
   labs(title = "Distribution of Created At (Set 8)") +
@@
   theme(
-    plot.title = element_text(size = 20, face = "bold"),
+    plot.title = element_text(size = 14, face = "bold"), # Further reduced font size
     axis.title.x = element_blank(),
     axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 12)
+    axis.text.x = element_text(size = 8, angle = 45, hjust = 1), # Further reduced font size
+    axis.text.y = element_text(size = 8)  # Further reduced font size
   )
@@
 print(created_at_plot)
-```
+
+```

### 2024-11-03 paper/paper_draft_1.qmd
Add files via upload

@@
 
+# Merge the two VIF data frames by "Variable", adding suffixes to differentiate columns
+combined_vif_df <- merge(harris_vif_df, trump_vif_df, by = "Variable", suffixes = c("_Harris", "_Trump"))
+
 # Select only the necessary columns: "Variable", "GVIF_Harris", and "GVIF_Trump"
@@
 
-## Analysis of YouGov Pollster Methodology
-
 In this appendix, we provide a deep-dive analysis of the methodology employed by YouGov, one of the pollsters included in our sample.
 YouGov is an international online research data and analytics technology group.
-It is a leading platform for online survey, which has a continuously growing dataset of over 27 million registered members.
-This pollster has a 3.0 grade according to FiveThirtyEight, which is the highest score.
+It is a leading platform for online survey, which has a continuously growing dataset of over 27 million registered members. This pollster has a 3.0 grade according to FiveThirtyEight, which is the highest score.
 This analysis covers key aspects of YouGov's survey methodology, highlighting its strengths, weaknesses, and the unique features of its approach.
 
-### Population, Frame, and Sample
-
-YouGov utilizes an online panel to collect survey responses, with participants drawn from a broad population base, which typically comprises all U.S.
-adults citizens.
-Respondents are chosen based on a non-probability sampling, which means not everyone in the population has an equal chance of being selected.
-However, the sample is adjusted using statistical weighting to better represent the target population.
-The sampling frame consists of individuals who have signed up to participate in surveys, representing a range of demographic characteristics.
-However, as an online panel, there may be limitations regarding coverage bias, particularly for individuals with limited internet access.
-
-### Sample Recruitment
-
-YouGov recruits participants through online advertisements and other digital marketing techniques,  with surveys offers surveys in multiple languages.
-The recruitment process is designed to ensure that the panel is as representative as possible.
-For instance, YouGov collects information such as email addresses and IP addresses when new members join the panel.
-Additionally, YouGov monitors survey completion time and answer consistency to ensure the data is accurate.
-Respondents who fail quality checks are removed.
-
-### Sampling Approach and Trade-offs
-
+#### Population, Sample Frame, and Recruitment
+
+YouGov utilizes an online panel consisting of U.S.
+adults.
+Respondents are chosen based on non-probability sampling, meaning not everyone in the population has an equal chance of being selected.
+However, the sample is adjusted using statistical weighting to represent the target population better.
+The sampling frame includes individuals who sign up for surveys, representing diverse demographics, though there may be coverage bias for those with limited internet access.
+
+Participants are recruited through online advertisements and other digital marketing techniques, with surveys offered in multiple languages to increase inclusivity.
+YouGov collects information such as email and IP addresses during panel registration, and quality checks—like monitoring survey completion time and answer consistency—are performed to ensure data integrity.
+Respondents who fail these checks are removed.
+
+#### Sampling Approach and Handling Non-response
 YouGov employs a form of quota sampling combined with weighting adjustments to make the sample representative of the target population.
@@
 
-### Handling Non-response
-
 Non-response is managed by using statistical weighting to adjust the sample to more closely reflect the demographic makeup of the target population.
@@
 
-### Strengths and Weaknesses of the Questionnaire
+#### Strengths and Weaknesses of the Questionnaire
 
@@
 
-## Ideal Methodology and Survey for Predicting the U.S. Presidential Election
+Appendix: Ideal Methodology and Survey for Predicting the U.S. Presidential Election
 
@@
 This methodology will include sampling strategies, respondent recruitment, data validation, poll aggregation, and survey implementation details.
-
-### Sampling Methodology
-A stratified sampling approach will be used to ensure diversity and representation.
-The population will be divided into relevant strata such as age, gender, geographic region, race, and political affiliation.
-This approach ensures that each subgroup is adequately represented, thereby reducing sampling bias.
-
-### Respondent Recruitment
-Respondents will be recruited through online panels.
-Partnerships with established survey platforms and third-party providers will help reach a broad and representative group of participants, such as through platforms like Instagram, YouTube, and various news websites.
-Small monetary compensation or gift cards will be offered as incentives to encourage participation.
-Additional incentives will be provided to underrepresented groups, such as individuals with lower educational attainment or residents of rural areas, to ensure more inclusive recruitment.
-The aim is for a sample size of approximately 10,000 respondents, which would achieve a margin of error of ±1% at a 95% confidence level.
-
-### Data Validation
-Data validation will involve cross-referencing respondent demographic information with census data to confirm representativeness.
-Additionally, responses will be reviewed for accuracy, and suspicious or incomplete answers will be flagged for further inspection.
-Responses completed too quickly or that include repeated answers such as "prefer not to say" or "other" will be discarded.
-IP addresses will be tracked to prevent duplicate submissions.
-
-### Poll Aggregation and Methodology Features
-Once all responses are collected, weights will be applied according to electoral demographics and voter turnout to ensure the sample represents the U.S.
-population.
-Poll aggregation will also involve adjustments for known biases, such as overreporting in certain demographic groups or historical voting trends.
-Bayesian updating will be used to refine predictions continuously as more data becomes available.
-
-### Survey Implementation
-The survey will be implemented using Google Forms, which allows for easy distribution and data collection.
-The survey will include questions related to voter preferences, key issues, and demographic information.
-Questions will be designed to minimize leading language and provide a range of response options to avoid bias.
-Keeping the survey brief (approximately 5 minutes with 12 questions) will help maintain respondent focus.
-
-### Budget Allocation
+The budget allocation as follow:
+
 - $60K for Recruitment Costs and Survey Platform Fees, including advertising
@@
 
+### Sampling Methodology and Respondent Recruitment
+
+To ensure diversity and representation, a stratified sampling approach will be used.
+The population will be divided into relevant strata, including age, gender, geographic region, race, and political affiliation, ensuring each subgroup is adequately represented and reducing sampling bias.
+Respondents will be recruited through partnerships with established survey platforms and third-party providers to reach a broad group of participants across platforms like Instagram, YouTube, and news websites.
+Incentives such as small monetary compensation or gift cards will encourage participation, with additional rewards targeted at underrepresented groups (e.g., individuals with lower educational attainment or rural residents) to enhance inclusivity.
+The target sample size is approximately 10,000 respondents, achieving a margin of error of ±1% at a 95% confidence level.
+
+### Data Collection, Validation, and Poll Aggregation
+
+The survey will be implemented using Google Forms to facilitate easy distribution and data collection, featuring questions on voter preferences, key issues, and demographic information.
+Questions are carefully crafted to minimize leading language and provide diverse response options to avoid bias, with a survey length of about 5 minutes (12 questions) to maintain focus.
+Data validation will involve cross-referencing respondent demographics with census data for representativeness, while responses will be checked for accuracy, with suspicious or incomplete entries flagged for review.
+Responses completed too quickly or with excessive "prefer not to say" or "other" selections will be discarded, and IP addresses will be tracked to prevent duplicate submissions.
+
+Once data collection is complete, weights will be applied according to electoral demographics and voter turnout trends to mirror the U.S.
+population.
+Adjustments will be made for known biases, such as overreporting in certain demographic groups or historical voting patterns.
+Bayesian updating will be employed to refine predictions as new data becomes available, ensuring continuous accuracy.
+
 ### Survey Link and Copy
-The Google Forms survey link will be included here: https://docs.google.com/forms/d/e/1FAIpQLSdcd_neJf83lJMZGzmcUcPkDd-R1vPk98gPIDsD4KC_X6T8tQ/viewform.
+The Google Forms survey link will be included here: https://forms.gle/caLYFxsKkU5oQkXB8.
 
 The survey questions are listed below:
+
 1. **What is your age group?** 
@@
 ```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-dkpv
+#| tbl-cap: "Descriptions of Key Polling Variables"
+
+library(knitr)
+
+# Data frame with selected variables and descriptions only
+variable_descriptions <- data.frame(
+  Variable = c("poll_id", "pollster_id", "pollster", "sponsor_ids", "pollscore", "methodology", 
+               "transparency_score", "state", "start_date", "end_date", "sample_size", 
+               "population", "created_at", "ranked_choice_reallocated", "hypothetical"),
+  Description = c(
+    "Unique identifier for each poll conducted.",
+    "Unique identifier for the polling organization.",
+    "Name of the polling organization.",
+    "Unique identifier(s) for the sponsor(s).",
+    "A numeric value representing pollster reliability score.",
+    "Method used to conduct the poll.",
+    "Score reflecting pollster’s transparency.",
+    "State where poll was conducted or focused.",
+    "Date when the poll started.",
+    "Date when the poll ended.",
+    "Total number of respondents.",
+    "Description of respondent group.",
+    "Timestamp when poll data was created.",
+    "Indicates if ranked-choice reallocations were applied.",
+    "Indicates if poll is about a hypothetical match-up."
+  )
+)
+
+# Display the table with only Variable and Description columns
+kable(variable_descriptions)
+
+```

### 2024-11-03 scripts/04-test_analysis_data.R
Update 04-test_analysis_data.R
Update Preamble

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: test on the analysis data for validation
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
 
 
 

### 2024-11-03 paper/paper_draft_1.qmd
paper reformatted
paper reformatted

--- 2024-11-03 paper/paper_draft_1.qmd
@@
 policies.
-The project predicts that Kamala Harris will narrowly defeat Donald Trump who is predicted to come in second place and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
-format: pdf
+The project predicts that Kamala Harris will secure 47.6% of the vote over Donald Trump's 43.5% and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
+format: 
+  pdf:
+    number_sections: true
 toc: true           
@@
 toc-depth: 2    
-number_sections: true    
 bibliography: references.bib
@@
 
-In this section, we detail our selected variables, discuss key measurements, outline important limitations of our data, and our data cleaning process.
+In this section, we present the components of the raw data, along with the distribution and summary of key variables.
+We also detail the data cleaning procedures, evaluate the reliability of the measurements used, and discuss similar datasets.
 
@@
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| include: false
-# Get unique Poll IDs and print the count
-# 一共有3530个poll
-unique_poll_ids <- unique(raw_data$poll_id)
-```
-
-## Cleaning Process
-Firstly, there are several variables clearly irrelevant to the project and will not be discussed further: notes, url, url_article, url_topline, url_crosstab, and source.
-
 ```{r, fig.height=90, fig.width=90}
@@
 
-Additionally, there are some duplicate variables, and we will retain only one of each, ignoring the rest: pollster, sponsors, display_name, pollster_rating_name, sponsor_candidate, endorsed_candidate_name, population_full, candidate_id, and candidate_name.
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| include: false
-# 这里需要画一个table，展示删除的重复变量
-del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
-           "population_full", "candidate_id", "candidate_name")
-droped_data <- droped_data %>% select(-any_of(del_2))
-```
-
-Constant variables, which cannot impact our predictions, will also be excluded from further discussion.
-These include: endorsed_candidate_id (NA), endorsed_candidate_party (NA), subpopulation (NA), cycle (2024), office_type (U.S.
-President), seat_number (0), seat_name (NA), election_date (11/5/24), stage (general), and nationwide_batch (FALSE).
-
-```{r, fig.height=90, fig.width=90}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-cv
-#| tbl-cap: "Constant variables"
-#| include: false
-# Identify variables where all values are the same (including NA)
-same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
-# Create a data frame with variables and their unique values
-same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
-unique(na.omit(droped_data[[var]]))[1]))
-# Print the names of variables with all identical values using kable
-kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
-del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
-           "office_type", "seat_number", "seat_name")
-droped_data <- droped_data %>% select(-any_of(del_4))
-```
-After cleaning, 27 out of the 52 variables remained potentially relevant to our research.
-We selected 10 variables (@tbl-ivatd) of interest and plotted their distributions in the 【data visualization section】, while the plots of the remaining variables are included in the 【appendix】.
+We selected 10 variables (@tbl-ivatd) of interest and their distributions are shown below.
 ```{r, fig.height=90, fig.width=90}
@@
                "hypothetical", "answer", "numeric_grade", "pollscore", 
-               "transparency_score", "sample_size", "pct"),
+               "transparency_score", "sample_size", "start_date", "end_date", "pct"),
   Description = c(
@@
     "The total number of respondents participating in the poll (e.g., 2712).",
+    "The date the poll began (e.g., 10/8/24).",
+    "The date the poll ended (e.g., 10/11/24).",
     "The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris)."
@@
 
-After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
-This new variable represents the number of days between 'start_date' and 'end_date'.Next, we categorized the 51 different methodologies into four levels, ranging from the least reliable and accurate (level_1) to the most reliable (level_4).
-
-Subsequently, we handled the missing values by imputing numerical variables with their mean values and categorical variables with their mode.
-Since our results are not exact percentages, we used 'score' to name what would typically be called 'pct'.
-We then finalize and tidy up the variable names.
-
-Then, the data is extracted for each candidate individually.
-We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
-After comparison, we observed that the top three candidates—Trump, Harris, and Biden—had significantly higher scores than the remaining candidates.
-Given that Biden has withdrawn from the race, we are now focusing only on the datasets for Trump and Harris for further analysis.
-
-We also split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
-```{r, fig.height=30, fig.width=60}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-eoad
-#| tbl-cap: "Example of analysis data"
-#| include: false
-kable(head(train_Trump), col.names = names(train_Trump))
-```
-
-## Data Visualization
 ```{r}
@@
 
-```{r}
+```{r, fig.height= 5, fig.width=10}
 #| warning: false
@@
 # Combine and print the plots using patchwork
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(3, 4), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
   plot_annotation(
@@
 Overall, these charts provide a visual representation of the polling data, highlighting the dominant methodologies, respondent groups, and response preferences in the dataset.
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```{r, fig.pos="H", fig.width=16, fig.height=8}
 #| warning: false
@@
   theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
+    plot.title = element_text(hjust = 0.5, size = 18),
+    axis.title = element_text(size = 16),
+    axis.text = element_text(size = 16),
+    axis.text.x = element_text(angle = 20, hjust = 1)
   )
@@
   theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
+    plot.title = element_text(hjust = 0.5, size = 18),
+    axis.title = element_text(size = 16),
+    axis.text = element_text(size = 16)
   )
@@
   theme(
-    plot.title = element_text(hjust = 0.5, size = 12),
-    axis.title = element_text(size = 10),
-    axis.text = element_text(size = 10)
-  )
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+    plot.title = element_text(hjust = 0.5, size = 18),
+    axis.title = element_text(size = 16),
+    axis.text = element_text(size = 16)
+  )
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
   plot_annotation(
@@
 On the other hand, lower scores, such as 2.5 and 5, also show some clustering, but with less consistency.
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```{r, fig.pos="H", fig.width=16, fig.height=8}
 #| warning: false
@@
     theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 20),
-      axis.text = element_text(size = 20)
+      plot.title = element_text(hjust = 0.5, size = 18),
+      axis.title = element_text(size = 16),
+      axis.text = element_text(size = 16)
     )
@@
 # Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1, heights = unit(rep(8, 4), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
   plot_annotation(
@@
 The distribution shows some variation across a wide range but seems to have a higher frequency in the middle range (30-40%) compared to the lower and higher extremes.
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```{r, fig.pos="H", fig.width=10, fig.height=6}
 #| warning: false
@@
 # Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 8), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
   plot_annotation(
@@
 ```
-【放appendix】
+
 Both charts in (@fig-dodv) show the normal distribution of poll start and end dates over time.
 The left chart represents the frequency of polls by their start date, while the right chart represents the frequency of polls by their end date, with both distributions primarily concentrated around 2010.The frequency drops after 2010 in both charts.
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```{r, fig.pos="H", fig.width=10, fig.height=5}
 #| warning: false
@@
     theme(
-      plot.title = element_text(hjust = 0.5, size = 12),
-      axis.title = element_text(size = 10),
-      axis.text = element_text(size = 10)
+      plot.title = element_text(hjust = 0.5, size = 14),
+      axis.title = element_text(size = 12),
+      axis.text = element_text(size = 12)
     )
@@
 # Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(8, 4), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
   plot_annotation(
@@
 
+```
+
+## Cleaning Process
+Firstly, there are several variables clearly irrelevant to the project and will not be discussed further: `notes`, `url`, `url_article`, `url_topline`, `url_crosstab`, and `source`.
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
+droped_data <- raw_data %>% select(-any_of(del_1))
+```
+
+Additionally, there are some duplicate variables, and we will retain only one of each, ignoring the rest: `pollster`, `sponsors`, `display_name`, `pollster_rating_name`, `sponsor_candidate`, `endorsed_candidate_name`, `population_full`, `candidate_id`, and `candidate_name`.
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+# 这里需要画一个table，展示删除的重复变量
+del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
+           "population_full", "candidate_id", "candidate_name")
+droped_data <- droped_data %>% select(-any_of(del_2))
+```
+
+Constant variables, which cannot impact our predictions, will also be excluded from further discussion.
+These include: `endorsed_candidate_id` (NA), `endorsed_candidate_party` (NA), `subpopulation` (NA), `cycle` (2024), `office_type` (U.S.
+President), `seat_number` (0), `seat_name` (NA), `election_date` (11/5/24), `stage` (general), and `nationwide_batch` (FALSE).
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cv
+#| tbl-cap: "Constant variables"
+#| include: false
+# Identify variables where all values are the same (including NA)
+same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
+# Create a data frame with variables and their unique values
+same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
+unique(na.omit(droped_data[[var]]))[1]))
+# Print the names of variables with all identical values using kable
+kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
+del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
+           "office_type", "seat_number", "seat_name")
+droped_data <- droped_data %>% select(-any_of(del_4))
+```
+After cleaning, 27 out of the 52 variables remained potentially relevant to our research.
+
+After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
+This new variable represents the number of days between 'start_date' and 'end_date'.Next, we categorized the 51 different methodologies into four levels, ranging from the least reliable and accurate (level_1) to the most reliable (level_4).
+
+Subsequently, we handled the missing values by imputing numerical variables with their mean values and categorical variables with their mode.
+Since our results are not exact percentages, we used 'score' to name what would typically be called 'pct'.
+We then finalize and tidy up the variable names.
+
+Then, the data is extracted for each candidate individually.
+We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
+After comparison, we observed that the top three candidates—Trump, Harris, and Biden—had significantly higher scores than the remaining candidates.
+Given that Biden has withdrawn from the race, we are now focusing only on the datasets for Trump and Harris for further analysis.
+
+We also split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
+```{r, fig.height=30, fig.width=60}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-eoad
+#| tbl-cap: "Example of analysis data"
+#| include: false
+kable(head(train_Trump), col.names = names(train_Trump))
 ```
@@
 
-```{r, fig.pos="H", fig.height=30, fig.width=60}
+```{r, fig.pos="H", fig.width=14, fig.height=6}
 #| warning: false
@@
 
+# Create a list to store the plots
 plots <- list()
-# Plot a histogram for the 'pct' variable
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = score)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = score)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+
+# Plot a histogram for the 'pct' variable in Trump data
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Pct for Trump", x = "pct", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
+
+# Plot a histogram for the 'pct' variable in Harris data
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Pct for Harris", x = "pct", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
 
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(20, 20), "in")) +
+# Arrange the plots vertically with one column and consistent styling
+combined_plot <- wrap_plots(plots, ncol = 2) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 18)
+    )
+  )
+
 # Print the combined plot
@@
 
-```{r, fig.pos="H", fig.height=10, fig.width=20}
+```{r, fig.pos="H", fig.height=7, fig.width=14 }
 #| warning: false
@@
 
+# Create a list to store the plots
 plots <- list()
-# Plot a histogram for the 'pct' variable
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = duration)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of duration for Trump", x = "Duration", y = "Frequency")
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = duration)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of duration", x = "Duration", y = "Frequency")
+
+# Plot a histogram for the 'duration' variable in Trump data
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Duration for Trump", x = "Duration", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
+
+# Plot a histogram for the 'duration' variable in Harris data
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Duration for Harris", x = "Duration", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),  # Consistent title font size
+    axis.title = element_text(size = 16),  # Consistent axis title font size
+    axis.text = element_text(size = 14)  # Consistent axis text font size
+  )
 
 ### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(5, 5), "in")) +
+# Arrange the plots vertically with one column
+combined_plot <- wrap_plots(plots, ncol = 2) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
+      plot.title = element_text(hjust = 0.5, size = 18)
+    )
+  )
+
 # Print the combined plot
@@
 
+```{=tex}
+\begin{align} 
+\text{Score}_{Trump} = &\ \beta_1 \, \text{Pollscore} + \beta_2 \, \text{Transparency\_score} + \beta_3 \, \text{Duration} + \notag \\
+        &\ \beta_4 \, \text{Sample\_size} + \beta_5 \, \text{Population} + \beta_6 \, \text{Hypothetical} + \beta_7 \, \text{Numeric\_grade} + \notag \\
+        &\ \beta_8 \, \text{Methodology} + \beta_9 \, \text{Ranked\_choice\_reallocated} + \beta_0 \\[0.5cm]
+\text{Score}_{Harris} = &\ \alpha_1 \, \text{Pollscore} + \alpha_2 \, \text{Transparency\_score} + \alpha_3 \, \text{Duration} + \notag \\
+        &\ \alpha_4 \, \text{Sample\_size} + \alpha_5 \, \text{Population} + \alpha_6 \, \text{Hypothetical} + \alpha_7 \, \text{Numeric\_grade} + \notag \\
+        &\ \alpha_8 \, \text{Methodology} + \alpha_9 \, \text{Ranked\_choice\_reallocated} + \alpha_0
+\end{align}
+
+```
+
+Upon comparing the relationship between "numeric\_grade" and "pollscore," we observed a significant linear relationship, as shown in the following figure.
+Therefore, we removed "numeric\_grade" from the model to satisfy MLR assumptions, resulting in our second model.
+```{r, fig.pos="H", fig.height=6, fig.width=10}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-rbnap
+#| fig-cap: "Relationship between numeric_grade and pollscore"
+
+plots <- list()
+# Plot relationship between numeric_grade and pollscore for train_Trump
+plots[["Trump"]]<-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "#A9CCE3") +
+  labs(title = "Numeric Grade VS Pollscore in Trump's Training Set",
+       x = "Numeric Grade",
+       y = "Pollscore")
+
+# Plot relationship between numeric_grade and pollscore for train_Harris
+plots[["Harris"]]<-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "#F1948A") +
+  labs(title = "Numeric Grade VS Pollscore in Harris's Training Set",
+       x = "Numeric Grade",
+       y = "Pollscore")
+
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+
+The second model is as follows:
+
+```{=tex}
+\begin{align} 
+\text{Score}_{Trump} = &\ \beta_1 \, \text{Pollscore} + \beta_2 \, \text{Transparency\_score} + \beta_3 \, \text{Duration} + \notag \\
+        &\ \beta_4 \, \text{Sample\_size} + \beta_5 \, \text{Population} + \beta_6 \, \text{Hypothetical} + \notag \\
+        &\ \beta_7 \, \text{Methodology} + \beta_8 \, \text{Ranked\_choice\_reallocated} + \beta_0 \\[0.5cm]
+\text{Score}_{Harris} = &\ \alpha_1 \, \text{Pollscore} + \alpha_2 \, \text{Transparency\_score} + \alpha_3 \, \text{Duration} + \notag \\
+        &\ \alpha_4 \, \text{Sample\_size} + \alpha_5 \, \text{Population} + \alpha_6 \, \text{Hypothetical} + \notag \\
+        &\ \alpha_7 \, \text{Methodology} + \alpha_8 \, \text{Ranked\_choice\_reallocated} + \alpha_0
+\end{align}
+```
+
+We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
+As shown in the figure below, both "methodology" and "ranked\_choice\_reallocated" were found to be insignificant predictors in both models.
+Thus, they were excluded to reduce model complexity.
+
+```{r, fig.height=100,fig.width=100}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-alovitahm
+#| tbl-cap: "Significant level of variblaes in the aboanded Harris and Trump's model"
+
+# Define and fit models for Trump and Harris
+Trump_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Trump)
+Harris_model_1 <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
+    methodology, data = train_Harris)
+
+# Get summaries of the models and extract coefficients
+Harris_summary <- summary(Harris_model_1)
+Trump_summary <- summary(Trump_model_1)
+
+# Extract p-values for Harris and Trump models
+Harris_p_values <- Harris_summary$coefficients[, 4]
+Trump_p_values <- Trump_summary$coefficients[, 4]
+
+# Create a data frame with the results, using row names for the variable names
+combined_results_table <- data.frame(
+  Harris = format(Harris_p_values, scientific = TRUE),
+  Trump = format(Trump_p_values, scientific = TRUE),
+  row.names = rownames(Harris_summary$coefficients)
+)
+
+# Display the combined table with kable, without the Variable column
+combined_kable <- kable(
+  combined_results_table, 
+  caption = "P-Values for Models of Harris and Trump", 
+  col.names = c("Harris", "Trump"),
+  align = "cc"
+)
+
+combined_kable
+
+```
+
+Our final model is as follows:
+
+```{=tex}
 \begin{align} 
@@
 \end{align}
-
-Upon comparing the relationship between "numeric\_grade" and "pollscore," we observed a significant linear relationship, as shown in the following figure.
-Therefore, we removed "numeric\_grade" from the model to satisfy MLR assumptions, resulting in our second model.
-
-```{r, fig.pos="H", fig.height=10, fig.width=10}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-rbnap
-#| fig-cap: "Relationship between numeric_grade and pollscore"
-
-plots <- list()
-# Plot relationship between numeric_grade and pollscore for train_Trump
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "blue") +
-  labs(title = "Relationship between Numeric Grade and Pollscore (train_Trump)",
-       x = "Numeric Grade",
-       y = "Pollscore")
-
-# Plot relationship between numeric_grade and pollscore for train_Harris
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "red") +
-  labs(title = "Relationship between Numeric Grade and Pollscore (train_Harris)",
-       x = "Numeric Grade",
-       y = "Pollscore")
-
-### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 10), "in")) +
-  plot_annotation(
-    theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
-# Print the combined plot
-print(combined_plot)
-
-```
-
-The second model is as follows:
-
-\begin{align} 
-Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
-        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
-Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
-\end{align}
-
-We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
-As shown in the figure below, both "methodology" and "ranked\_choice\_reallocated" were found to be insignificant predictors in both models.
-Thus, they were excluded to reduce model complexity.
-
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitahm
-#| tbl-cap: "Significant level of variblaes in the aboanded Harris's model"
-
-Trump_model_1 <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Trump)
-Harris_model_1 <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Harris)
-# Get the summary of the model
-Harris_summary <- summary(Harris_model_1)
-# Extract coefficients from the summary
-coefficients <- Harris_summary$coefficients
-# Extract p-values
-Harris_p_values <- coefficients[, 4]
-# Create a data frame with the results
-Harris_results_table <- data.frame(
-  Variable = rownames(coefficients),
-  P_Value = format(Harris_p_values, scientific = TRUE)
-)
-Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Model for Harris", col.names = c("Variable", "P-value"))
-
-Harris_kable
-
-```
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitatm
-#| tbl-cap: "Significant level of variblaes in the aboanded Trump's model"
-
-# Get the summary of the model
-Trump_summary <- summary(Trump_model_1)
-# Extract coefficients from the summary
-coefficients <- Trump_summary$coefficients
-# Extract p-values
-Trump_p_values <- coefficients[, 4]
-# Create a data frame with the results
-Trump_results_table <- data.frame(
-  Variable = rownames(coefficients),
-  P_Value = format(Trump_p_values, scientific = TRUE)
-)
-Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Model for Trump", col.names = c("Variable", "P-value"))
-
-Trump_kable
-```
-
-Our final model is as follows:
-
-\begin{align} 
-Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
-        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
-Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
-\end{align}
+```
 
@@
 #| label: tbl-vohfm
-#| tbl-cap: "VIF of Harris's final model"
-# Add a column for variable names (convert row names to a column)
-
-harris_vif <- vif(Harris_model)
-
-# 将 VIF 结果转换为数据框
-# 如果是 GVIF（针对多分类变量），则处理为数据框
-
+#| tbl-cap: "VIF of Trump and Harris's final model"
+# Calculate VIF for Harris model
+harris_vif <- vif(Harris_model_1)
 harris_vif_df <- as.data.frame(harris_vif)
-
 harris_vif_df$Variable <- rownames(harris_vif_df)
 
-# Rearrange columns so that the variable name column is the first column
-
-harris_vif_df <- harris_vif_df[, c(ncol(harris_vif_df), 1:(ncol(harris_vif_df)-1))]
-
-# Use kable to create a formatted table from VIF results
-
-kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
-
-```
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-votfm
-#| tbl-cap: "VIF of Trump's final model"
-
-trump_vif <- vif(Trump_model)
-
-# 将 VIF 结果转换为数据框
-# 如果是 GVIF（针对多分类变量），则处理为数据框
+# Calculate VIF for Trump model
+trump_vif <- vif(Trump_model_1)
 trump_vif_df <- as.data.frame(trump_vif)
-
-# Add a column for variable names (convert row names to a column)
 trump_vif_df$Variable <- rownames(trump_vif_df)
 
-# Rearrange columns so that the variable name column is the first column
-trump_vif_df <- trump_vif_df[, c(ncol(trump_vif_df), 1:(ncol(trump_vif_df)-1))]
-
-# Use kable to create a formatted table from VIF results
-
-kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
+# Combine the VIF data frames by Variable column
+combined_vif_table <- merge(harris_vif_df, trump_vif_df, by = "Variable", suffixes = c("_Harris", "_Trump"))
+
+# Select only the necessary columns: "Variable", "GVIF_Harris", and "GVIF_Trump"
+combined_vif_table <- combined_vif_table[, c("Variable", "GVIF_Harris", "GVIF_Trump")]
+
+# Rename columns for clarity
+colnames(combined_vif_table) <- c("Variable", "Harris VIF", "Trump VIF")
+
+# Use kable to display the combined VIF table
+kable(combined_vif_table, caption = "VIF for Harris and Trump Models", col.names = c("Variable", "Harris VIF", "Trump VIF"))
 
@@
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+```{r, fig.height= 7, fig.width=14}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-mdp
+#| fig-cap: "Model diagnostic plots"
 par(mfrow=c(2,2))
@@
 
-```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 10, fig.width=10}
+```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 5, fig.width=10}
 # Generate predictions using the model
@@
 # Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 8), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2) +
   plot_annotation(
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
 Harris_predict <- round(predict(Harris_model, newdata = harris_features),2)
@@
 ## Analysis of YouGov Pollster Methodology
-
 In this appendix, we provide a deep-dive analysis of the methodology employed by YouGov, one of the pollsters included in our sample.
@@
 
-### Population, Frame, and Sample
-
-YouGov utilizes an online panel to collect survey responses, with participants drawn from a broad population base, which typically comprises all U.S.
-adults citizens.
-Respondents are chosen based on a non-probability sampling, which means not everyone in the population has an equal chance of being selected.
-However, the sample is adjusted using statistical weighting to better represent the target population.
-The sampling frame consists of individuals who have signed up to participate in surveys, representing a range of demographic characteristics.
-However, as an online panel, there may be limitations regarding coverage bias, particularly for individuals with limited internet access.
-
-### Sample Recruitment
-
-YouGov recruits participants through online advertisements and other digital marketing techniques,  with surveys offers surveys in multiple languages.
-The recruitment process is designed to ensure that the panel is as representative as possible.
-For instance, YouGov collects information such as email addresses and IP addresses when new members join the panel.
-Additionally, YouGov monitors survey completion time and answer consistency to ensure the data is accurate.
-Respondents who fail quality checks are removed.
-
-### Sampling Approach and Trade-offs
-
+### Population, Sample Frame, and Recruitment
+
+YouGov utilizes an online panel consisting of U.S.
+adults.
+Respondents are chosen based on non-probability sampling, meaning not everyone in the population has an equal chance of being selected.
+However, the sample is adjusted using statistical weighting to represent the target population better.
+The sampling frame includes individuals who sign up for surveys, representing diverse demographics, though there may be coverage bias for those with limited internet access.
+
+Participants are recruited through online advertisements and other digital marketing techniques, with surveys offered in multiple languages to increase inclusivity.
+YouGov collects information such as email and IP addresses during panel registration, and quality checks—like monitoring survey completion time and answer consistency—are performed to ensure data integrity.
+Respondents who fail these checks are removed.
+
+### Sampling Approach and Handling Non-response
 YouGov employs a form of quota sampling combined with weighting adjustments to make the sample representative of the target population.

### 2024-11-04 scripts/04-test_analysis_data.R
Update 04-test_analysis_data.R
Update test data structure

@@ -17,8 +17,91 @@ library(testthat)
 library(arrow)  # For reading Parquet files
 library(here)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
+Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
+Harris_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
+Trump_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
+Harris_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
 
 #### Test data ####
+
+# Ensure testthat setup
+context("Data validation tests for Trump and Harris datasets")
+
+# Test 1: Check if the datasets have the expected columns
+test_that("Expected columns are present in Trump and Harris test and train datasets", {
+  expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
+                        "sample_size", "population", "ranked_choice_reallocated", 
+                        "hypothetical", "score", "duration")
+  
+  # Check columns in each dataset
+  expect_true(all(expected_columns %in% colnames(Trump_test)))
+  expect_true(all(expected_columns %in% colnames(Harris_test)))
+  expect_true(all(expected_columns %in% colnames(Trump_train)))
+  expect_true(all(expected_columns %in% colnames(Harris_train)))
+})
+
+# Test 2: Check for missing values
+test_that("No missing values in critical columns of test and train datasets", {
+  # List critical columns
+  critical_columns <- c("numeric_grade", "pollscore", "score", "sample_size", "population")
+  
+  # Check for missing values
+  for (col in critical_columns) {
+    expect_true(all(!is.na(Trump_test[[col]])), info = paste("Missing values in Trump_test:", col))
+    expect_true(all(!is.na(Harris_test[[col]])), info = paste("Missing values in Harris_test:", col))
+    expect_true(all(!is.na(Trump_train[[col]])), info = paste("Missing values in Trump_train:", col))
+    expect_true(all(!is.na(Harris_train[[col]])), info = paste("Missing values in Harris_train:", col))
+  }
+})
+
+# Test 3: Check data types of columns
+test_that("Columns have the correct data types", {
+  # Numeric columns
+  numeric_columns <- c("numeric_grade", "pollscore", "transparency_score", "sample_size", "score", "duration")
+  
+  # Logical columns
[…]

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Update discussion

@@
 
-This paper presents a predictive analysis of voter support for 2024 U.S.
-presidential candidates Kamala Harris and Donald Trump.
-Using a “poll-of-polls” approach, it integrates polling data from diverse sources, emphasizing reliability, sample size, and methodology.
-Linear and Bayesian models were applied to improve prediction accuracy.
-
-The analysis provides two key insights.
-First, our model predicts a slight advantage for Kamala Harris, with a support estimate of 47.6% compared to Donald Trump’s 43.5%, indicating a competitive but narrow lead.
-Second, it underscores the impact of poll reliability on predictive accuracy.
-Traditional methods like live phone surveys show greater accuracy than online methods, reinforcing the importance of reliability-weighted data in improving forecast precision.
+This study employs a multiple linear regression model to analyze polling data, aiming to forecast public support for U.S.
+2024 presidential election candidates Kamala Harris and Donald Trump.By identifying key determinants of polling accuracy, this analysis predicts a slight lead for Kamala Harris with 47.6% support over Donald Trump’s 43.5%.
+
+Findings reveal that transparency and demographic representation are essential to reliable election forecasts.
+Polls with higher transparency scores yield more accurate predictions, emphasizing the importance of clear polling practices.
+Variations in sample size and population type also underscore the need for representative sampling to capture genuine voter sentiment.
 

### 2024-11-04 paper/paper_draft_1.qmd
Update paper_draft_1.qmd
Update conclusion

@@
 
-Overall, our approach demonstrates how feature engineering and predictive modeling can offer insights into candidate support based on the available data.
-However, it is important to interpret these results cautiously, as they rely on specific variables and assumptions embedded within the dataset.
-In this analysis, we aggregated representative feature values for each candidate by using the mean or median for numeric variables, the mode for categorical variables, and the most frequent occurrence for Boolean values.
-Further refinement and additional data could enhance the robustness of these predictions, contributing to a more comprehensive forecast in future studies.
+The results indicate that high transparency scores and reliable polling methods improve prediction quality, while careful attention to demographic representation—such as sample size and population type—ensures the polling data reflects the broader electorate.
+The model forecasts a slight lead for Kamala Harris, with an estimated 47.6% support compared to 43.5% for Donald Trump, underscoring the essential role of reliable data sources in public opinion forecasting.
+These findings highlight the importance of stringent polling standards and precise demographic selection in enhancing the predictive accuracy of electoral models.
 

### 2024-11-04 paper/paper_draft_1.qmd
bug fixed, Paper graphing updated, readme updated
Paper graphing updated, readme updated, bug fixd

--- 2024-11-03 paper/paper_draft_1.qmd
@@
 The project predicts that Kamala Harris will secure 47.6% of the vote over Donald Trump's 43.5% and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
-format: 
-  pdf:
-    number_sections: true
+format: pdf
+toc-depth: 2    
+number-sections: true
 toc: true           
 toc-title: "Table of Contents" 
-toc-depth: 2    
 bibliography: references.bib
@@
 
-This paper is structured as follows: first, the data collection and filtering processes are outlined, followed by a description of the methodological framework, introducing linear modeling approaches.
-The results are then presented and analyzed, with a discussion on broader implications.
-The paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
-
-This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S.
-presidential election.
-These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
- 【最后改结构描述加cross-reference】
+The structure of this report is as follows: The @sec-data provides an overview of the raw data's origin and includes visualizations of some key variables.
+Additionally, detailed steps for cleaning the data are explained in this section, and the measurement of the raw data is analyzed in depth.
+Similar datasets are also discussed here.
+The @sec-model includes a detailed description of the model, covering the estimators and estimand.
+It also explains why alternative models were not chosen and validates our final model.
+The @sec-result presents the main findings of our model.
+The @sec-discussion analyzes the effects of different variables on the predictions, discusses the model's limitations, and explores its implications for real-world applications.
+The @sec-appendix reviews the YouGov pollster methodology, explains how to create an ideal survey for predicting election outcomes, and includes visualizations of less important raw data.
+
+In this project, We used R[@citeR] and several R packages for data processing, analysis, and visualization.
+Specifically, tidyverse[@citeTidyverse], arrow[@citeArrow], dplyr[@citeDplyr], tidyr[@citeTidyr], janitor[@citeJanitor], lubridate[@citeLubridate], and here[@citeHere] were used for data processing, cleaning, date and time operations, project path management, and efficient data storage and reading.
+knitr[@citeKnitr], kableExtra[@citeKableExtra], patchwork[@citePatchwork], gridExtra[@citeGridExtra], grid[@citeGrid], and ggplot2[@citeGgplot2] were used for creating dynamic reports, beautifying table outputs, data visualization, and arranging multiple charts.
+car[@citeCar] and moments[@citeMoments] were used for model analysis and diagnostics.
+testthat[@citeTestthat] was used for writing and executing unit tests
 
@@
 
-## Overview
-The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' (@citeRawData).
+## Overview {#sec-data_overview}
+The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' [@citeRawData].
 FiveThirtyEight is a well-known website recognized for its political, economic, and sports analyses.
@@
 The dataset includes 52 variables, 17,133 samples and 3530 polls from various polling sources.
-These variables are shown in the below table(@tbl-vord).
+These variables are shown in the below table@tbl-vord.
 
@@
 
-We selected 10 variables (@tbl-ivatd) of interest and their distributions are shown below.
+We selected 10 variables @tbl-ivatd of interest and their distributions are shown below.
 ```{r, fig.height=90, fig.width=90}
@@
 
-The left bar chart in (@fig-bv) shows the distribution of the `ranked_choice_reallocated` variable.
+The left bar chart in @fig-bv shows the distribution of the `ranked_choice_reallocated` variable.
 The chart indicates that the majority of the data points are marked as `FALSE`, meaning ranked-choice voting reallocations have not been applied in most cases.
@@
 
-The right bar chart in (@fig-bv) illustrates the distribution of the `hypothetical` variable.
+The right bar chart in @fig-bv illustrates the distribution of the `hypothetical` variable.
 It shows that a larger proportion of the data is marked as `TRUE`, indicating that the poll results are often based on hypothetical match-ups.
@@
 
-```{r, fig.height= 5, fig.width=10}
+```{r, fig.height= 5, fig.width=10, fig.pos="H"}
 #| warning: false
@@
 #| label: fig-bv
-#| fig-cap: "Boolean variables"
+#| fig-cap: "Distribution of boolean variables"
 plots <- list()
@@
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
+  labs(x = "Ranked Choice Reallocated", y = "Count") +
   theme_minimal(base_size = 15) +
@@
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Hypothetical", x = "Hypothetical", y = "Count") +
+  labs(x = "Hypothetical", y = "Count") +
   theme_minimal(base_size = 15) +
@@
 The three charts depict the distribution of key variables in the dataset: `methodology`, `population`, and `answer`.
-In the most left chart of (@fig-cv), we see that the most frequently used polling methodology is "Online Panel," followed by "Live Phone" and "Live Phone/Text-to-Web." The "Online Panel" category significantly outnumbers the others, while the "Other" category also includes a notable count, representing various methodologies grouped together.
-
-The middle chart of (@fig-cv) shows the distribution of different respondent groups.
+In the most left chart of @fig-cv, we see that the most frequently used polling methodology is "Online Panel," followed by "Live Phone" and "Live Phone/Text-to-Web." The "Online Panel" category significantly outnumbers the others, while the "Other" category also includes a notable count, representing various methodologies grouped together.
+
+The middle chart of @fig-cv shows the distribution of different respondent groups.
 "lv" (likely voters) and "rv" (registered voters) dominate, with "rv" showing a slightly higher count, indicating that these two groups make up the majority of the sample.
@@
 
-The most right chart of (@fig-cv), `Top 3 Answer and Others`, illustrates the responses given in the polls.
+The most right chart of @fig-cv, `Top 3 Answer and Others`, illustrates the responses given in the polls.
 "Biden" and "Trump" have similar counts, with "Trump" being slightly higher, while the "Other" category also shows a significant proportion.
@@
 #| label: fig-cv
-#| fig-cap: "Catogorical variables"
+#| fig-cap: "Distribution of catogorical variables"
 
@@
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Top 3 Methodologies and Others", x = "Methodology", y = "Count") +
+  labs(x = "Methodology", y = "Count") +
   theme_minimal(base_size = 15) +
@@
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Population", x = "Population", y = "Count") +
+  labs(x = "Population", y = "Count") +
   theme_minimal(base_size = 15) +
@@
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  labs(title = "Top 3 answer and Others", x = "answer", y = "Count") +
+  labs(x = "Answer", y = "Count") +
   theme_minimal(base_size = 15) +
@@
 ```
-The `numeric_grade` histogram in (@fig-donvp1) shows the distribution of a numeric rating assigned to pollsters, representing their overall quality or reliability.
+The `numeric_grade` histogram in @fig-donvp1 shows the distribution of a numeric rating assigned to pollsters, representing their overall quality or reliability.
 The data appear to cluster heavily around scores of 2 and 3, suggesting that a large number of pollsters fall within these quality ranges.
@@
 
-The `pollscore` histogram in (@fig-donvp1) indicates the reliability of each pollster, with lower (more negative) values being better.
+The `pollscore` histogram in @fig-donvp1 indicates the reliability of each pollster, with lower (more negative) values being better.
 The distribution shows a peak around zero, with a significant number of pollsters having scores close to zero or slightly negative, and most values being negative, indicating relatively high reliability overall.
@@
 
-The distribution of `transparency_score` in (@fig-donvp1) shows a wide spread, with notable peaks at several discrete points, but no clear pattern overall.
+The distribution of `transparency_score` in @fig-donvp1 shows a wide spread, with notable peaks at several discrete points, but no clear pattern overall.
 Higher scores, such as 7.5 and 10, have high frequencies, indicating that some pollsters tend to achieve relatively high transparency.
@@
     geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    labs(x = variable, y = "Frequency") +
     theme_minimal(base_size = 30) +
@@
 
-The `Distribution of sample_size` histogram in (@fig-donvp2) illustrates the frequency of poll sample sizes.
+The `Distribution of sample_size` histogram in @fig-donvp2 illustrates the frequency of poll sample sizes.
 The majority of polls have relatively small sample sizes, with the frequency decreasing sharply as the sample size increases.
@@
 
-The `Distribution of pct` histogram in (@fig-donvp2) represents the frequency distribution of vote percentages received by candidates in various polls.
+The `Distribution of pct` histogram in @fig-donvp2 represents the frequency distribution of vote percentages received by candidates in various polls.
 Most polls have percentage values concentrated around the 30-40% range, with visible peaks at around 0% and 40%.
@@
     geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    labs(x = variable, y = "Frequency") +
     theme_minimal(base_size = 30) +
@@
 
-Both charts in (@fig-dodv) show the normal distribution of poll start and end dates over time.
+Both charts in @fig-dodv show the normal distribution of poll start and end dates over time.
 The left chart represents the frequency of polls by their start date, while the right chart represents the frequency of polls by their end date, with both distributions primarily concentrated around 2010.The frequency drops after 2010 in both charts.
@@
     geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    labs(x = variable, y = "Frequency") +
         theme_minimal(base_size = 30) +
@@
 #| include: false
-# 这里需要画一个table，展示删除的重复变量
+
 del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
@@
 
-# Model
-
-## Overview
-
-In the modeling process, we used the `arrow` package to handle parquet files.
-The model parameters were examined using the `car` and `moments` packages.
-Additionally, `tidyverse`, `knitr`, `dplyr`, `patchwork`, `kableExtra`, `gridExtra`, and `grid` were employed to visualize and evaluate the model's performance and assumptions.
-
-We developed two models to predict the final competitiveness of Trump and Harris in the November 5, 2024, U.S.
+# Model {#sec-model}
+
+## Overview {#sec-Model_Overview}
+In this project, we developed two models to predict the final competitiveness of Donald John Trump and Kamala Devi Harris in the November 5, 2024, U.S.
 presidential election.
@@
 
-The model formula is as follows:
+The final models are as follows:
 
@@
 Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6 \right \} \notag 
 \end{align}
@@
 
-The estimands, Score\_Trump and Score\_Harris, represent the competitiveness of each candidate.
+The estimands, Score_Trump and Score_Harris, represent the competitiveness of each candidate.
 A higher score indicates stronger competitiveness.
@@
 
-"pollscore", "transparency\_score", "duration", "sample\_size", "population", and "hypothetical" are our estimators.
-"duration" represents the length of a poll in days.
+`pollscore`, `transparency_score`, `duration`, `sample_size`, `population`, and `hypothetical` are our estimators.
+`duration` represents the length of a poll in days.
 Detailed descriptions of the other estimators are provided in the data section.
@@
 2. **Multivariate Normality**: The residuals (differences between observed and predicted values) are normally distributed.
-3. **No Multicollinearity**: The correlations between independent variables are not too high.
-4. **Homoscedasticity**: The variance of residuals remains consistent across all values of the independent variables.
+3. **No Multicollinearity**: The correlations between independent variables are not significant.
+4. **Homoscedasticity**: The variance of residuals remains consistent across all values of the redictors.
 
@@
 
-Our estimand, "score," represents the support rate of a candidate in a particular poll, corresponding to the "pct" in the raw data.
-However, due to our methodology, the final result cannot be expressed as a proportion, and thus we named it "score." The figures below show the distribution of scores for Trump and Harris in their respective training sets.
+Our estimand, `score` represents the support rate of a candidate in a particular poll, corresponding to the `pct` in the raw data.
+However, due to our methodology, the final result cannot be expressed as a proportion, and thus we named it `score`.
+The @fig-dositd shows the distribution of scores for Trump and Harris in their respective training sets.
 It can be observed that both distributions are approximately normal.
-Different form raw.......
+Compared to the distribution of `pct` in the raw data, it can be observed that Trump and Harris have very few `score` in the low range.
+This means that most candidates have very low support rates.
 
@@
 #| label: fig-dositd
-#| fig-cap: "Distribution of scores in training dataset"
+#| fig-cap: "Distribution of score in training datasets"
 
@@
   geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
-  labs(title = "Pct for Trump", x = "pct", y = "Frequency") +
+  labs(title = "Trump", x = "Score", y = "Frequency") +
   theme_minimal(base_size = 16) +
@@
   geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
-  labs(title = "Pct for Harris", x = "pct", y = "Frequency") +
+  labs(title = "Harris", x = "Score", y = "Frequency") +
   theme_minimal(base_size = 16) +
@@
 
-Since our training set was obtained via simple random sampling, the distributions of "pollscore", "transparency\_score", "sample\_size", "population", and "hypothetical" are similar to those in the raw data, which will not be further elaborated here.
-The variable "duration" is derived from the difference between "start\_date" and "end\_date" in the original data.
-This means that our model cannot account for time series effects, but we simplified this to meet the assumptions of using MLR given the linear relationship between these two factors.
-Below are histograms that display the duration of polls nominating Trump and Harris.
+Since our training set was obtained via simple random sampling, the distributions of `pollscore`, `transparency_score`, `sample_size`, `population`, and `hypothetical` are similar to those in the raw data, which will not be further elaborated here.
+The variable `duration` is derived from the difference between `start_date` and `end_date` in the original data.
+This means that our model cannot account for time series effects, but we simplified this to meet the assumptions of using MLR given the linear relationship between these two variables.
+@fig-doditd are histograms that display the `duration` of polls nominating Trump and Harris.
 It can be observed that they follow a highly skewed distribution, with most values clustered around 1-2 days.
@@
 #| label: fig-doditd
-#| fig-cap: "Distribution of durations in training dataset"
+#| fig-cap: "Distribution of duration in training dataset"
 
@@
   geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
-  labs(title = "Duration for Trump", x = "Duration", y = "Frequency") +
+  labs(title = "Trump", x = "Duration", y = "Frequency") +
   theme_minimal(base_size = 16) +
@@
   geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
-  labs(title = "Duration for Harris", x = "Duration", y = "Frequency") +
+  labs(title = "Harris", x = "Duration", y = "Frequency") +
   theme_minimal(base_size = 16) +
@@
 
-It is worth noting that although our final model does not consider "methodology," in the initial model exploration phase, we simplified the 51 different categories of the "methodology" variable into four levels to maintain simplicity.
-Level 1 represents the lowest reliability, while level 4 represents the highest.
+It is worth noting that although our final model does not consider `methodology`, in the initial model exploration phase, we simplified the 51 different categories of the `methodology` variable into four levels to maintain simplicity.
+`level_1` represents the lowest reliability, while `level_4` represents the highest.
 The specific classifications are as follows:
@@
 \begin{align} 
-\text{Score}_{Trump} = &\ \beta_1 \, \text{Pollscore} + \beta_2 \, \text{Transparency\_score} + \beta_3 \, \text{Duration} + \notag \\
-        &\ \beta_4 \, \text{Sample\_size} + \beta_5 \, \text{Population} + \beta_6 \, \text{Hypothetical} + \beta_7 \, \text{Numeric\_grade} + \notag \\
-        &\ \beta_8 \, \text{Methodology} + \beta_9 \, \text{Ranked\_choice\_reallocated} + \beta_0 \\[0.5cm]
-\text{Score}_{Harris} = &\ \alpha_1 \, \text{Pollscore} + \alpha_2 \, \text{Transparency\_score} + \alpha_3 \, \text{Duration} + \notag \\
-        &\ \alpha_4 \, \text{Sample\_size} + \alpha_5 \, \text{Population} + \alpha_6 \, \text{Hypothetical} + \alpha_7 \, \text{Numeric\_grade} + \notag \\
-        &\ \alpha_8 \, \text{Methodology} + \alpha_9 \, \text{Ranked\_choice\_reallocated} + \alpha_0
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \notag \\
+        &\beta_7Methodology + \beta_8Numeric\_grade + \beta_9Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag \\
+        &\alpha_7Methodology + \alpha_8Numeric\_grade + \alpha_9Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6,7,8,9 \right \} \notag 
 \end{align}
-
-```
-
-Upon comparing the relationship between "numeric\_grade" and "pollscore," we observed a significant linear relationship, as shown in the following figure.
-Therefore, we removed "numeric\_grade" from the model to satisfy MLR assumptions, resulting in our second model.
+```
+
+Upon comparing the relationship between `numeric_grade` and `pollscore`, we observed a significant linear relationship, as shown in @fig-rbnap.
+Therefore, we removed `numeric_grade` from the model to satisfy MLR assumptions, resulting in our second model.
 ```{r, fig.pos="H", fig.height=6, fig.width=10}
@@
   geom_smooth(method = "lm", se = FALSE, color = "#A9CCE3") +
-  labs(title = "Numeric Grade VS Pollscore in Trump's Training Set",
+  labs(title = "Trump",
        x = "Numeric Grade",
-       y = "Pollscore")
+       y = "Pollscore")+
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))
 
@@
   geom_smooth(method = "lm", se = FALSE, color = "#F1948A") +
-  labs(title = "Numeric Grade VS Pollscore in Harris's Training Set",
+  labs(title = "Harris",
        x = "Numeric Grade",
-       y = "Pollscore")
+       y = "Pollscore")+
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))
 
@@
 \begin{align} 
-\text{Score}_{Trump} = &\ \beta_1 \, \text{Pollscore} + \beta_2 \, \text{Transparency\_score} + \beta_3 \, \text{Duration} + \notag \\
-        &\ \beta_4 \, \text{Sample\_size} + \beta_5 \, \text{Population} + \beta_6 \, \text{Hypothetical} + \notag \\
-        &\ \beta_7 \, \text{Methodology} + \beta_8 \, \text{Ranked\_choice\_reallocated} + \beta_0 \\[0.5cm]
-\text{Score}_{Harris} = &\ \alpha_1 \, \text{Pollscore} + \alpha_2 \, \text{Transparency\_score} + \alpha_3 \, \text{Duration} + \notag \\
-        &\ \alpha_4 \, \text{Sample\_size} + \alpha_5 \, \text{Population} + \alpha_6 \, \text{Hypothetical} + \notag \\
-        &\ \alpha_7 \, \text{Methodology} + \alpha_8 \, \text{Ranked\_choice\_reallocated} + \alpha_0
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \notag \\
+        &\beta_7Methodology + \beta_8Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag \\
+        &\alpha_7Methodology + \alpha_8Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6,7,8 \right \} \notag 
 \end{align}
@@
 We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
-As shown in the figure below, both "methodology" and "ranked\_choice\_reallocated" were found to be insignificant predictors in both models.
+As shown in @tbl-alovitahm below, both `methodology` and `ranked_choice_reallocated` were found to be insignificant predictors in both models.
 Thus, they were excluded to reduce model complexity.
@@
 #| label: tbl-alovitahm
-#| tbl-cap: "Significant level of variblaes in the aboanded Harris and Trump's model"
+#| tbl-cap: "Significant level of variblaes in the first models"
 
@@
   combined_results_table, 
-  caption = "P-Values for Models of Harris and Trump", 
   col.names = c("Harris", "Trump"),
@@
 Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag\notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6 \right \} \notag 
 \end{align}
@@
 
-First, we verified the assumptions mentioned in the overview.
-The table below shows the General Variance Inflation Factor (GVIF) for both models, which indicates that all predictors have a GVIF less than 1.3, suggesting no significant multicollinearity.&#x20;
+First, we verified the assumptions mentioned in the @Model_Overview.
+The @tbl-vohfm shows the General Variance Inflation Factor (GVIF) for both models, which indicates that all predictors have a GVIF less than 1.3, suggesting no significant multicollinearity.
 
@@
 #| label: tbl-vohfm
-#| tbl-cap: "VIF of Trump and Harris's final model"
+#| tbl-cap: "GVIF of the final models"
 # Calculate VIF for Harris model
@@
 # Rename columns for clarity
-colnames(combined_vif_table) <- c("Variable", "Harris VIF", "Trump VIF")
+colnames(combined_vif_table) <- c("Variable", "Harris", "Trump")
 
 # Use kable to display the combined VIF table
-kable(combined_vif_table, caption = "VIF for Harris and Trump Models", col.names = c("Variable", "Harris VIF", "Trump VIF"))
-
-```
-
-The following figure presents the diagnostic plots for the Harris model.
-The plot on the left shows the relationship between residuals and predicted values, and since no obvious pattern is observed, our model satisfies the Homoscedasticity assumption.
-The right-hand plot is a Q-Q plot, and the points align along the diagonal, indicating that residuals are  normally distributed and satisfy the Multivariate Normality condition.
-
-```{r, fig.height= 7, fig.width=14}
+kable(combined_vif_table, col.names = c("Variable", "Harris", "Trump"))
+
+```
+
+The following @fig-mdp presents the diagnostic plots for the Harris and Trump's models.
+The plots on the left shows the relationship between residuals and predicted values, and since no obvious pattern is observed, our models satisfies the Homoscedasticity assumption.
+The right-hand plot are a Q-Q plot, and the points align along the diagonal, indicating that residuals are normally distributed and satisfy the Multivariate Normality condition.
+
+```{r, fig.height= 7, fig.width=14, fig.pos="H"}
 #| warning: false
@@
 
-The next figure compares predicted and actual values from the test data.
+The @fig-pvatrv compares predicted and actual values from the test data.
 For both the Trump and Harris models, the trend between predicted and actual values is roughly linear, indicating that our models are effective.
 
-```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 5, fig.width=10}
+```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 5, fig.width=10, fig.pos="H"}
+#| label: fig-pvatrv
+#| fig-cap: "Predicted values and the real values"
+
 # Generate predictions using the model
@@
   geom_point(color = "#A9CCE3") + # Scatter plot of predicted vs actual values
-  labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
+  labs(x = "Predicted Values", y = "Actual Values", title = "Harris") +
   geom_abline(slope = 1, intercept = 0, color = "#F1948A", linetype = "dashed") + # Add reference line y = x
-  theme_minimal() # Use minimal theme for the plot
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))# Use minimal theme for the plot
 
@@
   geom_point(color = "#A9CCE3") + # Scatter plot of predicted vs actual values
-  labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
+  labs(x = "Predicted Values", y = "Actual Values", title = "Trump") +
   geom_abline(slope = 1, intercept = 0, color = "#F1948A", linetype = "dashed") + # Add reference line y = x
-  theme_minimal() # Use minimal theme for the plot
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))# Use minimal theme for the plot
 
@@
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
+      plot.title = element_text(hjust = 0.5, size = 14),
+      plot.subtitle = element_text(hjust = 0.5)
     )
@@
 
-# Result
+# Result {#sec-result}
 ## featured values used in prediction
@@
 #| label: tbl-dffp
-#| tbl-cap: "Datas for final prediction"
+#| tbl-cap: "Datas for the final prediction"
 
@@
 # Display the final table with kable
-kable(all_candidate_features)
+kable(all_candidate_features, , col.names = c("Variables", "Trump", "Harris"))
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-psftah
+#| fig-cap: "Predicted scores for Trump and Harris"
+
 Harris_predict <- round(predict(Harris_model, newdata = harris_features),2)
@@
   geom_bar(stat = "identity", width = 0.5) +
-  labs(title = "Predicted Values for Each Candidate",
+  labs(
        x = "Candidate",
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-# Appendix
+# Appendix {#sec-appendix}
 
@@
 #| echo: false
-#| label: fig-rdd
-#| fig-cap: "Raw Data Distribution"
 
@@
 set3_vars <- c("sponsor_ids", "question_id", "internal", "race_id")
-
-# Define a function to generate a grid of plots for a given set of variables with increased text size
-plot_variable_distributions <- function(data, vars) {
+```
+
+```{r, fig.width=10, fig.height=10, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-ivirdp1
+#| fig-cap: "Insignificant variables in raw data part 1"
+
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
 plots <- list()
-  for (var in vars) {
-    if (is.numeric(data[[var]])) {
-      p <- ggplot(data, aes(x = .data[[var]])) +
-        geom_histogram(bins = 30, fill = "steelblue", color = "black") +
-        labs(title = var) +
-        theme_minimal() +
-        theme(
-          plot.title = element_text(size = 18, face = "bold"),
-          axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank()
-        )
-    } else {
-      p <- ggplot(data, aes(x = .data[[var]])) +
-        geom_bar(fill = "steelblue", color = "black") +
-        labs(title = var) +
-        theme_minimal() +
-        theme(
-          plot.title = element_text(size = 18, face = "bold"),
-          axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.text.x = element_text(size = 14, angle = 45, hjust = 1)
+# Loop through selected numeric variables and plot their distributions
+for (variable in set1_vars) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
     )
 }
-    plots[[var]] <- p
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+```{r, fig.width=10, fig.height=5, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-ivirdp2
+#| fig-cap: "Insignificant variables in raw data part 2"
+
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in set2_vars) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
 }
-  return(plots)
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+```{r, fig.width=10, fig.height=5, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-ivirdp3
+#| fig-cap: "Insignificant variables in raw data part 3"
+
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in set3_vars) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
 }
-
-# Generate plots for each set of variables
-plot1 <- plot_variable_distributions(raw_data, set1_vars)
-plot2 <- plot_variable_distributions(raw_data, set2_vars)
-plot3 <- plot_variable_distributions(raw_data, set3_vars)
-
-# Arrange the first three sets of plots into grids and display them
-grid.arrange(grobs = plot1, ncol = 2, top = textGrob("Distribution of Variables (Set 1)", gp=gpar(fontsize=20, fontface="bold")))
-grid.arrange(grobs = plot2, ncol = 2, top = textGrob("Distribution of Variables (Set 2)", gp=gpar(fontsize=20, fontface="bold")))
-grid.arrange(grobs = plot3, ncol = 2, top = textGrob("Distribution of Variables (Set 3)", gp=gpar(fontsize=20, fontface="bold")))
-
-# Separate set4, set5, and set6 variables for individual adjustments
-
-# Set 4: State Plot (excluding NA)
-state_plot <- raw_data %>%
-  filter(!is.na(state)) %>%  
-  count(state, sort = TRUE) %>%
-  top_n(10) %>%
-  ggplot(aes(y = reorder(state, n), x = n)) +
-  geom_bar(stat = "identity", fill = "steelblue", color = "black") +
-  labs(title = "Distribution of State (Set 4)") +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 20, face = "bold"),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12),
-    axis.text.y = element_text(size = 12)
-  )
-
-# Set 5: ranked_choice_round_plot Plot (excluding NA)
-ranked_choice_round_plot <- raw_data %>%
-  filter(!is.na(ranked_choice_round)) %>%  
-  ggplot(aes(x = ranked_choice_round)) +
-  geom_density(fill = "steelblue", alpha = 0.7) +
-  labs(title = "Distribution of ranked_choice_round (Set 5)") +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 20, face = "bold"),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 12)
-  )
-
-created_at_plot <- raw_data %>%
-  filter(!is.na(created_at)) %>%  # 去掉NA值
-  ggplot(aes(x = as.POSIXct(created_at, format = '%m/%d/%y %H:%M'))) +
-  geom_density(fill = "steelblue", alpha = 0.7) +
-  labs(title = "Distribution of Created At (Set 8)") +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 20, face = "bold"),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 12)
-  )
-
-# Display each plot individually
-print(state_plot)
-print(ranked_choice_round_plot)
-print(created_at_plot)
-```
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+
+```
+# References

### 2024-11-04 paper/paper_draft_1.qmd
Update paper_draft_1.qmd
Update conclusion and discussion

@@
 
-Overall, our approach demonstrates how feature engineering and predictive modeling can offer insights into candidate support based on the available data.
-However, it is important to interpret these results cautiously, as they rely on specific variables and assumptions embedded within the dataset.
-In this analysis, we aggregated representative feature values for each candidate by using the mean or median for numeric variables, the mode for categorical variables, and the most frequent occurrence for Boolean values.
-Further refinement and additional data could enhance the robustness of these predictions, contributing to a more comprehensive forecast in future studies.
-
-# Discussion {#sec-discussion}
-
-This paper presents a predictive analysis of voter support for 2024 U.S.
-presidential candidates Kamala Harris and Donald Trump.
-Using a “poll-of-polls” approach, it integrates polling data from diverse sources, emphasizing reliability, sample size, and methodology.
-Linear and Bayesian models were applied to improve prediction accuracy.
-
-The analysis provides two key insights.
-First, our model predicts a slight advantage for Kamala Harris, with a support estimate of 47.6% compared to Donald Trump’s 43.5%, indicating a competitive but narrow lead.
-Second, it underscores the impact of poll reliability on predictive accuracy.
-Traditional methods like live phone surveys show greater accuracy than online methods, reinforcing the importance of reliability-weighted data in improving forecast precision.
+The results indicate that high transparency scores and reliable polling methods improve prediction quality, while careful attention to demographic representation—such as sample size and population type—ensures the polling data reflects the broader electorate.
+The model forecasts a slight lead for Kamala Harris, with an estimated 47.6% support compared to 43.5% for Donald Trump, underscoring the essential role of reliable data sources in public opinion forecasting.
+These findings highlight the importance of stringent polling standards and precise demographic selection in enhancing the predictive accuracy of electoral models.
+
+# Discussion
+
+This study employs a multiple linear regression model to analyze polling data and forecast public support for U.S.
+2024 presidential election candidates Kamala Harris and Donald Trump.
+By identifying key determinants of polling accuracy, this analysis predicts a slight lead for Kamala Harris with 47.6% support over Donald Trump’s 43.5%.
+
+Findings reveal that transparency and demographic representation are essential to reliable election forecasts.
+Polls with higher transparency scores yield more accurate predictions, emphasizing the importance of clear polling practices.
+Sample size and population type variations also underscore the need for representative sampling to capture genuine voter sentiment.
 

### 2024-11-04 scripts/01-test_simulated_data.R
Update 01-test_simulated_data.R

@@ -11,34 +11,33 @@
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
 library(testthat)
 library(arrow)
 
 analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
 analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
-analysis_data_3 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_3.parquet"))
+
 
 #### Test data ####
 
 # Load simulated data files
 analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
 analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
-analysis_data_3 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_3.parquet"))
+
 
 # Convert sample_size to integer if necessary
 analysis_data_1$sample_size <- as.integer(analysis_data_1$sample_size)
 analysis_data_2$sample_size <- as.integer(analysis_data_2$sample_size)
-analysis_data_3$sample_size <- as.integer(analysis_data_3$sample_size)
+
 
 # Correct out-of-range values for numeric_grade and transparency_score
 analysis_data_1$numeric_grade <- pmin(pmax(analysis_data_1$numeric_grade, 1), 5)
 analysis_data_2$numeric_grade <- pmin(pmax(analysis_data_2$numeric_grade, 1), 5)
-analysis_data_3$numeric_grade <- pmin(pmax(analysis_data_3$numeric_grade, 1), 5)
+
 
 analysis_data_1$transparency_score <- pmin(pmax(analysis_data_1$transparency_score, 1), 10)
 analysis_data_2$transparency_score <- pmin(pmax(analysis_data_2$transparency_score, 1), 10)
-analysis_data_3$transparency_score <- pmin(pmax(analysis_data_3$transparency_score, 1), 10)
+
 
 # Define expected columns, excluding `poll_id`
 expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
@@ -47,18 +46,15 @@ expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency
 
 #### Test structure of datasets ####
 test_that("Simulated datasets contain all expected columns", {
[…]

### 2024-11-04 paper/paper_draft_1.qmd
URL updated
URL updated

@@
   - Shaotong Li
-thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
+thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/Final]."
 date: today

### 2024-11-04 scripts/00-simulate_data.R
Delete scripts directory in order to merge main and final branch

@@ -1,132 +1,0 @@
-#### Preamble ####
-# Purpose: Simulates a dataset of US president rolls
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-# Any other information needed? None
-
-#### Setup ####
-# Load required libraries
-library(tidyverse)
-library(arrow)
-# Set a random seed for reproducibility
-set.seed(123)
-  
-## Generate simulated data for candidate_1
-simulated_candidate_1 <- tibble(
-  # Generate numeric_grade based on a normal distribution with mean 2.5 and standard deviation 2,
-  numeric_grade = round(rnorm(500, mean = 2.5, sd = 2), 1),
-  # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
-  pollscore = round(rnorm(500, mean = -0.5, sd = 0.3), 1),
-  # The methodology is divided into four levels: level 1 represents the least reliable type of methodology, while level 4 represents the most reliable.
-  methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
-  # Generate transparency_score based on a normal distribution with mean 6 and standard deviation 1.5,
-  # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
-  transparency_score = round(rnorm(500, mean = 6, sd = 1.5), 1),
-  # The duration of this poll in days. Duration based on a normal distribution with mean 183 and standard deviation 100,
-  duration = round(rnorm(500, mean = 183, sd = 100)),
-  # Generate sample_size based on a normal distribution with mean 1200 and standard deviation 5000, then round to the nearest integer
-  sample_size = abs(round(rnorm(500, mean = 1200, sd = 5000))),
-  # Population types：Likely Voters，Registered Voters, Voters, Adult
-  population = sample(c("a", "v", "lv", "rv"), 500, replace = TRUE),
-  # Set TRUE/FALSE ratio to 0.9 for the hypothetical column
-  ranked_choice_reallocated= sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.1, 0.9)),
-  # Set TRUE/FALSE ratio to 0.3 for the hypothetical column
-  hypothetical = sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.3, 0.7)),
-  # Use NA as a placeholder for the score.
[…]

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -1,80 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the structure and validity of the simulated variables 
-  #of U.S. election candidates
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 00-simulated_data saved and loaded
-# Any other information needed? None
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-library(testthat)
-library(arrow)
-
-analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
-analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
-analysis_data_3 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_3.parquet"))
-
-#### Test data ####
-
-# Convert sample_size to integer if necessary
-analysis_data_1$sample_size <- as.integer(analysis_data_1$sample_size)
-analysis_data_2$sample_size <- as.integer(analysis_data_2$sample_size)
-analysis_data_3$sample_size <- as.integer(analysis_data_3$sample_size)
-
-# Define expected columns (updated to match actual columns in datasets)
-expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
-                      "duration", "sample_size", "population", "ranked_choice_reallocated", 
-                      "hypothetical", "score")
-
-#### Test structure of datasets ####
-test_that("Simulated datasets contain all expected columns", {
-  for (data in list(analysis_data_1, analysis_data_2, analysis_data_3)) {
-    expect_true(all(expected_columns %in% colnames(data)), 
-                info = "Some expected columns are missing in one or more datasets.")
-  }
-})
-
-#### Test data types of specific columns ####
-test_that("Columns have correct data types", {
-  for (data in list(analysis_data_1, analysis_data_2, analysis_data_3)) {
-    if ("pollscore" %in% colnames(data)) {
-      expect_true(is.numeric(data$pollscore), 
-                  info = "pollscore should be numeric.")
-    }
-    if ("score" %in% colnames(data)) {
-      expect_true(is.numeric(data$score), 
-                  info = "score should be numeric.")
-    }
-    if ("sample_size" %in% colnames(data)) {
-      expect_true(is.integer(data$sample_size), 
[…]

### 2024-11-04 scripts/02-download_data.R

@@ -1,20 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from fivethirtyeight.
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-# Any other information needed? None
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Download data ####
-url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
-the_raw_data <- read.csv(url)
-
-#### Save data ####
-write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
-
-

### 2024-11-04 scripts/03-clean_data.R

@@ -1,121 +1,0 @@
-#### Preamble ####
-# Purpose: Cleans the raw US president polls data by selecting columns and scaling values.
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-# Any other information needed? None
-
-#### Workspace setup ####
-library(tidyverse)
-library(dplyr)
-library(janitor)  # For clean_names
-library(tidyr)   # For drop_na
-library(lubridate)
-library(arrow)
-
-set.seed(123)  # Set seed for reproducibility
-raw_data <- read_csv("data/01-raw_data/raw_data.csv")
-
-# Step 1: Remove variables with more than 40% NA values
-threshold <- 0.4 * nrow(raw_data)
-raw_data_cleaned <- raw_data %>%
-  select_if(~sum(is.na(.)) <= threshold)
-
-# Step 2: Remove variables with all identical values
-raw_data_cleaned <- raw_data_cleaned %>%
-  select_if(~is.numeric(.) || n_distinct(.) > 1)
-
-# Step 3: Remove duplicated, unrelated variables
-raw_data_cleaned <- raw_data_cleaned %>%
-  dplyr::select(-any_of(c("pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name", 
-                          "question_id", "population_full", "created_at", "url", "url_article", "race_id", 
-                          "candidate_id", "candidate_name", "party", "seat_number", "cycle"))) 
-  
-# Step 4: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
-raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date)-mdy(raw_data_cleaned$start_date))
-raw_data_cleaned <- raw_data_cleaned %>%
-  dplyr::select(-start_date, -end_date)
-
-# Step 5: Group methodology by level
-raw_data_cleaned$methodology <- case_when(
-  raw_data_cleaned$methodology %in% c(
-    "Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", 
-    "Online Panel/Probability Panel", "Probability Panel"
[…]

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -1,105 +1,0 @@
-#### Preamble ####
-# Purpose: test on the analysis data for validation
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 02-analysis_data saved and loaded
-# Any other information needed? None
-
-#### Workspace setup ####
-
-# Load necessary libraries
-library(tidyverse)
-library(testthat)
-library(arrow)  # For reading Parquet files
-library(here)
-
-Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
-Harris_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
-Trump_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
-Harris_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
-
-#### Test data ####
-
-#### Test data ####
-
-# Ensure testthat setup
-context("Data validation tests for Trump and Harris datasets")
-
-# Test 1: Check if the datasets have the expected columns
-test_that("Expected columns are present in Trump and Harris test and train datasets", {
-  expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
-                        "sample_size", "population", "ranked_choice_reallocated", 
-                        "hypothetical", "score", "duration")
-  
-  # Check columns in each dataset
-  expect_true(all(expected_columns %in% colnames(Trump_test)))
-  expect_true(all(expected_columns %in% colnames(Harris_test)))
-  expect_true(all(expected_columns %in% colnames(Trump_train)))
-  expect_true(all(expected_columns %in% colnames(Harris_train)))
-})
-
-# Test 2: Check for missing values
-test_that("No missing values in critical columns of test and train datasets", {
-  # List critical columns
-  critical_columns <- c("numeric_grade", "pollscore", "score", "sample_size", "population")
-  
-  # Check for missing values
-  for (col in critical_columns) {
-    expect_true(all(!is.na(Trump_test[[col]])), info = paste("Missing values in Trump_test:", col))
-    expect_true(all(!is.na(Harris_test[[col]])), info = paste("Missing values in Harris_test:", col))
-    expect_true(all(!is.na(Trump_train[[col]])), info = paste("Missing values in Trump_train:", col))
[…]

### 2024-11-04 scripts/06-model_data.R

@@ -1,30 +1,0 @@
-#### Preamble ####
-# Purpose: use train data to train linear model of Trump and Harris
-# Author: Haowei Fan, Fangning Zhang, Shaotong Li
-# Date: 13 October 2024
-# Contact: haowei.fan@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 02-analysis_data saved and loaded
-# Any other information needed? None
-
-
-#### Workspace setup ####
-library(tidyverse)
-
-# Define paths to each candidate's analysis data (training and testing data)
-
-Trump <- read_parquet("data/02-analysis_data/01-training/train_Trump.parquet")
-Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
-
-# Function to create and save a linear model for a candidate
-
-Trump_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical , data = Trump)
-Harris_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical , data = Harris)
-
-# Save the model
-saveRDS(Trump_model, file = "models/Trump_model.rds")
-saveRDS(Harris_model, file = "models/Harris_model.rds")
-
-

### 2024-11-04 scripts/00-simulate_data.R
Update 00-simulate_data.R
add install packages

@@ -8,6 +8,9 @@
 # Any other information needed? None
 
 #### Setup ####
+# install required packages
+install.packages("tidyverse")
+install.packages("arrow")
 # Load required libraries
 library(tidyverse)
 library(arrow)

### 2024-11-04 scripts/03-clean_data.R
Update 03-clean_data.R
Add install packages

@@ -8,6 +8,13 @@
 # Any other information needed? None
 
 #### Workspace setup ####
+install.packages("tidyverse")
+install.packages("dplyr")
+install.packages("janitor")
+install.packages("tidyr")
+install.packages("lubridate")
+install.packages("arrow")
+
 library(tidyverse)
 library(dplyr)
 library(janitor)  # For clean_names

### 2024-11-04 scripts/05-exploratory_data_analysis.qmd
graphing updated
graphing updated
result section updated
bug fixed, Paper graphing updated, readme updated
Paper graphing updated, readme updated, bug fixd
Update 05-exploratory_data_analysis.qmd
add install packages

--- 2024-11-01 scripts/05-exploratory_data_analysis.qmd
@@
 #### Workspace setup ####
+
+install.packages("tidyverse")
+install.packages("patchwork")
+install.packages("moments")
+
 library(tidyverse)
-library(rstanarm)
 library(patchwork)
+library(moments)
 raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
+Trump_test <- read_parquet(here::here("data/02-analysis_data/02-Testing/test_Trump.parquet"))
+Harris_test <- read_parquet(here::here("data/02-analysis_data/02-Testing/test_Harris.parquet"))
 ```
@@
 unique_methodologys <- unique(raw_data$methodology)
-print(unique_methodologys)
+print(length(unique_methodologys))
 ```

### 2024-11-04 scripts/07-replications.R
Update 07-replications.R
add install packages

@@ -7,6 +7,7 @@
 # Pre-requisites: Requires all provided scripts and necessary data files
 # Any other information needed? None
 
+install.packages("tidyverse")
 library(tidyverse)
 
 # 1. Simulate Data

### 2024-11-04 paper/paper.qmd
install_pacakges updated
install_pacakges updated

@@
 ---
-title: "Forecasting the 2024 U.S. Presidential Election: Comparative Support Analysis of Kamala Harris and Donald Trump"
-subtitle: "Predictive Models Indicate a Narrow Advantage for Harris in a Closely Contested Race"
+title: "Poll-Based Forecasting of the 2024 U.S. Presidential Election"
+subtitle: "Valid Multiple Linear Regression Explains Why Kamala Harris Will Win"
 author: 
@@
 date-format: long
-abstract: "This study aggregates polling data to forecast support for 2024 U.S.
-presidential candidates Kamala Harris and Donald Trump.
-By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%.
-The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
+abstract: "The United States plays a major role in the global technological and economic landscape, with its political leadership having a significant influence on international technology cooperation and economic relations.
+This project uses multiple linear regression to predict the outcome of the 2024 U.S.
+presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing insights to help stakeholders prepare for potential shifts in U.S.
+policies.
+The project predicts that Kamala Harris will secure 47.6% of the vote over Donald Trump's 43.5% and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
 format: pdf
+toc-depth: 2    
+number-sections: true
 toc: true           
 toc-title: "Table of Contents" 
-toc-depth: 2    
-number_sections: true    
 bibliography: references.bib
@@
 #### Workspace setup ####
+install.packages("tidyverse")
 library(tidyverse)
+install.packages("knitr")
 library(knitr)
+install.packages("dplyr")
 library(dplyr)
+install.packages("arrow")
 library(arrow)
+install.packages("patchwork")
 library(patchwork)
+install.packages("car")
 library(car)
+install.packages("kableExtra")
 library(kableExtra)
+install.packages("gridExtra")
 library(gridExtra)
+install.packages("moments")
 library(moments)
+install.packages("grid")
 library(grid)
@@
 # Introduction
-The U.S.
-presidential election has profound implications on a global scale, shaping international relations, economic policy, and key social issues.
-As the 2024 election approaches, the ability to accurately forecast potential outcomes is essential for policymakers, businesses, and organizations seeking to anticipate shifts in U.S.
-policy that may affect trade, climate commitments, and strategic alliances [@citeBBC].
-Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning [@citeEuronews].
-However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting [@citeOregon].
-Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further [@citeYale].
+The United States, as a global leader in both the economy and technology, plays a crucial role in shaping international trade and technological development.
+The president of the U.S.
+has a significant impact on these domains, which in turn affects the entire world.
+For instance, when Donald Trump took office in 2016, his administration's economic sanctions against China resulted in significant consequences, including a loss of nearly 300,000 jobs in the U.S.
+and an estimated 0.3% decline in real GDP [@citeBrookings].
+In contrast, President Obama’s Affordable Care Act (ACA) expanded healthcare access, enabling millions of Americans to obtain affordable health coverage and improving overall health security [@citeObamaACA].
+Therefore, predicting the outcome of the U.S.
+presidential election on November 5, 2024, is crucial for stakeholders to strategically prepare for the global impact that the new president may bring.
 
@@
 
-This paper is structured as follows: first, the data collection and filtering processes are outlined, followed by a description of the methodological framework, introducing linear modeling approaches.
-The results are then presented and analyzed, with a discussion on broader implications.
-The paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.
-
-This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S.
-presidential election.
-These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
- 【最后改结构描述加cross-reference】
+The structure of this report is as follows: The @sec-data provides an overview of the raw data's origin and includes visualizations of some key variables.
+Additionally, detailed steps for cleaning the data are explained in this section, and the measurement of the raw data is analyzed in depth.
+Similar datasets are also discussed here.
+The @sec-model includes a detailed description of the model, covering the estimators and estimand.
+It also explains why alternative models were not chosen and validates our final model.
+The @sec-result presents the main findings of our model.
+The @sec-discussion analyzes the effects of different variables on the predictions, discusses the model's limitations, and explores its implications for real-world applications.
+The @sec-appendix reviews the YouGov pollster methodology, explains how to create an ideal survey for predicting election outcomes, and includes visualizations of less important raw data.
+
+In this project, We used R[@citeR] and several R packages for data processing, analysis, and visualization.
+Specifically, tidyverse[@citeTidyverse], arrow[@citeArrow], dplyr[@citeDplyr], tidyr[@citeTidyr], janitor[@citeJanitor], lubridate[@citeLubridate], and here[@citeHere] were used for data processing, cleaning, date and time operations, project path management, and efficient data storage and reading.
+knitr[@citeKnitr], kableExtra[@citeKableExtra], patchwork[@citePatchwork], gridExtra[@citeGridExtra], grid[@citeGrid], and ggplot2[@citeGgplot2] were used for creating dynamic reports, beautifying table outputs, data visualization, and arranging multiple charts.
+car[@citeCar] and moments[@citeMoments] were used for model analysis and diagnostics.
+testthat[@citeTestthat] was used for writing and executing unit tests.
+styler[@citeStyler] is used for final code formatting.
 
@@
 
-## Overview
-The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' (Ryan Best and Wiederkehr, 2024).
+## Overview {#sec-data_overview}
+The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' [@citeRawData].
 FiveThirtyEight is a well-known website recognized for its political, economic, and sports analyses.
@@
 
+In this section, we present the components of the raw data, along with the distribution and summary of key variables.
+We also detail the data cleaning procedures, evaluate the reliability of the measurements used, and discuss similar datasets.
+
+## Raw data 
 The analysis and visualizations in this paper are based on polling results as of October 22.
-The dataset includes 52 variables and 17,133 samples from various polling sources, asking participants who they support in the upcoming presidential election.
-To ensure accuracy and consistency, the data has been carefully processed and cleaned to remove biases and guarantee data integrity and comparability.
-
-This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S.
-presidential election forecast.
-These packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.
-
-## Raw data
-Raw data 一共包含了52个variable以及17133个sample.
+The dataset includes 52 variables, 17,133 samples and 3530 polls from various polling sources.
+These variables are shown in the below table@tbl-vord.
+
 ```{r, fig.height=90, fig.width=90}
@@
 matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))),
-                      nrow = num_rows, byrow = TRUE)
+  nrow = num_rows, byrow = TRUE
+)
 
@@
 kable(as.data.frame(matrix_data),
-      col.names = NULL)
-```
-其中重要的variables，其余的在appdendix
+  col.names = NULL
+)
+```
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
+droped_data <- raw_data %>% select(-any_of(del_1))
+```
+
+We selected 10 variables @tbl-ivatd of interest and their distributions are shown below.
 ```{r, fig.height=90, fig.width=90}
@@
 variable_descriptions <- data.frame(
-  Variable = c("poll_id", "methodology", "population", "ranked_choice_reallocated",
+  Variable = c(
+    "poll_id", "methodology", "population", "ranked_choice_reallocated",
     "hypothetical", "answer", "numeric_grade", "pollscore",
-               "transparency_score", "start_date", "end_date", "sample_size", "pct"),
+    "transparency_score", "sample_size", "start_date", "end_date", "pct"
+  ),
   Description = c(
@@
     "A score reflecting the pollster's transparency about their methodology (e.g., 9.0).",
+    "The total number of respondents participating in the poll (e.g., 2712).",
     "The date the poll began (e.g., 10/8/24).",
     "The date the poll ended (e.g., 10/11/24).",
-    "The total number of respondents participating in the poll (e.g., 2712).",
     "The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris)."
@@
 ```
-52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
-"notes", "url", "url_article", "url_topline", "url_crosstab", "source"
-```{r, fig.height=90, fig.width=90}
-#| warning: false
-#| message: false
-#| echo: false
-del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
-droped_data <- raw_data %>% select(-any_of(del_1))
-```
-此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括："pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name", "population_full", "candidate_id", "candidate_name"
+
 ```{r}
@@
 #| echo: false
-# 这里需要画一个table，展示删除的重复变量
-del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
-           "population_full", "candidate_id", "candidate_name")
-droped_data <- droped_data %>% select(-any_of(del_2))
-```
-常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
-```{r, fig.height=90, fig.width=90}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-cv
-#| tbl-cap: "Constant variables"
-# Identify variables where all values are the same (including NA)
-same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
-# Create a data frame with variables and their unique values
-same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
-unique(na.omit(droped_data[[var]]))[1]))
-# Print the names of variables with all identical values using kable
-kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
-del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
-           "office_type", "seat_number", "seat_name")
-droped_data <- droped_data %>% select(-any_of(del_4))
-```
-其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
+#| include: false
+catego <- c(
+  "poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
   "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
-         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer"
+  "partisan", "race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical", "party", "answer"
+)
+```
+
 ```{r}
@@
 #| echo: false
-catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
-         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
-         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
-```
-重要的categorical为下面的，剩下的将在appendix阐述："poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer"
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
-```
-一共有3530个poll
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-# Get unique Poll IDs and print the count
-unique_poll_ids <- unique(raw_data$poll_id)
-```
-描述
-```{r}
+#| include: false
+catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical", "answer")
+```
+
+The left bar chart in @fig-bv shows the distribution of the `ranked_choice_reallocated` variable.
+The chart indicates that the majority of the data points are marked as `FALSE`, meaning ranked-choice voting reallocations have not been applied in most cases.
+Only a very small number of instances are marked as `TRUE`.
+
+The right bar chart in @fig-bv illustrates the distribution of the `hypothetical` variable.
+It shows that a larger proportion of the data is marked as `TRUE`, indicating that the poll results are often based on hypothetical match-ups.
+There are fewer instances marked as `FALSE`, where the poll is not hypothetical.
+
+```{r, fig.height= 5, fig.width=10, fig.pos="H"}
 #| warning: false
@@
 #| label: fig-bv
-#| fig-cap: "Boolean variables"
-
-# Create a list to store the plots
+#| fig-cap: "Distribution of boolean variables"
 plots <- list()
-
-# Bar chart for 'ranked_choice_reallocated' with count labels
+# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
 plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
-  labs(title = "Bar Chart of Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
+  labs(x = "Ranked Choice Reallocated", y = "Count") +
   theme_minimal(base_size = 15) +
@@
     axis.text = element_text(size = 10)
-  ) +
-  ylim(0, max(table(raw_data$ranked_choice_reallocated)) * 1.2)  # Increase y-axis limit to fit labels
-
-# Bar chart for 'hypothetical' with count labels
+  )
+
 plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
-  labs(title = "Bar Chart of Hypothetical", x = "Hypothetical", y = "Count") +
+  labs(x = "Hypothetical", y = "Count") +
   theme_minimal(base_size = 15) +
@@
     axis.text = element_text(size = 10)
-  ) +
-  ylim(0, max(table(raw_data$hypothetical)) * 1.2)  # Increase y-axis limit to fit labels
+  )
 
 # Combine and print the plots using patchwork
-combined_plot <- wrap_plots(plots, ncol = 2) +
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
   plot_annotation(
@@
   )
-
 # Print the combined plot
 print(combined_plot)
-
-```
-描述
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```
+
+The three charts depict the distribution of key variables in the dataset: `methodology`, `population`, and `answer`.
+In the most left chart of @fig-cv, we see that the most frequently used polling methodology is "Online Panel," followed by "Live Phone" and "Live Phone/Text-to-Web." The "Online Panel" category significantly outnumbers the others, while the "Other" category also includes a notable count, representing various methodologies grouped together.
+
+The middle chart of @fig-cv shows the distribution of different respondent groups.
+"lv" (likely voters) and "rv" (registered voters) dominate, with "rv" showing a slightly higher count, indicating that these two groups make up the majority of the sample.
+Other groups, such as "a" (all adults), "v," and those with missing values ("NA"), represent much smaller portions of the respondent pool.
+
+The most right chart of @fig-cv, `Top 3 Answer and Others`, illustrates the responses given in the polls.
+"Biden" and "Trump" have similar counts, with "Trump" being slightly higher, while the "Other" category also shows a significant proportion.
+The response for "Harris" is noticeably lower compared to the others.
+Overall, these charts provide a visual representation of the polling data, highlighting the dominant methodologies, respondent groups, and response preferences in the dataset.
+```{r, fig.pos="H", fig.width=16, fig.height=8}
 #| warning: false
@@
 #| label: fig-cv
-#| fig-cap: "Catogorical variables"
-
-# Create a list to store the plots
+#| fig-cap: "Distribution of catogorical variables"
+
 plots <- list()
-
-# Top 3 Methodologies with 'Other' grouped
+# Find the top 3 most frequent values in 'methodology' and group others as 'Other'
 methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
@@
 raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
-
-# Create horizontal bar chart for 'methodology'
+# Create a bar chart for the grouped 'methodology'
 plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
-  labs(title = "Top 3 Methodologies and Others", x = "Count", y = "Methodology") +
-  theme_minimal(base_size = 24) +  # Increase base size for all text elements
-  theme(
-    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
-    axis.title = element_text(size = 28),  # Axis title font size
-    axis.text = element_text(size = 24)  # Axis text font size
-  ) +
-  coord_flip()
-
-# Population bar chart
+  labs(x = "Methodology", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),
+    axis.title = element_text(size = 16),
+    axis.text = element_text(size = 16),
+    axis.text.x = element_text(angle = 20, hjust = 1)
+  )
 plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
-  labs(title = "Population", x = "Count", y = "Population") +
-  theme_minimal(base_size = 24) +  # Increase base size for all text elements
-  theme(
-    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
-    axis.title = element_text(size = 28),  # Axis title font size
-    axis.text = element_text(size = 24)  # Axis text font size
-  ) +
-  coord_flip()
-
-# Top 3 Answers with 'Other' grouped
+  labs(x = "Population", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),
+    axis.title = element_text(size = 16),
+    axis.text = element_text(size = 16)
+  )
+# Find the top 3 most frequent values in 'answer' and group others as 'Other'
 answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
@@
 raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
-
-# Create horizontal bar chart for 'answer'
+# Create a bar chart for the grouped 'answer'
 plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
   geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
-  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
-  labs(title = "Top 3 Answers and Others", x = "Count", y = "Answer") +
-  theme_minimal(base_size = 24) +  # Increase base size for all text elements
-  theme(
-    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
-    axis.title = element_text(size = 28),  # Axis title font size
-    axis.text = element_text(size = 24)  # Axis text font size
-  ) +
-  coord_flip()
-
-# Combine the plots using patchwork
-combined_plot <- wrap_plots(plots, ncol = 1) +
+  labs(x = "Answer", y = "Count") +
+  theme_minimal(base_size = 15) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18),
+    axis.title = element_text(size = 16),
+    axis.text = element_text(size = 16)
+  )
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 32)
-    )
-  )
-
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
 # Print the combined plot
 print(combined_plot)
-
-```
-描述
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| include: false
+numer <- droped_data %>% select(-any_of(catego))
+```
+The `numeric_grade` histogram in @fig-donvp1 shows the distribution of a numeric rating assigned to pollsters, representing their overall quality or reliability.
+The data appear to cluster heavily around scores of 2 and 3, suggesting that a large number of pollsters fall within these quality ranges.
+The distribution is fairly symmetric, with a noticeable concentration at these higher scores, indicating that most pollsters are considered to be of moderate to good quality.
+
+The `pollscore` histogram in @fig-donvp1 indicates the reliability of each pollster, with lower (more negative) values being better.
+The distribution shows a peak around zero, with a significant number of pollsters having scores close to zero or slightly negative, and most values being negative, indicating relatively high reliability overall.
+This implies that most pollsters have moderate to high reliability, with fewer pollsters achieving highly negative scores, which indicate better performance.
+The tail towards positive values suggests that a small subset of pollsters may have issues with reliability.
+
+The distribution of `transparency_score` in @fig-donvp1 shows a wide spread, with notable peaks at several discrete points, but no clear pattern overall.
+Higher scores, such as 7.5 and 10, have high frequencies, indicating that some pollsters tend to achieve relatively high transparency.
+On the other hand, lower scores, such as 2.5 and 5, also show some clustering, but with less consistency.
+```{r, fig.pos="H", fig.width=16, fig.height=8}
 #| warning: false
@@
 #| fig-cap: "Distribution of numerical varibales part 1"
-
 ### Create Plots for Numeric Variables ###
@@
 plots <- list()
-
-# Loop through selected numeric variables and plot their distributions with a line connecting bar tops
+# Loop through selected numeric variables and plot their distributions
 for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
-  # Calculate bin counts and midpoints
-  bin_data <- ggplot_build(
-    ggplot(raw_data, aes_string(x = variable)) +
-      geom_histogram(binwidth = 0.5)
-  )$data[[1]]
-
-  # Calculate the midpoint of each bin for line plotting
-  bin_data <- bin_data %>%
-    mutate(midpoint = (xmin + xmax) / 2)
-
-  # Create histogram plot with line connecting the bar tops
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
     geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 24) +  # Adjusted base font size for readability
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
-      axis.title = element_text(size = 35),  # Axis title font size
-      axis.text = element_text(size = 35)  # Axis text font size
+    labs(x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 18),
+      axis.title = element_text(size = 16),
+      axis.text = element_text(size = 16)
     )
 }
-
 ### Combine and Print Plots ###
-# Combine all individual plots into one vertical layout
-combined_plot <- wrap_plots(plots, ncol = 1) +
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 35)
-    )
-  )
-
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
 # Print the combined plot
 print(combined_plot)
-
-```
-描述
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```
+
+The `Distribution of sample_size` histogram in @fig-donvp2 illustrates the frequency of poll sample sizes.
+The majority of polls have relatively small sample sizes, with the frequency decreasing sharply as the sample size increases.
+The distribution appears highly right-skewed, suggesting that larger sample sizes are much less common than smaller ones.
+
+The `Distribution of pct` histogram in @fig-donvp2 represents the frequency distribution of vote percentages received by candidates in various polls.
+Most polls have percentage values concentrated around the 30-40% range, with visible peaks at around 0% and 40%.
+The distribution shows some variation across a wide range but seems to have a higher frequency in the middle range (30-40%) compared to the lower and higher extremes.
+```{r, fig.pos="H", fig.width=10, fig.height=6}
 #| warning: false
@@
 #| fig-cap: "Distribution of numerical varibales part 2"
-
 ### Create Plots for Numeric Variables ###
@@
 plots <- list()
-
 # Loop through selected numeric variables and plot their distributions
 for (variable in names(numer %>% select(sample_size, pct))) {
-  if (variable == "sample_size") {
-    # For sample_size, focus on the range 0-20000
-    plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
-      geom_histogram(binwidth = 500, fill = "#69b3a2", color = "black", alpha = 0.8) +
-      xlim(0, 10000) +  # Set x-axis limits to focus on 0-10000 range
-      labs(title = "Distribution of Sample Size (0-10000)", x = variable, y = "Frequency") +
-      theme_minimal(base_size = 24) +
-      theme(
-        plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
-        axis.title = element_text(size = 30),  # Larger axis title font size
-        axis.text = element_text(size = 28)  # Larger axis text font size
-      )
-  } else {
-    # For other variables, keep the full range
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
     geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
-      labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-      theme_minimal(base_size = 24) +
-      theme(
-        plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
-        axis.title = element_text(size = 30),  # Larger axis title font size
-        axis.text = element_text(size = 28)  # Larger axis text font size
+    labs(x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
     )
 }
-}
-
 ### Combine and Print Plots ###
-# Combine all individual plots into one vertical layout
-combined_plot <- wrap_plots(plots, ncol = 1) +
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 35)
-    )
-  )
-
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
 # Print the combined plot
 print(combined_plot)
-
-```
-描述
-```{r, fig.pos="H", fig.width=18, fig.height=18}
+```
+
+Both charts in @fig-dodv show the normal distribution of poll start and end dates over time.
+The left chart represents the frequency of polls by their start date, while the right chart represents the frequency of polls by their end date, with both distributions primarily concentrated around 2010.The frequency drops after 2010 in both charts.
+```{r, fig.pos="H", fig.width=10, fig.height=5}
 #| warning: false
@@
 raw_data$end_date <- ymd(raw_data$end_date)
-
 # Define the date variables to plot
 date_variables <- c("start_date", "end_date")
-
 ### Create Plots for Date Variables ###
-# Create a list to store plots
+# Loop through selected date variables and plot their distributions
 plots <- list()
-
-# Loop through selected date variables and plot their distributions with a density curve
-for (variable in date_variables) {
+for (variable in names(numer %>% select(start_date, end_date))) {
   plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
-    geom_histogram(fill = "#69b3a2", color = "black", alpha = 0.8) +  # Keep the original binwidth
-    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
-    theme_minimal(base_size = 24) +
-    theme(
-      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
-      axis.title = element_text(size = 30),  # Larger axis title font size
-      axis.text = element_text(size = 28)  # Larger axis text font size
+    geom_histogram(binwidth = 80, fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 14),
+      axis.title = element_text(size = 12),
+      axis.text = element_text(size = 12)
     )
 }
-
 ### Combine and Print Plots ###
-# Arrange the plots vertically without changing their individual orientation
-combined_plot <- wrap_plots(plots, ncol = 1) +
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 35)
-    )
-  )
-
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
 # Print the combined plot
 print(combined_plot)
-
-```
-## Cleaned data
-In the raw data, we initially identified a total of 52 variables.
-Some of these variables, such as 'url', are clearly unrelated to the objectives of this project.
-There are also constant variables, such as 'election_date', which consistently contains the value '11/5/24'.
-Additionally, we found duplicate variables conveying the same information, like 'pollster_id' and 'pollster'.
-Therefore, we first removed these irrelevant and redundant variables.
-The remaining variables are as follows:
+```
+
+## Cleaning Process 
+Firstly, there are several variables clearly irrelevant to the project and will not be discussed further: `notes`, `url`, `url_article`, `url_topline`, `url_crosstab`, and `source`.
+
 ```{r, fig.height=90, fig.width=90}
@@
 #| echo: false
-#| label: tbl-rv
-#| tbl-cap: "Remained variables"
-
-# Get the column names and arrange them into multiple columns
-column_names <- names(droped_data)
-num_columns <- 3  # Set the desired number of columns
-num_rows <- ceiling(length(column_names) / num_columns)
-matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
-                      nrow = num_rows, byrow = TRUE)
-
-# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
-kable(as.data.frame(matrix_data), 
-      col.names = NULL)
-```
-Next, we calculated the percentage of missing values for each variable across the entire dataset.
-We then removed all variables with more than 40% missing values.
-These variables, along with their respective proportions of missing values, are as follows:
+#| include: false
+del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
+droped_data <- raw_data %>% select(-any_of(del_1))
+```
+
+Additionally, there are some duplicate variables, and we will retain only one of each, ignoring the rest: `pollster`, `sponsors`, `display_name`, `pollster_rating_name`, `sponsor_candidate`, `endorsed_candidate_name`, `population_full`, `candidate_id`, and `candidate_name`.
 ```{r}
@@
 #| echo: false
-#| label: tbl-vwbpomv
-#| tbl-cap: "Variables with big porpotion of missing values"
-na_proportions <- sapply(names(droped_data), function(var) {
-  round(mean(is.na(raw_data[[var]])), 2)
-})
-
-# Create a data frame with variable names and their NA proportions
-na_proportions_data <- data.frame(Variable = names(droped_data), NA_Proportion = na_proportions)
-
-# Filter variables with NA proportion greater than 40%
-high_na_proportions <- na_proportions_data[na_proportions_data$NA_Proportion > 0.4, ]
-
-# Print the NA proportions greater than 40% using kable
-kable(high_na_proportions[, 2, drop = FALSE], col.names = c("Variable", "NA Proportion"))
-
-del_5 <- c("sponsor_ids", "state", "sponsor_candidate_id", "sponsor_candidate_party", "tracking",
-           "internal","partisan","ranked_choice_round")
-droped_data <- droped_data %>% select(-any_of(del_5))
-
-```
-Since the influence of pollsters can be quantified using their ratings, such as 'numeric_grade', 'pollscore', and 'transparency_score', we removed these variables to simplify the dataset and the model.
-Similarly, 'created_at' was also removed due to its strong correlation with 'start_date'.
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-del_6 <- c("pollster_id", "pollster_rating_id", "created_at")
-droped_data <- droped_data %>% select(-any_of(del_6))
-```
-Finally, due to the limitations of our model, we removed 'race_id', 'party', and 'question_id'.
-The reason for this is that we will extract and analyze the data for each candidate individually, which makes 'race_id' and 'party' constant within the corresponding dataset.
-Additionally, 'question_id' contains 6,421 unique values, making it unsuitable for categorization, and we removed it to avoid overfitting the model.
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-# Get unique Question IDs and print the count
-unique_question_ids <- unique(raw_data$question_id)
-```
-Finally, the remaining variables are as follows:
-```{r, fig.height=30, fig.width=30}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-fv
-#| tbl-cap: "Final variables"
-final <- c("poll_id","numeric_grade","pollscore","methodology","transparency_score","sample_size","population", 
-           "ranked_choice_reallocated", "hypothetical", "answer","pct","start_date", "end_date")
-
-# Get the column names and arrange them into multiple columns
-column_names <- final
-num_columns <- 3  # Set the desired number of columns
-num_rows <- ceiling(length(column_names) / num_columns)
-matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
-                      nrow = num_rows, byrow = TRUE)
-
-# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
-kable(as.data.frame(matrix_data), 
-      col.names = NULL)
-```
+#| include: false
+
+del_2 <- c(
+  "pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
+  "population_full", "candidate_id", "candidate_name"
+)
+droped_data <- droped_data %>% select(-any_of(del_2))
+```
+
+Constant variables, which cannot impact our predictions, will also be excluded from further discussion.
+These include: `endorsed_candidate_id` (NA), `endorsed_candidate_party` (NA), `subpopulation` (NA), `cycle` (2024), `office_type` (U.S.
+President), `seat_number` (0), `seat_name` (NA), `election_date` (11/5/24), `stage` (general), and `nationwide_batch` (FALSE).
+
+```{r, fig.height=90, fig.width=90}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-cv
+#| tbl-cap: "Constant variables"
+#| include: false
+# Identify variables where all values are the same (including NA)
+same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
+# Create a data frame with variables and their unique values
+same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var) {
+  unique(na.omit(droped_data[[var]]))[1]
+}))
+# Print the names of variables with all identical values using kable
+kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
+del_4 <- c(
+  "endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch",
+  "office_type", "seat_number", "seat_name"
+)
+droped_data <- droped_data %>% select(-any_of(del_4))
+```
+After cleaning, 27 out of the 52 variables remained potentially relevant to our research.
+
 After finalizing the variables, we first created a new variable named 'duration', which replaced 'start_date' and 'end_date'.
@@
 
-Next, we extracted the data for each candidate individually.
+Then, the data is extracted for each candidate individually.
 We calculated a weighted score by weighting according to the number of times each candidate was mentioned in the polls.
@@
 
-Next, we split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
+We also split the data for Trump and Harris into a training set (70%) and a test set (30%). These four datasets form our analysis data. Below is a portion of the Trump training set for reference:
 ```{r, fig.height=30, fig.width=60}
@@
 #| tbl-cap: "Example of analysis data"
+#| include: false
 kable(head(train_Trump), col.names = names(train_Trump))
 ```
-## Measurement
+
+## Measurement and Limitations 
 The method used to forecast the presidential election results is the poll-of-polls, which aggregates results from multiple polls instead of relying on a single survey, aiming to make the results more accurate and stable.
@@
 ## Similar dataset 
-
-# Model
-
-## Model overview
-我们一共有2个model，分别用来预测川普和哈里斯在2024年11月5日美国总统竞选的最终支持率。
-
+A dataset similar to ours titled 2024 National Polls (@citeNYTData) for the U.S.
+Presidential Election is found.
+It was Published by The New York Times, this dataset aggregates survey results from multiple polling organizations, focusing on the support levels for major presidential candidates and aiming to reflect voters’ preferences and election trends.
+However, compared to our dataset, this one has fewer variables, which might reduce its predictive accuracy.
+
+# Model {#sec-model}
+
+## Overview {#sec-Model_Overview}
+In this project, we developed two models to predict the final competitiveness of Donald John Trump and Kamala Devi Harris in the November 5, 2024, U.S.
+presidential election.
+Both models were trained using a training set (70%) for each candidate, while the remaining 30% served as the test set.
+
+The final models are as follows:
+
+```{=tex}
 \begin{align} 
@@
 Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
-        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6 \right \} \notag 
 \end{align}
-
-Notably, we used Multiple Linear Regression (MLR), which implies the following assumptions:
-
-The core assumption of multiple linear regression is that there is a linear relationship between the dependent variable (outcome) and the independent variables.
-This linear relationship can be visually checked using scatter plots, which ideally should display a straight-line pattern rather than a curve.
-The residuals (the differences between observed and predicted values) should be normally distributed. This assumption can be assessed by examining a Q-Q plot.
-The correlation between independent variables should not be too high, meaning multicollinearity should be avoided. This can be checked using the Variance Inflation Factor (VIF).
-Homoscedasticity: The variance of the error terms (residuals) should be consistent across all levels of the independent variables.
-Residuals plotted against predicted values should not display any obvious pattern.
-Furthermore, in our model, the variable "duration" is derived from the difference between "start_date" and "end_date" in the original data.
-This means our model cannot account for the effects brought by time series, but considering the linear relationship between these two, we simplified it to meet the assumptions of using MLR.
-
-Additionally, there are 51 different categories for the "methodology" variable in the original dataset.
-Having too many categories for a categorical variable would increase the complexity of our model, so we simplified it into four levels.
-Level 1 represents the lowest reliability of the methodology, while level 4 represents the highest.
+```
+
+The estimands, Score_Trump and Score_Harris, represent the competitiveness of each candidate.
+A higher score indicates stronger competitiveness.
+If the predicted score for one candidate is higher than the other, we consider that candidate to be the likely winner of the election.
+
+`pollscore`, `transparency_score`, `duration`, `sample_size`, `population`, and `hypothetical` are our estimators.
+`duration` represents the length of a poll in days.
+Detailed descriptions of the other estimators are provided in the data section.
+
+Notably, we used a Multiple Linear Regression (MLR) model, which implies the following assumptions:
+
+1. **Linear Relationship**: A linear relationship exists between the estimand and the estimators.
+2. **Multivariate Normality**: The residuals (differences between observed and predicted values) are normally distributed.
+3. **No Multicollinearity**: The correlations between independent variables are not significant.
+4. **Homoscedasticity**: The variance of residuals remains consistent across all values of the redictors.
+
+## Estimand and Estimators
+
+Our estimand, `score` represents the support rate of a candidate in a particular poll, corresponding to the `pct` in the raw data.
+However, due to our methodology, the final result cannot be expressed as a proportion, and thus we named it `score`.
+The @fig-dositd shows the distribution of scores for Trump and Harris in their respective training sets.
+It can be observed that both distributions are approximately normal.
+Compared to the distribution of `pct` in the raw data, it can be observed that Trump and Harris have very few `score` in the low range.
+This means that most candidates have very low support rates.
+
+```{r, fig.pos="H", fig.width=14, fig.height=6}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-dositd
+#| fig-cap: "Distribution of score in training datasets"
+
+# Create a list to store the plots
+plots <- list()
+
+# Plot a histogram for the 'pct' variable in Trump data
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Trump", x = "Score", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18), # Consistent title font size
+    axis.title = element_text(size = 16), # Consistent axis title font size
+    axis.text = element_text(size = 14) # Consistent axis text font size
+  )
+
+# Plot a histogram for the 'pct' variable in Harris data
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = score)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Harris", x = "Score", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18), # Consistent title font size
+    axis.title = element_text(size = 16), # Consistent axis title font size
+    axis.text = element_text(size = 14) # Consistent axis text font size
+  )
+
+### Combine and Print Plots ###
+# Arrange the plots vertically with one column and consistent styling
+combined_plot <- wrap_plots(plots, ncol = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 18)
+    )
+  )
+
+# Print the combined plot
+print(combined_plot)
+```
+
+Since our training set was obtained via simple random sampling, the distributions of `pollscore`, `transparency_score`, `sample_size`, `population`, and `hypothetical` are similar to those in the raw data, which will not be further elaborated here.
+The variable `duration` is derived from the difference between `start_date` and `end_date` in the original data.
+This means that our model cannot account for time series effects, but we simplified this to meet the assumptions of using MLR given the linear relationship between these two variables.
+@fig-doditd are histograms that display the `duration` of polls nominating Trump and Harris.
+It can be observed that they follow a highly skewed distribution, with most values clustered around 1-2 days.
+
+```{r, fig.pos="H", fig.height=7, fig.width=14 }
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-doditd
+#| fig-cap: "Distribution of duration in training dataset"
+
+# Create a list to store the plots
+plots <- list()
+
+# Plot a histogram for the 'duration' variable in Trump data
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Trump", x = "Duration", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18), # Consistent title font size
+    axis.title = element_text(size = 16), # Consistent axis title font size
+    axis.text = element_text(size = 14) # Consistent axis text font size
+  )
+
+# Plot a histogram for the 'duration' variable in Harris data
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = duration)) +
+  geom_histogram(binwidth = 2, fill = "#69b3a2", color = "black", alpha = 0.7) +
+  labs(title = "Harris", x = "Duration", y = "Frequency") +
+  theme_minimal(base_size = 16) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 18), # Consistent title font size
+    axis.title = element_text(size = 16), # Consistent axis title font size
+    axis.text = element_text(size = 14) # Consistent axis text font size
+  )
+
+### Combine and Print Plots ###
+# Arrange the plots vertically with one column
+combined_plot <- wrap_plots(plots, ncol = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 18)
+    )
+  )
+
+# Print the combined plot
+print(combined_plot)
+```
+
+It is worth noting that although our final model does not consider `methodology`, in the initial model exploration phase, we simplified the 51 different categories of the `methodology` variable into four levels to maintain simplicity.
+`level_1` represents the lowest reliability, while `level_4` represents the highest.
 The specific classifications are as follows:
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-mc
-#| tbl-cap: "Methodology classfication"
-
-# Create a summary data frame for the methodologies and their levels
-methodology_summary <- data.frame(
-  Level = c("level 1", "level 2", "level 3", "level 4"),
-  Methodologies = c(
-    paste(c("Email", "Email/Online Ad", "Live Phone/Text-to-Web/Email/Mail-to-Web/Mail-to-Phone", "Mail-to-Web/Mail-to-Phone", "Online Ad"), collapse = ", "),
-    paste(c("App Panel", "IVR", "IVR/Live Phone/Text/Online Panel/Email", "IVR/Online Panel", "IVR/Online Panel/Email", "IVR/Online Panel/Text-to-Web", "IVR/Online Panel/Text-to-Web/Email", "IVR/Text", "IVR/Text-to-Web", "IVR/Text-to-Web/Email", "Live Phone/Email", "Live Phone/Online Panel/Mail-to-Web", "Live Phone/Text/Online Ad", "Live Phone/Text-to-Web/Email", "Live Phone/Text-to-Web/Email/Mail-to-Web", "Live Phone/Text-to-Web/Online Ad", "Online Panel/Email", "Online Panel/Email/Text-to-Web", "Online Panel/Online Ad", "Text-to-Web/Email", "Text-to-Web/Online Ad"), collapse = ", "),
-    paste(c("IVR/Live Phone/Online Panel", "IVR/Live Phone/Online Panel/Text-to-Web", "IVR/Live Phone/Text", "IVR/Live Phone/Text-to-Web", "Live Phone/Online Panel/App Panel", "Live Phone/Online Panel/Text", "Live Phone/Online Panel/Text-to-Web", "Live Phone/Online Panel/Text-to-Web/Text", "Live Phone/Text", "Live Phone/Text/Online Panel", "Live Phone/Text-to-Web", "Live Phone/Text-to-Web/App Panel", "Online Panel", "Online Panel/Text", "Online Panel/Text-to-Web", "Online Panel/Text-to-Web/Text", "Text", "Text-to-Web"), collapse = ", "),
-    paste(c("Live Phone", "Live Phone/Online Panel", "Live Phone/Probability Panel", "Online Panel/Probability Panel", "Probability Panel"), collapse = ", ")
-  )
-)
-
-# Print the summary of methodologies and their levels using kable
-kable(methodology_summary, col.names = c("Level", "Methodologies")) %>%
-  column_spec(1, width = "1.5cm") %>% # Adjust the width of the first column
-  column_spec(2, width = "13cm")
-```
-The different methodologies were evaluated based on reliability scores ranging from 1 to 10.
-The scores of 51 combinations were calculated by averaging the individual scores of each methodology in the combination.
-The results were classified into four levels: high reliability (8.5-10), medium-high reliability (7-8.49), medium reliability (5-6.99), and low reliability (below 5).
-Methodologies were scored based on several criteria, including statistical rigor, representativeness, response rate, interaction quality, and cost efficiency.
-High-scoring methodologies, such as those employing strict statistical sampling methods like Probability Panels or those using Live Phone surveys with broad coverage and low refusal rates, received high scores due to their strong representativeness and reliability.
-Medium-high scoring methodologies included Online Panels, which offer good coverage and low cost but are susceptible to self-selection bias, and Text-to-Web methods, which improve response rates but may have limited representativeness depending on the target demographics.
-Medium-scoring methodologies, such as App Panels and IVR (Interactive Voice Response), tend to lack broad representativeness or have limitations in interaction quality, making them suitable for niche audiences but not generalizable to a wider population.
-Low-scoring methodologies, including Email Surveys and methods relying on Online Ads, often suffer from low response rates and significant selection bias, which negatively impact their reliability.
-These scoring criteria ensure that the methodologies are evaluated in a consistent manner, with higher scores reflecting stronger statistical foundations, broader representativeness, and better data quality.
-
-Additionally, the reason we only compared the data of Trump and Harris to predict which of them would win the election is that, after comparing the weighted competitiveness scores of all candidates, we found that the top three — Trump, Harris, and Biden — had significantly higher scores than the others.
-As shown in @tbl-t5c, the third-place candidate, Harris, had a weighted competitiveness score of 180714535, which is 5.15 times higher than the fourth-place score of 34987031.
-Considering that Biden has withdrawn from the race, we ultimately decided to only predict between the most competitive candidates, Trump and Harris.
-The specific weighting formula is as follows:
-
+**Methodologies were scored based on several criteria, including statistical rigor, representativeness, response rate, interaction quality, and cost efficiency.**
+
+- **High-scoring methodologies**: Methods such as Probability Panels or Live Phone surveys with broad coverage and low refusal rates received high scores due to strong representativeness and reliability.
+- **Medium-high scoring methodologies**: Online Panels and Text-to-Web methods were rated in this category.
+Online Panels are cost-effective but susceptible to self-selection bias, whereas Text-to-Web improves response rates but may lack representativeness depending on the target demographics.
+- **Medium-scoring methodologies**: App Panels and IVR (Interactive Voice Response) tend to lack broad representativeness or interaction quality, making them suitable only for niche audiences.
+- **Low-scoring methodologies**: Email Surveys and methods relying on Online Ads often have low response rates and significant selection bias, which undermines their reliability.
+
+## Alternative Models
+
+Below are our initial models. Their estimators included all variables from the analysis datasets.
+
+```{=tex}
 \begin{align} 
-& weighted\_score  = \frac{ {\textstyle \sum_{i  = 1}^{n}score_i} }{n}\times {\textstyle \sum_{i  = 1}^{n}Sample\_Size_i} \\
-& \text{Where: }\notag\\
-&\hspace{1cm}n\text{ represents the number of polls nominating this candidate.}\notag\\
-&\hspace{1cm}Score_i\text{ represents the score obtained by the candidate in the } i^{th}\text{ poll.}\notag\\
-&\hspace{1cm}Sample\_Size_i\text{ represents the sample size of the } i^{th}\text{ poll.}\notag
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \notag \\
+        &\beta_7Methodology + \beta_8Numeric\_grade + \beta_9Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag \\
+        &\alpha_7Methodology + \alpha_8Numeric\_grade + \alpha_9Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6,7,8,9 \right \} \notag 
 \end{align}
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-wsft5c
-#| tbl-cap: "Weighted score for top 5 candidates"
-# Define the directory path containing the parquet files
-p <- "data/03-cleaned_data"
-parquet_files <- list.files(path = here::here(p), full.names = TRUE)
-
-# Initialize an empty dataframe to store the weighted score for each file
-weighted_scores <- data.frame(Candidate = character(), Weighted_Score = numeric(), stringsAsFactors = FALSE)
-
-# Iterate over each parquet file
-for (file in parquet_files) {
-  # Read the parquet file
-  df <- read_parquet(here::here(file))
-
-  # Calculate the mean of score and sample_size
-  score_mean <- mean(df$score, na.rm = TRUE)
-  sample_size_mean <- mean(df$sample_size, na.rm = TRUE)
-
-  # Calculate the weighted score (multiply by total number of rows)
-  weighted_score <- score_mean * sample_size_mean * nrow(df)
-
-  # Append the result to the weighted_scores dataframe
-  weighted_scores <- rbind(weighted_scores, data.frame(Candidate = sub('_cleaned_data.parquet$', '', basename(file)), Weighted_Score = weighted_score))
-}
-
-# Get the top 5 weighted scores
-top_5_weighted_scores <- weighted_scores %>% 
-  arrange(desc(Weighted_Score)) %>% 
-  head(5)
-
-# Print the top 5 weighted scores using kable
-top_5_weighted_scores %>% kable()
-
-```
-
-## Model set-up
-### response variable
-在此章节中，我们用到的数据都是哈里斯和特朗普的训练集。
-score是我们模型的response variable，它代表的是某个候选人在某次选票中胜利的可能性，越大代表着该候选人竞选成功的概率越大，通常情况下与该候选人在那次选票中的支持率一样。
-下图可以看出来哈里斯和特朗普的score都接近于正态分布。其中川普的score呈现一个对称的趋势，其中最多的score是在50左右。训练集中，川普的score平均数是44.63，方差是24.68。相比之下，哈里斯的score分布有一些偏向于左侧的倾斜。训练集中，哈里斯的score平均数高于特朗普为46.92，方差略低于川普为20.96。值得注意的是川普数据的样本量为3960，而哈里斯只有1636.
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-sositd
-#| tbl-cap: "Sumarry of score in training datasets"
-# Calculate mean, variance, and sample size
-summary_stats <- bind_rows(
-  train_Trump %>% summarise(mean = round(mean(score, na.rm = TRUE), 2), variance = round(var(score, na.rm = TRUE), 2), sample_size = n()) %>% mutate(dataset = "train_Trump"),
-  train_Harris %>% summarise(mean = round(mean(score, na.rm = TRUE), 2), variance = round(var(score, na.rm = TRUE), 2), sample_size = n()) %>% mutate(dataset = "train_Harris")
-)
-
-# Display results using kable
-summary_stats %>%
-  select(dataset, mean, variance, sample_size) %>%
-  kable()
-
-```
-
-```{r, fig.pos="H", fig.height=30, fig.width=60}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-dositd
-#| fig-cap: "Distribution of scores in training dataset"
+```
+
+Upon comparing the relationship between `numeric_grade` and `pollscore`, we observed a significant linear relationship, as shown in @fig-rbnap.
+Therefore, we removed `numeric_grade` from the model to satisfy MLR assumptions, resulting in our second model.
+```{r, fig.pos="H", fig.height=6, fig.width=10}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-rbnap
+#| fig-cap: "Relationship between numeric_grade and pollscore"
 
 plots <- list()
-# Plot a histogram for the 'pct' variable
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = score)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = score)) +
-  geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Histogram of pct", x = "pct", y = "Frequency")
+# Plot relationship between numeric_grade and pollscore for train_Trump
+plots[["Trump"]] <- ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "#A9CCE3") +
+  labs(
+    title = "Trump",
+    x = "Numeric Grade",
+    y = "Pollscore"
+  ) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+
+# Plot relationship between numeric_grade and pollscore for train_Harris
+plots[["Harris"]] <- ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "#F1948A") +
+  labs(
+    title = "Harris",
+    x = "Numeric Grade",
+    y = "Pollscore"
+  ) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
 
@@
 # Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1, heights = unit(rep(20, 20), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2) +
   plot_annotation(
@@
 print(combined_plot)
-
-```
-
-### Predictor
-我们的predictors包含以下变量：
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-predictors <- c("pollscore","methodology","transparency_score","sample_size","population", 
-           "ranked_choice_reallocated", "hypothetical", "duration")
-predictors
-```
-
-下图展示了在川普的训练集中，numerical predictor 之间的关系。没有明显的趋势代表着它们之间没有明显的correlation。
-```{r, fig.width=10, fig.height=10}
-#| warning: false
-#| message: false
-#| echo: false
-data2 = train_Trump %>% select("pollscore","transparency_score","sample_size","duration")
-pairs( data2 , main = "Predictor vs predictor")
-```
-
-关于categorical的：。。。。。。。。。。。。。。。。
-
-### alternative models
-最开始我们的模型是
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-Trump_model_0 <- lm(
-  score ~ numeric_grade + pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Trump)
-Harris_model_0 <- lm(
-  score ~ numeric_grade + pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Harris)
-```
-
-因为我们考虑到numeric_grade和pollscore之间有强线性相关，我们舍弃了这一方案。
-```{r, fig.pos="H", fig.height=10, fig.width=10}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: fig-rbnap
-#| fig-cap: "Relationship between numeric_grade and pollscore"
-
-plots <- list()
-# Plot relationship between numeric_grade and pollscore for train_Trump
-plots[["Trump"]]<-ggplot(train_Trump, aes(x = numeric_grade, y = pollscore)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "blue") +
-  labs(title = "Relationship between Numeric Grade and Pollscore (train_Trump)",
-       x = "Numeric Grade",
-       y = "Pollscore")
-
-# Plot relationship between numeric_grade and pollscore for train_Harris
-plots[["Harris"]]<-ggplot(train_Harris, aes(x = numeric_grade, y = pollscore)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "red") +
-  labs(title = "Relationship between Numeric Grade and Pollscore (train_Harris)",
-       x = "Numeric Grade",
-       y = "Pollscore")
-
-### Combine and Print Plots ###
-# Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 10), "in")) +
-  plot_annotation(
-    theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
-    )
-  )
-# Print the combined plot
-print(combined_plot)
-
-```
-
-这个是我们的第二个方案。虽然predictors之间没有了相关性，但是methodology，ranked_choice_reallocated，这两个变量并不statistical significant，因为他们的p value都大于0.05.
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
+```
+
+The second model is as follows:
+
+```{=tex}
+\begin{align} 
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \notag \\
+        &\beta_7Methodology + \beta_8Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag \\
+        &\alpha_7Methodology + \alpha_8Ranked\_choice\_reallocated + \beta_0 \notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6,7,8 \right \} \notag 
+\end{align}
+```
+
+We determined the significance of each predictor in the model by checking if the p-value was less than 0.5.
+As shown in @tbl-alovitahm below, both `methodology` and `ranked_choice_reallocated` were found to be insignificant predictors in both models.
+Thus, they were excluded to reduce model complexity.
+
+```{r, fig.height=100,fig.width=100}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-alovitahm
+#| tbl-cap: "Significant level of variblaes in the first models"
+
+# Define and fit models for Trump and Harris
 Trump_model_1 <- lm(
   score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Trump)
+    methodology,
+  data = train_Trump
+)
 Harris_model_1 <- lm(
   score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical + ranked_choice_reallocated +
-    methodology, data = train_Harris)
-```
-
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitahm
-#| tbl-cap: "Significant level of variblaes in the aboanded Harris's model"
-# Get the summary of the model
+    methodology,
+  data = train_Harris
+)
+
+# Get summaries of the models and extract coefficients
 Harris_summary <- summary(Harris_model_1)
-# Extract coefficients from the summary
-coefficients <- Harris_summary$coefficients
-# Extract p-values
-Harris_p_values <- coefficients[, 4]
-# Create a data frame with the results
-Harris_results_table <- data.frame(
-  Variable = rownames(coefficients),
-  P_Value = format(Harris_p_values, scientific = TRUE)
-)
-Harris_kable <- kable(Harris_results_table[, 2, drop = FALSE], caption = "Model for Harris", col.names = c("Variable", "P-value"))
-
-Harris_kable
-
-```
-
-```{r, fig.height=100,fig.width=100}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-alovitatm
-#| tbl-cap: "Significant level of variblaes in the aboanded Trump's model"
-
-# Get the summary of the model
 Trump_summary <- summary(Trump_model_1)
-# Extract coefficients from the summary
-coefficients <- Trump_summary$coefficients
-# Extract p-values
-Trump_p_values <- coefficients[, 4]
-# Create a data frame with the results
-Trump_results_table <- data.frame(
-  Variable = rownames(coefficients),
-  P_Value = format(Trump_p_values, scientific = TRUE)
-)
-Trump_kable <- kable(Trump_results_table[, 2, drop = FALSE], caption = "Model for Trump", col.names = c("Variable", "P-value"))
-
-Trump_kable
-```
-
-因此，我们有有了最后的模型。
-
-## validation
-从您的结果来看，所有变量的 GVIF 值都在 1 到 1.3 之间，这些数值非常低，表明各个自变量之间的共线性很小，模型并没有因为共线性而受到显著影响。
+
+# Extract p-values for Harris and Trump models
+Harris_p_values <- Harris_summary$coefficients[, 4]
+Trump_p_values <- Trump_summary$coefficients[, 4]
+
+# Create a data frame with the results, using row names for the variable names
+combined_results_table <- data.frame(
+  Harris = format(Harris_p_values, scientific = TRUE),
+  Trump = format(Trump_p_values, scientific = TRUE),
+  row.names = rownames(Harris_summary$coefficients)
+)
+
+# Display the combined table with kable, without the Variable column
+combined_kable <- kable(
+  combined_results_table,
+  col.names = c("Harris", "Trump"),
+  align = "cc"
+)
+
+combined_kable
+```
+
+Our final model is as follows:
+
+```{=tex}
+\begin{align} 
+Score_{Trump} = &\beta_1Pollscore + \beta_2Transparency\_score + \beta_3Duration + \\
+        &\beta_4Sample\_size + \beta_5Population + \beta_6Hypothetical + \beta_0 \notag \\[0.5cm]
+Score_{Harris} = &\alpha_1Pollscore + \alpha_2Transparency\_score + \alpha_3Duration + \\
+        &\alpha_4Sample\_size + \alpha_5Population + \alpha_6Hypothetical + \alpha_0 \notag\notag \\[0.5cm]
+        &\text{Where } \beta_i \text{ and } \alpha_i \text{ 
+         are coefficients for } \forall i\in \left \{ 0,1,2,3,4,5,6 \right \} \notag 
+\end{align}
+```
+
+## Validation
+
+First, we verified the assumptions mentioned in the @Model_Overview.
+The @tbl-vohfm shows the General Variance Inflation Factor (GVIF) for both models, which indicates that all predictors have a GVIF less than 1.3, suggesting no significant multicollinearity.
+
 ```{r}
@@
 #| label: tbl-vohfm
-#| tbl-cap: "VIF of Harris's final model"
-# Add a column for variable names (convert row names to a column)
-
-harris_vif <- vif(Harris_model)
-
-# 将 VIF 结果转换为数据框
-# 如果是 GVIF（针对多分类变量），则处理为数据框
-
+#| tbl-cap: "GVIF of the final models"
+# Calculate VIF for Harris model
+harris_vif <- vif(Harris_model_1)
 harris_vif_df <- as.data.frame(harris_vif)
-
 harris_vif_df$Variable <- rownames(harris_vif_df)
 
-# Rearrange columns so that the variable name column is the first column
-
-harris_vif_df <- harris_vif_df[, c(ncol(harris_vif_df), 1:(ncol(harris_vif_df)-1))]
-
-# Use kable to create a formatted table from VIF results
-
-kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
-
-```
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-votfm
-#| tbl-cap: "VIF of Trump's final model"
-
-trump_vif <- vif(Trump_model)
-
-# 将 VIF 结果转换为数据框
-# 如果是 GVIF（针对多分类变量），则处理为数据框
+# Calculate VIF for Trump model
+trump_vif <- vif(Trump_model_1)
 trump_vif_df <- as.data.frame(trump_vif)
-
-# Add a column for variable names (convert row names to a column)
 trump_vif_df$Variable <- rownames(trump_vif_df)
 
-# Rearrange columns so that the variable name column is the first column
-trump_vif_df <- trump_vif_df[, c(ncol(trump_vif_df), 1:(ncol(trump_vif_df)-1))]
-
-# Use kable to create a formatted table from VIF results
-
-kable(harris_vif_df[, 2, drop = FALSE], format = "html", caption = "VIF for Harris Model")
-
-```
-
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-par(mfrow=c(2,2))
-plot(Harris_model,1)
-plot(Harris_model,2)
-```
-
-```{r}
-
-par(mfrow=c(2,2))
-plot(Trump_model,1)
-plot(Trump_model,2)
-```
-然后就是描述一下response variable是normal的，然后numerical variable没有显著关系（这些在打他部分有讲过）
-总结，满足了MLR的条件，说明我们的好
-```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 10, fig.width=10}
+# Combine the VIF data frames by Variable column
+combined_vif_table <- merge(harris_vif_df, trump_vif_df, by = "Variable", suffixes = c("_Harris", "_Trump"))
+
+# Select only the necessary columns: "Variable", "GVIF_Harris", and "GVIF_Trump"
+combined_vif_table <- combined_vif_table[, c("Variable", "GVIF_Harris", "GVIF_Trump")]
+
+# Rename columns for clarity
+colnames(combined_vif_table) <- c("Variable", "Harris", "Trump")
+
+# Use kable to display the combined VIF table
+kable(combined_vif_table, col.names = c("Variable", "Harris", "Trump"))
+```
+
+The following @fig-mdp presents the diagnostic plots for the Harris and Trump's models.
+The plots on the left shows the relationship between residuals and predicted values, and since no obvious pattern is observed, our models satisfies the Homoscedasticity assumption.
+The right-hand plot are a Q-Q plot, and the points align along the diagonal, indicating that residuals are normally distributed and satisfy the Multivariate Normality condition.
+
+```{r, fig.height= 7, fig.width=14, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-mdp
+#| fig-cap: "Model diagnostic plots"
+par(mfrow = c(2, 2))
+plot(Harris_model, 1)
+plot(Harris_model, 2)
+plot(Trump_model, 1)
+plot(Trump_model, 2)
+```
+
+The @fig-pvatrv compares predicted and actual values from the test data.
+For both the Trump and Harris models, the trend between predicted and actual values is roughly linear, indicating that our models are effective.
+
+```{r,message=FALSE, echo=FALSE,warning=FALSE,fig.height = 5, fig.width=10, fig.pos="H"}
+#| label: fig-pvatrv
+#| fig-cap: "Predicted values and the real values"
+
 # Generate predictions using the model
@@
 # Plot the predicted values vs actual values
-plots[["Harris"]]<-ggplot(results_df, aes(x = predictions, y = actual)) +
-  geom_point(color = "blue") + # Scatter plot of predicted vs actual values
-  labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
-  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + # Add reference line y = x
-  theme_minimal() # Use minimal theme for the plot
+plots[["Harris"]] <- ggplot(results_df, aes(x = predictions, y = actual)) +
+  geom_point(color = "#A9CCE3") + # Scatter plot of predicted vs actual values
+  labs(x = "Predicted Values", y = "Actual Values", title = "Harris") +
+  geom_abline(slope = 1, intercept = 0, color = "#F1948A", linetype = "dashed") + # Add reference line y = x
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5)) # Use minimal theme for the plot
 
@@
 # Plot the predicted values vs actual values
-plots[["Trump"]] <-ggplot(results_df_1, aes(x = predictions_1, y = actual_1)) +
-  geom_point(color = "blue") + # Scatter plot of predicted vs actual values
-  labs(x = "Predicted Values", y = "Actual Values", title = "Comparison of Predicted and Actual Values") +
-  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + # Add reference line y = x
-  theme_minimal() # Use minimal theme for the plot
+plots[["Trump"]] <- ggplot(results_df_1, aes(x = predictions_1, y = actual_1)) +
+  geom_point(color = "#A9CCE3") + # Scatter plot of predicted vs actual values
+  labs(x = "Predicted Values", y = "Actual Values", title = "Trump") +
+  geom_abline(slope = 1, intercept = 0, color = "#F1948A", linetype = "dashed") + # Add reference line y = x
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5)) # Use minimal theme for the plot
 
@@
 # Combine all individual plots into one using patchwork with 2 columns and 4 rows
-combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2, heights = unit(rep(4, 8), "in")) +
+combined_plot <- wrap_plots(plots, ncol = 1, nrow = 2) +
   plot_annotation(
     theme = theme(
-      plot.title = element_text(hjust = 0.5, size = 14)
+      plot.title = element_text(hjust = 0.5, size = 14),
+      plot.subtitle = element_text(hjust = 0.5)
     )
@@
 print(combined_plot)
-
-```
-
-# Result
+```
+
+## Model Discussion
+
+As noted above, our model combines the start and end dates of a poll into the "duration" variable, which prevents it from effectively capturing the time series impact on the estimand.
+Additionally, due to the weak linear relationship between the estimators and the estimand, the explanatory power of our model, as reflected by the adjusted R-Square, is relatively low.
+Polynomial Regression or Generalized Linear Models might be better choices in this context.
+Moreover, when significant relationships exist between estimators, our model might fail.
+
+# Result {#sec-result}
 ## featured values used in prediction
@@
 
-variables <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
+variables <- c(
+  "numeric_grade", "pollscore", "methodology", "transparency_score",
   "sample_size", "population", "ranked_choice_reallocated",
-               "hypothetical", "score", "duration")
+  "hypothetical", "score", "duration"
+)
 
@@
 # Display the final table with kable
-kable(all_candidate_features)
-
+kable(all_candidate_features, , col.names = c("Variables", "Trump", "Harris"))
 ```
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-Harris_predict <- round(predict(Harris_model, newdata = harris_features),2)
-Trump_predict <- round(predict(Trump_model, newdata = trump_features),2)
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-psftah
+#| fig-cap: "Predicted scores for Trump and Harris"
+
+Harris_predict <- round(predict(Harris_model, newdata = harris_features), 2)
+Trump_predict <- round(predict(Trump_model, newdata = trump_features), 2)
 
@@
   geom_bar(stat = "identity", width = 0.5) +
-  labs(title = "Predicted Values for Each Candidate",
+  labs(
     x = "Candidate",
-       y = "Prediction") +
+    y = "Prediction"
+  ) +
   theme_minimal() +
@@
 
-Overall, our approach demonstrates how feature engineering and predictive modeling can offer insights into candidate support based on the available data.
-However, it is important to interpret these results cautiously, as they rely on specific variables and assumptions embedded within the dataset.
-In this analysis, we aggregated representative feature values for each candidate by using the mean or median for numeric variables, the mode for categorical variables, and the most frequent occurrence for Boolean values.
-Further refinement and additional data could enhance the robustness of these predictions, contributing to a more comprehensive forecast in future studies.
-
-# Discussion
-
-This study employs a multiple linear regression model to analyze polling data, aiming to forecast public support for U.S.
-2024 presidential election candidates Kamala Harris and Donald Trump.By identifying key determinants of polling accuracy, this analysis predicts a slight lead for Kamala Harris with 47.6% support over Donald Trump’s 43.5%.
+The results indicate that high transparency scores and reliable polling methods improve prediction quality, while careful attention to demographic representation—such as sample size and population type—ensures the polling data reflects the broader electorate.
+The model forecasts a slight lead for Kamala Harris, with an estimated 47.6% support compared to 43.5% for Donald Trump, underscoring the essential role of reliable data sources in public opinion forecasting.
+These findings highlight the importance of stringent polling standards and precise demographic selection in enhancing the predictive accuracy of electoral models.
+
+# Discussion {#sec-discussion}
+
+This study employs a multiple linear regression model to analyze polling data and forecast public support for U.S.
+2024 presidential election candidates Kamala Harris and Donald Trump.
+By identifying key determinants of polling accuracy, this analysis predicts a slight lead for Kamala Harris with 47.6% support over Donald Trump’s 43.5%.
 
@@
 Polls with higher transparency scores yield more accurate predictions, emphasizing the importance of clear polling practices.
-Variations in sample size and population type also underscore the need for representative sampling to capture genuine voter sentiment.
+Sample size and population type variations also underscore the need for representative sampling to capture genuine voter sentiment.
 
@@
 
-# Appendix
+# Appendix {#sec-appendix}
 
 ## Analysis of YouGov Pollster Methodology
-
 In this appendix, we provide a deep-dive analysis of the methodology employed by YouGov, one of the pollsters included in our sample.
@@
 set3_vars <- c("sponsor_ids", "question_id", "internal", "race_id")
-
-# Define a function to generate a grid of plots for a given set of variables with increased text size
-plot_variable_distributions <- function(data, vars) {
+```
+
+```{r, fig.width=10, fig.height=10, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-ivirdp1
+#| fig-cap: "Insignificant variables in raw data part 1"
+
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
 plots <- list()
-  for (var in vars) {
-    if (is.numeric(data[[var]])) {
-      p <- ggplot(data, aes(x = .data[[var]])) +
-        geom_histogram(bins = 30, fill = "steelblue", color = "black") +
-        labs(title = var) +
-        theme_minimal() +
-        theme(
-          plot.title = element_text(size = 18, face = "bold"),
-          axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.x = element_blank(),
-          axis.text.y = element_blank()
-        )
-    } else {
-      p <- ggplot(data, aes(x = .data[[var]])) +
-        geom_bar(fill = "steelblue", color = "black") +
-        labs(title = var) +
-        theme_minimal() +
-        theme(
-          plot.title = element_text(size = 18, face = "bold"),
-          axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.text.x = element_text(size = 14, angle = 45, hjust = 1)
+# Loop through selected numeric variables and plot their distributions
+for (variable in set1_vars) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
     )
 }
-    plots[[var]] <- p
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+```{r, fig.width=10, fig.height=5, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-ivirdp2
+#| fig-cap: "Insignificant variables in raw data part 2"
+
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in set2_vars) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
 }
-  return(plots)
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+```{r, fig.width=10, fig.height=10, fig.pos="H"}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-ivirdp3
+#| fig-cap: "Insignificant variables in raw data part 3"
+
+### Create Plots for Numeric Variables ###
+# Create a list to store plots
+plots <- list()
+# Loop through selected numeric variables and plot their distributions
+for (variable in set3_vars) {
+  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
+    geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
+    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
+    theme_minimal(base_size = 30) +
+    theme(
+      plot.title = element_text(hjust = 0.5, size = 12),
+      axis.title = element_text(size = 10),
+      axis.text = element_text(size = 10)
+    )
 }
-
-# Generate plots for each set of variables
-plot1 <- plot_variable_distributions(raw_data, set1_vars)
-plot2 <- plot_variable_distributions(raw_data, set2_vars)
-plot3 <- plot_variable_distributions(raw_data, set3_vars)
-
-# Arrange the first three sets of plots into grids and display them
-grid.arrange(grobs = plot1, ncol = 2, top = textGrob("Distribution of Variables (Set 1)", gp=gpar(fontsize=20, fontface="bold")))
-grid.arrange(grobs = plot2, ncol = 2, top = textGrob("Distribution of Variables (Set 2)", gp=gpar(fontsize=20, fontface="bold")))
-grid.arrange(grobs = plot3, ncol = 2, top = textGrob("Distribution of Variables (Set 3)", gp=gpar(fontsize=20, fontface="bold")))
-
-# Separate set4, set5, and set6 variables for individual adjustments
-
-# Set 4: State Plot (excluding NA)
-state_plot <- raw_data %>%
-  filter(!is.na(state)) %>%  
-  count(state, sort = TRUE) %>%
-  top_n(10) %>%
-  ggplot(aes(y = reorder(state, n), x = n)) +
-  geom_bar(stat = "identity", fill = "steelblue", color = "black") +
-  labs(title = "Distribution of State (Set 4)") +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 20, face = "bold"),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12),
-    axis.text.y = element_text(size = 12)
-  )
-
-# Set 5: ranked_choice_round_plot Plot (excluding NA)
-ranked_choice_round_plot <- raw_data %>%
-  filter(!is.na(ranked_choice_round)) %>%  
-  ggplot(aes(x = ranked_choice_round)) +
-  geom_density(fill = "steelblue", alpha = 0.7) +
-  labs(title = "Distribution of ranked_choice_round (Set 5)") +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 20, face = "bold"),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 12)
-  )
-
-created_at_plot <- raw_data %>%
-  filter(!is.na(created_at)) %>%  # 去掉NA值
-  ggplot(aes(x = as.POSIXct(created_at, format = '%m/%d/%y %H:%M'))) +
-  geom_density(fill = "steelblue", alpha = 0.7) +
-  labs(title = "Distribution of Created At (Set 8)") +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 20, face = "bold"),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 12)
-  )
-
-# Display each plot individually
-print(state_plot)
-print(ranked_choice_round_plot)
-print(created_at_plot)
-```
+### Combine and Print Plots ###
+# Combine all individual plots into one using patchwork with 2 columns and 4 rows
+combined_plot <- wrap_plots(plots, ncol = 2, nrow = 2) +
+  plot_annotation(
+    theme = theme(
+      plot.title = element_text(hjust = 0.5, size = 14)
+    )
+  )
+# Print the combined plot
+print(combined_plot)
+```
+# References

### 2024-11-04 scripts/00-simulate_data.R

@@ -13,7 +13,7 @@ library(tidyverse)
 library(arrow)
 # Set a random seed for reproducibility
 set.seed(123)
-  
+
 ## Generate simulated data for candidate_1
 simulated_candidate_1 <- tibble(
   # Generate numeric_grade based on a normal distribution with mean 2.5 and standard deviation 2,
@@ -32,7 +32,7 @@ simulated_candidate_1 <- tibble(
   # Population types：Likely Voters，Registered Voters, Voters, Adult
   population = sample(c("a", "v", "lv", "rv"), 500, replace = TRUE),
   # Set TRUE/FALSE ratio to 0.9 for the hypothetical column
-  ranked_choice_reallocated= sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.1, 0.9)),
+  ranked_choice_reallocated = sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.1, 0.9)),
   # Set TRUE/FALSE ratio to 0.3 for the hypothetical column
   hypothetical = sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.3, 0.7)),
   # Use NA as a placeholder for the score.
@@ -40,33 +40,36 @@ simulated_candidate_1 <- tibble(
 )
 
 # Calculate the score based on other variables and the corresponding assumed weights.
-simulated_candidate_1$score = 
+simulated_candidate_1$score <-
   round(
-    simulated_candidate_1$numeric_grade * 4 + 
-  # Assume that numeric_grade, pollscore, and transparency_score are equally important, and their ranges are all from 0 to 10.
-  (10 - (simulated_candidate_1$pollscore +1) * 10) + # Because pollscore is the less the better
-  simulated_candidate_1$transparency_score + 
-  # When sample size > 800, the score + 10. When 300 <= sample size <= 800, the score +7. Other wise score +3
-  ifelse(simulated_candidate_1$sample_size > 8000, 10, 
-         ifelse((simulated_candidate_1$sample_size >= 3000) & (simulated_candidate_1$sample_size <= 8000), 7, 
-                ifelse(simulated_candidate_1$sample_size < 3000, 3, 0
-                       ))) +
-  # When the poll is reallocated, it get 0 in this factor. Otherwise it will get 10.
-  ifelse(simulated_candidate_1$ranked_choice_reallocated, 3, 10) +
[…]

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -1,6 +1,6 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated variables 
-  #of U.S. election candidates
+# Purpose: Tests the structure and validity of the simulated variables
+# of U.S. election candidates
 # Author: Haowei Fan, Fangning Zhang, Shaotong Li
 # Date: 13 October 2024
 # Contact: haowei.fan@mail.utoronto.ca
@@ -40,37 +40,48 @@ analysis_data_2$transparency_score <- pmin(pmax(analysis_data_2$transparency_sco
 
 
 # Define expected columns, excluding `poll_id`
-expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
-                      "duration", "sample_size", "population", "ranked_choice_reallocated", 
-                      "hypothetical", "score")
+expected_columns <- c(
+  "numeric_grade", "pollscore", "methodology", "transparency_score",
+  "duration", "sample_size", "population", "ranked_choice_reallocated",
+  "hypothetical", "score"
+)
 
 #### Test structure of datasets ####
 test_that("Simulated datasets contain all expected columns", {
   for (data in list(analysis_data_1, analysis_data_2)) {
-    expect_true(all(expected_columns %in% colnames(data)), 
-                info = "Some expected columns are missing in one or more datasets.")
+    expect_true(all(expected_columns %in% colnames(data)),
+      info = "Some expected columns are missing in one or more datasets."
+    )
   }
 })
 
 #### Test data types of specific columns ####
 test_that("Columns have correct data types", {
   for (data in list(analysis_data_1, analysis_data_2)) {
-    expect_true(is.numeric(data$numeric_grade), 
-                info = "numeric_grade should be numeric.")
-    expect_true(is.numeric(data$pollscore), 
-                info = "pollscore should be numeric.")
-    expect_true(is.character(data$methodology), 
-                info = "methodology should be character.")
-    expect_true(is.numeric(data$transparency_score), 
-                info = "transparency_score should be numeric.")
-    expect_true(is.integer(data$sample_size), 
-                info = "sample_size should be integer.")
-    expect_true(is.logical(data$ranked_choice_reallocated), 
-                info = "ranked_choice_reallocated should be logical.")
-    expect_true(is.logical(data$hypothetical), 
-                info = "hypothetical should be logical.")
-    expect_true(is.numeric(data$score), 
-                info = "score should be numeric.")
[…]

### 2024-11-04 scripts/02-download_data.R

@@ -15,6 +15,4 @@ url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
 the_raw_data <- read.csv(url)
 
 #### Save data ####
-write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
-
-
+write_csv(the_raw_data, "data/01-raw_data/raw_data.csv")

### 2024-11-04 scripts/03-clean_data.R

@@ -10,72 +10,72 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
-library(janitor)  # For clean_names
-library(tidyr)   # For drop_na
+library(janitor) # For clean_names
+library(tidyr) # For drop_na
 library(lubridate)
 library(arrow)
 
-set.seed(123)  # Set seed for reproducibility
+set.seed(123) # Set seed for reproducibility
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
 # Step 1: Remove variables with more than 40% NA values
 threshold <- 0.4 * nrow(raw_data)
 raw_data_cleaned <- raw_data %>%
-  select_if(~sum(is.na(.)) <= threshold)
+  select_if(~ sum(is.na(.)) <= threshold)
 
 # Step 2: Remove variables with all identical values
 raw_data_cleaned <- raw_data_cleaned %>%
-  select_if(~is.numeric(.) || n_distinct(.) > 1)
+  select_if(~ is.numeric(.) || n_distinct(.) > 1)
 
 # Step 3: Remove duplicated, unrelated variables
 raw_data_cleaned <- raw_data_cleaned %>%
-  dplyr::select(-any_of(c("pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name", 
-                          "question_id", "population_full", "created_at", "url", "url_article", "race_id", 
-                          "candidate_id", "candidate_name", "party", "seat_number", "cycle"))) 
-  
+  dplyr::select(-any_of(c(
+    "pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name",
+    "question_id", "population_full", "created_at", "url", "url_article", "race_id",
+    "candidate_id", "candidate_name", "party", "seat_number", "cycle"
+  )))
+
 # Step 4: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
-raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date)-mdy(raw_data_cleaned$start_date))
+raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date) - mdy(raw_data_cleaned$start_date))
[…]

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -14,7 +14,7 @@
 # Load necessary libraries
 library(tidyverse)
 library(testthat)
-library(arrow)  # For reading Parquet files
+library(arrow) # For reading Parquet files
 library(here)
 
 Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
@@ -29,10 +29,12 @@ context("Data validation tests for Trump and Harris datasets")
 
 # Test 1: Check if the datasets have the expected columns
 test_that("Expected columns are present in Trump and Harris test and train datasets", {
-  expected_columns <- c("numeric_grade", "pollscore", "methodology", "transparency_score", 
-                        "sample_size", "population", "ranked_choice_reallocated", 
-                        "hypothetical", "score", "duration")
-  
+  expected_columns <- c(
+    "numeric_grade", "pollscore", "methodology", "transparency_score",
+    "sample_size", "population", "ranked_choice_reallocated",
+    "hypothetical", "score", "duration"
+  )
+
   # Check columns in each dataset
   expect_true(all(expected_columns %in% colnames(Trump_test)))
   expect_true(all(expected_columns %in% colnames(Harris_test)))
@@ -44,7 +46,7 @@ test_that("Expected columns are present in Trump and Harris test and train datas
 test_that("No missing values in critical columns of test and train datasets", {
   # List critical columns
   critical_columns <- c("numeric_grade", "pollscore", "score", "sample_size", "population")
-  
+
   # Check for missing values
   for (col in critical_columns) {
     expect_true(all(!is.na(Trump_test[[col]])), info = paste("Missing values in Trump_test:", col))
@@ -58,10 +60,10 @@ test_that("No missing values in critical columns of test and train datasets", {
 test_that("Columns have the correct data types", {
   # Numeric columns
   numeric_columns <- c("numeric_grade", "pollscore", "transparency_score", "sample_size", "score", "duration")
-  
+
   # Logical columns
   logical_columns <- c("ranked_choice_reallocated", "hypothetical")
-  
+
   # Check data types in each dataset
   for (col in numeric_columns) {
     expect_true(is.numeric(Trump_test[[col]]), info = paste("Column not numeric in Trump_test:", col))
@@ -69,7 +71,7 @@ test_that("Columns have the correct data types", {
     expect_true(is.numeric(Trump_train[[col]]), info = paste("Column not numeric in Trump_train:", col))
[…]

### 2024-11-04 scripts/06-model_data.R

@@ -18,12 +18,14 @@ Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
 # Function to create and save a linear model for a candidate
 
 Trump_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical , data = Trump)
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical,
+  data = Trump
+)
 Harris_model <- lm(
-  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical , data = Harris)
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical,
+  data = Harris
+)
 
 # Save the model
 saveRDS(Trump_model, file = "models/Trump_model.rds")
 saveRDS(Harris_model, file = "models/Harris_model.rds")
-
-

### 2024-11-04 scripts/07-replications.R

@@ -32,7 +32,3 @@ message("Analysis data testing complete.")
 # 6. Model Data
 source("scripts/06-model_data.R")
 message("Modeling data complete.")
-
-
-
-

### 2024-11-04 other/literature/ElectionForcast_linearmodel.qmd
merging from branch: Final
merging from branch: Final

--- 2024-11-01 other/literature/ElectionForcast_linearmodel.qmd
@@
   Candidate = c("Donald Trump", "Kamala Harris"),
-  Predicted_Support = c(mean(candidate_data$Trump_Predicted_Support, na.rm = TRUE), 
-                        mean(candidate_data$Harris_Predicted_Support, na.rm = TRUE))
+  Predicted_Support = c(
+    mean(candidate_data$Trump_Predicted_Support, na.rm = TRUE),
+    mean(candidate_data$Harris_Predicted_Support, na.rm = TRUE)
+  )
 )
@@
   geom_text(aes(label = paste0(round(Predicted_Support, 1), "%")),
-            vjust = -0.5, size = 5) +
-  labs(title = "",
+    vjust = -0.5, size = 5
+  ) +
+  labs(
+    title = "",
     x = "Candidate",
-       y = "Predicted Support (%)") +
+    y = "Predicted Support (%)"
+  ) +
   theme_minimal() +
@@
   geom_text(aes(label = ifelse(Support > 5, paste0(round(Support, 1), "%"), "")),
-            position = position_stack(vjust = 0.5), color = "white", size = 5)
+    position = position_stack(vjust = 0.5), color = "white", size = 5
+  )
 
@@
 print(pie_chart)
-
 ```

### 2024-11-04 paper/paper.qmd
merging from branch: Final
merging from branch: Final

@@
 This project uses multiple linear regression to predict the outcome of the 2024 U.S.
-presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing insights to help stakeholders prepare for potential shifts in U.S.
+presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing direction to help stakeholders prepare for potential shifts in U.S.
 policies.
@@
 #| echo: false
+#### Install packages ####
+required_packages <- c("tidyverse","knitr","dplyr","arrow","patchwork","car","kableExtra","gridExtra","moments")
+for (pkg in required_packages) {
+  if (!requireNamespace(pkg,quietly = TRUE)) {
+    install.packages(pkg)
+  }
+}
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+#| echo: false
 #### Workspace setup ####
-install.packages("tidyverse")
+
 library(tidyverse)
-install.packages("knitr")
+
 library(knitr)
-install.packages("dplyr")
+
 library(dplyr)
-install.packages("arrow")
+
 library(arrow)
-install.packages("patchwork")
+
 library(patchwork)
-install.packages("car")
+
 library(car)
-install.packages("kableExtra")
+
 library(kableExtra)
-install.packages("gridExtra")
+
 library(gridExtra)
-install.packages("moments")
+
 library(moments)
-install.packages("grid")
+
 library(grid)

### 2024-11-04 scripts/00-simulate_data.R

@@ -1,0 +1,142 @@
+#### Preamble ####
+# Purpose: Simulates a dataset of US president rolls
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+#### Setup ####
+# install required packages
+install.packages("tidyverse")
+install.packages("arrow")
+# Load required libraries
+library(tidyverse)
+library(arrow)
+# Set a random seed for reproducibility
+set.seed(123)
+
+## Generate simulated data for candidate_1
+simulated_candidate_1 <- tibble(
+  # Generate numeric_grade based on a normal distribution with mean 2.5 and standard deviation 2,
+  numeric_grade = round(rnorm(500, mean = 2.5, sd = 2), 1),
+  # Generate pollscore based on a normal distribution with mean -0.5 and standard deviation 0.3,
+  pollscore = round(rnorm(500, mean = -0.5, sd = 0.3), 1),
+  # The methodology is divided into four levels: level 1 represents the least reliable type of methodology, while level 4 represents the most reliable.
+  methodology = sample(c("level1", "level2", "level3", "level4"), 500, replace = TRUE),
+  # Generate transparency_score based on a normal distribution with mean 6 and standard deviation 1.5,
+  # then ensure the values are within the range [1, 10], round to the nearest 0.5, then map to a range of 0 to 10
+  transparency_score = round(rnorm(500, mean = 6, sd = 1.5), 1),
+  # The duration of this poll in days. Duration based on a normal distribution with mean 183 and standard deviation 100,
+  duration = round(rnorm(500, mean = 183, sd = 100)),
+  # Generate sample_size based on a normal distribution with mean 1200 and standard deviation 5000, then round to the nearest integer
+  sample_size = abs(round(rnorm(500, mean = 1200, sd = 5000))),
+  # Population types：Likely Voters，Registered Voters, Voters, Adult
+  population = sample(c("a", "v", "lv", "rv"), 500, replace = TRUE),
+  # Set TRUE/FALSE ratio to 0.9 for the hypothetical column
+  ranked_choice_reallocated = sample(c(TRUE, FALSE), 500, replace = TRUE, prob = c(0.1, 0.9)),
+  # Set TRUE/FALSE ratio to 0.3 for the hypothetical column
[…]

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -1,0 +1,171 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the simulated variables
+# of U.S. election candidates
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 00-simulated_data saved and loaded
+# Any other information needed? None
+
+#### Workspace setup ####
+
+install.packages("tidyverse")
+install.packages("testthat")
+install.packages("arrow")
+
+library(tidyverse)
+library(testthat)
+library(arrow)
+
+analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
+analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
+
+
+#### Test data ####
+
+# Load simulated data files
+analysis_data_1 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_1.parquet"))
+analysis_data_2 <- read_parquet(here::here("data", "00-simulated_data", "simulated_candidate_2.parquet"))
+
+
+# Convert sample_size to integer if necessary
+analysis_data_1$sample_size <- as.integer(analysis_data_1$sample_size)
+analysis_data_2$sample_size <- as.integer(analysis_data_2$sample_size)
+
+
+# Correct out-of-range values for numeric_grade and transparency_score
+analysis_data_1$numeric_grade <- pmin(pmax(analysis_data_1$numeric_grade, 1), 5)
+analysis_data_2$numeric_grade <- pmin(pmax(analysis_data_2$numeric_grade, 1), 5)
+
+
+analysis_data_1$transparency_score <- pmin(pmax(analysis_data_1$transparency_score, 1), 10)
+analysis_data_2$transparency_score <- pmin(pmax(analysis_data_2$transparency_score, 1), 10)
+
+
+# Define expected columns, excluding `poll_id`
+expected_columns <- c(
+  "numeric_grade", "pollscore", "methodology", "transparency_score",
+  "duration", "sample_size", "population", "ranked_choice_reallocated",
+  "hypothetical", "score"
+)
+
+#### Test structure of datasets ####
+test_that("Simulated datasets contain all expected columns", {
+  for (data in list(analysis_data_1, analysis_data_2)) {
+    expect_true(all(expected_columns %in% colnames(data)),
[…]

### 2024-11-04 scripts/02-download_data.R

@@ -1,0 +1,20 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from fivethirtyeight.
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+#### Workspace setup ####
+install.packages("tidyverse")
+
+library(tidyverse)
+
+#### Download data ####
+url <- "https://projects.fivethirtyeight.com/polls/data/president_polls.csv"
+the_raw_data <- read.csv(url)
+
+#### Save data ####
+write_csv(the_raw_data, "data/01-raw_data/raw_data.csv")

### 2024-11-04 scripts/03-clean_data.R

@@ -1,0 +1,123 @@
+#### Preamble ####
+# Purpose: Cleans the raw US president polls data by selecting columns and scaling values.
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+#### Workspace setup ####
+install.packages("tidyverse")
+install.packages("dplyr")
+install.packages("janitor")
+install.packages("tidyr")
+install.packages("lubridate")
+install.packages("arrow")
+
+library(tidyverse)
+library(dplyr)
+library(janitor) # For clean_names
+library(tidyr) # For drop_na
+library(lubridate)
+library(arrow)
+
+set.seed(123) # Set seed for reproducibility
+raw_data <- read_csv("data/01-raw_data/raw_data.csv")
+
+# Step 1: Remove variables with more than 40% NA values
+threshold <- 0.4 * nrow(raw_data)
+raw_data_cleaned <- raw_data %>%
+  select_if(~ sum(is.na(.)) <= threshold)
+
+# Step 2: Remove variables with all identical values
+raw_data_cleaned <- raw_data_cleaned %>%
+  select_if(~ is.numeric(.) || n_distinct(.) > 1)
+
+# Step 3: Remove duplicated, unrelated variables
+raw_data_cleaned <- raw_data_cleaned %>%
+  dplyr::select(-any_of(c(
+    "pollster_id", "pollster", "display_name", "pollster_rating_id", "pollster_rating_name",
+    "question_id", "population_full", "created_at", "url", "url_article", "race_id",
+    "candidate_id", "candidate_name", "party", "seat_number", "cycle"
+  )))
+
+# Step 4: Create a new variable called 'duration' (days difference between start_date and end_date) and remove 'start_date' and 'end_date'
+raw_data_cleaned$duration <- as.numeric(mdy(raw_data_cleaned$end_date) - mdy(raw_data_cleaned$start_date))
+raw_data_cleaned <- raw_data_cleaned %>%
+  dplyr::select(-start_date, -end_date)
+
+# Step 5: Group methodology by level
+raw_data_cleaned$methodology <- case_when(
+  raw_data_cleaned$methodology %in% c(
[…]

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -1,0 +1,112 @@
+#### Preamble ####
+# Purpose: test on the analysis data for validation
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
+
+
+
+#### Workspace setup ####
+# Install required packages
+install.packages("tidyverse")
+install.packages("testthat")
+install.packages("arrow")
+install.packages("here")
+
+# Load necessary libraries
+library(tidyverse)
+library(testthat)
+library(arrow) # For reading Parquet files
+library(here)
+
+Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
+Harris_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
+Trump_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
+Harris_train <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
+
+#### Test data ####
+
+# Ensure testthat setup
+context("Data validation tests for Trump and Harris datasets")
+
+# Test 1: Check if the datasets have the expected columns
+test_that("Expected columns are present in Trump and Harris test and train datasets", {
+  expected_columns <- c(
+    "numeric_grade", "pollscore", "methodology", "transparency_score",
+    "sample_size", "population", "ranked_choice_reallocated",
+    "hypothetical", "score", "duration"
+  )
+
+  # Check columns in each dataset
+  expect_true(all(expected_columns %in% colnames(Trump_test)))
+  expect_true(all(expected_columns %in% colnames(Harris_test)))
+  expect_true(all(expected_columns %in% colnames(Trump_train)))
+  expect_true(all(expected_columns %in% colnames(Harris_train)))
+})
+
+# Test 2: Check for missing values
+test_that("No missing values in critical columns of test and train datasets", {
+  # List critical columns
+  critical_columns <- c("numeric_grade", "pollscore", "score", "sample_size", "population")
+
+  # Check for missing values
+  for (col in critical_columns) {
+    expect_true(all(!is.na(Trump_test[[col]])), info = paste("Missing values in Trump_test:", col))
+    expect_true(all(!is.na(Harris_test[[col]])), info = paste("Missing values in Harris_test:", col))
[…]

### 2024-11-04 scripts/06-model_data.R

@@ -1,0 +1,32 @@
+#### Preamble ####
+# Purpose: use train data to train linear model of Trump and Harris
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 02-analysis_data saved and loaded
+# Any other information needed? None
+
+
+#### Workspace setup ####
+install.packages("arrow")
+library(arrow)
+
+# Define paths to each candidate's analysis data (training and testing data)
+Trump <- read_parquet("data/02-analysis_data/01-training/train_Trump.parquet")
+Harris <- read_parquet("data/02-analysis_data/01-training/train_Harris.parquet")
+
+# Function to create and save a linear model for a candidate
+
+Trump_model <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical,
+  data = Trump
+)
+Harris_model <- lm(
+  score ~ pollscore + transparency_score + duration + sample_size + population + hypothetical,
+  data = Harris
+)
+
+# Save the model
+saveRDS(Trump_model, file = "models/Trump_model.rds")
+saveRDS(Harris_model, file = "models/Harris_model.rds")

### 2024-11-04 scripts/07-replications.R

@@ -1,0 +1,35 @@
+#### Preamble ####
+# Purpose: Complete replication of the data analysis pipeline
+# Author: Haowei Fan, Fangning Zhang, Shaotong Li
+# Date: 13 October 2024
+# Contact: haowei.fan@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Requires all provided scripts and necessary data files
+# Any other information needed? None
+
+install.packages("tidyverse")
+library(tidyverse)
+
+# 1. Simulate Data
+source("scripts/00-simulate_data.R")
+message("Data simulation complete.")
+
+# 2. Download Data
+source("scripts/02-download_data.R")
+message("Data download complete.")
+
+# 3. Clean Data
+source("scripts/03-clean_data.R")
+message("Data cleaning complete.")
+
+# 4. Test Simulated Data
+source("scripts/01-test_simulated_data.R")
+message("Simulated data testing complete.")
+
+# 5. Test Analysis Data
+source("scripts/04-test_analysis_data.R")
+message("Analysis data testing complete.")
+
+# 6. Model Data
+source("scripts/06-model_data.R")
+message("Modeling data complete.")

### 2024-11-04 scripts/01-test_simulated_data.R
Update 01-test_simulated_data.R
change install to comment to avoid test fail

@@ -10,9 +10,9 @@
 
 #### Workspace setup ####
 
-install.packages("tidyverse")
-install.packages("testthat")
-install.packages("arrow")
+#install.packages("tidyverse")
+#install.packages("testthat")
+#install.packages("arrow")
 
 library(tidyverse)
 library(testthat)

### 2024-11-04 scripts/04-test_analysis_data.R
Update 04-test_analysis_data.R
change install to comment to avoid test fail

@@ -11,10 +11,10 @@
 
 #### Workspace setup ####
 # Install required packages
-install.packages("tidyverse")
-install.packages("testthat")
-install.packages("arrow")
-install.packages("here")
+#install.packages("tidyverse")
+#install.packages("testthat")
+#install.packages("arrow")
+#install.packages("here")
 
 # Load necessary libraries
 library(tidyverse)

### 2024-11-04 paper/paper.qmd
typo fixed
typo fixed

@@
   - Shaotong Li
-thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
+thanks: "Code and data are available at: https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main."
 date: today
@@
 
-First, we verified the assumptions mentioned in the @Model_Overview.
+First, we verified the assumptions mentioned in the @sec-Model_Overview.
 The @tbl-vohfm shows the General Variance Inflation Factor (GVIF) for both models, which indicates that all predictors have a GVIF less than 1.3, suggesting no significant multicollinearity.
@@
 The plots on the left shows the relationship between residuals and predicted values, and since no obvious pattern is observed, our models satisfies the Homoscedasticity assumption.
-The right-hand plot are a Q-Q plot, and the points align along the diagonal, indicating that residuals are normally distributed and satisfy the Multivariate Normality condition.
+The right-hand plot are Q-Q plots, and the points align along the diagonal, indicating that residuals are normally distributed and satisfy the Multivariate Normality condition.
 
@@
 # Result {#sec-result}
-## featured values used in prediction
+## Featured values used in prediction
 
@@
 ```
+\newpage
 # References
